### 2021-02-25 quant_estimate/pse_quant_algo.tex
algo : PSE Quant Test Algo

\documentclass{article}

\usepackage{algorithm,algpseudocode}

\algnewcommand{\algorithmicforeach}{\textbf{for each}}
\algdef{SE}[FOR]{ForEach}{EndForEach}[1]
{\algorithmicforeach\ #1\ \algorithmicdo}% \ForEach{#1}
{\algorithmicend\ \algorithmicforeach}% \EndForEach
\usepackage{listings}
\usepackage{xcolor} % for setting colors

% set the default code style
\lstset{
	frame=tb, % draw a frame at the top and bottom of the code block
	tabsize=4, % tab space width
	showstringspaces=false, % don't mark spaces in strings
	numbers=left, % display line numbers on the left
	commentstyle=\color{red}, % comment color
	keywordstyle=\color{blue}, % keyword color
	stringstyle=\color{gray} % string color
}

\begin{document}
\begin{lstlisting}[language=C++, caption={C++ code using listings}]
int main(void)
{
	int a, d;
	// forall variable
	klee_make_symbolic(&a, sizeof(a), "a_sym");
	// PSE variable : Uniformly distributed [0 to 650]
	make_pse_symbolic<int>(&d, sizeof(d), "d_prob_sym", 0, 650);
	int c = a + 100;

	// case 1
	if (a > 50)	{
		c = a + 75;
	}	else	{
		c = a - 75;
	}

	// case 2
	if (d > 60)
		d = 250;

	// case 3 -> Complex Case
	if (c > d)
		c = d;

	return 0;
}
\end{lstlisting}
\begin{algorithm}
    \caption{Complex Case : (Testing Based Estimation)}
    \begin{algorithmic}[1]
        \ForEach{$a \in A$}%
        \State command \algorithmiccomment{This is a comment}
        \State another command \algorithmiccomment{This is another comment}
        \EndForEach
    \end{algorithmic}
\end{algorithm}

\end{document}

### 2021-02-25 quant_estimate/pse_quant_algo.tex
Draft-1 : PSE Quant Test Algo

@@
 
-	// case 1
+	// case 1 -> Pure Forall Predicate
 	if (a > 50)	{
@@
 
-	// case 2
+	// case 2 -> Pure PSE Predicate
 	if (d > 60)
@@
 \end{lstlisting}
+
 \begin{algorithm}
@@
     \begin{algorithmic}[1]
-        \ForEach{$a \in A$}%
-        \State command \algorithmiccomment{This is a comment}
-        \State another command \algorithmiccomment{This is another comment}
+        \ForEach{$p \in Paths$}%
+        \State c := ConstraintSet(p) \algorithmiccomment{Path Constraints for p}
+        \State m := Solve(c) \algorithmiccomment{solution for the path constraints}
+        \State forallConcreteSet = \{ \}
+        	\ForEach{$v \in ForallVars(p)$}%
+        	\State concreteSet.append(\{key : v, val : m[v]\}) \algorithmiccomment{forall values}
+        	\EndForEach
+        \State executeCV(program, concreteSet, c)
         \EndForEach
@@
 
+\begin{algorithm}
+	\caption{Complex Case : (k-samples)}
+	\begin{algorithmic}[1]
+		\ForEach{$p \in Paths$}%
+		\State c := ConstraintSet(p) \algorithmiccomment{Path Constraints for p}
+		\State m := Solve(c) \algorithmiccomment{solution for the path constraints}
+		\State forallConcreteSet = \{ \}
+			\ForEach{$v \in ForallVars(p)$}%
+			\State concreteSet.append(\{key : v, val : m[v]\}) \algorithmiccomment{forall values}
+			\EndForEach
+		\EndForEach
+	\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[H]
+	\caption{PSE Sampling Algorithm}
+	\begin{algorithmic}[1]
+		\Function{PSESample}{$\mathtt{x}, de, \varphi, \sigma, P, I$}
+		\Let{$\delta$}{Generate an unused name for a probabilistic symbolic variable}
+		\State{$P[\delta] = de$}
+		\State{$I[\delta] = \{\delta\}$}
+		\State{$\sigma[\mathtt{x}] = \delta$}
+		\State\Return{$(\varphi,\sigma,P,I)$}
+		\EndFunction
+	\end{algorithmic}
+\end{algorithm}
+
 \end{document}

### 2021-02-25 quant_estimate/pse_quant_algo.tex
Draft-1 Edit
Draft-1 Edit (Add Optimize)

--- 2021-02-25 quant_estimate/pse_quant_algo.tex
@@
 
-\usepackage{algorithm,algpseudocode}
+\usepackage{algorithm, algpseudocode}
 
@@
 {\algorithmicend\ \algorithmicforeach}% \EndForEach
-\usepackage{listings}
-\usepackage{xcolor} % for setting colors
+\usepackage{minted}
 
-% set the default code style
-\lstset{
-	frame=tb, % draw a frame at the top and bottom of the code block
-	tabsize=4, % tab space width
-	showstringspaces=false, % don't mark spaces in strings
-	numbers=left, % display line numbers on the left
-	commentstyle=\color{red}, % comment color
-	keywordstyle=\color{blue}, % keyword color
-	stringstyle=\color{gray} % string color
-}
+\title{PSE Quant Sampling Algorithm}
+\author{Sumit Lahiri}
 
 \begin{document}
-\begin{lstlisting}[language=C++, caption={C++ code using listings}]
+	\maketitle
+
+We try to formulate a way to compute path probabilities using \texttt{symbolic execution} and \texttt{testing} based technique.  
+\begin{minted}{c} 
 int main(void)
 {
-	int a, d;
-	// forall variable
+	int a; // unintialized
+	int d = std::uniform_distribution<rd_seed>(0, 650);
+
+	// forall variable : (INT_MIN to INT_MAX)
 	klee_make_symbolic(&a, sizeof(a), "a_sym");
+
 	// PSE variable : Uniformly distributed [0 to 650]
 	make_pse_symbolic<int>(&d, sizeof(d), "d_prob_sym", 0, 650);
+
 	int c = a + 100;
 
-	// case 1
+	// case 1 : Pure Forall Predicate
 	if (a > 50) {
@@
 
-	// case 2
-	if (d > 60)
-		d = 250;
+	// case 2 : Pure PSE Predicate
+	if (d > 60) d = 250;
 
-	// case 3 -> Complex Case
-	if (c > d)
-		c = d;
+	// case 3 : Dependence Case
+	if (c > d) c = d;
 
+	// Probabilistic query : assert(P(c != d) < 0.5)
+	// Opitimize here : 
+	//	Optimal value of forall (a) such that P(c != d) is close to 0.5 	
 	return 0;
 }
-\end{lstlisting}
-\begin{algorithm}
-    \caption{Complex Case : (Testing Based Estimation)}
+\end{minted}
+
+\begin{algorithm}[H]
+    \caption{Dependence Case : (Testing Based Estimation)}
     \begin{algorithmic}[1]
-        \ForEach{$a \in A$}%
-        \State command \algorithmiccomment{This is a comment}
-        \State another command \algorithmiccomment{This is another comment}
+        \ForEach{$p \in Paths$}%
+        \State $c := ConstraintSet(p)$ \algorithmiccomment{Path Constraints for p}
+        \State $m := Optimize(query,  c)$ \algorithmiccomment{solution for the path constraints}
+        \State $concreteSet = \{ \}$
+        	\ForEach{$v \in ForallVars(p)$} \algorithmiccomment{ForallVars p $\rightarrow $ forall} %
+        	\State $concreteSet.append(\{key : v, val : m[v]\})$ \algorithmiccomment{Candidate Values}
+        	\EndForEach
+        \State $executeCV(program, concreteSet)$
         \EndForEach
@@
 
+\begin{algorithm}[H]
+	\caption{executeCV : PSE Sampled Normal Execution}
+	\begin{algorithmic}[1]
+		\Function{executeCV}{$P : program, C : concreteSet$}
+			\ForEach{$v \in ForallVars(p)$}%
+			\State value(v) := concreteSet(v) \algorithmiccomment{Use values from ConcreteSet}
+			\EndForEach
+			\State ... \algorithmiccomment{proceed with normal execution}
+		\EndFunction
+	\end{algorithmic}
+\end{algorithm}
+
 \end{document}

### 2021-02-26 quant_estimate/pse_quant_algo.tex
Run : Manual Example Added

@@
 	// Probabilistic query : assert(P(c != d) < 0.5)
-	// Opitimize here : 
+	// Optimize here : 
 	//	Optimal value of forall (a) such that P(c != d) is close to 0.5 	
@@
 
+For the sample program given above, we first resort to using \texttt{symbolic execution} to generate \texttt{path constraints} for all the feasible paths that this program can take and then convert the \texttt{path constraints} into an \texttt{formal logic} optimization problem that gives an \texttt{assignment} to \texttt{forall} variables such that it leads to optimum violation of the $query$.
+
+\begin{minted}{python}
+def generateCandidates(k: int):
+	opt = z3.Optimize()
+	a = z3.Int("a_sym")
+	d = z3.Int("d_prob_sym")
+
+	opt.add(d >= 0)
+	opt.add(d <= 650)
+	opt.add(a > 50)
+	opt.add(z3.Not(d > 60))
+	opt.add(a + 75 > d)
+
+	opt.maximize(a - d - 75) 	# Query to optimize
+	n = 0
+	while opt.check() == z3.sat and n != k:
+		m = opt.model()
+		n += 1
+		print("%s = %s" % (a, m[a]))
+		print("%s = %s" % (d, m[d]))
+		opt.add(a != m[a])
+\end{minted}
+
 \end{document}

### 2021-02-26 example1.cpp

@@ -6,7 +6,7 @@
 
 int main(void)
 {
-    int a, d;
+    int a = 53, d;
 
     // forall variable
     klee_make_symbolic(&a, sizeof(a), "a_sym");

### 2021-02-26 quant_estimate/simple_example/example.py

@@ -10,28 +10,28 @@ Trying a manual example here.
 """
 
 
-def generateConstraints():
+def generateCandidates(k: int):
     opt = z3.Optimize()
     a = z3.Int("a_sym")
     d = z3.Int("d_prob_sym")
 
     opt.add(d >= 0)
     opt.add(d <= 650)
-
     opt.add(a > 50)
     opt.add(z3.Not(d > 60))
     opt.add(a + 75 > d)
 
-    ## Need to Check this.
-    opt.minimize(a - d - 75)
+    # Need to Check this.
+    opt.maximize(a - d - 75)
 
-    while opt.check() == z3.sat:
+    n = 0
+    while opt.check() == z3.sat and n != k:
         m = opt.model()
-        for d in m.decls():
-            print("%s = %s" % (d.name(), m[d]))
-        opt.add(z3.Not(a == m[a]))
-        opt.add(z3.Not(d == m[d]))
+        n += 1
+        print("%s = %s" % (a, m[a]))
+        print("%s = %s" % (d, m[d]))
+        opt.add(z3.Or(a != m[a]))
 
 
 if __name__ == "__main__":
-    generateConstraints()
+    generateCandidates(15)

### 2021-03-04 quant_estimate/pse_quant_algo.tex
WIP : Updated PSE Document (Automation Pending)

@@
 \begin{algorithm}[H]
-    \caption{Dependence Case : (Testing Based Estimation)}
+	\caption{Candidates : (Testing Based Estimation)}
 	\begin{algorithmic}[1]
@@
 \begin{minted}{python}
-def generateCandidates(k: int):
+def generateCandidates(k: int): # Candidates Algorithm
 	opt = z3.Optimize()
@@
 
+We now explore a slightly different example which is more involved in terms of the constraints and query that the user can pose at the end of the \texttt{symbolic execution}.
+
+\begin{minted}{c}
+	int a, b, c, d;
+
+	// forall variables : (INT_MIN to INT_MAX)
+	klee_make_symbolic(&a, sizeof(a), "a_sym");
+	klee_make_symbolic(&b, sizeof(b), "b_sym");
+	klee_make_symbolic(&c, sizeof(c), "c_sym");
+
+	// PSE variables
+	make_pse_symbolic<int>(&d, sizeof(d), "d_prob_sym", 0, 500);
+	// PSE variable : Random Sampling
+	std::default_random_engine generator;
+	std::uniform_int_distribution<int> distribution(0, 500);
+
+	if (a + b > c + d)
+	{
+		if (a > b) {
+			a = 100;
+			b = 500;
+		} else {
+			a = 500;
+			b = 100;
+		}
+	} else {
+		if (c > d) {
+			a = 100;
+			c = 100;
+			b = 600;
+			d = distribution(generator);
+		} else {
+			a = 600;
+			c = 600;
+			b = 100;
+			d = distribution(generator);
+		}
+	}
+	if (a + c > b + d)
+	{
+		a = 200;
+		b = -150;
+		c = -20;
+		d = distribution(generator);
+	}
+\end{minted}
+
+Below we show a sample of the type of the \texttt{queries} that a user can make in the context of the example shown above.
+
+\begin{minted}{c}
+	assert(a + b + c + d <= 1100);
+
+	Case : 1
+	[Query Parse] : P(a + b + c + d <= 1100) >= 0.5
+	Query : assert fails atleast half of the times.
+
+	Case : 2
+	[Query Parse] : P(a + b + c + d <= 1100) <= 0.5
+	Query : assert fails atmost half of the times.
+
+	Case : 3
+	[Query Parse] : P(a + b + c + d <= 1100) == 0.5
+	Query : assert fails exactly half of the times.
+\end{minted}
+
+Based on the query posed, we get \texttt{candidate} models by converting the code into a \texttt{optimization} query and solve this optimization problem using any off-the-shelf 
+\texttt{SMT Solver} to get model values for the forall variables that contribute to maximum 
+violation of the \texttt{query} constraint.
+
+\begin{minted}{c}
+	Path : [And(d_prob_sym >= 0, d_prob_sym <= 500), 
+	a_sym + b_sym > c_sym + d_prob_sym, 
+	a_sym > b_sym, 500 + d_prob_sym < 100 + c_sym]
+		Model : 1
+			a_sym = 402
+			b_sym = 0
+			c_sym = 401
+		Model : 2
+			a_sym = 404
+			b_sym = -1
+			c_sym = 402
+	Path : [And(d_prob_sym >= 0, d_prob_sym <= 500), 
+	a_sym + b_sym > c_sym + d_prob_sym, 
+	a_sym > b_sym, Not(500 + d_prob_sym < 100 + c_sym)]
+		Model : 1
+			a_sym = 1
+			b_sym = 0
+			c_sym = 0
+		Model : 2
+			a_sym = 0
+			b_sym = -1
+			c_sym = -2
+	Path : [And(d_prob_sym >= 0, d_prob_sym <= 500), 
+	a_sym + b_sym > c_sym + d_prob_sym, 
+	Not(a_sym > b_sym), 100 + d_prob_sym < 500 + c_sym]
+		Model : 1
+			a_sym = -199
+			b_sym = -199
+			c_sym = -399
+		Model : 2
+			a_sym = -200
+			b_sym = -197
+			c_sym = -398
+	Path : [And(d_prob_sym >= 0, d_prob_sym <= 500), 
+	a_sym + b_sym > c_sym + d_prob_sym, 
+	Not(a_sym > b_sym), Not(100 + d_prob_sym < 500 + c_sym)]
+		...
+\end{minted}
+
+Here \texttt{P(condition)} represents the sum path \texttt{probabilities} for a given \texttt{condition} to hold with some deterministic value as posed in the queries shown above.
+
+We now do a \texttt{transformation} pass over the program and instrument the count of the given \texttt{condition} failing.
+In the \texttt{transforamtion} pass, we make the \texttt{program} take values that we find as \texttt{candidate} models upon following \texttt{Algorithm 1}
+
+\begin{minted}{c}
+	int a, b, c, d, assert_satisfy = 0, termCount = 35000;
+
+	// forall variables take values from stdin.
+	// pass values that conform to a candidate model
+	scanf("%d", &a); // (INT_MIN to INT_MAX)
+	scanf("%d", &b); // (INT_MIN to INT_MAX)
+	scanf("%d", &c); // (INT_MIN to INT_MAX)
+
+	while(termCount--) {
+		...
+		(code remains same)
+		(run the code in a while loop)
+		...
+		// Added by transformation pass
+		// We take a count of how many times the 
+		// posed query is satisfied.
+		if (a + b + c + d - 1100 <= 0) {
+			assert_satisfy++;
+		}
+	}
+\end{minted}
+
 \end{document}

### 2021-03-04 example1.cpp

@@ -3,36 +3,73 @@
 // RUN: %klee --output-dir=%t.klee-out --libc=klee --max-forks=25 --write-no-tests --exit-on-error --optimize --disable-inlining --search=nurs:depth --use-cex-cache %t1.bc
 
 #include "PSE.h"
+#include <assert.h>
+#include <random>
 
 int main(void)
 {
-    int a = 53, d;
+    int a, b, c, d;
 
     // forall variable
     klee_make_symbolic(&a, sizeof(a), "a_sym");
+    klee_make_symbolic(&b, sizeof(b), "b_sym");
+    klee_make_symbolic(&c, sizeof(c), "c_sym");
 
     // PSE variable
-    make_pse_symbolic<int>(&d, sizeof(d), "d_prob_sym", 0, 650);
+    make_pse_symbolic<int>(&d, sizeof(d), "d_prob_sym", 0, 500);
 
-    int c = a + 100;
+    // PSE variable : Random Sampling
+    std::default_random_engine generator;
+    std::uniform_int_distribution<int> distribution(0, 500);
 
-    // case 1
-    if (a > 50)
+    if (a + b > c + d)
     {
-        c = a + 75;
+        if (a > b)
+        {
+            a = 100;
+            b = 500;
+        }
+        else
+        {
+            a = 500;
+            b = 100;
+        }
     }
     else
     {
-        c = a - 75;
+        if (c > d)
+        {
+            a = 100;
+            c = 100;
+            b = 600;
+            d = distribution(generator);
+        }
+        else
+        {
+            a = 600;
+            c = 600;
+            b = 100;
+            d = distribution(generator);
+        }
     }
 
-    // case 2
-    if (d > 60)
-        d = 250;
+    if (a + c > b + d)
+    {
+        a = 200;
+        b = -150;
+        c = -20;
+        d = distribution(generator);
+    }
 
-    // case 3 -> Complex Case
-    if (c > d)
-        c = d;
+    // assert(a + b + c + d <= 1100);
 
+    // Query Parse : P(a + b + c + d <= 1100) >= 0.5
+    // Query : assert fails atleast half of the times.
+
+    // Query Parse : P(a + b + c + d <= 1100) <= 0.5
+    // Query : assert fails atmost half of the times.
+
+    // Query Parse : P(a + b + c + d <= 1100) == 0.5
+    // Query : assert fails exactly half of the times.
     return 0;
 }

### 2021-03-04 example1_mod.cpp

@@ -1,0 +1,57 @@
+#include <iostream>
+#include <random>
+
+int main(void)
+{
+    int a, b, c, d;
+
+    // forall variable
+    scanf("%d", &a);
+    scanf("%d", &b);
+    scanf("%d", &c);
+
+    // PSE variable : Random Sampling
+    std::default_random_engine generator;
+    std::uniform_int_distribution<int> distribution(0, 500);
+
+    if (a + b > c + d)
+    {
+        if (a > b)
+        {
+            a = 100;
+            b = 500;
+        }
+        else
+        {
+            a = 500;
+            b = 100;
+        }
+    }
+    else
+    {
+        if (c > d)
+        {
+            a = 100;
+            c = 100;
+            b = 600;
+            d = distribution(generator);
+        }
+        else
+        {
+            a = 600;
+            c = 600;
+            b = 100;
+            d = distribution(generator);
+        }
+    }
+
+    if (a + c > b + d)
+    {
+        a = 200;
+        b = -150;
+        c = -20;
+        d = distribution(generator);
+    }
+
+    return 0;
+}

### 2021-03-04 montyhall.cpp

@@ -13,89 +13,89 @@
 bool montyhall(bool door_switch)
 {
 
-  int host_door = 0;
-  int car_door, choice;
+	int host_door = 0;
+	int car_door, choice;
 
-  make_pse_symbolic(&choice, sizeof(choice), "choice_pse_var_sym", 0, 3);
-  make_pse_symbolic(&car_door, sizeof(car_door), "car_door_sym", 0, 3);
-  klee_make_symbolic(&host_door, sizeof(host_door), "host_door_sym");
+	make_pse_symbolic(&choice, sizeof(choice), "choice_pse_var_sym", 0, 3);
+	make_pse_symbolic(&car_door, sizeof(car_door), "car_door_sym", 0, 3);
+	klee_make_symbolic(&host_door, sizeof(host_door), "host_door_sym");
 
-  /**
-     * Based on car door and choice, choose a host door. 
-    */
-  if (car_door != 1 && choice != 1)
-  {
-    host_door = 1;
-  }
-  else if (car_door != 2 && choice != 2)
-  {
-    host_door = 2;
-  }
-  else
-  {
-    host_door = 3;
-  }
+	/**
+	 * Based on car door and choice, choose a host door. 
+	*/
+	if (car_door != 1 && choice != 1)
+	{
+		host_door = 1;
+	}
+	else if (car_door != 2 && choice != 2)
+	{
+		host_door = 2;
+	}
+	else
+	{
+		host_door = 3;
+	}
 
-  /**
-     * Based door_switch and host_door, change choices. 
-    */
-  if (door_switch)
-  {
-    klee_dump_kquery_state();
-    if (host_door == 1)
-    {
-      if (choice == 2)
-      {
-        choice = 3;
-      }
-      else
-      {
-        choice = 2;
-      }
-    }
-    else if (host_door == 2)
-    {
-      if (choice == 1)
-      {
-        choice = 3;
-      }
-      else
-      {
-        choice = 1;
-      }
-    }
-    else
-    {
-      if (choice == 1)
-      {
-        choice = 2;
-        klee_dump_symbolic_details(&choice, "choice_branch");
-      }
-      else
-      {
-        choice = 1;
-      }
-    }
-  }
+	/**
+	 * Based door_switch and host_door, change choices. 
+	*/
+	if (door_switch)
+	{
+		klee_dump_kquery_state();
+		if (host_door == 1)
+		{
[…]

### 2021-03-04 quant_estimate/example1/candidates.py

@@ -1,0 +1,159 @@
+# -*- coding: utf-8 -*-
+
+import z3
+
+"""
+Below are a list of constraints that dictate which 
+path is taken during actual program execution. 
+We process KLEE constraints and simplify them to get these 
+constraints. 
+"""
+
+# ==== Will be Autogenerated by PyKLEE ====
+a, b, c, d = z3.Ints('a_sym b_sym c_sym d_prob_sym')
+
+klee_assume = z3.And(d >= 0, d <= 500)
+
+cond1 = (a + b > c + d)
+notcond1 = z3.Not(a + b > c + d)
+
+cond2 = (a > b)
+notcond2 = z3.Not(a > b)
+
+cond3 = (c > d)
+notcond3 = z3.Not(c > d)
+
+cond4 = (500 + d < 100 + c)
+notcond4 = z3.Not(500 + d < 100 + c)
+
+cond5 = (100 + d < 500 + c)
+notcond5 = z3.Not(100 + d < 500 + c)
+
+"""
+Paths generated are reported by KLEE. 
+"""
+
+path1 = [klee_assume, cond1, cond2, cond4]
+path2 = [klee_assume, cond1, cond2, notcond4]
+path3 = [klee_assume, cond1, notcond2, cond5]
+path4 = [klee_assume, cond1, notcond2, notcond5]
+path5 = [klee_assume, notcond1, cond3]
+path6 = [klee_assume, notcond1, cond3]
+
+paths = [path1, path2, path3, path4, path5, path6]
+# ==== Will be Autogenerated by PyKLEE ====
+
+
+# ==== Automatically added By Query Parse ====
+class ProbQueryObject:
+    """ 
+    This object is responsible for storing the query proposed by the user
+    The user may specify as a comment in the C/C++ code used to symbex via KLEE
+    """
+
+    def __init__(self, objective, objectiveType):
+        self.objective = objective
+        self.type = objectiveType
+        self.predicates = []
+        self.eval = eval(self.objective)
+
+    def __repr__(self):
+        pass
+
+    def __str__(self):
+        pass
+
+    def __index__(self, index):
+        return self.predicates[index]
+
+    def __getitem__(self, key):
+        pass
+
+    def getObjective(self):
+        return self.objective
+
+    def typeObjective(self):
+        return self.type
+
+    def processObjective(self):
+        # process objective & return each predicate
+        return self.predicates
+
+# Will automate this more later on.
+
+
+class Optimizer:
+    def __init__(self):
[…]

### 2021-03-04 quant_estimate/simple_example/example.py

@@ -1,37 +1,0 @@
-import z3
-
-"""
-Trying a manual example here.
-    "(Sle 0 (ReadLSB w32 0 d_prob_sym))",
-    "(Sle (ReadLSB w32 0 d_prob_sym) 650)",
-    "(Slt 50 (ReadLSB w32 0 a_sym))",
-    "(Eq false (Slt 60 (ReadLSB w32 0 d_prob_sym)))",
-    "(Eq false (Slt (ReadLSB w32 0 d_prob_sym) (Add w32 75 (ReadLSB w32 0 a_sym))))"
-"""
-
-
-def generateCandidates(k: int):
-    opt = z3.Optimize()
-    a = z3.Int("a_sym")
-    d = z3.Int("d_prob_sym")
-
-    opt.add(d >= 0)
-    opt.add(d <= 650)
-    opt.add(a > 50)
-    opt.add(z3.Not(d > 60))
-    opt.add(a + 75 > d)
-
-    # Need to Check this.
-    opt.maximize(a - d - 75)
-
-    n = 0
-    while opt.check() == z3.sat and n != k:
-        m = opt.model()
-        n += 1
-        print("%s = %s" % (a, m[a]))
-        print("%s = %s" % (d, m[d]))
-        opt.add(z3.Or(a != m[a]))
-
-
-if __name__ == "__main__":
-    generateCandidates(15)

### 2021-03-04 quant_estimate/pse_quant_algo.tex
WIP : Estimation Counts

@@
 	make_pse_symbolic<int>(&d, sizeof(d), "d_prob_sym", 0, 500);
+
 	// PSE variable : Random Sampling
@@
 	}
+
 	if (a + c > b + d)
 	{
-		a = 200;
-		b = -150;
-		c = -20;
 		d = distribution(generator);

### 2021-03-04 estimate_example1/candidates.py

@@ -12,23 +12,23 @@ constraints.
 """
 
 # ==== Will be Autogenerated by PyKLEE ====
-a, b, c, d = z3.Ints('a_sym b_sym c_sym d_prob_sym')
+a, b, c, d = z3.Ints("a_sym b_sym c_sym d_prob_sym")
 
 klee_assume = z3.And(d >= 0, d <= 500)
 
-cond1 = (a + b > c + d)
+cond1 = a + b > c + d
 notcond1 = z3.Not(a + b > c + d)
 
-cond2 = (a > b)
+cond2 = a > b
 notcond2 = z3.Not(a > b)
 
-cond3 = (c > d)
+cond3 = c > d
 notcond3 = z3.Not(c > d)
 
-cond4 = (500 + d < 100 + c)
+cond4 = 500 + d < 100 + c
 notcond4 = z3.Not(500 + d < 100 + c)
 
-cond5 = (100 + d < 500 + c)
+cond5 = 100 + d < 500 + c
 notcond5 = z3.Not(100 + d < 500 + c)
 
 """
@@ -48,7 +48,7 @@ paths = [path1, path2, path3, path4, path5, path6]
 
 # ==== Automatically added By Query Parse ====
 class ProbQueryObject:
-    """ 
+    """
     This object is responsible for storing the query proposed by the user
     The user may specify as a comment in the C/C++ code used to symbex via KLEE
     """
@@ -80,6 +80,7 @@ class ProbQueryObject:
     def processObjective(self):
         # process objective & return each predicate
         return self.predicates
+
 
 # Will automate this more later on.
 
@@ -121,20 +122,18 @@ def generateCandidates(k: int):
 
         print(f"Path {index + 1} : {path}")
         optpath = z3.Optimize()
-        queryObj = ProbQueryObject("a + b + c + d - 100 <= 0", ">=")
+        queryObj = ProbQueryObject("a + b + c + d - 1100 <= 0", "<=")
 
         # This will get automated later to parse query
         # and retrieve directly from ProbQueryObject
 
         # COMMENT : Need to discuss the query constraints for this program.
-        optpath.add(a + b + c + d - 1100 <= 0)
-        objective = (a + b + c + d - 1100)
-        foralls = z3.Sum(a, b, c)
+        optpath.add(a + b + c >= 900)
+        objective = a + b + c + d - 1100
 
         # Add the constraints and get candidate model from z3.
         for conds in path:
             optpath.add(conds)
-            optpath.maximize(foralls)
[…]

### 2021-03-04 estimate_example1/executeCV.py

@@ -18,8 +18,11 @@ def build():
     try:
         # print(f"Building Binary Example {example}.c")
         output = run(
-            f'g++ {codeFile} -o {executable}',
-            shell=True, capture_output=True, text=True)
+            f"g++ {codeFile} -o {executable}",
+            shell=True,
+            capture_output=True,
+            text=True,
+        )
     except CalledProcessError as err:
         print(f"Build Error : {err}")
     else:
@@ -31,8 +34,11 @@ def executeCV(index, executable, inFile, outfile, errFile):
     try:
         # print(f"Running Binary Example {example}.c")
         output = run(
-            f'{executable} < {inFile} > {outfile} 2> {errFile}',
-            shell=True, capture_output=True, text=True)
+            f"{executable} < {inFile} > {outfile} 2> {errFile}",
+            shell=True,
+            capture_output=True,
+            text=True,
+        )
     except CalledProcessError as err:
         print(f"Execute Error : {err}")
     else:
@@ -47,13 +53,16 @@ if __name__ == "__main__":
     executeThreads = []
     with alive_bar(len(os.listdir(inputFilePath))) as executeBar:
         for index, inputFile in enumerate(os.listdir(inputFilePath)):
-            worker_thread = threading.Thread(target=executeCV, args=(
-                index,
-                executable,
-                os.path.join(inputFilePath, inputFile),
-                os.path.join(outputFilePath, f"output_{index}.txt"),
-                os.path.join(outputFilePath, f"output_err_{index}.txt")
-            ))
+            worker_thread = threading.Thread(
+                target=executeCV,
+                args=(
+                    index,
+                    executable,
+                    os.path.join(inputFilePath, inputFile),
+                    os.path.join(outputFilePath, f"output_{index}.txt"),
+                    os.path.join(outputFilePath, f"output_err_{index}.txt"),
+                ),
+            )
             executeThreads.append(worker_thread)
             time.sleep(0.3)
             worker_thread.start()

### 2021-03-04 example1_mod.cpp

@@ -55,9 +55,6 @@ int main(void)
 
         if (a + c > b + d)
         {
-            a = 200;
-            b = -150;
-            c = -20;
             d = distribution(generator);
         }
 

### 2021-03-11 quant_estimate/pse_quant_algo.tex
OPT : Optimization Queries

--- 2021-02-26 quant_estimate/pse_quant_algo.tex
@@
 \usepackage{algorithm, algpseudocode}
+\usepackage{graphicx}
 
@@
 
+We now explore a slightly different example which is more involved in terms of the constraints and query that the user can pose at the end of the \texttt{symbolic execution}.
+In the below example we bound the values for \texttt{foralls} for example sake.
+
+\begin{minted}{c}
+// forall variable
+klee_make_symbolic(&a, sizeof(a), "a_sym");       // [0, 1]
+klee_make_symbolic(&c, sizeof(b), "c_sym");       // [1, 10]
+klee_make_symbolic(&d, sizeof(c), "d_sym");       // [0, 5]
+klee_make_symbolic(&win, sizeof(win), "win_sym"); // win == 1
+
+// PSE variable
+make_pse_symbolic<int>(&b, sizeof(b), "b_prob_sym", 0, 1);
+make_pse_symbolic<int>(&e, sizeof(e), "e_prob_sym", 1, 6);
+
+klee_assume(a >= 0 && a <= 1);
+klee_assume(c >= 1 && c <= 10);
+klee_assume(d >= 0 && d <= 5);
+
+if (a > b)				     // maximize a
+{
+	if (c + e < 15)			// minimize c
+	{
+		win = 1;			
+		win_ones++;
+	}
+	else
+	{
+		win = 0;
+		win_zeros++;
+	}
+}
+else
+{
+	if (d + e > 1)			// maximize d
+	{
+		win = 1;
+		win_ones++;
+	}
+	else
+	{
+		win = 0;
+		win_zeros++;
+	}
+}
+\end{minted}
+
+Below we show a sample of the type of the \texttt{queries} that a user can make in the context of the example shown above.
+
+\begin{minted}{c}
+	assert(P(win == 1) > 0.8);
+\end{minted}
+
+Based on the query posed, we get \texttt{candidate} models by converting the code into a \texttt{optimization} query and solve this optimization problem using any off-the-shelf 
+\texttt{SMT Solver} to get model values for the forall variables that contribute to maximum 
+violation of the \texttt{query} constraint.
+
+Based on the example we do the following \texttt{optimizations}. one on \texttt{Path 1} and the other on \texttt{Path 3} where \texttt{win == 1}
+
+\begin{minted}{c}
+	Path 1 : maximize((a - b) + 11 - (c + e))
+\end{minted}
+
+\begin{minted}{c}
+	Path 3 : maximize((b - a) + (d + e) - 1)
+\end{minted}
+
+On the other two paths, we \texttt{minimize} the same. \texttt{win == 1} on the \texttt{green} edged paths. \\
+
+\includegraphics[scale=0.35]{exectree1.png}
+
+\begin{minted}{c}
+Path 1 : [And(a_sym >= 0, a_sym <= 1), And(c_sym >= 1, c_sym <= 10),
+ And(d_sym >= 0, d_sym <= 5), And(b_prob_sym >= 0, b_prob_sym <= 1), 
+ And(e_prob_sym >= 1, e_prob_sym <= 6), win_sym == 1, b_prob_sym < 
+ a_sym, c_sym + e_prob_sym < 15]
+	Model : 1
+		a_sym = 1
+		c_sym = 1
+		d_sym = 0
+	Model : 2
+		a_sym = 1
+		c_sym = 2
+		d_sym = 0
+	Model : 3
+		a_sym = 1
+		c_sym = 3
+		d_sym = 0
+Path 2 : [And(a_sym >= 0, a_sym <= 1), And(c_sym >= 1, c_sym <= 10), 
+And(d_sym >= 0, d_sym <= 5), And(b_prob_sym >= 0, b_prob_sym <= 1), 
+And(e_prob_sym >= 1, e_prob_sym <= 6), b_prob_sym < a_sym, Not(c_sym 
++ e_prob_sym < 15)]
+	Model : 1
+		a_sym = 1
+		c_sym = 9
+		d_sym = 0
+	Model : 2
+		a_sym = 1
+		c_sym = 10
+		d_sym = 0
+Path 3 : [And(a_sym >= 0, a_sym <= 1), And(c_sym >= 1, c_sym <= 10), 
+And(d_sym >= 0, d_sym <= 5), And(b_prob_sym >= 0, b_prob_sym <= 1), 
+And(e_prob_sym >= 1, e_prob_sym <= 6), win_sym == 1, Not(b_prob_sym 
+< a_sym), d_sym + e_prob_sym > 1]
+	Model : 1
+		a_sym = 0
+		c_sym = 1
+		d_sym = 0
+	Model : 2
+		a_sym = 0
+		c_sym = 2
+		d_sym = 0
+	Model : 3
+		a_sym = 0
+		c_sym = 3
+		d_sym = 1
+
+		...
+\end{minted}
+
+Here \texttt{P(win == 1)} is the query of interest to us so we optimize along those paths where this condition holds. \\
+
+We now do a \texttt{transformation} pass over the program and instrument the count of the given \texttt{condition} failing.
+In the \texttt{transforamtion} pass, we make the \texttt{program} take values that we find as \texttt{candidate} models upon following \texttt{Algorithm 1}
+
+\begin{minted}{c}
+// Take in candidate vector for [foralls]
+scanf("%d", &a); // [0, 1]
+scanf("%d", &c); // [1, 10]
+scanf("%d", &d); // [0, 5]
+
+// // PSE variable : Random Sampling
+std::default_random_engine generator;
+std::uniform_int_distribution<int> distribution1(0, 1); // b
+std::uniform_int_distribution<int> distribution2(1, 6); // e
+
+while (term_count--) // term_count > 500000 (large sample)
+{
+	b = distribution1(generator);
+	e = distribution2(generator);
+
+	if (a > b) { // 
+		if (c + e < 15) {
+			win = 1;
+			win_ones++;
+		} else {
+			...
+		}
+	} else {
+		if (d + e > 1) {
+			win = 1;
+			win_ones++;
+		} else {
+			...
+		}
+	}
+	run++;
+} // P(win==1) is win_ones/run;
+\end{minted}
+
+We tweaked the values in such a way that for a very small number of candidate vectors the \texttt(probabilistic) assert fails and our algorithm must now catch that.
+Indeed we find that for the following assignments to \texttt{forall} variables, the assert fails.
+
+\begin{minted}{c}
+	Fail : P(win == 1)  :  0.754100
+		Vals -> a : 1, c : 10, d : 0
+\end{minted}
+
+For other \texttt{candidate} vectors, we find that the \texttt{probabilistic} asserts actually hold and will not cause a violation during execution under normal condiditons.
+
+\begin{minted}{c}
+	Pass : P(win == 1)  :  1.000000
+		Vals -> a : 0, c : 7, d : 4
+	Pass : P(win == 1)  :  1.000000
+		Vals -> a : 1, c : 4, d : 4
+	Pass : P(win == 1)  :  1.000000
+		Vals -> a : 1, c : 1, d : 3
+	Pass : P(win == 1)  :  1.000000
+		Vals -> a : 0, c : 6, d : 4
+	Pass : P(win == 1)  :  0.834900
+		Vals -> a : 0, c : 7, d : 0
+	Pass : P(win == 1)  :  0.834900
+		Vals -> a : 0, c : 2, d : 0
+	Pass : P(win == 1)  :  1.000000
+		Vals -> a : 0, c : 10, d : 2
+	Pass : P(win == 1)  :  0.917800
+		Vals -> a : 1, c : 3, d : 0
+			...
+\end{minted}
 \end{document}

### 2021-03-11 estimate_example1/candidates.py

@@ -43,6 +43,7 @@ path4 = [klee_assume1, klee_assume2, klee_assume3,
          klee_assume4, klee_assume5, notcond1, notcond3]
 
 paths = [path1, path2, path3, path4]
+
 # ==== Will be Autogenerated by PyKLEE ====
 
 
@@ -132,6 +133,10 @@ def generateCandidates(k: int):
         # Add the constraints and get candidate model from z3.
         for conds in path:
             optpath.add(conds)
+            if conds == klee_assume6 and path == path1:
+                optpath.maximize((a - b) + 11 - (c + e))
+            if conds == klee_assume6 and path == path3:
+                optpath.maximize((b - a) + (d + e) - 1)
 
         n = 0
         # TODO : Automate it later get MODELs.

### 2021-03-11 example1_mod.cpp

@@ -5,7 +5,7 @@
 int main(void)
 {
     int a, b, c, d, e, win;
-    int win_ones = 0, a_more_b = 0, win_zeros = 0, run = 0, term_count = 10000;
+    int win_ones = 0, a_more_b = 0, win_zeros = 0, run = 0, term_count = 50000;
 
     scanf("%d", &a); // [0, 1]
     scanf("%d", &c); // [1, 10]
@@ -70,8 +70,8 @@ int main(void)
     printf("P(a > b) : %f\n", (double)a_more_b / run);
     printf("Vals -> a : %d, c : %d, d : %d\n", a, c, d);
 
-    // assert(pwin >= 0.5f);
-    // COMMENT : assert(P(win == 1) > 0.5);
+    // assert(pwin >= 0.8f);
+    // COMMENT : assert(P(win == 1) > 0.8);
     // COMMENT : Assert fails only when c >= 9 and d == -5 [a:0, c:9, d:-5] or [a:0, c:10, d:-5]
     return 0;
 }

### 2021-03-11 probesmt.sh

@@ -9,4 +9,4 @@ rm -rf estimate_example1/results.txt
 
 python3 estimate_example1/genCandidateM.py
 python3 estimate_example1/candidates.py  
-python3 estimate_example1/executeCV.py foralls
+python3 estimate_example1/executeCV.py inputs

### 2021-03-16 quant_estimate/constraints_log_montyhall.tex
WIP : Monty Hall Constraints PDF

\documentclass{article}

\usepackage{algorithm, algpseudocode}
\usepackage{graphicx}

\algnewcommand{\algorithmicforeach}{\textbf{for each}}
\algdef{SE}[FOR]{ForEach}{EndForEach}[1]
{\algorithmicforeach\ #1\ \algorithmicdo}% \ForEach{#1}
{\algorithmicend\ \algorithmicforeach}% \EndForEach
\usepackage{minted}

\title{Monty Hall Constraints}
\author{Sumit Lahiri}

\begin{document}
	\maketitle
	Parse results after processing \texttt{KLEE} dump for \texttt{Monty Hall} Example.
	\begin{minted}{c}
Path : 1
	0 <= door_switch_pse_var_sym
	door_switch_pse_var_sym <= 1
	0 <= choice_pse_var_sym
	choice_pse_var_sym <= 3
	0 <= car_door_sym
	car_door_sym <= 3
	!((!(car_door_sym == 1) && !(choice_pse_var_sym == 1)))
	!((!(car_door_sym == 2) && !(choice_pse_var_sym == 2)))
	!(!(door_switch_pse_var_sym == 0))

Path : 2
	0 <= door_switch_pse_var_sym
	door_switch_pse_var_sym <= 1
	0 <= choice_pse_var_sym
	choice_pse_var_sym <= 3
	0 <= car_door_sym
	car_door_sym <= 3
	!((!(car_door_sym == 1) && !(choice_pse_var_sym == 1)))
	(!(car_door_sym == 2) && !(choice_pse_var_sym == 2))
	!(door_switch_pse_var_sym == 0)
	!(choice_pse_var_sym == 1)

Path : 3
	0 <= door_switch_pse_var_sym
	door_switch_pse_var_sym <= 1
	0 <= choice_pse_var_sym
	choice_pse_var_sym <= 3
	0 <= car_door_sym
	car_door_sym <= 3
	!((!(car_door_sym == 1) && !(choice_pse_var_sym == 1)))
	!((!(car_door_sym == 2) && !(choice_pse_var_sym == 2)))
	!(door_switch_pse_var_sym == 0)
	choice_pse_var_sym == 1

Path : 4
	0 <= door_switch_pse_var_sym
	door_switch_pse_var_sym <= 1
	0 <= choice_pse_var_sym
	choice_pse_var_sym <= 3
	0 <= car_door_sym
	car_door_sym <= 3
	!((!(car_door_sym == 1) && !(choice_pse_var_sym == 1)))
	!((!(car_door_sym == 2) && !(choice_pse_var_sym == 2)))
	!(door_switch_pse_var_sym == 0)
	!(choice_pse_var_sym == 1)

Path : 5
	0 <= door_switch_pse_var_sym
	door_switch_pse_var_sym <= 1
	0 <= choice_pse_var_sym
	choice_pse_var_sym <= 3
	0 <= car_door_sym
	car_door_sym <= 3
	(!(car_door_sym == 1) && !(choice_pse_var_sym == 1))
	!(!(door_switch_pse_var_sym == 0))
	choice_pse_var_sym == car_door_sym

Path : 6
	0 <= door_switch_pse_var_sym
	door_switch_pse_var_sym <= 1
	0 <= choice_pse_var_sym
	choice_pse_var_sym <= 3
	0 <= car_door_sym
	car_door_sym <= 3
	(!(car_door_sym == 1) && !(choice_pse_var_sym == 1))
	!(!(door_switch_pse_var_sym == 0))
	!(choice_pse_var_sym == car_door_sym)

Path : 7
	0 <= door_switch_pse_var_sym
	door_switch_pse_var_sym <= 1
	0 <= choice_pse_var_sym
	choice_pse_var_sym <= 3
	0 <= car_door_sym
	car_door_sym <= 3
	!((!(car_door_sym == 1) && !(choice_pse_var_sym == 1)))
	(!(car_door_sym == 2) && !(choice_pse_var_sym == 2))
	!(!(door_switch_pse_var_sym == 0))
	choice_pse_var_sym == car_door_sym

Path : 8
	0 <= door_switch_pse_var_sym
	door_switch_pse_var_sym <= 1
	0 <= choice_pse_var_sym
	choice_pse_var_sym <= 3
	0 <= car_door_sym
	car_door_sym <= 3
	!((!(car_door_sym == 1) && !(choice_pse_var_sym == 1)))
	(!(car_door_sym == 2) && !(choice_pse_var_sym == 2))
	!(!(door_switch_pse_var_sym == 0))
	!(choice_pse_var_sym == car_door_sym)

Path : 9
	0 <= door_switch_pse_var_sym
	door_switch_pse_var_sym <= 1
	0 <= choice_pse_var_sym
	choice_pse_var_sym <= 3
	0 <= car_door_sym
	car_door_sym <= 3
	(!(car_door_sym == 1) && !(choice_pse_var_sym == 1))
	!(door_switch_pse_var_sym == 0)
	!(choice_pse_var_sym == 2)
	car_door_sym == 2

Path : 10
	0 <= door_switch_pse_var_sym
	door_switch_pse_var_sym <= 1
	0 <= choice_pse_var_sym
	choice_pse_var_sym <= 3
	0 <= car_door_sym
	car_door_sym <= 3
	(!(car_door_sym == 1) && !(choice_pse_var_sym == 1))
	!(door_switch_pse_var_sym == 0)
	!(choice_pse_var_sym == 2)
	!(car_door_sym == 2)

Path : 11
	0 <= door_switch_pse_var_sym
	door_switch_pse_var_sym <= 1
	0 <= choice_pse_var_sym
	choice_pse_var_sym <= 3
	0 <= car_door_sym
	car_door_sym <= 3
	(!(car_door_sym == 1) && !(choice_pse_var_sym == 1))
	!(door_switch_pse_var_sym == 0)
	choice_pse_var_sym == 2
	car_door_sym == 3

Path : 12
	0 <= door_switch_pse_var_sym
	door_switch_pse_var_sym <= 1
	0 <= choice_pse_var_sym
	choice_pse_var_sym <= 3
	0 <= car_door_sym
	car_door_sym <= 3
	(!(car_door_sym == 1) && !(choice_pse_var_sym == 1))
	!(door_switch_pse_var_sym == 0)
	choice_pse_var_sym == 2
	!(car_door_sym == 3)

Path : 13
	0 <= door_switch_pse_var_sym
	door_switch_pse_var_sym <= 1
	0 <= choice_pse_var_sym
	choice_pse_var_sym <= 3
	0 <= car_door_sym
	car_door_sym <= 3
	!((!(car_door_sym == 1) && !(choice_pse_var_sym == 1)))
	(!(car_door_sym == 2) && !(choice_pse_var_sym == 2))
	!(door_switch_pse_var_sym == 0)
	choice_pse_var_sym == 1
	car_door_sym == 3

Path : 14
	0 <= door_switch_pse_var_sym
	door_switch_pse_var_sym <= 1
	0 <= choice_pse_var_sym
	choice_pse_var_sym <= 3
	0 <= car_door_sym
	car_door_sym <= 3
	!((!(car_door_sym == 1) && !(choice_pse_var_sym == 1)))
	(!(car_door_sym == 2) && !(choice_pse_var_sym == 2))
	!(door_switch_pse_var_sym == 0)
	choice_pse_var_sym == 1
	!(car_door_sym == 3)
	\end{minted}
\end{document}

### 2021-03-16 postprocess/pathconstraints.py

@@ -16,14 +16,15 @@ def genericParse(expr):
         return
     if expr.get("action") == "Eq":
         right = expr.get("right", None)
+        left = expr.get("left", None)
         const = expr.get("const", None)
         boolean = expr.get("bool", None)
         if right is not None:
             parsedRight = genericParse(right)
-            variable = right.get("var", None)
+            rvariable = right.get("var", None)
             if const is not None:
                 # print(f'{variable} == {const}')
-                return f'{variable} == {const}'
+                return f'{rvariable} == {const}'
             if boolean is not None:
                 if boolean == "true":
                     # print(f'{parsedRight}')
@@ -31,6 +32,23 @@ def genericParse(expr):
                 if boolean == "false":
                     # print(f'!({parsedRight})')
                     return f'!({parsedRight})'
+
+        if left is not None:
+            parsedLeft = genericParse(left)
+            lvariable = left.get("var", None)
+            if const is not None:
+                # print(f'{variable} == {const}')
+                return f'{lvariable} == {const}'
+            if boolean is not None:
+                if boolean == "true":
+                    # print(f'{parsedRight}')
+                    return parsedLeft
+                if boolean == "false":
+                    # print(f'!({parsedRight})')
+                    return f'!({parsedLeft})'
+
+        # print(f'{lvariable} == {rvariable}')
+        return(f'{lvariable} == {rvariable}')
 
     if expr.get("action") == "And":
         right = expr.get("right", None)

### 2021-03-18 quant_estimate/pse_quant_algo.tex
WIP : Quant Example Draft

@@
 
-\title{PSE Quant Sampling Algorithm}
-\author{Sumit Lahiri}
+\title{Quantitative Sampling for \\ \texttt{Probabilistic Assert Failures}}
+\author{Sumit Lahiri \\ \texttt{IIT Kanpur}}
 
@@
 We try to formulate a way to compute path probabilities using \texttt{symbolic execution} and \texttt{testing} based technique.
+
 \begin{minted}{c} 
@@
 	// Optimize here : 
-	//	Optimal value of forall (a) such that P(c != d) is close to 0.5 	
+	//	Optimal value of forall variable 'a' 
+	//        such that P(c != d) is close to 0.5 	
 	return 0;
@@
 	run++;
-} // P(win==1) is win_ones/run;
+}
+
+// The probabilistic assert is the following
+// assert(P(win == 1) >= 0.8), where P(win == 1) win_ones/run;
+
 \end{minted}
@@
 For other \texttt{candidate} vectors, we find that the \texttt{probabilistic} asserts actually hold and will not cause a violation during execution under normal condiditons.
+We show the results of some of the winning cases here.
 

### 2021-03-18 estimate_montyhall/candidates.py
WIP : Monty Hall

@@ -11,38 +11,121 @@ constraints.
 """
 
 # ==== Will be Autogenerated by PyKLEE ====
-a, b, c, d, e, win = z3.Ints("a_sym b_prob_sym c_sym d_sym e_prob_sym win_sym")
+door_switch_pse_sym, choice_pse_sym, car_door_pse_sym = z3.Ints(
+    "door_switch_pse_sym choice_pse_sym car_door_pse_sym")
 
-klee_assume1 = z3.And(a >= 0, a <= 1)
-klee_assume2 = z3.And(c >= 1, c <= 10)
-klee_assume3 = z3.And(d >= 0, d <= 5)
-klee_assume4 = z3.And(b >= 0, b <= 1)
-klee_assume5 = z3.And(e >= 1, e <= 6)
-klee_assume6 = win == 1
 
-cond1 = b < a
-notcond1 = z3.Not(b < a)
+klee_assume1 = z3.And((0 <= door_switch_pse_sym), (door_switch_pse_sym <= 1))
+klee_assume2 = z3.And((0 <= choice_pse_sym), (choice_pse_sym <= 3))
+klee_assume3 = z3.And((0 <= car_door_pse_sym), (car_door_pse_sym <= 3))
 
-cond2 = 15 > c + e
-notcond2 = z3.Not(15 > c + e)
-
-cond3 = 1 < d + e
-notcond3 = z3.Not(1 < d + e)
 
 """
 Paths generated are reported by KLEE. 
 """
 
-path1 = [klee_assume1, klee_assume2, klee_assume3,
-         klee_assume4, klee_assume5, klee_assume6, cond1, cond2]
-path2 = [klee_assume1, klee_assume2, klee_assume3,
-         klee_assume4, klee_assume5, cond1, notcond2]
-path3 = [klee_assume1, klee_assume2, klee_assume3,
-         klee_assume4, klee_assume5, klee_assume6, notcond1, cond3]
-path4 = [klee_assume1, klee_assume2, klee_assume3,
-         klee_assume4, klee_assume5, notcond1, notcond3]
+path1 = [z3.Not(z3.And(z3.Not(car_door_pse_sym == 1), z3.Not(choice_pse_sym == 1))),
+         z3.Not(z3.And(z3.Not(car_door_pse_sym == 2),
+                       z3.Not(choice_pse_sym == 2))),
+         z3.Not(z3.Not(door_switch_pse_sym == 0))
+         ]
 
-paths = [path1, path2, path3, path4]
+path2 = [
[…]

### 2021-03-18 estimate_montyhall/executeCV.py

@@ -87,7 +87,7 @@ if __name__ == "__main__":
                     with open(os.path.join(pwd, "pathprobs.txt"), mode="a") as pathprobs:
                         pathprobs.write(
                             f'{assertQuery} : {value} : {line[-1].strip()}\n')
-                    if float(value) > 0.50:
+                    if float(value) < 0.5:
                         with open(os.path.join(pwd, "results.txt"), mode="a") as resultFile:
                             resultFile.write(
                                 f'Fail : {assertQuery} : {value} : {line[-1].strip()}\n')

### 2021-03-18 quant_estimate/constraints_log_montyhall.tex
WIP : Monty Hall

@@
 	\end{minted}
+
+We present the observations for the \texttt{Monty Hall}. \\ \\ \\
+
+\begin{minted}{c}
+-  For door_switch == 0
+	(P(win) >= 0.5) passes,
+
+-  For door_switch == 1 
+	(P(win) >= 0.5) fails,
+
+-  When count(door_switch == 0) == count(door_switch == 1) 
+	(P(win) <= 0.5) fails 
+	(P(win) >= 0.5) passes.
+
+-  When ever count(door_switch == 0) < count(door_switch == 1) with bias 
+		Higher probability of winning when the person switches.
+			(P(win) <= 0.5) fails :
+
+	Fail : P(choice == car_door)  :  0.860216  
+	Fail : P(choice == car_door)  :  0.520136  
+	Fail : P(choice == car_door)  :  0.780963   
+		...
+
+-  When ever count(door_switch == 0) > count(door_switch == 1)  with bias
+		(P(win) >= 0.5) fails :
+
+	Fail : P(choice == car_door)  :  0.499620   
+	Fail : P(choice == car_door)  :  0.379960  
+	Fail : P(choice == car_door)  :  0.139769   
+		...
+\end{minted}
+
 \end{document}

### 2021-04-27 shared/analysis.tex
Suitable Benchmark Examples

\documentclass[usenames,dvipsnames,acmsmall]{acmart}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[nounderscore]{syntax}
\usepackage{bussproofs}
\usepackage{mathtools}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{minted}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{minted}

\begin{document}
	\begin{figure}
		\begin{minted}{python}
	def progam1(inpt):
		prob, _ = inpt
		z = 0
		flip = 0
		while (flip == 0):
			d = bernoulli.rvs(size=1, p=prob)[0]
			if d:
				flip = 1
			else:
				z = z + 1
		return z

	assert(z > (1 - prob)/prob)
		\end{minted}
		\caption{Program listing for finding probabilistic \texttt{assert} violation.}
	\end{figure}
	\begin{figure}
		\begin{minted}{c}
	int main()
	{
		double prob;
		int d, z = 0, flip = 0;

		make_pse_symbolic(&flip, sizeof(flip), "flip_pse_sym", 0, 1);
		make_pse_symbolic(&prob, sizeof(prob), "prob_sym", 0, 1);
		klee_make_symbolic(&z, sizeof(z), "z_sym");
		klee_assume(z >= 0);

		std::random_device rd{};
		std::mt19937 rng{rd()};
		std::bernoulli_distribution rvs(prob);

		while (flip == 0) {
			int d = rvs(rng);
			if (d) {
				flip = 1;
			} else {
				// must be executed more 
				// for the assert to pass. 
				z += 1; 
			}
		}

		return 0;
	}
		\end{minted}
		\caption{\texttt{Translate()} of the program for testing the \texttt{assert}. }
	\end{figure}
	\begin{figure}
		\begin{minted}{c}
		long long int termCount = 50000, unroll = 2500;
		while (termCount--)
		{
			flip = 0;
			z = 0;
			scanf("%Lf", &prob);

			...

			while (flip == 0 && unroll--) {
				int d = rvs(rng);
				if (d) {
					flip = 1;
				} else { 
					z += 1; 
				}
				if (z > ((double)(1 - prob) / (prob)))
					win++;
				flip_runs++;
			}
			program_runs++;
		}
		\end{minted}
		\caption{\texttt{Translate()} of the program for testing the \texttt{assert}. }
	\end{figure}
	\begin{figure}
			\begin{minted}{python}
		(flip_pse_sym <= 1),
		(0 <= flip_pse_sym),
		(prob_sym <= 1),
		(0.000001 < prob_sym),
		(0 <= z_sym),

		FAIL : (z_sym * prob_sym - (1 - prob_sym) <= 0)
		\end{minted}
		\caption{Constraints without optimization step.}
	\end{figure}
	\begin{figure}
		\begin{minted}{python}
		(flip_pse_sym <= 1),
		(0 <= flip_pse_sym),
		(prob_sym <= 1),
		(0.000001 < prob_sym),
		(0 <= z_sym),

		FAIL : (z_sym * prob_sym - (1 - prob_sym) <= 0)
		optimize : maximize(prob_sym)
		\end{minted}
		\caption{Constraints with optimization step.}
	\end{figure}
	\begin{table}
		\centering
		\caption{Comparing \texttt{prob(p)} value to cases Vs \texttt{assert} status for \texttt{optimization} over \texttt{prob} value}
		\label{}
		\begin{tabular}{ c | c | c | c | c } 
			\toprule
			\texttt{Flip Runs} & \texttt{Program Runs}& \texttt{prob(p)} & \texttt{z (Last)} & \texttt{(1-p)/p} \\ 
			\hline\hline
			49999 & 50000 & 0.9999990463 & 0 & 0.0000009537 \\ \hline 
			49999 & 50000 & 0.9999995232 & 0 & 0.0000004768 \\ \hline 
			49999 & 50000 & 0.9999998808 & 0 & 0.0000001192 \\ \hline 
			49999 & 50000 & 0.9999999991 & 0 & 0.0000000009 \\ \hline 
			49999 & 50000 & 1.0000000000 & 0 & 0.0000000000 \\ \hline 
			50000 & 50000 & 0.9999847412 & 0 & 0.0000152590 \\ \hline 
			50001 & 50000 & 0.9999694825 & 0 & 0.0000305184 \\ \hline 
			50003 & 50000 & 0.9998779298 & 0 & 0.0001220851 \\ \hline 
			50008 & 50000 & 0.9997558596 & 0 & 0.0002442000 \\ \hline 
			50016 & 50000 & 0.9995117192 & 0 & 0.0004885193 \\ \hline 
			50045 & 50000 & 0.9990234385 & 0 & 0.0009775161 \\ \hline 
			50822 & 50000 & 0.9843750156 & 0 & 0.0158729998 \\ \hline 
			53303 & 50000 & 0.9375000625 & 0 & 0.0666665956 \\ \hline 
			57237 & 50000 & 0.8750001250 & 0 & 0.1428569796 \\ \hline 
			99385 & 50000 & 0.5000005000 & 0 & 0.9999980000 \\ \hline 
			\bottomrule
		\end{tabular}
	\end{table}
	\begin{table}
		\centering
		\caption{Comparing \texttt{prob(p)} value to cases where assert \texttt{\color[HTML]{CB0000} failure} occurs for \texttt{no optimization} case}
		\label{}
		\begin{tabular}{ c | c | c | c | c } 
			\toprule
			\texttt{Flip Runs} & \texttt{Program Runs}& \texttt{prob(p)} & \texttt{z (Last)} & \texttt{(1-p)/p} \\ 
			\hline\hline
			49999 & 50000 & 1.0000000000 & 0 & 0.0000000000 \\ \hline 
			12798121 & 50000 & 0.0039072461 & 121 & 254.9347362328 \\ \hline 
			2118330 & 50000 & 0.0234384766 & 3 & 41.6648888947 \\ \hline 
			3191133 & 50000 & 0.0156259844 & 27 & 62.9959681516 \\ \hline 
			1592312 & 50000 & 0.0312509687 & 85 & 30.9990080819 \\ \hline 
			802573 & 50000 & 0.0625009375 & 6 & 14.9997600036 \\ \hline  
			404577 & 50000 & 0.1250008750 & 3 & 6.9999440004 \\ \hline 
			199379 & 50000 & 0.2500007500 & 2 & 2.9999880000 \\ \hline 
			133424 & 50000 & 0.3750006250 & 1 & 1.6666622222 \\ \hline 
			99661 & 50000 & 0.5000005000 & 0 & 0.9999980000 \\ \hline 
			\bottomrule
		\end{tabular}
	\end{table}
	\begin{table}
		\centering
		\caption{Comparing \texttt{prob(p)} value to cases where assert \texttt{\color[HTML]{036400} passed} without \texttt{optimization} step.}
		\label{}
		\begin{tabular}{ c | c | c | c | c } 
			\toprule
			\texttt{Flip Runs} & \texttt{Program Runs}& \texttt{prob(p)} & \texttt{z (Last)} & \texttt{(1-p)/p} \\ 
			\hline\hline
			2551264 & 50000 & 0.0195322305 & 60 & 50.1974298071 \\ \hline 
			6371788 & 50000 & 0.0078134922 & 169 & 126.9837458595 \\ \hline 
			4280156 & 50000 & 0.0117197383 & 303 & 84.3261373592 \\ \hline 
			1592312 & 50000 & 0.0312509687 & 85 & 30.9990080819 \\ \hline
			266112 & 50000 & 0.1875008125 & 7 & 4.3333102223 \\ \hline 
			\bottomrule
		\end{tabular}
	\end{table}
\end{document}

### 2021-04-27 benchmark/ex10.py

@@ -1,0 +1,31 @@
+import random
+import numpy as np
+from scipy.stats import bernoulli
+
+
+def ex10(inpt):
+    x = 0
+    n = 30  # N
+    y = 0
+    prob = inpt[0]
+    while(n > 0):
+        d = bernoulli.rvs(size=1, p=prob)[0]
+        if(d):
+            x = x + 1
+        else:
+            y = y + 1
+        n = n - 1
+    return x*y
+
+
+'''
+Simulation of fair coin
+Prinsys Paper
+Lst 7
+I = [x = 0 ∧ y − 1 = 0] − [x − 1 = 0 ∧ y = 0]  #as per prinsys template
+'''
+'''
+x -> [0,1],    y -> [0,1]
+
+Guess: True
+'''

### 2021-04-27 benchmark/ex18.py

@@ -1,0 +1,41 @@
+import random
+import numpy as np
+from scipy.stats import bernoulli
+
+'''
+src: http://www-i2.informatik.rwth-aachen.de/pub/index.php?type=download&pub_id=1274
+pg-120
+Fig 5.9
+
+I = [x ≥ 0 and x − n ≤ 0 and n − M ≤ 0] * (x/M - p*n/M + p) 
+
+'''
+'''
+x -> [0,0], n -> [0,0]               recheck
+guess: [x ≥ 0 and x − n ≤ 0 and n − M ≤ 0]
+x -> [0,4], n -> [0,4]
+'''
+
+
+def ex18(inpt):
+    x = 0
+    n = 0
+    prob = inpt[0]
+    M = 5
+    while n - M + 1 <= 0:
+        d = bernoulli.rvs(size=1, p=prob)[0]
+        if d:
+            x = x + 1
+        n = n + 1
+    return n
+
+
+'''
+src: https://moves.rwth-aachen.de/wp-content/uploads/WS1819/probprog/prob-prog-2018-lec89.pdf
+Joost-Pieter Katoen
+I = [t = A ∧ c = 0]+ [t = A ∧ c = 1] * (p1/(p1 + p2 - p1 * p2))+ \
+ [t = B ∧ c = 1] * ((1 - p2)/(p1 + p2 - p1 * p2))
+'''
+'''
+c -> [0,1],   t -> ['A','B'],  n -> [0,+inf]
+'''

### 2021-04-27 benchmark/ex20.py

@@ -1,0 +1,57 @@
+import random
+import numpy as np
+from scipy.stats import bernoulli
+
+'''
+Max 3SAT problem
+Theorem 2.1 in http://timroughgarden.org/w16/l/l18.pdf
+
+I= [n<=10] + [n>10] * (n*(7/8)*m)
+
+Post=n*(7/8)*m
+'''
+
+
+def ex20(inpt):
+    prob1, prob2 = inpt
+    n = 0
+    x1, x2, x3 = 0, 0, 0
+    z = 0
+    while(n <= 10):
+        d1 = bernoulli.rvs(size=1, p=prob1)[0]
+        if(d1):
+            x1 = 1
+        else:
+            x1 = 0
+        d2 = bernoulli.rvs(size=1, p=prob2)[0]
+        if(d2):
+            x2 = 1
+        else:
+            x2 = 0
+        d3 = bernoulli.rvs(size=1, p=prob2)[0]
+        if(d3):
+            x3 = 1
+        else:
+            x3 = 0
+
+        c1 = x1 + x2 + x3  # c1 = "x1 or x2 or x3"
+        if c1 >= 1:
+            c1 = 1
+        c2 = x1 + (1-x2) + x3  # c2 = "not x1 or x2 or x3"
+        if c2 >= 1:
+            c2 = 1
+        c3 = (1-x1) + x2 + x3  # c3 = "not x2 or x1 or x3"
+        if c3 >= 1:
+            c3 = 1
+        n = n + 1
+        z = c1 + c2 + c3
+    return z
+
+
+'''
+Kaminski pg 125
+I = [x-1 >= 0] + [x-1 < 0] * z
+'''
+'''
+x -> [-1,20],  z -> [0,+inf]
+'''

### 2021-04-27 benchmark/ex25.py

@@ -1,0 +1,34 @@
+import random
+import numpy as np
+from scipy.stats import bernoulli
+
+'''
+product.v2
+
+Pre-expectation:	n*n
+Post-expectation:	4*x*y
+
+Lagrange Interpolation output:
+
+Invariant:		n^2 + 2*n*y + 2*n*x + 4*x*y 
+
+'''
+'''
+x -> [1,+inf], n->[0,N],  y->[1,1]
+'''
+
+
+def ex25(inpt):
+    n = N
+    x = 1  # random
+    y = 1  # random
+    prob1, prob2 = inpt
+    while(n > 0):
+        d1 = bernoulli.rvs(size=1, p=prob1)[0]
+        if(d1):
+            x = x + 1
+        d2 = bernoulli.rvs(size=1, p=prob2)[0]
+        if(d2):
+            y = y + 1
+        n = n - 1
+    return (4 * x * y)

### 2021-04-27 benchmark/ex7.py

@@ -1,0 +1,37 @@
+import random
+import numpy as np
+from scipy.stats import bernoulli
+
+'''
+Lagrange Interpolation paper
+Binomial Distribution
+I=[y >= 0 and n − 1 >= 0] * (x + p * n * y)
+'''
+'''
+x -> [0,+inf],    n -> [0,10]
+'''
+
+
+def ex7(inpt):
+    x = 0
+    n = 10  # N
+    y = 10  # N
+    prob = inpt[0]
+    while(n > 0):
+        d = bernoulli.rvs(size=1, p=prob)[0]
+        if(d):
+            x = x + y
+        n = n-1
+    return x
+
+
+'''
+Lagrange Interpolation paper
+Binomial Distribution 2 (bin2)
+I = [y >= 0 and n − 1 >= 0] * (x + (0.125)* n * n + 0.125 * n − 0.75 * n * y)
+
+p=0.25
+'''
+'''
+x -> [0,+inf],    n -> [0,10],   [n-x <= 10]
+'''

### 2021-04-27 benchmark/ex8.py

@@ -1,0 +1,28 @@
+import random
+import numpy as np
+from scipy.stats import bernoulli
+
+
+def ex8(inpt):
+    x = 0
+    n = 10  # N
+    y = 10  # N
+    prob = inpt[0]
+    while(n > 0):
+        d = bernoulli.rvs(size=1, p=prob)[0]
+        if(d):
+            x = x + n
+        else:
+            x = x + y
+        n = n - 1
+    return x
+
+
+'''
+Lagrange Interpolation paper
+Sum of Random Series
+I= [n − 1 >= 0] * (x + (1/4) * n * n + (1/4) * n)
+'''
+'''
+x -> [0,+inf],    n -> [0,10],  [n - x <= 10]
+'''

### 2021-04-27 benchmark/ex9.py

@@ -1,0 +1,32 @@
+import random
+import numpy as np
+from scipy.stats import bernoulli
+
+
+def ex9(inpt):
+    x = 0
+    n = 10  # N
+    prob = inpt[0]
+    while(n > 0):
+        d = bernoulli.rvs(size=1, p=prob)[0]
+        if(d):
+            x = x + n
+        n = n - 1
+    return x
+
+
+'''
+Lagrange Interpolation paper
+Product of dependent random variables
+I = -(1/4) * n + x * y + (1/2) * x * n + (1/2) * y * n + \
+(1/4) * n^2 
+
+Lagrange output:
+
+pre=n(n-1) 
+post=xy 
+invariant = n^2 + 2nx + 2ny + 4xy - n
+'''
+'''
+x -> [0,+inf],    n -> [0,30],    y -> [0,+inf]
+'''

### 2021-04-27 benchmark/example_bloomfilter.cpp

@@ -1,0 +1,23 @@
+#include <iostream>
+#include <bf/all.hpp>
+
+int main()
+{
+    bf::basic_bloom_filter b(0.8, 100);
+
+    // Add two elements.
+    b.add("foo");
+    b.add(42);
+
+    // Test set membership
+    std::cout << b.lookup("foo") << std::endl; // 1
+    std::cout << b.lookup("bar") << std::endl; // 0
+    std::cout << b.lookup(42) << std::endl;    // 1
+
+    // Remove all elements.
+    b.clear();
+    std::cout << b.lookup("foo") << std::endl; // 0
+    std::cout << b.lookup(42) << std::endl;    // 0
+
+    return 0;
+}

### 2021-04-27 benchmark/example_hyperloglog.cpp

@@ -1,0 +1,52 @@
+#include <iostream>
+#include <fstream>
+
+// DataSketches/
+#include <DataSketches/hll.hpp>
+
+//simplified file operations and no error handling for clarity
+int main(int argc, char **argv)
+{
+    const int lg_k = 11;
+    const auto type = datasketches::HLL_4; // this is the default, but explicit here for illustration
+
+    // this section generates two sketches with some overlap and serializes them into files
+    {
+        // 100000 distinct keys
+        datasketches::hll_sketch sketch1(lg_k, type); // type is optional, defaults to HLL_4
+        for (int key = 0; key < 100000; key++)
+            sketch1.update(key);
+        std::ofstream os1("hll_sketch1.bin");
+        sketch1.serialize_compact(os1);
+
+        // 100000 distinct keys
+        datasketches::hll_sketch sketch2(lg_k, type); // type is optional, defaults to HLL_4
+        for (int key = 50000; key < 150000; key++)
+            sketch2.update(key);
+        std::ofstream os2("hll_sketch2.bin");
+        sketch2.serialize_compact(os2);
+    }
+
+    // this section deserializes the sketches, produces union and prints the result
+    {
+        std::ifstream is1("hll_sketch1.bin");
+        datasketches::hll_sketch sketch1 = datasketches::hll_sketch::deserialize(is1);
+
+        std::ifstream is2("hll_sketch2.bin");
+        datasketches::hll_sketch sketch2 = datasketches::hll_sketch::deserialize(is2);
+
+        datasketches::hll_union u(lg_k);
+        u.update(sketch1);
+        u.update(sketch2);
+        datasketches::hll_sketch sketch = u.get_result(type); // type is optional, defaults to HLL_4
+
+        // debug summary of the union result sketch
+        sketch.to_string(std::cout);
+
+        std::cout << "Distinct count estimate: " << sketch.get_estimate() << std::endl;
+        std::cout << "Distinct count lower bound 95% confidence: " << sketch.get_lower_bound(2) << std::endl;
+        std::cout << "Distinct count upper bound 95% confidence: " << sketch.get_upper_bound(2) << std::endl;
+    }
+
+    return 0;
+}

### 2021-04-27 prinsys_benchmark.py

@@ -1,779 +1,0 @@
-import random
-import numpy as np
-from scipy.stats import bernoulli
-
-'''
-ex0c
-
-
-Prinsys paper
-Lst 1
-I = [z >= 0] * z + [z >= 0 and flip == 0] * (1 - prob)/prob
-'''
-'''
-z -> [0,+inf], flip -> [0,1]
-I' = z + [flip == 0] * (1 - prob)/prob
-
-I' [flip == 0] = [flip == 0] (z + (1 - prob)/prob)
-
-wp(body, I') = prob * wp(flip = 1, I') + (1-prob) * wp(z = z+1, I')
-= prob * (z + 0) + (1-prob) * (z + 1 + [flip == 0] * (1 - prob)/prob)) 
-= z + (1-prob) + [flip == 0] * (1-prob) * (1 - prob)/prob
-= [flip != 0] (z + 1-prob) + [flip == 0] * (z + 1-prob + (1-prob) * (1 - prob)/prob)
-= [flip != 0] (z + 1-prob) + [flip == 0] * (z + (1-prob)/prob)
-[flip == 0] *wp(body, I') + [flip != 0] z
-= [flip == 0] * (z + (1-prob)/prob) + [flip != 0] z 
-= I' 
-'''
-
-
-def ex0(inpt):
-    prob, _ = inpt
-    z = 0
-    flip = 0
-    while (flip == 0):
-        d = bernoulli.rvs(size=1, p=prob)[0]
-        if d:
-            flip = 1
-        else:
-            z = z + 1
-    return z
-# I -> post cond.
-# Post == Pre
-# (z > (1-prob)/prob)
-
-
-'''
-I = [z >= 0] * z + [z >= 0 and flip == 0] * (1 - prob)/prob 
-Assertion Invariant: TODO
-'''
-
-
-def ex0a(inpt):
-    prob, _ = inpt
-    z = 0
-    x = 0
-    flip = 0
-    while (flip == 0):
-        d = bernoulli.rvs(size=1, p=prob)[0]
-        if d:
-            flip = 1
-        else:
-            x = x * 2
-            z = z + 1
-    return z
-
-
-'''
-I = [z >= 0] * z + [z >= 0 and flip == 0] * 2 * (1 - prob)/prob 
-Assertion Invariant: TODO
-'''
-
-
-def ex0b(inpt):
-    prob, _ = inpt
-    z = 0
-    i = 0
-    flip = 0
[…]

### 2021-04-27 run_foralls.sh

@@ -7,6 +7,5 @@ rm -rf $1/foralls/*
 rm -rf $1/pathprobs.txt
 rm -rf $1/results.txt
 
-python3 $1/genCandidateM.py
 python3 $1/candidates.py  
 python3 $1/executeCV.py foralls

### 2021-04-29 shared/analysis.tex
Benchmark Example 7

@@
 		\begin{minted}{python}
-	def progam1(inpt):
-		prob, _ = inpt
-		z = 0
-		flip = 0
-		while (flip == 0):
+	def ex7(inpt):
+		x = 0
+		n = 10  # N This is a forall.
+		y = 10  # N This is a forall.
+		prob = inpt[0] # This is a forall. 
+		while(n > 0):
 			d = bernoulli.rvs(size=1, p=prob)[0]
-			if d:
-				flip = 1
-			else:
-				z = z + 1
-		return z
+			if(d): 
+				x = x + y # x is probabilistic here
+			n = n-1
+		return x
 
-	assert(z > (1 - prob)/prob)
+	# Expected Value of "x"
+	# E[x] = prob * n * y
+	assert((P(x - (prob * n * y)) <= 0) <= 0.6)
 		\end{minted}
@@
 	\begin{figure}
+	\begin{minted}{python}
+		(0.0000001 < prob_sym),
+		(1 <= y_sym),
+		(prob_sym <= 1),
+		(10 <= n_sym)
+	\end{minted}
+	\caption{Constraints on \texttt{Path-1} where control flow is in the \texttt{while} loop.}
+	\end{figure}
+	\begin{figure}
+		\begin{minted}{python}
+		(0.0000001 < prob_sym),
+		(1 <= y_sym),
+		(prob_sym <= 1),
+		n_sym == 0 # Exit from Loop
+		\end{minted}
+		\caption{Constraints on \texttt{Path-2} where control flow exits the \texttt{while} loop.}
+	\end{figure}
+\begin{figure}
 	\begin{minted}{c}
-	int main()
+	double prob;
+	int x, n, y;
+
+	// forall variables
+	klee_make_symbolic(&y, sizeof(y), "y_sym");
+	klee_make_symbolic(&n, sizeof(n), "n_sym");
+	make_pse_symbolic(&prob, sizeof(prob), "prob_sym", 0, 1);
+
+	// Some restrictions on the values.
+	klee_assume(y >= 0);
+	klee_assume(10 <= n);
+
+	// Work around for silent concretization of prob.
+	prob = 0.5;
+
+	// Prob Sym Variables.
+	make_pse_symbolic(&x, sizeof(x), "x_pse_sym", 0, 2147483647);
+
+	std::default_random_engine generator;
+	std::bernoulli_distribution bernoulli_rvs(prob);
+
+	// This is the "inner" loop which affects the final value of "x".
+	while (n > 0)
 	{
-		double prob;
-		int d, z = 0, flip = 0;
-
-		make_pse_symbolic(&flip, sizeof(flip), "flip_pse_sym", 0, 1);
-		make_pse_symbolic(&prob, sizeof(prob), "prob_sym", 0, 1);
-		klee_make_symbolic(&z, sizeof(z), "z_sym");
-		klee_assume(z >= 0);
-
-		std::random_device rd{};
-		std::mt19937 rng{rd()};
-		std::bernoulli_distribution rvs(prob);
-
-		while (flip == 0) {
-			int d = rvs(rng);
-			if (d) {
-				flip = 1;
-			} else {
-				// must be executed more 
-				// for the assert to pass. 
-				z += 1; 
-			}
+		int d = bernoulli_rvs(generator);
+		if (d)
+			x = x + y;
+		n = n - 1;
 	}
@@
 	return 0;
+	\end{minted}
+	\caption{\texttt{KLEE Transformation} of the program for testing the \texttt{assert}. }
+\end{figure}
+
+	\begin{figure}
+		\begin{minted}{c}
+	long double prob;
+	int x, n, y, n_start, y_start;
+	long long unsigned int win = 0, loop_run = 0, prob_runs = 0;
+
+	scanf("%d", &n);
+	scanf("%d", &y);
+	scanf("%Lf", &prob);
+
+	n_start = n;
+	y_start = y;
+
+	while (termCount--)
+	{
+		x = 0;
+		int n_loop = n; // maintain "n" for re-runs of loop.
+
+		// program execution
+		std::default_random_engine generator;
+		std::bernoulli_distribution bernoulli_rvs(prob);
+
+		// "n" gets changed, we need to maintain the loop. 
+		while (n_loop > 0)
+		{
+			int d = bernoulli_rvs(generator);
+			if (d)
+			{
+				// This doesn't favours the "win" condition.
+				x = x + y;
+			}
+			n_loop -= 1;
+
+			// Iterations of the inner loop.
+			// How many times the probabilistic loop gets executed?
+			prob_runs++;
+		}
+
+		// Sample for probability. This is the assert condition.
+		if ((double)x - (prob * n * y) <= 0)
+			win++;
+
+		// No. of times the program gets executed.
+		loop_run++;
 	}
 		\end{minted}
-		\caption{\texttt{Translate()} of the program for testing the \texttt{assert}. }
-	\end{figure}
-	\begin{figure}
-		\begin{minted}{c}
-		long long int termCount = 50000, unroll = 2500;
-		while (termCount--)
-		{
-			flip = 0;
-			z = 0;
-			scanf("%Lf", &prob);
-
-			...
-
-			while (flip == 0 && unroll--) {
-				int d = rvs(rng);
-				if (d) {
-					flip = 1;
-				} else { 
-					z += 1; 
-				}
-				if (z > ((double)(1 - prob) / (prob)))
-					win++;
-				flip_runs++;
-			}
-			program_runs++;
-		}
-		\end{minted}
-		\caption{\texttt{Translate()} of the program for testing the \texttt{assert}. }
-	\end{figure}
-	\begin{figure}
-			\begin{minted}{python}
-		(flip_pse_sym <= 1),
-		(0 <= flip_pse_sym),
-		(prob_sym <= 1),
-		(0.000001 < prob_sym),
-		(0 <= z_sym),
-
-		FAIL : (z_sym * prob_sym - (1 - prob_sym) <= 0)
-		\end{minted}
-		\caption{Constraints without optimization step.}
-	\end{figure}
-	\begin{figure}
-		\begin{minted}{python}
-		(flip_pse_sym <= 1),
-		(0 <= flip_pse_sym),
-		(prob_sym <= 1),
-		(0.000001 < prob_sym),
-		(0 <= z_sym),
-
-		FAIL : (z_sym * prob_sym - (1 - prob_sym) <= 0)
-		optimize : maximize(prob_sym)
-		\end{minted}
-		\caption{Constraints with optimization step.}
+		\caption{Testing \texttt{Translate()} of the program for testing the \texttt{assert}. }
 	\end{figure}
@@
 		\centering
-		\caption{Comparing \texttt{prob(p)} value to cases Vs \texttt{assert} status for \texttt{optimization} over \texttt{prob} value}
+		\caption{Comparing \texttt{prob(p)} value Vs \texttt{assert} status for low values of \texttt{prob(p)} shown for limited iterations.}
 		\label{}
-		\begin{tabular}{ c | c | c | c | c } 
+		\begin{tabular}{ c | c | c | c | c | c | c } 
 			\toprule
-			\texttt{Flip Runs} & \texttt{Program Runs}& \texttt{prob(p)} & \texttt{z (Last)} & \texttt{(1-p)/p} \\ 
+			\texttt{prob-value} & \texttt{Program Runs}& \texttt{Loop Runs} & \texttt{Wins} & \texttt{P((x - (prob * n * y)) <= 0)}  & \texttt{n} & \texttt{y} \\ 
 			\hline\hline
-			49999 & 50000 & 0.9999990463 & 0 & 0.0000009537 \\ \hline 
-			49999 & 50000 & 0.9999995232 & 0 & 0.0000004768 \\ \hline 
-			49999 & 50000 & 0.9999998808 & 0 & 0.0000001192 \\ \hline 
-			49999 & 50000 & 0.9999999991 & 0 & 0.0000000009 \\ \hline 
-			49999 & 50000 & 1.0000000000 & 0 & 0.0000000000 \\ \hline 
-			50000 & 50000 & 0.9999847412 & 0 & 0.0000152590 \\ \hline 
-			50001 & 50000 & 0.9999694825 & 0 & 0.0000305184 \\ \hline 
-			50003 & 50000 & 0.9998779298 & 0 & 0.0001220851 \\ \hline 
-			50008 & 50000 & 0.9997558596 & 0 & 0.0002442000 \\ \hline 
-			50016 & 50000 & 0.9995117192 & 0 & 0.0004885193 \\ \hline 
-			50045 & 50000 & 0.9990234385 & 0 & 0.0009775161 \\ \hline 
-			50822 & 50000 & 0.9843750156 & 0 & 0.0158729998 \\ \hline 
-			53303 & 50000 & 0.9375000625 & 0 & 0.0666665956 \\ \hline 
-			57237 & 50000 & 0.8750001250 & 0 & 0.1428569796 \\ \hline 
-			99385 & 50000 & 0.5000005000 & 0 & 0.9999980000 \\ \hline 
+			0.0000001298 & 100000 & 5600000 & 100000 & 1.000000 & 56 & 21 \\ \hline
+			0.0000001596 & 100000 & 4000000 & 100000 & 1.000000 & 40 & 17 \\ \hline
+			0.0000003384 & 100000 & 3600000 & 100000 & 1.000000 & 36 & 28 \\ \hline
+			0.0000039147 & 100000 & 2800000 & 100000 & 1.000000 & 28 & 18 \\ \hline
+			0.0000077294 & 100000 & 2300000 & 100000 & 1.000000 & 23 & 24 \\ \hline
+			0.0000153588 & 100000 & 2700000 & 100000 & 1.000000 & 27 & 16 \\ \hline
+			0.0000306176 & 100000 & 2100000 & 100000 & 1.000000 & 21 & 15 \\ \hline
+			0.0000611352 & 100000 & 2200000 & 100000 & 1.000000 & 22 & 14 \\ \hline
+			0.0001221703 & 100000 & 2000000 & 100000 & 1.000000 & 20 & 11 \\ \hline
+			0.0002442406 & 100000 & 2600000 & 100000 & 1.000000 & 26 & 10 \\ \hline
+			0.0004883812 & 100000 & 1900000 & 100000 & 1.000000 & 19 & 13 \\ \hline
+			0.0009766624 & 100000 & 1800000 & 100000 & 1.000000 & 18 & 9 \\ \hline
+			0.0019532248 & 100000 & 2500000 & 100000 & 1.000000 & 25 & 12 \\ \hline
+			0.0039063496 & 100000 & 2400000 & 100000 & 1.000000 & 24 & 8 \\ \hline
+			{\textbf{ \color[HTML]{036400} 0.0078125992}} & {\textbf{\color[HTML]{036400} 100000}} & {\textbf{\color[HTML]{036400} 1700000}} & {\textbf{\color[HTML]{036400} 0}} & {\textbf{\color[HTML]{036400} 0.000000}} & {\textbf{\color[HTML]{036400} 17}} & {\textbf{\color[HTML]{036400} 7}} \\ \hline
+			0.0156250984 & 100000 & 1600000 & 0 & 0.000000 & 16 & 5 \\ \hline
+			0.0312500969 & 100000 & 1400000 & 0 & 0.000000 & 14 & 6 \\ \hline
+			0.0625000937 & 100000 & 1300000 & 0 & 0.000000 & 13 & 4 \\ \hline
+			0.2500000750 & 100000 & 1100000 & 0 & 0.000000 & 11 & 2 \\ \hline
+			0.5000000500 & 100000 & 1000000 & 0 & 0.000000 & 10 & 1 \\ \hline
+			\bottomrule
+		\end{tabular}
+	\end{table}
+	\begin{figure}
+\begin{minted}{python}
+	(0.0075243180 < prob_sym),
+	(1 <= y_sym),
+	(prob_sym <= 0.0078125992),
+	(10 <= n_sym)
+	\end{minted}
+	\caption{Narrowing constraints on \texttt{Path-1} where control flow is in the \texttt{while} loop.}
+\end{figure}
+\begin{table}
+	\centering
+	\caption{Comparing \texttt{prob(p)} value to cases Vs \texttt{assert} status for low values of \texttt{prob(p)} on narrowing}
+	\label{}
+	\begin{tabular}{ c | c | c | c | c | c | c } 
+		\toprule
+		\texttt{prob-value} & \texttt{Program Runs}& \texttt{Loop Runs} & \texttt{Wins} & \texttt{P((x - (prob * n * y)) <= 0)}  & \texttt{n} & \texttt{y} \\ 
+		\hline\hline
+		0.0068589250 & 100000 & 2500000 & 100000 & 1.000000 & 25 & 12 \\ \hline
+		0.0068665544 & 100000 & 1600000 & 100000 & 1.000000 & 16 & 5 \\ \hline
+		0.0068970719 & 100000 & 1400000 & 100000 & 1.000000 & 14 & 6 \\ \hline
+		0.0069581071 & 100000 & 1300000 & 100000 & 1.000000 & 13 & 4 \\ \hline
+		0.0070801774 & 100000 & 1200000 & 100000 & 1.000000 & 12 & 3 \\ \hline
+		0.0073243180 & 100000 & 1100000 & 100000 & 1.000000 & 11 & 2 \\ \hline
+		{\textbf{ \color[HTML]{036400} 0.0078125992}} & {\textbf{\color[HTML]{036400} 100000}} & {\textbf{\color[HTML]{036400} 1700000}} & {\textbf{\color[HTML]{036400} 0}} & {\textbf{\color[HTML]{036400} 0.000000}} & {\textbf{\color[HTML]{036400} 17}} & {\textbf{\color[HTML]{036400} 7}} \\ \hline
+		0.0156250984 & 100000 & 1600000 & 0 & 0.000000 & 16 & 5 \\ \hline
 		\bottomrule
@@
 	\centering
-		\caption{Comparing \texttt{prob(p)} value to cases where assert \texttt{\color[HTML]{CB0000} failure} occurs for \texttt{no optimization} case}
+	\caption{Comparing \texttt{prob(p)} value to cases Vs \texttt{assert} status for low values of \texttt{prob(p)} on further narrowing}
 	\label{}
-		\begin{tabular}{ c | c | c | c | c } 
+	\begin{tabular}{ c | c | c | c | c | c | c } 
 		\toprule
-			\texttt{Flip Runs} & \texttt{Program Runs}& \texttt{prob(p)} & \texttt{z (Last)} & \texttt{(1-p)/p} \\ 
+		\texttt{prob-value} & \texttt{Program Runs}& \texttt{Loop Runs} & \texttt{Wins} & \texttt{P((x - (prob * n * y)) <= 0)}  & \texttt{n} & \texttt{y} \\ 
 		\hline\hline
-			49999 & 50000 & 1.0000000000 & 0 & 0.0000000000 \\ \hline 
-			12798121 & 50000 & 0.0039072461 & 121 & 254.9347362328 \\ \hline 
-			2118330 & 50000 & 0.0234384766 & 3 & 41.6648888947 \\ \hline 
-			3191133 & 50000 & 0.0156259844 & 27 & 62.9959681516 \\ \hline 
-			1592312 & 50000 & 0.0312509687 & 85 & 30.9990080819 \\ \hline 
-			802573 & 50000 & 0.0625009375 & 6 & 14.9997600036 \\ \hline  
-			404577 & 50000 & 0.1250008750 & 3 & 6.9999440004 \\ \hline 
-			199379 & 50000 & 0.2500007500 & 2 & 2.9999880000 \\ \hline 
-			133424 & 50000 & 0.3750006250 & 1 & 1.6666622222 \\ \hline 
-			99661 & 50000 & 0.5000005000 & 0 & 0.9999980000 \\ \hline 
-			\bottomrule
-		\end{tabular}
-	\end{table}
-	\begin{table}
-		\centering
-		\caption{Comparing \texttt{prob(p)} value to cases where assert \texttt{\color[HTML]{036400} passed} without \texttt{optimization} step.}
-		\label{}
-		\begin{tabular}{ c | c | c | c | c } 
-			\toprule
-			\texttt{Flip Runs} & \texttt{Program Runs}& \texttt{prob(p)} & \texttt{z (Last)} & \texttt{(1-p)/p} \\ 
-			\hline\hline
-			2551264 & 50000 & 0.0195322305 & 60 & 50.1974298071 \\ \hline 
-			6371788 & 50000 & 0.0078134922 & 169 & 126.9837458595 \\ \hline 
-			4280156 & 50000 & 0.0117197383 & 303 & 84.3261373592 \\ \hline 
-			1592312 & 50000 & 0.0312509687 & 85 & 30.9990080819 \\ \hline
-			266112 & 50000 & 0.1875008125 & 7 & 4.3333102223 \\ \hline 
+		0.0075603531 & 100000 & 1300000 & 100000 & 1.000000 & 13 & 4 \\ \hline
+		0.0075963883 & 100000 & 1200000 & 100000 & 1.000000 & 12 & 3 \\ \hline
+		0.0076684586 & 100000 & 1100000 & 100000 & 1.000000 & 11 & 2 \\ \hline
+		0.0077243207 & 100000 & 2100000 & 0 & 0.000000 & 21 & 24 \\ \hline
+		0.0077243234 & 100000 & 2800000 & 0 & 0.000000 & 28 & 16 \\ \hline
+	{\textbf{ \color[HTML]{036400} 0.0078125992}} & {\textbf{\color[HTML]{036400} 100000}} & {\textbf{\color[HTML]{036400} 1700000}} & {\textbf{\color[HTML]{036400} 0}} & {\textbf{\color[HTML]{036400} 0.000000}} & {\textbf{\color[HTML]{036400} 17}} & {\textbf{\color[HTML]{036400} 7}} \\ \hline
 		\bottomrule

### 2021-04-29 estimate_example1/paths.py

@@ -1,66 +1,0 @@
-import z3
-
-d_sym, c_sym, a_sym, b_prob_sym, e_prob_sym = z3.Ints("d_sym c_sym a_sym b_prob_sym e_prob_sym")
-
-path1 = [
-(0 <= b_prob_sym),
-(b_prob_sym <= 1),
-(1 <= e_prob_sym),
-(e_prob_sym <= 6),
-(0 <= a_sym),
-(a_sym <= 1),
-(1 <= c_sym),
-(c_sym <= 10),
-(0 <= d_sym),
-(d_sym <= 5),
-(b_prob_sym < a_sym),
-((e_prob_sym + c_sym) < 15)
-]
-
-path2 = [
-(0 <= b_prob_sym),
-(b_prob_sym <= 1),
-(1 <= e_prob_sym),
-(e_prob_sym <= 6),
-(0 <= a_sym),
-(a_sym <= 1),
-(1 <= c_sym),
-(c_sym <= 10),
-(0 <= d_sym),
-(d_sym <= 5),
-(b_prob_sym < a_sym),
-z3.Not(((e_prob_sym + c_sym) < 15))
-]
-
-path3 = [
-(0 <= b_prob_sym),
-(b_prob_sym <= 1),
-(1 <= e_prob_sym),
-(e_prob_sym <= 6),
-(0 <= a_sym),
-(a_sym <= 1),
-(1 <= c_sym),
-(c_sym <= 10),
-(0 <= d_sym),
-(d_sym <= 5),
-z3.Not((b_prob_sym < a_sym)),
-(1 < (e_prob_sym + d_sym))
-]
-
-path4 = [
-(0 <= b_prob_sym),
-(b_prob_sym <= 1),
-(1 <= e_prob_sym),
-(e_prob_sym <= 6),
-(0 <= a_sym),
-(a_sym <= 1),
-(1 <= c_sym),
-(c_sym <= 10),
-(0 <= d_sym),
-(d_sym <= 5),
-z3.Not((b_prob_sym < a_sym)),
-z3.Not((1 < (e_prob_sym + d_sym)))
-]
-
-
-paths = [path1, path2, path3, path4]

### 2021-04-29 estimate_example1/preprocess.py

@@ -1,23 +1,0 @@
-# -*- coding: utf-8 -*-
-
-import os
-import sys
-
-
-def transformPass(code_file):
-    code = []
-    with open(code_file, mode="r+") as fileptr:
-        code_lines = fileptr.readlines()
-        for lines in code_lines:
-            if lines.strip().startswith("klee_make_symbolic", 0):
-                forallVar = lines.strip().split(",")[0].split("&")[1].strip()
-                print(f"forall : {forallVar}")
-                code.append(f"scanf(%d, &{forallVar});")
-            if lines.strip().startswith("make_pse_symbolic", 0):
-                forallVar = lines.strip().split(",")[0].split("&")[1].strip()
-                print(f"ProbVar : {forallVar}")
-                code.append(f"scanf(%d, &{forallVar});")
-
-
-if __name__ == '__main__':
-    transformPass(sys.argv[1])

### 2021-04-29 estimate_example2/candidates.py

@@ -1,170 +1,0 @@
-# -*- coding: utf-8 -*-
-
-import z3
-import os
-
-"""
-Below are a list of constraints that dictate which 
-path is taken during actual program execution. 
-We process KLEE constraints and simplify them to get these 
-constraints. 
-"""
-
-# ==== Will be Autogenerated by PyKLEE ====
-a, b, c, d, e, win = z3.Ints("a_sym b_prob_sym c_sym d_sym e_prob_sym win_sym")
-
-klee_assume1 = z3.And(a >= 0, a <= 1)
-klee_assume2 = z3.And(c >= 1, c <= 10)
-klee_assume3 = z3.And(d >= 0, d <= 5)
-klee_assume4 = z3.And(b >= 0, b <= 1)
-klee_assume5 = z3.And(e >= 1, e <= 6)
-klee_assume6 = win == 1
-
-cond1 = b < a
-notcond1 = z3.Not(b < a)
-
-cond2 = 15 > c + e
-notcond2 = z3.Not(15 > c + e)
-
-cond3 = 1 < d + e
-notcond3 = z3.Not(1 < d + e)
-
-"""
-Paths generated are reported by KLEE. 
-"""
-
-path1 = [klee_assume1, klee_assume2, klee_assume3,
-         klee_assume4, klee_assume5, klee_assume6, cond1, cond2]
-path2 = [klee_assume1, klee_assume2, klee_assume3,
-         klee_assume4, klee_assume5, cond1, notcond2]
-path3 = [klee_assume1, klee_assume2, klee_assume3,
-         klee_assume4, klee_assume5, klee_assume6, notcond1, cond3]
-path4 = [klee_assume1, klee_assume2, klee_assume3,
-         klee_assume4, klee_assume5, notcond1, notcond3]
-
-paths = [path1, path2, path3, path4]
-
-# ==== Will be Autogenerated by PyKLEE ====
-
-
-# ==== Automatically added By Query Parse ====
-class ProbQueryObject:
-    """
-    This object is responsible for storing the query proposed by the user
-    The user may specify as a comment in the C/C++ code used to symbex via KLEE
-    """
-
-    def __init__(self, objective, objectiveType):
-        self.objective = objective
-        self.type = objectiveType
-        self.predicates = []
-        # self.eval = eval(self.objective)
-
-    def __repr__(self):
-        pass
-
-    def __str__(self):
-        pass
-
-    def __index__(self, index):
-        return self.predicates[index]
-
-    def __getitem__(self, key):
[…]

### 2021-04-29 estimate_example2/genCandidateM.py

@@ -1,18 +1,0 @@
-# -*- coding: utf-8 -*-
-
-import os
-
-pwd = os.path.dirname(__file__)
-inputFilePath = os.path.join(pwd, "foralls")
-
-a, c, d = 0, 0, 0
-
-for a in range(2):
-    for c in range(10):
-        for d in range(10):
-            with open(
-                os.path.join(inputFilePath, f"model_{a}_{c}_{d}.txt"), mode="w"
-            ) as fileptr:
-                fileptr.write(f"{a}\n")
-                fileptr.write(f"{c + 1}\n")
-                fileptr.write(f"{d}\n")

### 2021-04-29 estimate_example2/paths.py

@@ -1,50 +1,0 @@
-import z3
-
-a_sym, c_sym, b_sym = z3.Ints("a_sym c_sym b_sym")
-
-path1 = [
-    (90 <= c_sym),
-    (c_sym <= 120),
-    (0 <= a_sym),
-    (a_sym <= 10000),
-    (0 <= b_sym),
-    (b_sym <= 10000),
-    z3.Not(z3.And((0 < a_sym), (0 < c_sym))),
-    ((b_sym + a_sym) < c_sym)
-]
-
-path2 = [
-    (90 <= c_sym),
-    (c_sym <= 120),
-    (0 <= a_sym),
-    (a_sym <= 10000),
-    (0 <= b_sym),
-    (b_sym <= 10000),
-    z3.Not(z3.And((0 < a_sym), (0 < c_sym))),
-    z3.Not(((b_sym + a_sym) < c_sym))
-]
-
-path3 = [
-    (90 <= c_sym),
-    (c_sym <= 120),
-    (0 <= a_sym),
-    (a_sym <= 10000),
-    (0 <= b_sym),
-    (b_sym <= 10000),
-    z3.And((0 < a_sym), (0 < c_sym)),
-    ((b_sym + a_sym) < c_sym)
-]
-
-path4 = [
-    (90 <= c_sym),
-    (c_sym <= 120),
-    (0 <= a_sym),
-    (a_sym <= 10000),
-    (0 <= b_sym),
-    (b_sym <= 10000),
-    z3.And((0 < a_sym), (0 < c_sym)),
-    z3.Not(((b_sym + a_sym) < c_sym))
-]
-
-
-paths = [path1, path2, path3, path4]

### 2021-04-29 estimate_example3/candidates.py

@@ -1,8859 +1,0 @@
-# -*- coding: utf-8 -*-
-
-import z3
-import os
-
-"""
-Below are a list of constraints that dictate which 
-path is taken during actual program execution. 
-We process KLEE constraints and simplify them to get these 
-constraints. 
-"""
-
-# ==== Will be Autogenerated by PyKLEE ====
-import z3
-
-(
-    j_sym_1,
-    j_sym_3,
-    j_sym_5,
-    j_sym_6,
-    k_sym,
-    j_sym_8,
-    j_sym_4,
-    j_sym_7,
-    j_sym_2,
-    j_sym,
-) = z3.Ints(
-    "j_sym_1 j_sym_3 j_sym_5 j_sym_6 k_sym j_sym_8 j_sym_4 j_sym_7 j_sym_2 j_sym"
-)
-
-path1 = [
-    (1 <= k_sym),
-    (k_sym <= 10),
-    (0 <= j_sym),
-    (j_sym <= k_sym),
-    z3.Not((j_sym < k_sym)),
-    (j_sym_1 < k_sym),
-    (j_sym_2 < k_sym),
-    z3.Not((j_sym_3 < k_sym)),
-    z3.Not((j_sym_4 < k_sym)),
-    z3.Not((j_sym_5 < k_sym)),
-    z3.Not((j_sym_6 < k_sym)),
-    z3.Not((j_sym_7 < k_sym)),
-    (j_sym_8 < k_sym),
-]
-
-path2 = [
-    (1 <= k_sym),
-    (k_sym <= 10),
-    (0 <= j_sym),
-    (j_sym <= k_sym),
-    z3.Not((j_sym < k_sym)),
-    (j_sym_1 < k_sym),
-    (j_sym_2 < k_sym),
-    z3.Not((j_sym_3 < k_sym)),
-    z3.Not((j_sym_4 < k_sym)),
-    z3.Not((j_sym_5 < k_sym)),
-    z3.Not((j_sym_6 < k_sym)),
-    z3.Not((j_sym_7 < k_sym)),
-    z3.Not((j_sym_8 < k_sym)),
-]
-
-path3 = [
-    (1 <= k_sym),
-    (k_sym <= 10),
-    (0 <= j_sym),
-    (j_sym <= k_sym),
[…]

### 2021-04-29 estimate_example3/executeCV.py

@@ -1,98 +1,0 @@
-import os
-import sys
-import threading
-import logging
-import time
-from alive_progress import alive_bar
-from subprocess import run, CalledProcessError
-
-pwd = os.path.dirname(__file__)
-
-executable = os.path.join(pwd, os.pardir, "bin/example")
-codeFile = os.path.join(pwd, os.pardir, "example1_mod.cpp")
-
-inputFilePath = os.path.join(pwd, sys.argv[1])
-outputFilePath = os.path.join(pwd, "outputs")
-
-
-def build():
-    try:
-        # print(f"Building Binary Example {example}.c")
-        output = run(
-            f"g++ {codeFile} -o {executable}",
-            shell=True,
-            capture_output=True,
-            text=True,
-        )
-    except CalledProcessError as err:
-        print(f"Build Error : {err}")
-    else:
-        print(f"Return : {output.returncode}")
-    return output.returncode
-
-
-def executeCV(executable, inFile, outfile, errFile):
-    try:
-        # print(f"Running Binary Example {example}.c")
-        output = run(
-            f"{executable} < {inFile} > {outfile} 2> {errFile}",
-            shell=True,
-            capture_output=True,
-            text=True,
-        )
-    except CalledProcessError as err:
-        print(f"Execute Error : {err}")
-    else:
-        pass
-    return output.returncode
-
-
-logging.basicConfig(level=logging.DEBUG)
-
-if __name__ == "__main__":
-    build()
-    executeThreads = []
-    with alive_bar(len(os.listdir(inputFilePath))) as executeBar:
-        for index, inputFile in enumerate(os.listdir(inputFilePath)):
-            worker_thread = threading.Thread(
-                target=executeCV,
-                args=(
-                    executable,
-                    os.path.join(inputFilePath, inputFile),
-                    os.path.join(outputFilePath, f"output_{index}.txt"),
-                    os.path.join(outputFilePath, f"output_err_{index}.txt"),
-                ),
-            )
-            executeThreads.append(worker_thread)
-            worker_thread.start()
-            time.sleep(0.2)
-            executeBar()
-
-    for index, worker in enumerate(executeThreads):
-        worker.join()
-
-    num_outs = len(os.listdir(outputFilePath))
-    sumtotal = 0.0
-    count = 0
-
-    with alive_bar(num_outs) as executeBar:
-        for index, outputFile in enumerate(os.listdir(outputFilePath)):
-            if "err" not in outputFile:
[…]

### 2021-04-29 estimate_example3/paths.py

@@ -1,8724 +1,0 @@
-import z3
-
-(
-    j_sym_1,
-    j_sym_3,
-    j_sym_5,
-    j_sym_6,
-    k_sym,
-    j_sym_8,
-    j_sym_4,
-    j_sym_7,
-    j_sym_2,
-    j_sym,
-) = z3.Ints(
-    "j_sym_1 j_sym_3 j_sym_5 j_sym_6 k_sym j_sym_8 j_sym_4 j_sym_7 j_sym_2 j_sym"
-)
-
-path1 = [
-    (1 <= k_sym),
-    (k_sym <= 10),
-    (0 <= j_sym),
-    (j_sym <= k_sym),
-    z3.Not((j_sym < k_sym)),
-    (j_sym_1 < k_sym),
-    (j_sym_2 < k_sym),
-    z3.Not((j_sym_3 < k_sym)),
-    z3.Not((j_sym_4 < k_sym)),
-    z3.Not((j_sym_5 < k_sym)),
-    z3.Not((j_sym_6 < k_sym)),
-    z3.Not((j_sym_7 < k_sym)),
-    (j_sym_8 < k_sym),
-]
-
-path2 = [
-    (1 <= k_sym),
-    (k_sym <= 10),
-    (0 <= j_sym),
-    (j_sym <= k_sym),
-    z3.Not((j_sym < k_sym)),
-    (j_sym_1 < k_sym),
-    (j_sym_2 < k_sym),
-    z3.Not((j_sym_3 < k_sym)),
-    z3.Not((j_sym_4 < k_sym)),
-    z3.Not((j_sym_5 < k_sym)),
-    z3.Not((j_sym_6 < k_sym)),
-    z3.Not((j_sym_7 < k_sym)),
-    z3.Not((j_sym_8 < k_sym)),
-]
-
-path3 = [
-    (1 <= k_sym),
-    (k_sym <= 10),
-    (0 <= j_sym),
-    (j_sym <= k_sym),
-    z3.Not((j_sym < k_sym)),
-    z3.Not((j_sym_1 < k_sym)),
-    (j_sym_2 < k_sym),
-    z3.Not((j_sym_3 < k_sym)),
-    z3.Not((j_sym_4 < k_sym)),
-    z3.Not((j_sym_5 < k_sym)),
-    z3.Not((j_sym_6 < k_sym)),
-    z3.Not((j_sym_7 < k_sym)),
-    (j_sym_8 < k_sym),
-]
-
-path4 = [
[…]

### 2021-04-29 estimate_example3/preprocess.py

@@ -1,23 +1,0 @@
-# -*- coding: utf-8 -*-
-
-import os
-import sys
-
-
-def transformPass(code_file):
-    code = []
-    with open(code_file, mode="r+") as fileptr:
-        code_lines = fileptr.readlines()
-        for lines in code_lines:
-            if lines.strip().startswith("klee_make_symbolic", 0):
-                forallVar = lines.strip().split(",")[0].split("&")[1].strip()
-                print(f"forall : {forallVar}")
-                code.append(f"scanf(%d, &{forallVar});")
-            if lines.strip().startswith("make_pse_symbolic", 0):
-                forallVar = lines.strip().split(",")[0].split("&")[1].strip()
-                print(f"ProbVar : {forallVar}")
-                code.append(f"scanf(%d, &{forallVar});")
-
-
-if __name__ == "__main__":
-    transformPass(sys.argv[1])

### 2021-04-29 estimate_example5/candidates.py

@@ -1,8 +1,8 @@
 # -*- coding: utf-8 -*-
 
 import z3
-import sys
 import os
+import sys
 
 """
 Below are a list of constraints that dictate which 
@@ -12,33 +12,34 @@ constraints.
 """
 
 # ==== Will be Autogenerated by PyKLEE ====
-
-z_sym, flip_pse_sym = z3.Ints("z_sym flip_pse_sym")
+n_sym, y_sym, = z3.Ints("n_sym y_sym")
 prob_sym = z3.Real("prob_sym")
 
 path1 = [
-    (flip_pse_sym <= 1),
-    (0 <= flip_pse_sym),
-    (prob_sym <= 1),
-    (0.000001 < prob_sym),
-    (0 <= z_sym),
-    flip_pse_sym == 0
+    (0.0075243180 < prob_sym),
+    (1 <= y_sym),
+    (prob_sym <= 0.0078125992),
+    (10 <= n_sym)
 ]
 
 path2 = [
-    (flip_pse_sym <= 1),
-    (0 <= flip_pse_sym),
-    (prob_sym <= 1),
-    (0.000001 < prob_sym),
-    (0 <= z_sym),
-    z3.Not(flip_pse_sym == 0)
+    (0.0075243180 < prob_sym),
+    (1 <= y_sym),
+    (prob_sym <= 0.0078125992),
+    n_sym == 0
 ]
 
-paths = [path1]
+
+paths = [path1, path2]
+
 
 # ==== Will be Autogenerated by PyKLEE ====
 
+
 pwd = os.path.dirname(__file__)
+if not os.path.isdir("inputs"):
+    os.mkdir("inputs")
+
 inputFilePath = os.path.join(pwd, "inputs")
 
 
@@ -47,7 +48,7 @@ def generateCandidates(k: int):
 
         print(f"Path {index + 1} : {path}")
         optpath = z3.Optimize()
-        optpath.set("timeout", 10000)
+        optpath.set("timeout", 5000)
 
         # This will get automated later to parse query
         # and retrieve directly from ProbQueryObject
@@ -57,19 +58,20 @@ def generateCandidates(k: int):
         for conds in path:
             optpath.add(conds)
 
-        # COMMENT : Need to frame this optimization properly
-        optpath.add(z_sym * prob_sym - (1 - prob_sym) <= 0)
-        optpath.maximize(prob_sym)
+        # COMMENT : Need to frame this optimization properly. How to automate it?
[…]

### 2021-04-29 estimate_example5/executeCV.py

@@ -12,6 +12,8 @@ executable = os.path.join(pwd, os.pardir, "bin/example5")
 codeFile = os.path.join(pwd, os.pardir, "example5_mod.cpp")
 
 inputFilePath = os.path.join(pwd, sys.argv[1])
+if not os.path.isdir("outputs"):
+    os.mkdir("outputs")
 outputFilePath = os.path.join(pwd, "outputs")
 
 
@@ -80,19 +82,27 @@ if __name__ == "__main__":
             if "err" not in outputFile:
                 with open(os.path.join(outputFilePath, outputFile), mode="r") as fileptr:
                     line = fileptr.readlines()
+
+                    # COMMENT : Output format -> P(expression) : value in first line.
                     assertQuery = line[0].strip().split(':')[0]
                     value = line[0].strip().split(':')[1]
                     sumtotal += float(value)
                     count += 1
+
+                    # COMMENT : What is the probability of the assert holding?
                     with open(os.path.join(pwd, "pathprobs.txt"), mode="a") as pathprobs:
                         pathprobs.write(
                             f'{assertQuery} : {value} : {line[-1].strip()}\n')
-                    if float(value) < 0.5:
-                        with open(os.path.join(pwd, "results.txt"), mode="a") as resultFile:
+
+                    # COMMENT : Print when the condition fails.
+                    # COMMENT : When does the assert fail? Mention that condition here.
+                    if float(value) >= 0.6:
+                        with open(os.path.join(pwd, "assert_failures.txt"), mode="a") as resultFile:
                             resultFile.write(
                                 f'Fail : {assertQuery} : {value} : {line[-1].strip()}\n')
             time.sleep(0.1)
             executeBar()
 
+    # COMMENT : Final probability across all paths
     prob = sumtotal/count
-    print(f'{assertQuery} : {prob}')
+    print(f'Combining all program paths : {assertQuery} : {prob}')

### 2021-04-29 estimate_example5/paths.py

@@ -1,24 +1,138 @@
 import z3
 
-z_sym, flip_pse_sym = z3.Ints("z_sym flip_pse_sym")
-prob_sym = z3.Real("prob_sym")
+n_sym, y_sym, prob_sym = z3.Ints("n_sym y_sym prob_sym")
 
 path1 = [
-    (flip_pse_sym <= 1),
-    (0 <= flip_pse_sym),
+    (0 <= prob_sym),
+    (0 <= y_sym),
     (prob_sym <= 1),
-    (0 < prob_sym),
-    (0 <= z_sym),
-    flip_pse_sym == 0
+    (1 <= n_sym)
 ]
 
 path2 = [
-    (flip_pse_sym <= 1),
-    (0 <= flip_pse_sym),
+    (0 <= prob_sym),
+    (0 <= y_sym),
     (prob_sym <= 1),
-    (0 < prob_sym),
-    (0 <= z_sym),
-    z3.Not(flip_pse_sym == 0)
+    z3.Not((1 <= n_sym)),
+    z3.Not((0 < (n_sym + 4294967295)))
 ]
 
-paths = [path1, path2]
+path3 = [
+    (0 <= prob_sym),
+    (0 <= y_sym),
+    (prob_sym <= 1),
+    z3.Not((1 <= n_sym)),
+    (0 < (n_sym + 4294967295)),
+    z3.Not((0 < (n_sym + 4294967294)))
+]
+
+path4 = [
+    (0 <= prob_sym),
+    (0 <= y_sym),
+    (prob_sym <= 1),
+    z3.Not((1 <= n_sym)),
+    (0 < (n_sym + 4294967295)),
+    (0 < (n_sym + 4294967294)),
+    z3.Not((0 < (n_sym + 4294967293)))
+]
+
+path5 = [
+    (0 <= prob_sym),
+    (0 <= y_sym),
+    (prob_sym <= 1),
+    z3.Not((1 <= n_sym)),
+    (0 < (n_sym + 4294967295)),
+    (0 < (n_sym + 4294967294)),
+    (0 < (n_sym + 4294967293)),
+    z3.Not((0 < (n_sym + 4294967292)))
+]
+
+path6 = [
+    (0 <= prob_sym),
+    (0 <= y_sym),
+    (prob_sym <= 1),
+    z3.Not((1 <= n_sym)),
+    (0 < (n_sym + 4294967295)),
+    (0 < (n_sym + 4294967294)),
+    (0 < (n_sym + 4294967293)),
[…]

### 2021-04-29 estimate_montyhall/candidates.py

@@ -1,321 +1,0 @@
-# -*- coding: utf-8 -*-
-
-import z3
-import os
-
-"""
-Below are a list of constraints that dictate which 
-path is taken during actual program execution. 
-We process KLEE constraints and simplify them to get these 
-constraints. 
-"""
-
-# ==== Will be Autogenerated by PyKLEE ====
-car_door_pse_sym, door_switch_pse_sym, choice_pse_sym = z3.Ints(
-    "car_door_pse_sym door_switch_pse_sym choice_pse_sym")
-
-path1 = [
-    (0 <= door_switch_pse_sym),
-    (door_switch_pse_sym <= 1),
-    (0 <= choice_pse_sym),
-    (choice_pse_sym <= 3),
-    (0 <= car_door_pse_sym),
-    (car_door_pse_sym <= 3),
-    z3.Not(z3.And(z3.Not(car_door_pse_sym == 1), z3.Not(choice_pse_sym == 1))),
-    z3.Not(z3.And(z3.Not(car_door_pse_sym == 2), z3.Not(choice_pse_sym == 2))),
-    z3.Not(z3.Not(door_switch_pse_sym == 0))
-]
-
-path2 = [
-    (0 <= door_switch_pse_sym),
-    (door_switch_pse_sym <= 1),
-    (0 <= choice_pse_sym),
-    (choice_pse_sym <= 3),
-    (0 <= car_door_pse_sym),
-    (car_door_pse_sym <= 3),
-    z3.Not(z3.And(z3.Not(car_door_pse_sym == 1), z3.Not(choice_pse_sym == 1))),
-    z3.And(z3.Not(car_door_pse_sym == 2), z3.Not(choice_pse_sym == 2)),
-    z3.Not(door_switch_pse_sym == 0),
-    z3.Not(choice_pse_sym == 1)
-]
-
-path3 = [
-    (0 <= door_switch_pse_sym),
-    (door_switch_pse_sym <= 1),
-    (0 <= choice_pse_sym),
-    (choice_pse_sym <= 3),
-    (0 <= car_door_pse_sym),
-    (car_door_pse_sym <= 3),
-    z3.Not(z3.And(z3.Not(car_door_pse_sym == 1), z3.Not(choice_pse_sym == 1))),
-    z3.Not(z3.And(z3.Not(car_door_pse_sym == 2), z3.Not(choice_pse_sym == 2))),
-    z3.Not(door_switch_pse_sym == 0),
[…]

### 2021-04-29 estimate_montyhall/executeCV.py

@@ -1,98 +1,0 @@
-import os
-import sys
-import threading
-import logging
-import time
-from alive_progress import alive_bar
-from subprocess import run, CalledProcessError
-
-pwd = os.path.dirname(__file__)
-
-executable = os.path.join(pwd, os.pardir, "bin/montyhall")
-codeFile = os.path.join(pwd, os.pardir, "montyhall_mod.cpp")
-
-inputFilePath = os.path.join(pwd, sys.argv[1])
-outputFilePath = os.path.join(pwd, "outputs")
-
-
-def build():
-    try:
-        # print(f"Building Binary Example {example}.c")
-        output = run(
-            f"g++ {codeFile} -o {executable}",
-            shell=True,
-            capture_output=True,
-            text=True,
-        )
-    except CalledProcessError as err:
-        print(f"Build Error : {err}")
-    else:
-        print(f"Return : {output.returncode}")
-    return output.returncode
-
-
-def executeCV(executable, inFile, outfile, errFile):
-    try:
-        # print(f"Running Binary Example {example}.c")
-        output = run(
-            f"{executable} < {inFile} > {outfile} 2> {errFile}",
-            shell=True,
-            capture_output=True,
-            text=True,
-        )
-    except CalledProcessError as err:
-        print(f"Execute Error : {err}")
-    else:
-        pass
-    return output.returncode
-
-
-logging.basicConfig(level=logging.DEBUG)
-
-if __name__ == "__main__":
-    build()
-    executeThreads = []
-    with alive_bar(len(os.listdir(inputFilePath))) as executeBar:
-        for index, inputFile in enumerate(os.listdir(inputFilePath)):
-            worker_thread = threading.Thread(
-                target=executeCV,
-                args=(
-                    executable,
-                    os.path.join(inputFilePath, inputFile),
-                    os.path.join(outputFilePath, f"output_{index}.txt"),
-                    os.path.join(outputFilePath, f"output_err_{index}.txt"),
-                ),
-            )
-            executeThreads.append(worker_thread)
-            worker_thread.start()
-            time.sleep(0.2)
-            executeBar()
-
-    for index, worker in enumerate(executeThreads):
-        worker.join()
-
-    num_outs = len(os.listdir(outputFilePath))
-    sumtotal = 0.0
-    count = 0
-
-    with alive_bar(num_outs) as executeBar:
-        for index, outputFile in enumerate(os.listdir(outputFilePath)):
-            if "err" not in outputFile:
[…]

### 2021-04-29 estimate_montyhall/genCandidateM.py

@@ -1,25 +1,0 @@
-# -*- coding: utf-8 -*-
-
-import os
-import random
-
-pwd = os.path.dirname(__file__)
-inputFilePath = os.path.join(pwd, "foralls")
-sampleList = [0, 1]
-
-for i in range(21):
-    randomList = random.choices(
-        sampleList, weights=(50 + 2 * i, 50 - 2 * i), k=1000001)
-
-    with open(os.path.join(inputFilePath, f"model_monty_less_{i}.txt"), mode="w") as fileptr:
-        for i in randomList:
-            fileptr.write(f"{i}\n")
-
-
-for i in range(21):
-    randomList = random.choices(
-        sampleList, weights=(50 - 2 * i, 50 + 2 * i), k=1000001)
-
-    with open(os.path.join(inputFilePath, f"model_monty_more_{i}.txt"), mode="w") as fileptr:
-        for i in randomList:
-            fileptr.write(f"{i}\n")

### 2021-04-29 estimate_montyhall/paths.py

@@ -1,187 +1,0 @@
-import z3
-
-choice_pse_sym, door_switch_pse_sym, car_door_pse_sym = z3.Ints("choice_pse_sym door_switch_pse_sym car_door_pse_sym")
-
-path1 = [
-(0 <= door_switch_pse_sym),
-(door_switch_pse_sym <= 1),
-(0 <= choice_pse_sym),
-(choice_pse_sym <= 3),
-(0 <= car_door_pse_sym),
-(car_door_pse_sym <= 3),
-z3.Not(z3.And(z3.Not(car_door_pse_sym == 1), z3.Not(choice_pse_sym == 1))),
-z3.Not(z3.And(z3.Not(car_door_pse_sym == 2), z3.Not(choice_pse_sym == 2))),
-z3.Not(z3.Not(door_switch_pse_sym == 0))
-]
-
-path2 = [
-(0 <= door_switch_pse_sym),
-(door_switch_pse_sym <= 1),
-(0 <= choice_pse_sym),
-(choice_pse_sym <= 3),
-(0 <= car_door_pse_sym),
-(car_door_pse_sym <= 3),
-z3.Not(z3.And(z3.Not(car_door_pse_sym == 1), z3.Not(choice_pse_sym == 1))),
-z3.And(z3.Not(car_door_pse_sym == 2), z3.Not(choice_pse_sym == 2)),
-z3.Not(door_switch_pse_sym == 0),
-z3.Not(choice_pse_sym == 1)
-]
-
-path3 = [
-(0 <= door_switch_pse_sym),
-(door_switch_pse_sym <= 1),
-(0 <= choice_pse_sym),
-(choice_pse_sym <= 3),
-(0 <= car_door_pse_sym),
-(car_door_pse_sym <= 3),
-z3.Not(z3.And(z3.Not(car_door_pse_sym == 1), z3.Not(choice_pse_sym == 1))),
-z3.Not(z3.And(z3.Not(car_door_pse_sym == 2), z3.Not(choice_pse_sym == 2))),
-z3.Not(door_switch_pse_sym == 0),
-choice_pse_sym == 1
-]
-
-path4 = [
-(0 <= door_switch_pse_sym),
-(door_switch_pse_sym <= 1),
-(0 <= choice_pse_sym),
-(choice_pse_sym <= 3),
-(0 <= car_door_pse_sym),
-(car_door_pse_sym <= 3),
[…]

### 2021-04-29 example5.cpp

@@ -8,34 +8,40 @@
 #include <vector>
 #include "PSE.h"
 
-int unroll = 10000;
-
 int main()
 {
-    double prob = 0.6;
-    int d, z = 0, flip = 0;
+    double prob = 0.5;
+    int x, n, y;
 
-    make_pse_symbolic(&flip, sizeof(flip), "flip_pse_sym", 0, 1);
+    // forall variables
+    klee_make_symbolic(&y, sizeof(y), "y_sym");
+    klee_make_symbolic(&n, sizeof(n), "n_sym");
     make_pse_symbolic(&prob, sizeof(prob), "prob_sym", 0, 1);
-    klee_make_symbolic(&z, sizeof(z), "z_sym");
-    klee_assume(z >= 0);
+    klee_assume(y >= 0);
+    klee_assume(1 <= n && n <= 10);
 
-    std::random_device rd{};
-    std::mt19937 rng{rd()};
-    std::bernoulli_distribution rvs(prob);
+    // Work around for silent concretization of prob.
+    prob = 0.5;
 
-    while (flip == 0)
+    // Prob Sym Variables.
+    make_pse_symbolic(&x, sizeof(x), "x_pse_sym", 0, 2147483647);
+
+    std::default_random_engine generator;
+    std::bernoulli_distribution bernoulli_rvs(prob);
+
+    while (n > 0)
     {
-        int d = rvs(rng);
+        int d = bernoulli_rvs(generator);
         if (d)
-        {
-            flip = 1;
-        }
-        else
-        {
-            z += 1;
-        }
+            x = x + y;
+        n = n - 1;
     }
-
     return 0;
 }
+
+/**
+ * assert(Prob(x - prob * n * y <= 0) <= 0.6)
+ * E(x) <= prob * n * y 
+ * prob, n & y are foralls
+ * x is not a forall. 
+*/

### 2021-04-29 example5_mod.cpp

@@ -8,54 +8,63 @@
 #include <vector>
 #include "PSE.h"
 
-int unroll = 2500;
-long long int termCount = 50000;
+// int unroll = 2500;
+long long int termCount = 100000;
 
 int main()
 {
-    long double prob = 0.00000000001;
-    int d, flip = 0, win = 0;
-    long long unsigned int z = 0, run = 0, prob_runs = 0;
+    long double prob = 0.500;
+    int x = 0, n = 10, y = 10, n_start, y_start;
+    long long unsigned int win = 0, loop_run = 0, prob_runs = 0;
+
+    scanf("%d", &n);
+    scanf("%d", &y);
+    scanf("%Lf", &prob);
+
+    n_start = n;
+    y_start = y;
 
     while (termCount--)
     {
-        flip = 0;
-        z = 0;
-        scanf("%Lf", &prob);
+        x = 0;
+        int n_loop = n;
 
-        std::random_device rd{};
-        std::mt19937 rng{rd()};
+        // program execution
+        std::default_random_engine generator;
+        std::bernoulli_distribution bernoulli_rvs(prob);
 
-        std::bernoulli_distribution rvs(prob);
-
-        // fprintf(stderr, "prob : %Lf\n", prob);
-        while (flip == 0 && unroll--)
+        while (n_loop > 0)
         {
-            int d = rvs(rng);
+            int d = bernoulli_rvs(generator);
             if (d)
             {
-                flip = 1;
+                // This doesn't favours the "win" condition.
+                x = x + y;
             }
-            else
-            {
-                z += 1;
-            }
-            if (z > ((double)(1 - prob) / (prob)))
-                win++;
-            run++;
+            n_loop -= 1;
+
+            // Iterations of the loop.
+            prob_runs++;
         }
-        prob_runs++;
+
+        // Sample for probability. This is the assert condition.
+        if ((double)x - (prob * n * y) <= 0)
+            win++;
+
+        // No. of times the program gets executed.
+        loop_run++;
     }
 
-    auto pwin = (double)win / run;
-    // printf("P(z > (1-p)/p) : %f\nRuns : %d\n", pwin, run);
-    // fprintf(stdout, "prob(p) : %Lf\n", prob);
[…]

### 2021-04-29 run.sh

@@ -1,6 +1,6 @@
 clang++ -I $HOME/klee/include -c -emit-llvm -std=c++17 -g -O0 -Xclang -disable-O0-optnone $1.cpp
 
-klee --write-kqueries --set-ptree-dump $1.bc --set-ptree-dump
+klee --search=random-state --search=nurs:md2u --write-kqueries $1.bc --set-ptree-dump 
 ktest-tool klee-last/test000001.ktest
 
 g++ -std=c++14 -march=native -I $HOME/klee/include/ -L $HOME/klee/lib/ $1.cpp -lkleeRuntest

### 2021-04-29 run_foralls.sh

@@ -9,3 +9,10 @@ rm -rf $1/results.txt
 
 python3 $1/candidates.py  
 python3 $1/executeCV.py foralls
+
+# python3 estimate_example5/candidates.py 15
+# python3 estimate_example5/executeCV.py inputs
+# cd estimate_example5/outputs/
+# cat *txt | sort 
+# cd ../../
+# python3 postprocess/z3write.py example5_processed/example5_paths.json > estimate_example5/paths.py

### 2021-04-29 testing/paths.py

@@ -1,0 +1,67 @@
+import z3
+
+d_sym, c_sym, a_sym, b_prob_sym, e_prob_sym = z3.Ints(
+    "d_sym c_sym a_sym b_prob_sym e_prob_sym")
+
+path1 = [
+    (0 <= b_prob_sym),
+    (b_prob_sym <= 1),
+    (1 <= e_prob_sym),
+    (e_prob_sym <= 6),
+    (0 <= a_sym),
+    (a_sym <= 1),
+    (1 <= c_sym),
+    (c_sym <= 10),
+    (0 <= d_sym),
+    (d_sym <= 5),
+    (b_prob_sym < a_sym),
+    ((e_prob_sym + c_sym) < 15)
+]
+
+path2 = [
+    (0 <= b_prob_sym),
+    (b_prob_sym <= 1),
+    (1 <= e_prob_sym),
+    (e_prob_sym <= 6),
+    (0 <= a_sym),
+    (a_sym <= 1),
+    (1 <= c_sym),
+    (c_sym <= 10),
+    (0 <= d_sym),
+    (d_sym <= 5),
+    (b_prob_sym < a_sym),
+    z3.Not(((e_prob_sym + c_sym) < 15))
+]
+
+path3 = [
+    (0 <= b_prob_sym),
+    (b_prob_sym <= 1),
+    (1 <= e_prob_sym),
+    (e_prob_sym <= 6),
+    (0 <= a_sym),
+    (a_sym <= 1),
+    (1 <= c_sym),
+    (c_sym <= 10),
+    (0 <= d_sym),
+    (d_sym <= 5),
+    z3.Not((b_prob_sym < a_sym)),
+    (1 < (e_prob_sym + d_sym))
+]
+
+path4 = [
+    (0 <= b_prob_sym),
+    (b_prob_sym <= 1),
+    (1 <= e_prob_sym),
+    (e_prob_sym <= 6),
+    (0 <= a_sym),
+    (a_sym <= 1),
+    (1 <= c_sym),
+    (c_sym <= 10),
+    (0 <= d_sym),
+    (d_sym <= 5),
+    z3.Not((b_prob_sym < a_sym)),
+    z3.Not((1 < (e_prob_sym + d_sym)))
+]
+
+
+paths = [path1, path2, path3, path4]

### 2021-05-09 shared/analysis.tex

--- 2021-04-27 shared/analysis.tex
@@
 		\begin{minted}{python}
-	def progam1(inpt):
-		prob, _ = inpt
-		z = 0
-		flip = 0
-		while (flip == 0):
-			d = bernoulli.rvs(size=1, p=prob)[0]
-			if d:
-				flip = 1
-			else:
-				z = z + 1
-		return z
 
-	assert(z > (1 - prob)/prob)
+	double prob, path_prob = 1, choice_prob = 1;
+	int sum = 0;
+
+	klee_make_symbolic(&prob, f"prob_sym_{i}");
+	for i in range(10):
+		int d;
+		klee_make_symbolic(&d, f"d_sym_{i}");
+
+		d = bernoulli(prob);
+		(d == 1) ? choice_prob = prob : choice_prob = (1 - prob);
+		path_prob = path_prob * choice_prob;
+
+		sum = sum + d;
+
+	klee_dump(path_prob)
+	klee_dump(sum) // E[heads in "n" runs] 
 		\end{minted}
-		\caption{Program listing for finding probabilistic \texttt{assert} violation.}
+		\caption{Program listing for $n$ bernoulli trails experiment.}
 	\end{figure}
+
+We consider a independent $bernoulli$ trials here of flipping a fair coin "$n$" times. 
+\[ 
+{choice\_prob} = 
+\begin{cases} 
+	p & \textrm{if $d$ value is 1 corresponding to getting a "heads"} \\
+	1-p & \textrm{if $d$ value is 0 corresponding to getting a "tails"}
+\end{cases}
+\]
+
+for example, on the $i^{th}$ run \texttt{$\vec{d}$} can have a value.
+\[
+\vec{d}_{i} = encode(<0,0,0,1,1,0,1,1,1,0>)
+\]
+
+Based on the value of the $\vec{d}_{i}$, we get $w_{i}$ value using $choice\_prob$. 
+\begin{equation}
+	w_{i} = {(p)^{x_i} * (1-p)^{n-x_i}}
+\end{equation}
+where $x_i$ denotes the number of $heads$ in the $i^{th}$ randomized run and for $n$ runs. \texttt{n = 10} for the case in the above example. \\
+
+We consider top "$k$" randomized runs now for the optimization query. The expression for \texttt{optimization} thus becomes 
+\[	
+	maximize(\sum_{i=1}^{k}{w_i})
+\]
+On substituting the value of $w_i$ from (1).
+\begin{equation}	
+	maximize(\sum_{i=1}^{k}{(p)^{x_i} * (1-p)^{n-x_i}})
+\end{equation}
+
 \begin{figure}
-		\begin{minted}{c}
-	int main()
-	{
-		double prob;
-		int d, z = 0, flip = 0;
+	\begin{equation}	
+		Objective = maximize(\sum_{i=1}^{k}{(p)^{x_i} * (1-p)^{n-x_i}}) \mid \forall (i, j) [{x_i} \neq {x_j}]
+	\end{equation}
+	\caption{Optimization Expression for $k$ randomized paths}
+	\label{eq:optimization-1}
+\end{figure}
 
-		make_pse_symbolic(&flip, sizeof(flip), "flip_pse_sym", 0, 1);
-		make_pse_symbolic(&prob, sizeof(prob), "prob_sym", 0, 1);
-		klee_make_symbolic(&z, sizeof(z), "z_sym");
-		klee_assume(z >= 0);
+After performing the optimization above, we get different values of $\vec{d_i}$.
+For $i^{th}$ randomized run.
+we get a \texttt{single} one hot encoded \texttt{$\vec{d}$} vector.
+We show below the encoding for a few $i$ values.
+\[
+\vec{d}_{1} = encode(<0,0,0,1,1,0,1,1,1,0>)
+\]
+\[
+\vec{d}_{3} = encode(<0,1,0,1,1,0,0,0,1,0>)
+\]
+\[
+\vec{d}_{4} = encode(<1,0,1,0,1,0,1,1,0,1>)
+\]
+\[
+...
+\]
 
-		std::random_device rd{};
-		std::mt19937 rng{rd()};
-		std::bernoulli_distribution rvs(prob);
+We run the optimization by renaming the $k$ \texttt{pse} variables set appropriately and then impose the $distinct$ clause so that we don't run the optimization on the same $randomized$ runs again. \\
 
-		while (flip == 0) {
-			int d = rvs(rng);
-			if (d) {
-				flip = 1;
-			} else {
-				// must be executed more 
-				// for the assert to pass. 
-				z += 1; 
-			}
-		}
+For best approximation of the expected value of heads in $n$ trials,
+\begin{equation}	
+	EV(heads) = (\sum_{i=1}^{k}{w_i * sum_i})
+\end{equation}
+where both $w_i$ and $sum_i$ can both be computed from the corresponding $\vec{d_i}$ expression we get from the $model$  of the $optimization$ query Eq~\ref{eq:optimization-1}
 
-		return 0;
-	}
-		\end{minted}
-		\caption{\texttt{Translate()} of the program for testing the \texttt{assert}. }
-	\end{figure}
-	\begin{figure}
-		\begin{minted}{c}
-		long long int termCount = 50000, unroll = 2500;
-		while (termCount--)
-		{
-			flip = 0;
-			z = 0;
-			scanf("%Lf", &prob);
-
-			...
-
-			while (flip == 0 && unroll--) {
-				int d = rvs(rng);
-				if (d) {
-					flip = 1;
-				} else { 
-					z += 1; 
-				}
-				if (z > ((double)(1 - prob) / (prob)))
-					win++;
-				flip_runs++;
-			}
-			program_runs++;
-		}
-		\end{minted}
-		\caption{\texttt{Translate()} of the program for testing the \texttt{assert}. }
-	\end{figure}
-	\begin{figure}
-			\begin{minted}{python}
-		(flip_pse_sym <= 1),
-		(0 <= flip_pse_sym),
-		(prob_sym <= 1),
-		(0.000001 < prob_sym),
-		(0 <= z_sym),
-
-		FAIL : (z_sym * prob_sym - (1 - prob_sym) <= 0)
-		\end{minted}
-		\caption{Constraints without optimization step.}
-	\end{figure}
-	\begin{figure}
-		\begin{minted}{python}
-		(flip_pse_sym <= 1),
-		(0 <= flip_pse_sym),
-		(prob_sym <= 1),
-		(0.000001 < prob_sym),
-		(0 <= z_sym),
-
-		FAIL : (z_sym * prob_sym - (1 - prob_sym) <= 0)
-		optimize : maximize(prob_sym)
-		\end{minted}
-		\caption{Constraints with optimization step.}
-	\end{figure}
-	\begin{table}
-		\centering
-		\caption{Comparing \texttt{prob(p)} value to cases Vs \texttt{assert} status for \texttt{optimization} over \texttt{prob} value}
-		\label{}
-		\begin{tabular}{ c | c | c | c | c } 
-			\toprule
-			\texttt{Flip Runs} & \texttt{Program Runs}& \texttt{prob(p)} & \texttt{z (Last)} & \texttt{(1-p)/p} \\ 
-			\hline\hline
-			49999 & 50000 & 0.9999990463 & 0 & 0.0000009537 \\ \hline 
-			49999 & 50000 & 0.9999995232 & 0 & 0.0000004768 \\ \hline 
-			49999 & 50000 & 0.9999998808 & 0 & 0.0000001192 \\ \hline 
-			49999 & 50000 & 0.9999999991 & 0 & 0.0000000009 \\ \hline 
-			49999 & 50000 & 1.0000000000 & 0 & 0.0000000000 \\ \hline 
-			50000 & 50000 & 0.9999847412 & 0 & 0.0000152590 \\ \hline 
-			50001 & 50000 & 0.9999694825 & 0 & 0.0000305184 \\ \hline 
-			50003 & 50000 & 0.9998779298 & 0 & 0.0001220851 \\ \hline 
-			50008 & 50000 & 0.9997558596 & 0 & 0.0002442000 \\ \hline 
-			50016 & 50000 & 0.9995117192 & 0 & 0.0004885193 \\ \hline 
-			50045 & 50000 & 0.9990234385 & 0 & 0.0009775161 \\ \hline 
-			50822 & 50000 & 0.9843750156 & 0 & 0.0158729998 \\ \hline 
-			53303 & 50000 & 0.9375000625 & 0 & 0.0666665956 \\ \hline 
-			57237 & 50000 & 0.8750001250 & 0 & 0.1428569796 \\ \hline 
-			99385 & 50000 & 0.5000005000 & 0 & 0.9999980000 \\ \hline 
-			\bottomrule
-		\end{tabular}
-	\end{table}
-	\begin{table}
-		\centering
-		\caption{Comparing \texttt{prob(p)} value to cases where assert \texttt{\color[HTML]{CB0000} failure} occurs for \texttt{no optimization} case}
-		\label{}
-		\begin{tabular}{ c | c | c | c | c } 
-			\toprule
-			\texttt{Flip Runs} & \texttt{Program Runs}& \texttt{prob(p)} & \texttt{z (Last)} & \texttt{(1-p)/p} \\ 
-			\hline\hline
-			49999 & 50000 & 1.0000000000 & 0 & 0.0000000000 \\ \hline 
-			12798121 & 50000 & 0.0039072461 & 121 & 254.9347362328 \\ \hline 
-			2118330 & 50000 & 0.0234384766 & 3 & 41.6648888947 \\ \hline 
-			3191133 & 50000 & 0.0156259844 & 27 & 62.9959681516 \\ \hline 
-			1592312 & 50000 & 0.0312509687 & 85 & 30.9990080819 \\ \hline 
-			802573 & 50000 & 0.0625009375 & 6 & 14.9997600036 \\ \hline  
-			404577 & 50000 & 0.1250008750 & 3 & 6.9999440004 \\ \hline 
-			199379 & 50000 & 0.2500007500 & 2 & 2.9999880000 \\ \hline 
-			133424 & 50000 & 0.3750006250 & 1 & 1.6666622222 \\ \hline 
-			99661 & 50000 & 0.5000005000 & 0 & 0.9999980000 \\ \hline 
-			\bottomrule
-		\end{tabular}
-	\end{table}
-	\begin{table}
-		\centering
-		\caption{Comparing \texttt{prob(p)} value to cases where assert \texttt{\color[HTML]{036400} passed} without \texttt{optimization} step.}
-		\label{}
-		\begin{tabular}{ c | c | c | c | c } 
-			\toprule
-			\texttt{Flip Runs} & \texttt{Program Runs}& \texttt{prob(p)} & \texttt{z (Last)} & \texttt{(1-p)/p} \\ 
-			\hline\hline
-			2551264 & 50000 & 0.0195322305 & 60 & 50.1974298071 \\ \hline 
-			6371788 & 50000 & 0.0078134922 & 169 & 126.9837458595 \\ \hline 
-			4280156 & 50000 & 0.0117197383 & 303 & 84.3261373592 \\ \hline 
-			1592312 & 50000 & 0.0312509687 & 85 & 30.9990080819 \\ \hline
-			266112 & 50000 & 0.1875008125 & 7 & 4.3333102223 \\ \hline 
-			\bottomrule
-		\end{tabular}
-	\end{table}
 \end{document}

### 2021-05-10 shared/analysis.tex
WIP : Optimization Query

@@
 
-for example, on the $i^{th}$ run \texttt{$\vec{d}$} can have a value.
+concretely, on the $i^{th}$ run \texttt{$\vec{d}$} can have a value as below, \texttt{one-hot} encoded $w.r.t$ the outcome of $heads$ or $tails$.
 \[
@@
 where $x_i$ denotes the number of $heads$ in the $i^{th}$ randomized run and for $n$ runs. \texttt{n = 10} for the case in the above example. \\
-
+\begin{equation}
+	w_{i} = {(p)^{x_i} * (1-p)^{10-x_i}}
+\end{equation}
 We consider top "$k$" randomized runs now for the optimization query. The expression for \texttt{optimization} thus becomes 
@@
 
+\section{Expression for $k$-paths}
+
+Specify the \texttt{renaming} and \texttt{constraint} solving over the \texttt{optimization} expression. Write out this algorithm formally. \\
+
+For $k = 5$, the five \texttt{constraint} sets and \texttt{optimization} expressions are : ...
 \end{document}

### 2021-05-10 estimate_newsampling/candidates.py

@@ -1,0 +1,140 @@
+# -*- coding: utf-8 -*-
+
+import z3
+import os
+import sys
+
+# https://z3prover.github.io/api/html/classz3py_1_1_rat_num_ref.html#a1012d6314d35530c58f9c018269ec867
+def num(r):
+    """
+    Convert from Z3 to python float values.
+    """
+    return float(r.numerator_as_long()) / float(r.denominator_as_long())
+
+
+def get_value(r):
+    """
+    Convert from Z3 to python values.
+    """
+    if z3.is_int_value(r):
+        return r.as_long()
+    elif z3.is_algebraic_value(r):
+        return round(num(r.approx(15)), 10)
+    elif z3.is_rational_value(r):
+        return r.as_decimal(20)
+    elif r is None:
+        None
+    else:
+        return num(r)
+
+
+"""
+Below are a list of constraints that dictate which 
+path is taken during actual program execution. 
+We process KLEE constraints and simplify them to get these 
+constraints. 
+"""
+
+# ==== Will be Autogenerated by PyKLEE ====
+
+# candidatePaths = 5  # Top "k" paths.
+# n_iters = 10  # "n" bernoulli trails (independent fair coin flips)
+
+# choice_sym_vars = [
+#     [z3.Real(f"choice_{i}_{k}") for i in range(n_iters)] for k in range(candidatePaths)
+# ]
+# d_sym_vars = [
+#     [z3.Real(f"d_{i}_{k}") for i in range(n_iters)] for k in range(candidatePaths)
+# ]
+# path_prob_sym_vars = [z3.Int(f"path_prob_{i}") for i in range(candidatePaths)]
+# probability_vars = [z3.Real(f"path_prob_{k}") for k in range(candidatePaths)]
+# expected_heads = [z3.Real(f"sum_d_heads_{k}") for k in range(candidatePaths)]
+
+# for k in range(candidatePaths):
+#     choice_probs = 1
+#     for i in range(n_iters):
+#         choice_sym_vars[k][i] = z3.If(
+#             d_sym_vars[k][i] == 1, probability_vars[k], 1 - probability_vars[k]
+#         )
+#         choice_probs = choice_probs * choice_sym_vars[k][i]
+#         sum_heads = sum_heads + d_sym_vars[k][i]
+#     path_prob_sym_vars[k] = choice_probs
+
+# ==== Will be Autogenerated by PyKLEE ====
+
+
+# pwd = os.path.dirname(__file__)
[…]

### 2021-05-11 shared/analysis.tex
WIP : Assert Violation

@@
 	\begin{equation}	
-		Objective = maximize(\sum_{i=1}^{k}{(p)^{x_i} * (1-p)^{n-x_i}}) \mid \forall (i, j) [{x_i} \neq {x_j}]
+		Objective = maximize(\sum_{i=1}^{k}{(p)^{x_i} * (1-p)^{n-x_i}}) \quad \mid \forall (i, j) [{x_i} \neq {x_j}]
 	\end{equation}
@@
 \begin{equation}	
-	EV(heads) = (\sum_{i=1}^{k}{w_i * sum_i})
+	w_i = \prod_{j=1}^n choice\_prob_{i}(j) ,
+	\quad
+	sum_i = \sum_{j=1}^n components(\vec{d_i}) ,
+\end{equation}
+\begin{equation}
+	EV(heads) = (\sum_{i=1}^{k}{w_i * sum_i}),
+	\quad
+	Error = n * prob - EV(heads)
 \end{equation}
@@
 
-Specify the \texttt{renaming} and \texttt{constraint} solving over the \texttt{optimization} expression. Write out this algorithm formally. \\
+For $k = 5$ \& $n = 10$ the two \texttt{constraint} sets and \texttt{optimization} expressions are as follows :
 
-For $k = 5$, the five \texttt{constraint} sets and \texttt{optimization} expressions are : ...
+\begin{equation}	
+	w_1 = \prod_{j=1}^{10} choice\_prob_{1}(j) ,
+	\quad
+	sum_1 = \sum_{j=1}^{10} components(\vec{d_1}) ,
+\end{equation}
+\begin{equation}	
+	w_2 = \prod_{j=1}^{10} choice\_prob_{2}(j) ,
+	\quad
+	sum_2 = \sum_{j=1}^{10} components(\vec{d_2}) ,
+\end{equation}
+\begin{equation}	
+	w_3 = \prod_{j=1}^{10} choice\_prob_{3}(j) ,
+	\quad
+	sum_3 = \sum_{j=1}^{10} components(\vec{d_3}) ,
+\end{equation}
+\begin{equation}	
+	w_4 = \prod_{j=1}^{10} choice\_prob_{4}(j) ,
+	\quad
+	sum_4 = \sum_{j=1}^{10} components(\vec{d_4}) ,
+\end{equation}
+\begin{equation}	
+	w_5 = \prod_{j=1}^{10} choice\_prob_{5}(j) ,
+	\quad
+	sum_5 = \sum_{j=1}^{10} components(\vec{d_5}) ,
+\end{equation}
+\begin{equation}
+	EV(heads) = (\sum_{i=1}^{k}{w_i * sum_i}),
+\end{equation}
+\begin{equation}
+	\enspace
+	EV(heads) = (w_1 * sum_1 \enspace + \enspace w_2 * sum_2 \enspace + \enspace w_3 * sum_3 \enspace + \enspace w_4 * sum_4 \enspace + \enspace w_5 * sum_5)
+\end{equation}
+\begin{equation}
+	\enspace
+	Objective = maximize(w_1 * sum_1 \enspace + \enspace w_2 * sum_2 \enspace + \enspace w_3 * sum_3 \enspace + \enspace w_4 * sum_4 \enspace + \enspace w_5 * sum_5)
+\end{equation}
 \end{document}

### 2021-05-11 estimate_newsampling/candidates.py

@@ -3,6 +3,9 @@
 import z3
 import os
 import sys
+import json
+import time
+from alive_progress import alive_bar
 from scipy.stats import bernoulli
 
 # https://z3prover.github.io/api/html/classz3py_1_1_rat_num_ref.html#a1012d6314d35530c58f9c018269ec867
@@ -14,10 +17,15 @@ def num(r):
 
 
 def get_value(r):
+    # https://stackoverflow.com/questions/12598408/z3-python-getting-python-values-from-model/12600208
     """
     Convert from Z3 to python values.
     """
-    if z3.is_int_value(r):
+    if z3.is_true(r):
+        return z3.is_true(r)
+    elif z3.is_false(r):
+        return z3.is_false(r)
+    elif z3.is_int_value(r):
         return r.as_long()
     elif z3.is_algebraic_value(r):
         return round(num(r.approx(15)), 10)
@@ -57,8 +65,10 @@ def generateCandidates(k: int, n: int, prob: float):
     candidatePaths = k  # Top "k" paths.
     n_iters = n  # "n" bernoulli trails (independent fair coin flips)
 
+    error_mass = z3.Real("error_mass_expectation")
     sum_of_k = z3.Real("sum_of_k")
     sigma_w_i = z3.Real("sigma_w_i")
+    assert_violated = z3.Bool("assert_violated")
 
     choice_sym_vars = [
         [z3.Real(f"choice_{k}_{i}") for i in range(n_iters)]
@@ -80,58 +90,65 @@ def generateCandidates(k: int, n: int, prob: float):
     # COMMENT : Supply the timeout in minute value.
     optpath.set("timeout", 60000 * int(sys.argv[4]))
 
-    # "k" models. One model for each randomized run.
-    for k in range(candidatePaths):
+    with alive_bar(candidatePaths) as executeBar:
 
-        # initalization
-        sum_heads = 0
-        path_prob = 1
-        expected_heads_run = 0
+        # "k" models. One model for each randomized run.
+        for k in range(candidatePaths):
 
-        # optpath.add(0.0001 <= probability_vars[k])
-        # optpath.add(probability_vars[k] < 1.0)
+            # initalization
+            sum_heads = 0
+            path_prob = 1
+            expected_heads_run = 0
 
-        # Prob value is now concrete, so we get a single number at the end.
-        optpath.add(probability_vars[k] == float(prob))
+            # optpath.add(0.0001 <= probability_vars[k])
[…]

### 2021-05-11 estimate_newsampling/gridRun.sh

@@ -1,0 +1,11 @@
+#!/usr/bin/bash
+
+for k in 5 10 20 40 80 100;
+do 
+    for prob in 0.0 0.1 0.15 0.2 0.25 0.3 0.35 0.4 0.45 0.5 0.55 0.6 0.65 0.7 0.75 0.8 0.85 0.9 0.95 1;
+    do
+        echo  "[Z3] Running for prob : ${prob}, k (sum-terms) : ${k} [Saving to models/prob_${prob}_dir/z3models_${k}_${prob}_n10.log]"
+        mkdir -p models/prob_${prob}_dir
+        python3 candidates.py $k 10 $prob 3 > models/prob_${prob}_dir/z3models_${k}_${prob}_n10.log
+    done
+done

### 2021-05-12 shared/analysis.tex
feat : Cases of Assert Violation

@@
 	double prob, path_prob = 1, choice_prob = 1;
-	int sum = 0;
+	int sum = 0, n = 0;
 
 	klee_make_symbolic(&prob, f"prob_sym_{i}");
-	for i in range(10):
+	klee_make_symbolic(&n, f"n_symbolic");
+	for i in range(n):
 		int d;
@@
 	\begin{equation}	
-		Objective = maximize(\sum_{i=1}^{k}{(p)^{x_i} * (1-p)^{n-x_i}}) \quad \mid \forall (i, j) [{x_i} \neq {x_j}]
+		Objective_1 = maximize(\sum_{i=1}^{k}{(p)^{x_i} * (1-p)^{n-x_i}}) \quad \mid \forall (i, j) \enspace [{x_i} \neq {x_j}]
 	\end{equation}
@@
 \[
-...
+	....
 \]
-
 We run the optimization by renaming the $k$ \texttt{pse} variables set appropriately and then impose the $distinct$ clause so that we don't run the optimization on the same $randomized$ runs again. \\
-
-For best approximation of the expected value of heads in $n$ trials,
+\begin{equation}	
+	\forall (i, j) \enspace [\vec{d_i} \neq \vec{d_j}]
+\end{equation} \\
+We approximate the value of $expected$ heads in the above program, with the following equations.
 \begin{equation}	
@@
 where both $w_i$ and $sum_i$ can both be computed from the corresponding $\vec{d_i}$ expression we get from the $model$  of the $optimization$ query Eq~\ref{eq:optimization-1}
-
-\section{Expression for $k$-paths}
 
@@
 \begin{equation}
+	\vec{d_1} \neq \vec{d_2} \neq \vec{d_3} \neq \vec{d_4} \neq \vec{d_5}
+\end{equation}
+\begin{equation}
 	EV(heads) = (\sum_{i=1}^{k}{w_i * sum_i}),
@@
 	\enspace
-	Objective = maximize(w_1 * sum_1 \enspace + \enspace w_2 * sum_2 \enspace + \enspace w_3 * sum_3 \enspace + \enspace w_4 * sum_4 \enspace + \enspace w_5 * sum_5)
+	Objective_2 = maximize(w_1 * sum_1 \enspace + \enspace w_2 * sum_2 \enspace + \enspace w_3 * sum_3 \enspace + \enspace w_4 * sum_4 \enspace + \enspace w_5 * sum_5)
 \end{equation}
+Statistically, maximizing $Objective_1$ must also maximize $Objective_2$ and thus we make the query $maximize(\sum_{i=1}^{k}{w_i})$ to the optimizing solver finally.
 \end{document}

### 2021-05-12 estimate_newsampling/gridRun.sh

@@ -1,15 +1,15 @@
 #!/usr/bin/bash
 
 timeout=$1
-for n in 8 9 10 11;
+for n in 5 6 7 8;
 do 
-    for prob in 0.435 0.455 0.515 0.565 0.606 0.616 0.666;
+    for prob in 0.10 0.20 0.25 0.30 0.35 0.40 0.45 0.50 0.55 0.60 0.65 0.70 0.75 0.80 0.85 0.90 0.95;
     do
-        for k in 250 500 1000 2000;
+        for k in 8 16 32 64 128 256;
         do
             echo  "[Z3] Running for prob : ${prob}, n-flips : ${n}, k (sum-terms) : ${k} [Saving to models/prob_${prob}_${n}_dir/z3models_${k}_${prob}_${n}.json]"
             mkdir -p models/prob_${prob}_${n}_dir
-            python3 candidates.py $k $n $prob $timeout models/prob_${prob}_${n}_dir/z3models_${k}_${prob}_${n}.json
+            timeout ${timeout}m python3 candidates.py $k $n $prob $timeout models/prob_${prob}_${n}_dir/z3models_${k}_${prob}_${n}.json
         done
     done
 done

### 2021-05-12 shared/analysis.tex
WIP : Pdf

@@
 \usepackage{graphicx}
+\usepackage{graphicx}
 \usepackage{booktabs}
@@
 \begin{document}
+	\begin{figure}
+		\begin{minted}{python}
+		def count_heads(prob : float, n : int):
+			x = 0
+			while(n > 0):
+				d = bernoulli.rvs(size=1, p=prob)[0]
+				x = x + d
+				n = n - 1
+			return x
+		\end{minted}
+	\caption{Program to $count$ heads over $n$ bernoulli trials.}
+	\end{figure}
+	\begin{figure}
+		\begin{minted}{python}
+		if (prob <= 0.5) E(x) < 0.4 * n else E(x) >= 0.6 * n
+		\end{minted}
+	\caption{\texttt{Assert} we want to check for failure.}
+	\end{figure}
 	\begin{figure}
@@
 		\end{minted}
-		\caption{Program listing for $n$ bernoulli trails experiment.}
+		\caption{Program listing for $n$ bernoulli trails experiment with transformation for \texttt{KLEE}.}
 	\end{figure}
@@
 Statistically, maximizing $Objective_1$ must also maximize $Objective_2$ and thus we make the query $maximize(\sum_{i=1}^{k}{w_i})$ to the optimizing solver finally.
+
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.15]{abstract.pdf}
+	\caption{Multiple $random$ paths corresponding to different $\vec{d}$'s but a single $abstract$ path.}
+\end{figure}
+
+\begin{figure}
+	\begin{minted}{python}
+	prob = 0.435, n = 8 (8 coin flips), k = 240 (randomized paths)
+	prob = 0.551, n = 5 (5 coin flips), k = 27 (randomized paths) 
+	\end{minted}
+	\caption{Values for \texttt{Assert} failure.}
+\end{figure}
 \end{document}

### 2021-05-13 shared/analysis.tex
WIP : Optimization

@@
 \end{equation}
-Statistically, maximizing $Objective_1$ must also maximize $Objective_2$ and thus we make the query $maximize(\sum_{i=1}^{k}{w_i})$ to the optimizing solver finally.
+We can make multiple optimization $objectives$ be fulfilled in one query, but the best results are produced for the $Objective_2$ since it minimizes the $error$ most.
+
+\begin{equation}
+	Obj_{1} = maximize(\sum_{i=1}^{k}{w_i * x _i}) \quad \mid \quad
+	Obj_{2} = minimize(n * prob - \sum_{i=1}^{k}{w_i * x_i})
+\end{equation}
 
@@
 	\centering
-	\includegraphics[scale=0.15]{abstract.pdf}
+	\includegraphics[scale=0.16]{abstract.pdf}
 	\caption{Multiple $random$ paths corresponding to different $\vec{d}$'s but a single $abstract$ path.}
@@
 \end{figure}
+
 \end{document}

### 2021-05-13 estimate_newsampling/candidates.py

@@ -95,6 +95,9 @@ def generateCandidates(k: int, n: int, prob: float):
 
     optpath.add(probability_factor == float(prob))
 
+    # COMMENT : General Case where the we are finding an optimal prob.
+    # optpath.add(z3.And(probability_factor <= 1, probability_factor > 0))
+
     with alive_bar(candidatePaths) as executeBar:
 
         # "k" models. One model for each randomized run.
@@ -105,9 +108,6 @@ def generateCandidates(k: int, n: int, prob: float):
             path_prob = 1
             expected_heads_run = 0
 
-            # optpath.add(0.0001 <= probability_vars[k])
-            # optpath.add(probability_vars[k] < 1.0)
-
             # Prob value is now concrete, so we get a single number at the end.
             optpath.add(probability_vars[k] == probability_factor)
 
@@ -116,11 +116,6 @@ def generateCandidates(k: int, n: int, prob: float):
 
                 optpath.add(0 <= d_sym_vars[k][i])
                 optpath.add(d_sym_vars[k][i] <= 1)
-
-                # COMMENT : Value of "d" must come from a distribution?
-                # optpath.add(
-                #     d_sym_vars[k][i] == int(bernoulli.rvs(size=1, p=float(prob))[0])
-                # )
 
                 # Choice Prob ITE.
                 optpath.add(
@@ -161,7 +156,7 @@ def generateCandidates(k: int, n: int, prob: float):
 
     # Sigma(w(i)) value
     optpath.add(sigma_w_i == z3.Sum(path_prob_sym_vars))
-    # optpath.add(z3.And(sigma_w_i >= 0, sigma_w_i <= n_iters * prob))
+    # optpath.add(z3.And(sigma_w_i >= 0, sigma_w_i <= 1))
 
     optpath.add(error_mass == (n_iters * prob - sum_of_k))
 
@@ -208,10 +203,10 @@ def generateCandidates(k: int, n: int, prob: float):
 
     optpath.maximize(sigma_w_i)
     # optpath.maximize(sum_of_k)
-    # optpath.minimize(error_mass)
 
-    # for k in range(candidatePaths):
-    #     optpath.maximize(path_prob_sym_vars[k])
+    # COMMENT : This is not be done in general case.
+    # Only for this example it works.
+    # optpath.minimize(error_mass)
 
     # print(optpath.assertions())
     print(optpath.check())
[…]

### 2021-05-13 estimate_newsampling/gridRun.sh

@@ -1,15 +1,15 @@
 #!/usr/bin/bash
 
-timeout=$1
+timeoutf=3
 for n in 10;
 do 
-    for prob in 0.10 0.20 0.80 0.70 0.90;
+    for prob in 0.10 0.20 0.30 0.80 0.70 0.90 0.95;
     do
         for k in 8 16 32 64 128 256;
         do
             echo  "[Z3] Running for prob : ${prob}, n-flips : ${n}, k (sum-terms) : ${k} [Saving to models/prob_${prob}_${n}_dir/z3models_${k}_${prob}_${n}.json]"
             mkdir -p models/prob_${prob}_${n}_dir
-            python3 candidates.py $k $n $prob $timeout models/prob_${prob}_${n}_dir/z3models_${k}_${prob}_${n}.json
+            python3 candidates.py $k $n $prob $timeoutf models/prob_${prob}_${n}_dir/z3models_${k}_${prob}_${n}.json
         done
     done
 done

### 2021-05-13 estimate_newsampling/heatmap.py

@@ -3,15 +3,15 @@ import seaborn as sn
 import matplotlib.pyplot as plt
 
 data = [
-    [1, 0.72, 0.66, 0.65, 0.64, 0.0, 0.0, 0.0],
-    [2, 1.81, 1.85, 1.55, 0.0, 0.0, 0.0, 0.0],
+    [1, 0.89, 0.94, 0.89, 0.54, 0.71, 0.0, 0.0],
+    [2, 1.91, 1.94, 1.85, 1.56, 1.61, 1.25, 0.0],
     [3, 2.975, 2.88, 2.80, 2.66, 2.43, 2.05, 1.44],
     [4, 3.99, 3.93, 3.85, 3.74, 3.51, 3.00, 0.0],
     [5, 4.95, 4.92, 4.83, 4.694, 4.38, 3.54, 2.70],
     [6, 5.76, 5.60, 5.63, 5.53, 5.17, 0.0, 0.0],
-    [7, 5.95, 5.63, 6.03, 5.28, 5.63, 0.0, 0.0],
-    [8, 5.82, 5.67, 5.05, 4.27, 0.0, 0.0, 0.0],
-    [9, 3.07, 2.89, 2.65, 0.0, 0.0, 0.0, 0.0],
+    [7, 5.94, 5.80, 6.07, 5.65, 5.74, 4.25, 0.0],
+    [8, 5.23, 4.81, 5.10, 5.64, 4.67, 3.55, 0.0],
+    [9, 3.07, 2.71, 3.23, 3.95, 4.21, 2.17, 0.0],
     [9.5, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0],
 ]
 

### 2021-05-13 estimate_newsampling/runner.sh

@@ -1,0 +1,10 @@
+#!/usr/bin/bash
+
+prob=$1
+n=$2
+k=$3
+timeoutf=$4
+
+echo  "[Z3] Running for prob : ${prob}, n-flips : ${n}, k (sum-terms) : ${k} [Saving to models/prob_${prob}_${n}_dir/z3models_${k}_${prob}_${n}.json]"
+mkdir -p models/prob_${prob}_${n}_dir
+python3 candidates.py $k $n $prob $timeoutf models/prob_${prob}_${n}_dir/z3models_${k}_${prob}_${n}.json

### 2021-05-13 estimate_newsampling/candidates.py
Optimization Step-1

@@ -156,7 +156,7 @@ def generateCandidates(k: int, n: int, prob: float):
 
     # Sigma(w(i)) value
     optpath.add(sigma_w_i == z3.Sum(path_prob_sym_vars))
-    # optpath.add(z3.And(sigma_w_i >= 0, sigma_w_i <= 1))
+    optpath.add(z3.And(sigma_w_i >= 0, sigma_w_i <= 1))
 
     optpath.add(error_mass == (n_iters * prob - sum_of_k))
 

### 2021-05-23 shared/analysis.tex
Optimization Step-1
WIP : QSORT

@@
 \usepackage{mathtools}
+
 \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
@@
 \begin{equation}
-	Obj_{1} = maximize(\sum_{i=1}^{k}{w_i * x _i}) \quad \mid \quad
-	Obj_{2} = minimize(n * prob - \sum_{i=1}^{k}{w_i * x_i})
+	Objective_{2} = maximize(\sum_{i=1}^{k}{w_i * x _i})
 \end{equation}
@@
 
+\section{QuickSort Example}
+
+Consider a pivot vector $\vec{p_{abs}}$ that \texttt{KLEE} produces over a single abstract path.
+We consider a $10$ element array as shown above.
+The $pivot$ indices for $\vec{p_{abs}}$ as choosen from a $random$ distribution.
+
+\begin{equation}
+	arr[10] = \begin{tabular}{||c|c|c|c|c|c|c|c|c|c||}
+		\hline
+		$a_0$ & $a_1$ & $a_2$ & $a_3$ & $a_4$ & $a_5$ & $a_6$ & $a_7$ & $a_8$ & $a_9$ \\
+		\hline
+	\end{tabular}
+\end{equation} \\
+
+A possible assignment of the indexes choosen as $pivot$ indices along this $abstract$ path can be as shown below.
+
+\begin{equation}
+	\vec{p_{abs}} = \begin{tabular}{||c|c|c|c|c|c||}
+		\hline
+		$a_9$ & $a_8$ & $a_2$ & $a_3$ & $a_8$ & $a_8$ \\
+		\hline
+	\end{tabular}
+\end{equation} \\
+
+For same \texttt{forall} values in $arr[10]$, we can have different random runs and on each run, the $\vec{pivot}$ vector will have a different assignment of values as indices.
+We are showing 5 different $\vec{pvot_{r_{j}}}$ vectors, each corresponding to a valid random run $j$.
+
+\begin{equation}
+	\vec{pvot_{r_{1}}} = \begin{tabular}{||c|c|c|c|c|c||}
+		\hline
+		$a_9$ & $a_4$ & $a_4$ & $a_2$ & $a_9$ & $a_9$ \\
+		\hline
+	\end{tabular}
+\end{equation}
+
+\begin{equation}
+	\vec{pvot_{r_{2}}} = \begin{tabular}{||c|c|c|c|c||}
+		\hline
+		$a_9$ & $a_9$ & $a_7$ & $a_7$ & $a_7$ \\
+		\hline
+	\end{tabular}
+\end{equation}
+
+\begin{equation}
+	\vec{pvot_{r_{3}}} = \begin{tabular}{||c|c|c|c|c|c||}
+		\hline
+		$a_9$ & $a_4$ & $a_1$ & $a_4$ & $a_9$ & $a_9$ \\
+		\hline
+	\end{tabular}
+\end{equation}
+
+\begin{equation}
+	\vec{pvot_{r_{4}}} = \begin{tabular}{||c|c|c|c|c|c||}
+		\hline
+		$a_9$ & $a_3$ & $a_1$ & $a_9$ & $a_6$ & $a_9$ \\
+		\hline
+	\end{tabular}
+\end{equation}
+
+\begin{equation}
+	\vec{pvot_{r_{5}}} = \begin{tabular}{||c|c|c|c|c|c||}
+		\hline
+		$a_9$ & $a_5$ & $a_3$ & $a_1$ & $a_9$ & $a_8$ \\
+		\hline
+	\end{tabular}
+\end{equation}
+
+\begin{equation}
+	\vec{pvot_{r_{6}}} = \begin{tabular}{||c|c|c|c|c|c|c||}
+		\hline
+		$a_9$ & $a_2$ & $a_1$ & $a_9$ & $a_6$ & $a_6$ & $a_9$ \\
+		\hline
+	\end{tabular}
+\end{equation}
+
+\begin{equation}
+	\vec{pvot_{r_{7}}} = \begin{tabular}{||c|c|c|c|c|c|c||}
+		\hline
+		$a_9$ & $a_9$ & $a_9$ & $a_5$ & $a_5$ & $a_9$ & $a_8$ \\
+		\hline
+	\end{tabular}
+\end{equation} \\
+
+For each of the random run we maintain a variable $count_j$ that tells us the total number of comparision that happened in a particular random run $j$.
+
+We want to $assert$ the following.
+
+\begin{equation}
+	E[count_j] = n * log(n) \enspace \mid \enspace \forall j \in random \enspace runs.
+\end{equation}
+
 \end{document}

### 2021-05-23 benchmark_quicksort.cpp

@@ -6,15 +6,6 @@
 #include <assert.h>
 #include <random>
 
-#define SIZE 4
-int count = 0, counter = 0, swap_count = 0;
-
-/**
- * @brief Quick Sort Example
- * analyze the expected number of comparisons in Randomized Quicksort
- * optimize on getting the maximum expected number of comparisons
- */
-
 /**
  * @brief Initial Specs
  * Create an array of static size, say 5 elements. 
@@ -23,63 +14,61 @@ int count = 0, counter = 0, swap_count = 0;
  * 
  * Must not branch on the SWAP operation after PIVOT selection. 
  * Convert to ITEs.
+ * 
+ * analyze the expected number of comparisons in Randomized Quicksort
+ * optimize on getting the maximum expected number of comparisons
+ * E[count] = n * log(n) for any given random run. 
  */
+
+#define SIZE 10
+int count = 0, counter = 0, swap_count = 0;
 
 void swap(int &a, int &b)
 {
     int temp = a;
-    klee_dump_symbolic_details(&temp, "temp_str_a");
-
     a = b;
-    int temp2 = b;
     b = temp;
-
-    klee_dump_symbolic_details(&temp2, "temp_str_b");
 }
 
 int partition(int arr[], int left, int right)
 {
     // pivot element
-    int pivot = arr[right];
-    int i = (left - 1);
+    int pivot, r, i = (left - 1);
 
     /**
      * @brief We need to extract count as a 
      * symbolic expression in the comparision.
      */
 
-    int r = 0;
-    counter += 1;
-
-    auto klm = std::to_string(counter);
+    auto __counter = std::to_string(counter++);
 
     // COMMENT : Symbolic Expression for compare count.
     std::string c_symbolic("count_");
-    c_symbolic += klm;
+    c_symbolic += __counter;
     c_symbolic += "_sym";
     klee_make_symbolic(&count, sizeof(count), c_symbolic.c_str());
 
     // COMMENT : Symbolic Expression for swap count.
     std::string swap_symbolic("swap_");
-    swap_symbolic += klm;
+    swap_symbolic += __counter;
     swap_symbolic += "_sym";
     klee_make_symbolic(&swap_count, sizeof(swap_count), swap_symbolic.c_str());
 
-    // COMMENT : Symbolic Expression for pivot.
[…]

### 2021-05-23 quicksort_example/candidates.py

@@ -1,0 +1,135 @@
+# -*- coding: utf-8 -*-
+
+import z3
+import os
+import sys
+import json
+import time
+from alive_progress import alive_bar
+
+# from scipy.stats import bernoulli
+
+# https://z3prover.github.io/api/html/classz3py_1_1_rat_num_ref.html#a1012d6314d35530c58f9c018269ec867
+def num(r):
+    """
+    Convert from Z3 to python float values.
+    """
+    return float(r.numerator_as_long()) / float(r.denominator_as_long())
+
+
+def get_value(r):
+    # https://stackoverflow.com/questions/12598408/z3-python-getting-python-values-from-model/12600208
+    """
+    Convert from Z3 to python values.
+    """
+    if z3.is_true(r):
+        return z3.is_true(r)
+    elif z3.is_false(r):
+        return z3.is_false(r)
+    elif z3.is_int_value(r):
+        return r.as_long()
+    elif z3.is_algebraic_value(r):
+        return round(num(r.approx(15)), 10)
+    elif z3.is_rational_value(r):
+        return r.as_decimal(20)
+    elif r is None:
+        None
+    else:
+        return num(r)
+
+
+"""
+Below are a list of constraints that dictate which 
+path is taken during actual program execution. 
+We process KLEE constraints and simplify them to get these 
+constraints. 
+"""
+
+# pwd = os.path.dirname(__file__)
+# if not os.path.isdir(os.path.join(pwd, "inputs")):
+#     os.mkdir(os.path.join(pwd, "inputs"))
+
+# inputFilePath = os.path.join(pwd, "inputs")
+
+z3.set_option(
+    precision=10,
+    rational_to_decimal=True,
+    max_args=10000000,
+    max_lines=10000000,
+    max_depth=10000000,
+    max_visited=10000000,
+)
+
+z3.set_param("smt.random_seed", int(time.time()))
+
+def generateCandidates(k=20):
+    optpath = z3.Optimize()
+    # COMMENT : Supply the timeout in minute value.
+    # optpath.set("timeout", 60000 * int(sys.argv[4]))
+
+    pivot = z3.Int("pivot")
+    pivot_index = z3.Int("pivot_index")
+    left_sum = z3.Int("left_sum")
+    right_sum = z3.Int("right_sum")
+
+    left_count = [z3.Int(f"left_{i}") for i in range(k)]
[…]

### 2021-05-27 shared/analysis.tex
WIP : QSORT

@@
 
-For each of the random run we maintain a variable $count_j$ that tells us the total number of comparision that happened in a particular random run $j$.
-
-We want to $assert$ the following.
+The probability mass associated with the $i_{th}$ random run as is given below considering each $pivot$ selection being an independent selection.
 
 \begin{equation}
-	E[count_j] = n * log(n) \enspace \mid \enspace \forall j \in random \enspace runs.
+	w_i = (1 / n) * \prod_{j=1}^{k} 1 / l_j  * \prod_{j=1}^{k} 1 / r_j \quad \mid \quad for \enspace k-partitons
+\end{equation}
+
+\begin{equation}
+	where \enspace l_j = count(l_{terms}), \enspace r_j = count(r_{terms}) \quad \mid \quad in \enspace j^{th} \enspace partition. 
 \end{equation}

### 2021-05-27 quicksort_example/quicksort_z3.py

@@ -10,6 +10,7 @@ import json
 import z3
 
 pivot_vector_choices = []
+prob_vector = []
 
 
 def num(r):
@@ -55,10 +56,18 @@ def partition_quicksort(solver, arr, temp_arr, start, end, pivot_vector, compare
 
     compare = 0
     range_iter = (end - start) + 1
+    prob_value = 1 / range_iter
+
+    prob_vector.append(prob_value)
 
     pivot = z3.Int("pivot")
     solver.add(z3.Or([pivot == temp_arr[i + start]
                for i in range(range_iter)]))
+
+    if len(pivot_vector_choices) >= 1:
+        pivot_choices = pivot_vector_choices[-1]
+        solver.add(z3.Or([pivot != pivot_choices[i]
+                   for i in range(len(pivot_choices))]))
 
     solver.check()
     model = solver.model()
@@ -122,10 +131,10 @@ def run_sort_concrete(solver, arr):
     # solver.add(arr[8] == 18)
     # solver.add(arr[9] == 1)
 
-    range_constraint = [z3.And(arr[i] > 1, arr[i] < 1000000)
-                        for i in range(forall_elems)]
+    # range_constraint = [z3.And(arr[i] > 1, arr[i] < 1000000)
+    #                     for i in range(forall_elems)]
 
-    solver.add(range_constraint)
+    # solver.add(range_constraint)
     solver.add(z3.Distinct(arr))
 
     solver.check()
@@ -133,14 +142,17 @@ def run_sort_concrete(solver, arr):
     temp_arr = [get_value(init_model[arr[i]]) for i in range(len(arr))]
     solver.pop()
 
-    print(temp_arr)
     quicksort_z3(solver, arr, temp_arr, 0, len(
         arr) - 1, pivot_vector, compare_vector)
 
+    print(temp_arr)
     return temp_arr, pivot_vector, compare_vector
 
 
+model_count = 5000
 forall_elems = 10
+sigma_w_i = []
+compare_vector_run = []
 
 if __name__ == "__main__":
 
@@ -148,15 +160,28 @@ if __name__ == "__main__":
     solver = z3.Solver()
     arr = [z3.Int(f"arr_{i}") for i in range(forall_elems)]
 
-    models = 3
+    models = model_count
     while(models > 0):
-        temp_arr, pivot_vector, compare_vector = run_sort_concrete(solver, arr)
+        temp_arr, pivot_vector, compare_vector = run_sort_concrete(
+            solver, arr)
 
[…]

### 2021-05-27 quicksort_example/quicksort_z3.py
WIP : QSORT -- analysis

@@ -52,7 +52,9 @@ def find_index_pivot(arr, elem):
             return index
 
 
-def partition_quicksort(solver, arr, temp_arr, start, end, pivot_vector, compare_vector):
+def partition_quicksort(
+    solver, arr, temp_arr, start, end, pivot_vector, compare_vector
+):
 
     compare = 0
     range_iter = (end - start) + 1
@@ -61,13 +63,13 @@ def partition_quicksort(solver, arr, temp_arr, start, end, pivot_vector, compare
     prob_vector.append(prob_value)
 
     pivot = z3.Int("pivot")
-    solver.add(z3.Or([pivot == temp_arr[i + start]
-               for i in range(range_iter)]))
+    solver.add(z3.Or([pivot == temp_arr[i + start] for i in range(range_iter)]))
 
     if len(pivot_vector_choices) >= 1:
         pivot_choices = pivot_vector_choices[-1]
-        solver.add(z3.Or([pivot != pivot_choices[i]
-                   for i in range(len(pivot_choices))]))
+        solver.add(
+            z3.Or([pivot != pivot_choices[i] for i in range(len(pivot_choices))])
+        )
 
     solver.check()
     model = solver.model()
@@ -104,13 +106,28 @@ def quicksort_z3(solver, arr, temp_arr, start, end, pivot_vector, compare_vector
     if start < end:
         solver.push()
         pivot_index_sort = partition_quicksort(
-            solver, arr, temp_arr, start, end, pivot_vector, compare_vector)
+            solver, arr, temp_arr, start, end, pivot_vector, compare_vector
+        )
         solver.pop()
         # print(f"Start: {start}, End: {end}, Pivot Index: {pivot_index_sort}")
-        quicksort_z3(solver, arr, temp_arr, start,
-                     pivot_index_sort - 1, pivot_vector, compare_vector)
-        quicksort_z3(solver, arr, temp_arr, pivot_index_sort +
-                     1, end, pivot_vector, compare_vector)
+        quicksort_z3(
+            solver,
+            arr,
+            temp_arr,
+            start,
+            pivot_index_sort - 1,
+            pivot_vector,
+            compare_vector,
+        )
+        quicksort_z3(
+            solver,
+            arr,
+            temp_arr,
+            pivot_index_sort + 1,
+            end,
[…]

### 2021-06-22 shared/Paper-Draft/PSE-POPL-2021.tex
WIP : POPL'22 Paper Draft

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
%%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
\documentclass[acmsmall]{acmart}\settopmatter{}

%% Journal information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{POPL} % CONF = POPL or ICFP or OOPSLA
\acmArticle{1}
\acmYear{2022}
\acmMonth{1}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

%% Copyright information
%% Supplied to authors (based on authors' rights management selection;
%% see authors.acm.org) by publisher for camera-ready submission;
%% use 'none' for review submission.
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\copyrightyear{2018}           %% If different from \acmYear

%% Bibliography style
\bibliographystyle{ACM-Reference-Format}
%% Citation style
%% Note: author/year citations are required for papers published as an
%% issue of PACMPL.
\citestyle{acmauthoryear}   %% For author/year citations

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Note: Authors migrating a paper from PACMPL format to traditional
%% SIGPLAN proceedings format must update the '\documentclass' and
%% topmatter commands above; see 'acmart-sigplanproc-template.tex'.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
%% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
%% http://ctan.org/pkg/subcaption
\usepackage{mathtools}
\usepackage{algpseudocode,algorithm,algorithmicx}
%\usepackage{amsmath, amssymb,amsthm, stmaryrd}

%%% Macros %%%

\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}
\newcommand{\DeclareAutoPairedDelimiter}[3]{%
	\expandafter\DeclarePairedDelimiter\csname Auto\string#1\endcsname{#2}{#3}%
	\begingroup\edef\x{\endgroup
		\noexpand\DeclareRobustCommand{\noexpand#1}{%
			\expandafter\noexpand\csname Auto\string#1\endcsname*}}%
	\x}
\DeclareAutoPairedDelimiter{\deno}{\llbracket}{\rrbracket}

\newcommand*\Let[2]{\State #1 $\gets$ #2}
\newcommand*\dom[1]{\mathrm{dom}\left( #1 \right)}

% Switch Statement Commands
% New definitions
\algnewcommand\algorithmicswitch{\textbf{switch}}
\algnewcommand\algorithmiccase{\textbf{case}}
\algnewcommand\algorithmicassert{\texttt{assert}}
\algnewcommand\Assert[1]{\State \algorithmicassert(#1)}%
% New "environments"
\algdef{SE}[SWITCH]{Switch}{EndSwitch}[1]{\algorithmicswitch\ #1\ \algorithmicdo}{\algorithmicend\ \algorithmicswitch}%
\algdef{SE}[CASE]{Case}{EndCase}[1]{\algorithmiccase\ #1}{\algorithmicend\ \algorithmiccase}%
\algtext*{EndSwitch}%
\algtext*{EndCase}%

\begin{document}

	%% Title information
	\title[PSE]{Probabilistic Symbolic Execution}         %% [Short Title] is optional;
	%% when present, will be used in
	%% header instead of Full Title.
	%\titlenote{with title note}             %% \titlenote is optional;
	%% can be repeated if necessary;
	%% contents suppressed with 'anonymous'
	%\subtitle{Subtitle}                     %% \subtitle is optional
	%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
	%% can be repeated if necessary;
	%% contents suppressed with 'anonymous'

	%% Author information
	%% Contents and number of authors suppressed with 'anonymous'.
	%% Each author should be introduced by \author, followed by
	%% \authornote (optional), \orcid (optional), \affiliation, and
	%% \email.
	%% An author may have multiple affiliations and/or emails; repeat the
	%% appropriate command.
	%% Many elements are not rendered, but should be provided for metadata
	%% extraction tools.

	%% Author with single affiliation.
	\author{First1 Last1}
	\authornote{with author1 note}          %% \authornote is optional;
	%% can be repeated if necessary
	\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
	\affiliation{
		\position{Position1}
		\department{Department1}              %% \department is recommended
		\institution{Institution1}            %% \institution is required
		\streetaddress{Street1 Address1}
		\city{City1}
		\state{State1}
		\postcode{Post-Code1}
		\country{Country1}                    %% \country is recommended
	}
	\email{first1.last1@inst1.edu}          %% \email is recommended

	%% Author with two affiliations and emails.
	\author{First2 Last2}
	\authornote{with author2 note}          %% \authornote is optional;
	%% can be repeated if necessary
	\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
	\affiliation{
		\position{Position2a}
		\department{Department2a}             %% \department is recommended
		\institution{Institution2a}           %% \institution is required
		\streetaddress{Street2a Address2a}
		\city{City2a}
		\state{State2a}
		\postcode{Post-Code2a}
		\country{Country2a}                   %% \country is recommended
	}
	\email{first2.last2@inst2a.com}         %% \email is recommended
	\affiliation{
		\position{Position2b}
		\department{Department2b}             %% \department is recommended
		\institution{Institution2b}           %% \institution is required
		\streetaddress{Street3b Address2b}
		\city{City2b}
		\state{State2b}
		\postcode{Post-Code2b}
		\country{Country2b}                   %% \country is recommended
	}
	\email{first2.last2@inst2b.org}         %% \email is recommended

	%% Abstract
	%% Note: \begin{abstract}...\end{abstract} environment must come
	%% before \maketitle command
	\begin{abstract}
		TODO: Write Abstract
	\end{abstract}

	%% 2012 ACM Computing Classification System (CSS) concepts
	%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
	%% TODO: Get CSS Concepts
	\begin{CCSXML}
		<ccs2012>
		<concept>
		<concept_id>10011007.10011006.10011008</concept_id>
		<concept_desc>Software and its engineering~General programming languages</concept_desc>
		<concept_significance>500</concept_significance>
		</concept>
		<concept>
		<concept_id>10003456.10003457.10003521.10003525</concept_id>
		<concept_desc>Social and professional topics~History of programming languages</concept_desc>
		<concept_significance>300</concept_significance>
		</concept>
		</ccs2012>
	\end{CCSXML}

	\ccsdesc[500]{Software and its engineering~General programming languages}
	\ccsdesc[300]{Social and professional topics~History of programming languages}
	%% End of generated code

	%% Keywords
	%% comma separated list
	\keywords{keyword1, keyword2, keyword3}  %% \keywords are mandatory in final camera-ready submission

	%% \maketitle
	%% Note: \maketitle command must come after title commands, author
	%% commands, abstract environment, Computing Classification System
	%% environment and commands, and keywords command.
	\maketitle

	\section{Introduction}
	\label{sec:intro}

	\subsection{Contributions}
	\label{sec:contrib}

	\section{Motivating Example}
	\label{sec:example}

	\section{Probabilistic Symbolic Execution Algorithm}
	\label{sec:pse}
	In this section, we present our technique for augmenting traditional symbolic execution to support probabilistic programs with discrete sampling instructions. 
	%
	We begin with a short review of a traditional symbolic execution algorithm and then discuss how we calculate exact path probabilities.

	\subsection{Background}
	\label{sec:trad_sym_exec}
	{\color{red} Subhajit \& Sumit: If you could add a high-level description of symb. exec., maybe an algorithm, that would be great!\\}
	\textit{Symbolic execution} is a program analysis technique where a program is run on \textit{symbolic} inputs and all program operations are replaced with those which manipulate these symbolic variables.
	%
	During execution, program state is encoded symbolically in two parts: a path condition which is a conjunctive formula, $\varphi$, which records the branch conditions which are true for that particular path, and a mapping from program variables to symbolic expressions containing constants and \textit{symbolic variables}, $\sigma$.
	%
	When execution reaches an assignment of the form $\mathtt{x} = e$, where $e$ is a constant or program variable, $\sigma[\mathtt{x}] = \sigma[e]$.
	%
	Similarly, if $e = e_1 \oplus e_2$, where $\oplus$ is an arbitrary binary operation, $\sigma[\mathtt{x}] = \sigma[e_1] \oplus \sigma[e_2]$. 
	%
	When execution reaches a branch guarded by the condition $c$, execution proceeds down both branches, one where $\varphi = \varphi \wedge \sigma[c]$, and the other where $\varphi = \varphi \wedge \neg \sigma[c]$.

	\subsection{Adding Probabilistic Sampling}
	We now consider the problem of performing symbolic execution on a simple imperative probabilistic programming language, \textbf{pWhile}:
	%
	\[
	P := \mathbf{skip} \mid \mathtt{x} \leftarrow e \mid \mathtt{x} \xleftarrow{\$} d \mid P ; P \mid \mathbf{if}~e~\mathbf{then}~P~\mathbf{else}~P \mid \mathbf{while}~e~\mathbf{do}~P 
	\]

	Above, $\mathtt{x}$ is a program variable, $e$ is an expression, and $d$ is a \textit{discrete} distribution expression. 
	%
	In order to support sampling instructions we make the following additions to traditional symbolic execution:
	%
	\begin{itemize}
		\item \textit{Probabilistic symbolic variables.} We distiguish two types of symbolic variables: \textit{universally quantified} symbolic variables (identical to those in traditional symbolic execution), and \textit{probabilistic} symbolic variables.
		% 
		For each unique sampling instruction a new probabilistic symbolic variable is created to denote the result of sample.
		\item \textit{Distribution map.} We add a new mapping from probabilistic symbolic variables to distribution expressions, $P$, which tracks the distribution from which a probabilistic symbolic variable was originally sampled from.
		\item \textit{Path probability.} For each path, we adjoin a path probability expression, $p$, which is parameterized by universally quantified symbolic variables.
	\end{itemize}

	\begin{algorithm}[H]
		\caption{PSE Assignment Algorithm}
		\begin{algorithmic}[1]
			\Function{PSEAssignment}{$\mathtt{x}, e, \varphi, \sigma, P, I$}
			\Let{$e_{sym}$}{Convert $v$ into a symbolic expression using $\sigma$}
			\State{$\sigma[\mathtt{x}] = e_{sym}$}
			\State\Return{$(\varphi,\sigma, P, I)$}
			\EndFunction
		\end{algorithmic}
	\end{algorithm}

	\begin{algorithm}
		\caption{PSE Sampling Algorithm}
		\label{alg:sample}
		\begin{algorithmic}[1]
			\Function{PSESample}{$\mathtt{x}, d, \varphi, \sigma, P$}
			\Let{$\delta$}{Generate a fresh probabilistic symbolic variable}
			\State{$\sigma[\mathtt{x}] = \delta$}
			\State{$P[\delta] = d$}
			\State\Return{$(\varphi,\sigma,P)$}
			\EndFunction
		\end{algorithmic}
	\end{algorithm}

	\begin{algorithm}
		\caption{PSE Branch Algorithm}
		\label{alg:branch}
		\begin{algorithmic}[1]
			\Function{PSEBranch}{$c, \varphi, \sigma, P$}
			\Let{$c_{sym}$}{$\sigma[c]$}
			\Let{$(\delta_1,\ldots,\delta_n)$}{$\dom{P}$}
			\Let{$(d_1,\ldots,d_n)$}{$(P[\delta_1],\ldots,P[\delta_n])$}
			\Let{$p_c$}{$\frac{\displaystyle\sum_{(v_1,\ldots,v_n) \in \dom{d_1} \times \cdots\times \dom{d_n}} [(c_{sym} \wedge \varphi)\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]}{\displaystyle\sum_{(v_1,\ldots,v_n) \in \dom{d_1} \times \cdots\times \dom{d_n}}[\varphi\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]}$}\\
			\Return{$((\varphi \wedge c_{sym}, \sigma,P,p_c), (\varphi \wedge \neg c_{sym}, \sigma,P,1-p_c))$}
			\EndFunction
		\end{algorithmic}
	\end{algorithm}

	\begin{algorithm}
		\caption{Getting Path Constraints : Symbolic Execution}
		\label{alg:symbex}
		\begin{algorithmic}[1]
			\Function{SymbEx}{$P_{prog} : Program$}
				\Let{$\varphi_{paths}$}{[]}, {$Ex_{stack}$} $\leftarrow$ {[]} \algorithmiccomment{List to store all the path conditions.}
				\Let{$I_{0}$}{\textsc{getStartInstruction}($P_{prog}$)}
				\Let{$S_{0}$}{[$I_{0}$, $\phi_{path}$, $\Delta$]} \algorithmiccomment{Empty Initial State}
				\State {$Ex_{stack}$.\textsc{Push}({$S_{0}$})} \algorithmiccomment{Start with $S_{cur}$ in Execution Stack}
				\While{$Ex_{stack}$ != $\phi$}
					\Let{$S_{cur}$}{$Ex_{stack}$.\textsc{Pop}( )}, $I_{cur} \leftarrow S_{cur}[1]$ \algorithmiccomment{Start State, [$I_{0}$, $\phi_{path}$, $\Delta$]}
					\Switch{\textsc{instType}($I_{cur}$)}
					\Case{v := e} \algorithmiccomment{Assignment Instruction}
						\Let{$I_{cur}$}{\textsc{getNextInstruction}($I_{cur}$)}
						\Let{$S_{cur}$}{[$I_{cur}$, $\phi_{path}$, $\Delta$[v $\rightarrow$ \textsc{Eval($e$, $\Delta$)}]]}
						\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
					\EndCase
					\Case{\textbf{if} $(c_{sym})$ \textbf{then} $P_{1}$ \textbf{else} $P_{2}$} \algorithmiccomment{Branch Instruction}
						\If{(\textsc{isSat}($c_{sym}$) $\wedge$ \textsc{isSat}($\neg c_{sym}$))} \algorithmiccomment{Both cases SAT}
							\Let{$S_{true}$, $S_{false}$}{\textsc{Fork}({$S_{cur}$, $\Delta$})}		
							\Let{$I_{1}$}{\textsc{getStartInstruction}($P_{1}$)}, {$I_{2}$} $\leftarrow$ {\textsc{getStartInstruction}($P_{2}$)}	
							\Let{$S_{true}$}{[$I_{1}$, $\phi_{path} \wedge c_{sym}$, $\Delta$]},
							{$S_{false}$} $\leftarrow$ {[$I_{2}$, $\phi_{path} \wedge (\neg c_{sym})$, $\Delta$]}
							\State {$Ex_{stack}$.\textsc{Push}({$S_{false}$})}
							\State {$Ex_{stack}$.\textsc{Push}({$S_{true}$})} \algorithmiccomment{Start with True State}
						\ElsIf{\textsc{isSat}($c_{sym}$)} \algorithmiccomment{True case SAT}
							\Let{$I_{cur}$}{\textsc{getStartInstruction}($P_{1}$)}
							\Let {$S_{cur}$}{[$I_{cur}$, $\phi_{path} \wedge c_{sym}$, $\Delta$]}
							\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
						\ElsIf{\textsc{isSat}($\neg c_{sym}$)} \algorithmiccomment{False case SAT}
							\Let{$I_{cur}$}{\textsc{getStartInstruction}($P_{2}$)}
							\Let{$S_{cur}$}{[$I_{2}$, $\phi_{path} \wedge (\neg c_{sym})$, $\Delta$]}
							\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
						\Else \algorithmiccomment{$c_{sym}$ UNSAT}
							\Let{$I_{cur}$}{\textsc{getNextInstruction}($I_{cur}$)}
							\Let{$S_{cur}$}{[$I_{cur}$, $\phi_{path}$, $\Delta$]}
							\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
						\EndIf
					\EndCase
					\Case{\textbf{assume}$(v == expr)$} \algorithmiccomment{Assume Instruction}
						\Let{$I_{cur}$}{\textsc{getNextInstruction}($I_{cur}$)}	
						\If{\textsc{isSat}($v == expr$)}
							\Let{$S_{cur}$}{[$I_{cur}$, $\phi_{path} \wedge (v == expr)$, $\Delta$]}
						\Else 
							\Let{$S_{cur}$}{[$I_{cur}$, $\phi_{path} \wedge $(\textsc{false}), $\Delta$]}
						\EndIf
						\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
					\EndCase
					\Case{\textbf{HALT}} \algorithmiccomment{Terminate Instruction}
						\Let{$\phi_{path}^{'}$}$S_{cur}$[2] \algorithmiccomment{End of a Path}
						\Let{$\varphi_{paths}$}{$\varphi_{paths}$.\textsc{Append}($\phi_{path}^{'}$)}		
					\EndCase
					\EndSwitch
				\EndWhile \\
				\Return{$\varphi_{paths}$}
			\EndFunction
		\end{algorithmic}
	\end{algorithm}

	When a sampling statement, $\mathtt{x} \xleftarrow{\$} d$, is reached, a fresh probabilistic symbolic variable, $\delta$, is created, $\sigma$ is updated to be $\sigma[\mathtt{x}] = \delta$, and the original distribution $d$ is recorded in $P$ by setting $P[\delta] = d$.
	%
	Note that with the inclusion of probabilistic symbolic variables we can now either branch on universally quantified or probabilistic symbolic variables (or both).
	%
	For guards whose symbolic version does not contain any probabilistic symbolic variables, probabilstic symbolic execution works nearly identically to traditional symbolic execution, save one detail: the probability of taking the branch. 
	%
	If $c_{sym}$ is a symbolic expression which represents the guard to a branch, and $c_{sym}$ does not contain any probabilistic symbolic variables, then we define the probability of taking the ``true'' branch is $[c_{sym}]$, and the probability of taking the ``false'' branch is $[\neg c_{sym}]$, where $[\cdot]$ are Iverson brackets.

	For probabilistic branches, i.e. guards which branch on probabilistic symbolic variables, Alg.~\ref{alg:branch} is used instead of the traditional symbolic execution branch algorithm.
	%
	Without loss of generality, consider a branch of the form $\mathbf{if}~c~\mathbf{then}~P_1~\mathbf{else}~P_2$ where $c$ is a probabilistic branch.
	%
	As before, we define $c_{sym} = \sigma[c]$.
	%
	The core of Alg.~\ref{alg:branch} is computing the probability of taking each branch.
	%
	We interpret probabilistic branches as a conditioning operation on the distributions which are mentioned in the guard of the branch.
	%
	Under this interpretation, we aim to compute $\Pr[c_{sym} \mid \varphi]$ where $\varphi$ is the current path condition formula.

	% Add small example 
	We use a form of model counting in order to compute $p_c$, the probability of $c$ being true.
	%
	Note that each probabilistic symbolic variable, $\delta$, is mapped to exactly one distribution, $d$, and therefore, $\delta \in \dom{d}$.
	%
	So, assuming there are $n$ probabilistic symbolic variables, $\delta_1,\ldots,\delta_n$, and so $n$ distributions, $d_1,\ldots,d_n$, the set of all possible values $\delta_1,\ldots,\delta_n$ be is $\mathcal{D} = \dom{d_1} \times \cdots \times \dom{d_n}$.
	%
	We then count the number of \textit{assignments} from $\mathcal{D}$ which satisfy $c_{sym} \wedge \varphi$ and $\varphi$, and divide these two quantities as shown on line 5 of Alg.~\ref{alg:branch}.
	%
	In Section~\ref{sec:formalization} we have a proof of correctness for this quantity, but the intuition is by applying the definition of conditional probability.
	%
	Note that $p_c$ is not necessarily a value, but rather a symbolic expression containing constants and universally quantified symbolic variables.
	%
	We exploit the fact that the sum of the conditional probabilities of the branch outcomes is 1, which allows us to avoid computing the probability of taking the ``false'' branch directly.

	\subsection{Formalization}
	\label{sec:formalization}

	In this section we present the formalization of our method. First, we will present our notation and definitions, and then provide proofs of correctness and soundness of our technique.

	\subsubsection{Notation \& Definitions}
	\label{sec:notation}

	The goal of this section is to describe how $R=(\varphi,\sigma,P)$, the inputs to Alg.~\ref{alg:branch} is an abstraction of a \textit{distribution of program memories} before a branch guarded by a program expression $c$.
	% 
	To begin, we will define some notation:
	\begin{itemize}
		\item Let $Vars$ be the set of all program variables, $ForallSymVars$ be the set of all universally quantified symbolic variables, $ProbSymVars$ be the set of all probabilistic symbolic variables, $SymVars = ForallSymVars \cup ProbSymVars$ be the combined set of all symbolic variables, and $Vals$ be the set of all values. 
		\item Let $a_f: ForallSymVars \rightarrow Vals$ be an assignment of universally quantified symbolic variables to values and let $ForallAssign$ be the set of all such assignments.
		\item Similarly, let $a_p : ProbSymVars \rightarrow Vals$ be an assignment of probabilistic symbolic variables to values and let $ProbAssign$ be the set of all such assignments.
		\item Let $m : Vars \rightarrow Vals$ be a program memory which translates program variables into values, and let $Mems$ be the set of all program memories.
		\item Let $de : Mems \rightarrow (Vals \rightarrow [0,1])$ be a distribution expression parameterized by program memories, and let $DistExprs$ be the set of all distribution expressions.
		\item Let $d : ForallAssign \times Mems \rightarrow [0,1]$ be a distribution of program memories parameterized by assignments to universally quantified symbolic variables and let $MemDists$ be the set of all parameterized distributions of program memories.
	\end{itemize}

	Additionally, we will use emphatic brackets for two purposes:
	\begin{itemize}
		\item If $e \in ProgExprs$ is a \textit{program} expression containing the program variables $\mathtt{x}_1,\ldots,\mathtt{x}_n \in Vars$, and $m \in Mems$, then
		\[
		\deno{e}m = \text{eval}(e[\mathtt{x}_1 \mapsto m(\mathtt{x}_1),\ldots,\mathtt{x}_n \mapsto m(\mathtt{x}_n)])
		\]
		\item If $e \in SymExprs$ is a \textit{symbolic} expression containing the symbolic variables $\alpha_1,\ldots,\alpha_n \in ForallSymVars$ and $\delta_1,\ldots,\delta_m \in ProbSymVars$, and $a_f \in ForallAssign$ and $a_p \in ProbAssign$, then
		\[
		\deno{e}a_fa_p = \text{eval}(e[\alpha_1\mapsto a_f(\alpha_1),\ldots,\alpha_n \mapsto a_f(\alpha_n), \delta_1 \mapsto a_p(\delta_1), \ldots, \delta_m \mapsto a_p(\delta_m)])
		\]
	\end{itemize}

	With this notation in hand, we can now define what it means for $R$ to be an abstraction of a distribution of programs memories.

	\begin{definition}
		\label{def:combined}
		Let $R = (\varphi, \sigma, P)$ be the abstraction generated by the symbolic execution algorithm where $\varphi: ForallAssign \times ProbAssign \rightarrow \{0,1\}$ denotes whether the path condition is true or false under the given assignments, $\sigma : Vars \rightarrow SymExprs$ is the mapping from program variables to symbolic expressions generated through symbolic execution, and $P : ForallAssign \rightarrow ProbSymVars \rightharpoonup (Vals \rightarrow [0,1])$  is the mapping from probabilistic symbolic variables to the distribution it is sampled from parameterized by assignments of forall symbolic variables.
		% 
		Additionally, for every assignment of forall symbolic variables, $a_f \in ForallAssign$, $\mathrm{domain}(P(a_f)) = \{\delta_1,\ldots,\delta_k\}$.
		% 
		Let $\alpha_1,\ldots,\alpha_l \in ForallSymVars$ be the forall symbolic variables which correspond to the $l$ parameters to the program.
		% 
		For every assignment of probabilistic and forall symbolic variables, $a_f \in ForallAssign, a_p \in ProbAssign$, let $\nu : ForallAssign \rightarrow (ProbAssign \rightarrow [0,1])$ be a distribution of assignments of probabilistic symbolic variables parameterized by assignments of forall symbolic variables, defined as
		\[
		\nu(a_f,a_p) \triangleq \prod_{i=1}^k \Pr_{v \sim P(a_f,\delta_i)}[v = a_p(\delta_i)].
		\]
		% 
		We say that a distribution $d$ satisfies our abstraction $R$ if, for all assignments of forall symbolic variables, $a_f \in ForallAssign$, $\displaystyle\Pr_{a_p' \sim \nu(a_f)}[\varphi(a_f,a_p') = 1] > 0$, and if $\mu : ForallAssign \rightarrow (ProbAssign \rightarrow [0,1])$ is defined as 
		\[
		\mu(a_f,a_p) = \cfrac{\Pr_{a_p' \sim \nu(a_f)}[a_p' = a_p \land \varphi(a_f,a_p') = 1]}{\Pr_{a_p' \sim \nu(a_f)}[\varphi(a_f,a_p')=1]}.
		\]
		Additionally, define $\text{convertToMem} : (Vars \rightarrow SymExprs) \rightarrow ForallAssign \rightarrow ProbAssign \rightarrow Mem$ as
		\begin{equation*}
			\text{convertToMem}(\sigma,a_f,a_p) \triangleq \lambda (\mathtt{x}: Vars)~.~\deno{\sigma(\mathtt{x})}a_fa_p,
		\end{equation*}
		and let $\text{convertFromMem}(\sigma,a_f,m) = (\text{convertToMem}(\sigma,a_f))^{-1}(m)$.
		% 
		Then,
		\[
		d(a_f,m) = \sum_{a_p \in \text{convertFromMem}(\sigma,a_f,m)} \mu(a_f,a_p).
		\]
	\end{definition}

	We additionally define the semantics for the three main types of statements which concerns probabilistic symbolic execution: assignments, probabilistic samples, and branches.

	\begin{definition}[Assignment Semantics]
		Let $d \in MemDists$ be a distribution of program memories parameterized by assignments to forall symbolic variables. Let $\mathtt{x} = e$ be an arbitrary assignment of the program variable $\mathtt{x} \in Vars$ to the program expression $e \in ProgExprs$. Let $\text{assign}_{\mathtt{x}=e} : Mems \rightarrow Mems$ is defined as
		\[
		\text{assign}_{\mathtt{x}=e}(m) = \lambda(\mathtt{y} : Vars)
		\begin{cases}
			\deno{e}m & \text{if $\mathtt{x} = \mathtt{y}$}\\
			m(\mathtt{y}) & \text{otherwise}
		\end{cases}
		\]
		and let $\text{unassign}_{\mathtt{x}=e} = \text{assign}_{\mathtt{x}=e}^{-1}$. Then we define $d_{\mathtt{x}=e}$ to be the distribution over program memories parameterized by assignments to forall symbolic variables after executing the assignment statement $\mathtt{x}=e$ to be
		\[
		d_{\mathtt{x}=e}(a_f,m) = \sum_{m' \in \text{unassign}_{\mathtt{x}=e}(m)} d(a_f,m').
		\]
	\end{definition}

	\begin{definition}[Sampling Semantics]
		Let $d \in MemDists$ be a distribution of program memories parameterized by assignments to forall symbolic variables. Let $\mathtt{x} \sim de$ be an arbitrary sampling instruction which assigns the program variable $\mathtt{x} \in Vars$ to a random element from the distribution of values parameterized by a memory, represented as a distribution expression $de \in DistExprs$. Let $\text{desample} : Vars \times Mems \rightarrow \mathcal{P}(Mems)$ be defined as
		\[
		\text{desample}(\mathtt{x},m) = \{ m'\in Mems \mid \forall (\mathtt{y} \in Vars)~.~(\mathtt{y} \neq \mathtt{x} \wedge m'(\mathtt{y}) = m(\mathtt{y}))\}.
		\]
		Then, we define $d_{\mathtt{x} \sim de}$ to be the distribution over program memories parameterized by assignments to forall symbolic variables after executing the sampling statement $\mathtt{x} \sim de$ to be
		\[
		d_{\mathtt{x} \sim de}(a_f,m) = \sum_{m' \in \text{desample}(m)} (\deno{de}a_f)(m(\mathtt{x})) \cdot d(a_f,m').
		\]
	\end{definition}

	\begin{definition}[Conditional Distribution of Program Memories]
		\label{def:cond}
		Let $a_f \in ForallAssign$ be an arbitrary assignment of forall symbolic variables, $c$ be a guard of an \texttt{if} condition, $d \in MemDists$ be a distribution of program memories parameterized by assignments to forall symbolic variables, and $\mathtt{x}_1,\ldots,\mathtt{x}_n \in Vars$ be all of the program variables in $c$. Then for all program memories $m \in Mems$, $d$ conditioned on a guard $c$ being true, represented as $d_c$ is defined as
		\[
		d_c(a_f,m) = \frac{\Pr_{m' \sim d(a_f)}\left[ m' = m \land \deno{c}m' = \mathtt{true} \right]}{\Pr_{m' \sim d(a_f)}\left[ \deno{c}m' = \mathtt{true} \right]}
		\]
		Similarly, for all program memories $m \in Mems$, $d$ conditioned on a guard $c$ being false, represented as $d_{\neg c}$ is defined as
		\[
		d_{\neg c}(a_f,m) = \frac{\Pr_{m' \sim d(a_f)}\left[ m' = m \land \deno{c}m' = \mathtt{false} \right]}{\Pr_{m' \sim d(a_f)}\left[ \deno{c}m' = \mathtt{false} \right]}
		\]
	\end{definition}

	\subsubsection{Proofs}
	\label{sec:proofs}

	\section{Implementation}
	\label{sec:implementation}

	{\color{red} Subhajit \& Sumit: Write something about KLEE and the implementation here!}

	We use a robust symbolic execution engine, \textsc{KLEE} to generate the \textit{path constraints} corresponding to each path that our tool explores. \textsc{KLEE} starts by running the program under an enviroment where all \textit{program inputs} are replaced with \textit{symbolic} variables that can be assigned any value from it's domain. For the purpose of our implementation, we modify \textsc{KLEE} to support creation of \textit{probabilistic symbolic} variables whose values can be sampled from a distribution and dump the whole set of \textit{path} constraints that is stored in the \textit{state} corresponding to the current execution of the program at each of (1) \textit{assignment}, (2) \textit{branch}, \& (3) \textit{assume} statements. These dumps are later refined and used by the tool for further processing.
	\section{Case Studies}
	\label{sec:case_studies}

	\section{Evaluation}
	\label{sec:eval}

	\section{Related Work}
	\label{sec:related}
	{\color{red} Subhajit \& Sumit: If you could both start looking into related work (Mayhap, original PSE paper, Axprof, P4WN, PSI), that would be great!}
	\begin{itemize}
		\item Compare and Contrast with Mayhap, PSE, AxProf, P4WN \& PSI.
		\item Explain how we differ by not using a Model Counting but a Constraint Solving approach.
		\item Support for \textsc{ForAll} variables along with \textit{probabilistic} variables. 
	\end{itemize}
	\section{Conclusion \& Future Work}
	\label{sec:conclusion}

	%% Acknowledgments
	\begin{acks}                            %% acks environment is optional
		%% contents suppressed with 'anonymous'
		%% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
		%% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
		%% acknowledge financial support and will be used by metadata
		%% extraction tools.
		% This material is based upon work supported by the
		% \grantsponsor{GS100000001}{National Science
		%   Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
		% No.~\grantnum{GS100000001}{nnnnnnn} and Grant
		% No.~\grantnum{GS100000001}{mmmmmmm}.  Any opinions, findings, and
		% conclusions or recommendations expressed in this material are those
		% of the author and do not necessarily reflect the views of the
		% National Science Foundation.
	\end{acks}

	%% Bibliography
	%\bibliography{bibfile}

	%% Appendix
	\appendix
	\section{Appendix}

	Text of appendix \ldots

\end{document}

### 2021-06-23 shared/Paper-Draft/PSE-POPL-2021.tex
WIP : Implementation Section

@@
 					\EndCase
-					\Case{\textbf{if} $(c_{sym})$ \textbf{then} $P_{1}$ \textbf{else} $P_{2}$} \algorithmiccomment{Branch Instruction}
+					\Case{\textbf{if} $(c_{sym})$ \textbf{then} $P_{1}$ \textbf{else} $P_{2}$} \algorithmiccomment{Branch Instruction} \label{line:branch}
 						\If{(\textsc{isSat}($c_{sym}$) $\wedge$ \textsc{isSat}($\neg c_{sym}$))} \algorithmiccomment{Both cases SAT}
-							\Let{$S_{true}$, $S_{false}$}{\textsc{Fork}({$S_{cur}$, $\Delta$})}		
-							\Let{$I_{1}$}{\textsc{getStartInstruction}($P_{1}$)}, {$I_{2}$} $\leftarrow$ {\textsc{getStartInstruction}($P_{2}$)}	
-							\Let{$S_{true}$}{[$I_{1}$, $\phi_{path} \wedge c_{sym}$, $\Delta$]},
-							{$S_{false}$} $\leftarrow$ {[$I_{2}$, $\phi_{path} \wedge (\neg c_{sym})$, $\Delta$]}
+							\Let{$I_{1}$}{\textsc{getStartInstruction}($P_{1}$)} \Let{$I_{2}$} {\textsc{getStartInstruction}($P_{2}$)}	
+							\Let{$S_{true}$}{[$I_{1}$, $\phi_{path} \wedge c_{sym}$, $\Delta$]}
+							\Let{$S_{false}$}{[$I_{2}$, $\phi_{path} \wedge (\neg c_{sym})$, $\Delta$]}
 							\State {$Ex_{stack}$.\textsc{Push}({$S_{false}$})}
@@
 					\Case{\textbf{HALT}} \algorithmiccomment{Terminate Instruction}
-						\Let{$\phi_{path}^{'}$}$S_{cur}$[2] \algorithmiccomment{End of a Path}
-						\Let{$\varphi_{paths}$}{$\varphi_{paths}$.\textsc{Append}($\phi_{path}^{'}$)}		
+						\Let{$\varphi_{paths}$}{$\varphi_{paths}$.\textsc{Append}($\phi_{path}$)}		
 					\EndCase
@@
 	We use a robust symbolic execution engine, \textsc{KLEE} to generate the \textit{path constraints} corresponding to each path that our tool explores.
-\textsc{KLEE} starts by running the program under an enviroment where all \textit{program inputs} are replaced with \textit{symbolic} variables that can be assigned any value from it's domain.
+For each path in the program, \textsc{KLEE} stores a list of \textit{constraints} that encodes the whole path.
+These constraints are over \textit{program} variables that have been marked \texttt{make\_symbolic()} by the user and are stored in \textsc{KLEE} as \textit{metadata} in the \textit{state} data structure during the symbolic execution of the program.
+Apart from \textit{path constraints}, the \textit{state} contains a mapping of \textit{symbolic} variables to \textit{symbolic} expressions or \textit{concrete} values (in the case of concrete execution) and a list of \textit{instructions} currently getting executed as a part of the \textit{state}.
+
+	\textsc{KLEE} assigns values to these \textit{symbolic} variables by solving the current set of \textit{constraints} seen so far in the program path as described in Algorithm~\ref{alg:symbex} and also by concretizing some of the values that get evaluated as a result of \textit{concrete} execution.
+Upon reaching a \textit{branch} instruction at Line~\ref{line:branch} in Algorithm~\ref{alg:symbex}, \textsc{KLEE} forks the current \textit{state} by making two identical copies of it and then appending to each of \textit{new} states one additional constraint encoding the \textit{true} and \textit{false} side of the branch and adds it to the \textit{execution} stack containing \textit{states} that need to explored next.
+The process continues untill all the \textit{states} in the \textit{execution} stack are explored.
+
 	For the purpose of our implementation, we modify \textsc{KLEE} to support creation of \textit{probabilistic symbolic} variables whose values can be sampled from a distribution and dump the whole set of \textit{path} constraints that is stored in the \textit{state} corresponding to the current execution of the program at each of (1) \textit{assignment}, (2) \textit{branch}, \& (3) \textit{assume} statements.

### 2021-06-23 shared/Paper-Draft/PSE-POPL-2021.tex
WIP : Implementation Section

@@
 For each path in the program, \textsc{KLEE} stores a list of \textit{constraints} that encodes the whole path.
-These constraints are over \textit{program} variables that have been marked \texttt{make\_symbolic()} by the user and are stored in \textsc{KLEE} as \textit{metadata} in the \textit{state} data structure during the symbolic execution of the program.
-Apart from \textit{path constraints}, the \textit{state} contains a mapping of \textit{symbolic} variables to \textit{symbolic} expressions or \textit{concrete} values (in the case of concrete execution) and a list of \textit{instructions} currently getting executed as a part of the \textit{state}.
+These constraints are over \textit{program} variables that have been marked \texttt{make\_symbolic()} by the user and are stored in \textsc{KLEE} as \textit{metadata} in the \textit{state} data structure during the \textit{dynamic} symbolic execution of the program.
 
 	\textsc{KLEE} assigns values to these \textit{symbolic} variables by solving the current set of \textit{constraints} seen so far in the program path as described in Algorithm~\ref{alg:symbex} and also by concretizing some of the values that get evaluated as a result of \textit{concrete} execution.
-Upon reaching a \textit{branch} instruction at Line~\ref{line:branch} in Algorithm~\ref{alg:symbex}, \textsc{KLEE} forks the current \textit{state} by making two identical copies of it and then appending to each of \textit{new} states one additional constraint encoding the \textit{true} and \textit{false} side of the branch and adds it to the \textit{execution} stack containing \textit{states} that need to explored next.
+Upon reaching the \textit{branch} instruction at Line~\ref{line:branch} in Algorithm~\ref{alg:symbex}, \textsc{KLEE} forks the current \textit{state} by making two identical copies of it and then appending to each of \textit{new} states one additional constraint encoding the \textit{true} and \textit{false} side of the branch and adds it to the \textit{execution} stack containing \textit{states} that need to explored next.
 The process continues untill all the \textit{states} in the \textit{execution} stack are explored.
+Apart from \textit{path constraints}, the \textit{state} also contains a mapping of \textit{symbolic} variables to expressions that are either  \textit{symbolic} or \textit{concrete} (in the case of concrete execution of the program) and a list of \textit{instructions} currently getting executed as a part of the \textit{state}.
 

### 2021-06-23 shared/Paper-Draft/PSE-POPL-2021.tex
WIP : Baseline Experiments

@@
 							\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
-						\Else \algorithmiccomment{$c_{sym}$ UNSAT}
+						\Else \algorithmiccomment{Unconditional Branch}
 							\Let{$I_{cur}$}{\textsc{getNextInstruction}($I_{cur}$)}
@@
 
-	We use a robust symbolic execution engine, \textsc{KLEE} to generate the \textit{path constraints} corresponding to each path that our tool explores.
+	We use a robust dynamic symbolic execution engine, \textsc{KLEE} to generate the \textit{path constraints} corresponding to each path that our tool explores.
 For each path in the program, \textsc{KLEE} stores a list of \textit{constraints} that encodes the whole path.
@@
 
-	\textsc{KLEE} assigns values to these \textit{symbolic} variables by solving the current set of \textit{constraints} seen so far in the program path as described in Algorithm~\ref{alg:symbex} and also by concretizing some of the values that get evaluated as a result of \textit{concrete} execution.
-Upon reaching the \textit{branch} instruction at Line~\ref{line:branch} in Algorithm~\ref{alg:symbex}, \textsc{KLEE} forks the current \textit{state} by making two identical copies of it and then appending to each of \textit{new} states one additional constraint encoding the \textit{true} and \textit{false} side of the branch and adds it to the \textit{execution} stack containing \textit{states} that need to explored next.
+	\textsc{KLEE} assigns values to these \textit{symbolic} variables by employing an \textsc{SMT Solver} for solving the current set of \textit{constraints} seen so far in the program path as described in Algorithm~\ref{alg:symbex} and also by concretizing some of the values that get evaluated as a result of \textit{concrete} execution (Eg.
+return value from external function calls).
+Upon reaching the \textit{branch} instruction at Line~\ref{line:branch} in Algorithm~\ref{alg:symbex}, \textsc{KLEE} forks the current \textit{state} by making two identical copies of it and then appending to each of \textit{new} states one additional constraint encoding the \textit{true} and \textit{false} side of the branch and adds it to the \textit{execution} stack containing \textit{states} that need to be explored next.
 The process continues untill all the \textit{states} in the \textit{execution} stack are explored.
@@
 		\item Compare and Contrast with Mayhap, PSE, AxProf, P4WN \& PSI.
-		\item Explain how we differ by not using a Model Counting but a Constraint Solving approach.
+		\item Explain how we differ by not using Model Counting but a Constraint Solving approach.
 		\item Support for \textsc{ForAll} variables along with \textit{probabilistic} variables. 

### 2021-06-23 baseline-exp/runner.sh

@@ -1,0 +1,27 @@
+#!/usr/bin/env bash
+set -e
+set -u
+set -o pipefail
+
+export CC=$(which clang)
+export CXX=$(which clang++)
+export RUNNER=$1
+
+rm -rf bin/* 
+rm -rf output/*
+rm -rf tests/*
+
+# dd if=/dev/random of=tests/input01.txt bs=32 count=1
+# dd if=/dev/random of=tests/input02.txt bs=32 count=1
+# dd if=/dev/random of=tests/input03.txt bs=32 count=1
+# head -c 32 /dev/zero > tests/input04.txt
+# dd if=/dev/random of=tests/input05.txt bs=32 count=1
+# head -c 32 /dev/zero > tests/input06.txt
+
+cd bin/
+CC=$CC CXX=$CXX cmake -DCMAKE_CXX_FLAGS="-w" -DCMAKE_EXPORT_COMPILE_COMMANDS=ON ../
+clang-tidy -checks=* -p bin/ ../src/${RUNNER}.cpp
+make -j 12
+cd ../
+
+bin/${RUNNER}

### 2021-06-23 baseline-exp/src/init.cpp

@@ -1,0 +1,15 @@
+#include <cstdio>
+#include <init.h>
+#include <iostream>
+#include <string>
+#include <unordered_map>
+#include <vector>
+
+int main() {
+  /**
+   * @brief Initialize the FORALL Variables.
+   *
+   */
+
+  return 0;
+}

### 2021-06-23 baseline-exp/runner.sh
WIP : Baseline Experiments

@@ -19,7 +19,7 @@ rm -rf tests/*
 # head -c 32 /dev/zero > tests/input06.txt
 
 cd bin/
-CC=$CC CXX=$CXX cmake -DCMAKE_CXX_FLAGS="-w" -DCMAKE_EXPORT_COMPILE_COMMANDS=ON ../
+CC=$CC CXX=$CXX cmake -DCMAKE_CXX_FLAGS="-w -fsanitize=address -fsanitize=leak" -DCMAKE_EXPORT_COMPILE_COMMANDS=ON ../
 clang-tidy -checks=* -p bin/ ../src/${RUNNER}.cpp
 make -j 12
 cd ../

### 2021-06-23 baseline-exp/src/freivalds_multiple.cpp

@@ -105,5 +105,6 @@ int main() {
     // klee_dump_kquery_state();
     std::cout << "Win! \n";
   }
+
   return 0;
 }

### 2021-06-23 baseline-exp/src/monotone_binary_search.cpp

@@ -1,0 +1,68 @@
+#include <cmath>
+#include <cstdio>
+#include <iostream>
+#include <string>
+#include <unordered_map>
+#include <vector>
+
+#define N 100
+
+size_t monotone_check(unsigned char *f) {
+  unsigned char last = f[0];
+  size_t count = 0;
+  for (size_t i = 1; i < N; i++) {
+    if (last > f[i]) {
+      count++;
+    }
+    last = f[i];
+  }
+  return count;
+}
+
+int main() {
+  unsigned char f[N];
+  for (int i = 0; i < N; i++) {
+    unsigned char temp;
+    // klee_make_symbolic(&temp, sizeof(temp), "f");
+    f[i] = temp;
+  }
+  //  klee_make_symbolic(&f, sizeof(f), "f");
+
+  size_t x;
+  //   klee_make_symbolic(&x, sizeof(x), "x");
+  //   klee_assume(x >= 0);
+  //   klee_assume(x < N);
+  //   klee_assume(monotone_check(f) == x);
+
+  unsigned char l = (unsigned char)ceil(log2(N)) - 1;
+  unsigned char a = 0;
+  unsigned char b = N - 1;
+
+  unsigned char i;
+  //   make_pse_symbolic(&i, sizeof(i), "i", (unsigned char)0,
+  // (unsigned char)(N - 1));
+
+  bool reject = false;
+
+  for (unsigned char t = 0; t < l; t++) {
+    unsigned char p = (unsigned char)ceil((double(a + b)) / (double)2.0);
+    if (i <= p) {
+      if (f[i] > f[p]) {
+        reject = true;
+      }
+      b = p;
+    } else {
+      if (f[i] < f[p]) {
+        reject = true;
+      }
+      a = p + 1;
+    }
+  }
+
+  if (!reject) {
+    // klee_dump_kquery_state();
+    std::cout << "!reject \n";
+  }
+
+  return 0;
+}

### 2021-06-24 shared/Paper-Draft/PSE-POPL-2021.tex
WIP : Baseline Experiments
WIP : BaseLine

@@
 			\Function{SymbEx}{$P_{prog} : Program$}
-				\Let{$\varphi_{paths}$}{[]}, {$Ex_{stack}$} $\leftarrow$ {[]} \algorithmiccomment{List to store all the path conditions.}
+				\Let{$\varphi_{paths}$}{[]}, {$Ex_{stack}$} $\leftarrow$ {[]}, $\Delta \leftarrow$ {[]}, $\phi_{paths} \leftarrow \phi$  \algorithmiccomment{Initialization}
 				\Let{$I_{0}$}{\textsc{getStartInstruction}($P_{prog}$)}
@@
 					\Let{$S_{cur}$}{$Ex_{stack}$.\textsc{Pop}( )}, $I_{cur} \leftarrow S_{cur}[1]$ \algorithmiccomment{Start State, [$I_{0}$, $\phi_{path}$, $\Delta$]}
-					\Switch{\textsc{instType}($I_{cur}$)}
-					\Case{v := e} \algorithmiccomment{Assignment Instruction}
+					\Switch{\textsc{instType}($I_{cur}$)} \label{line:inst_case}
+					\Case{v := e} \algorithmiccomment{Assignment Instruction} \label{line:assign}
 						\Let{$I_{cur}$}{\textsc{getNextInstruction}($I_{cur}$)}
@@
 							\Let{$I_{1}$}{\textsc{getStartInstruction}($P_{1}$)} \Let{$I_{2}$} {\textsc{getStartInstruction}($P_{2}$)}	
-							\Let{$S_{true}$}{[$I_{1}$, $\phi_{path} \wedge c_{sym}$, $\Delta$]}
-							\Let{$S_{false}$}{[$I_{2}$, $\phi_{path} \wedge (\neg c_{sym})$, $\Delta$]}
+							\Let{$S_{true}$}{[$I_{1}$, $\phi_{path} \wedge c_{sym}$, $\Delta$]} \label{line:true_state}
+							\Let{$S_{false}$}{[$I_{2}$, $\phi_{path} \wedge (\neg c_{sym})$, $\Delta$]} \label{line:false_state}
 							\State {$Ex_{stack}$.\textsc{Push}({$S_{false}$})}
@@
 					\EndCase
-					\Case{\textbf{assume}$(v == expr)$} \algorithmiccomment{Assume Instruction}
+					\Case{\textbf{assume}$(v == expr)$} \algorithmiccomment{Assume Instruction} \label{line:assume}
 						\Let{$I_{cur}$}{\textsc{getNextInstruction}($I_{cur}$)}	
@@
 These constraints are over \textit{program} variables that have been marked \texttt{make\_symbolic()} by the user and are stored in \textsc{KLEE} as \textit{metadata} in the \textit{state} data structure during the \textit{dynamic} symbolic execution of the program.
-
-	\textsc{KLEE} assigns values to these \textit{symbolic} variables by employing an \textsc{SMT Solver} for solving the current set of \textit{constraints} seen so far in the program path as described in Algorithm~\ref{alg:symbex} and also by concretizing some of the values that get evaluated as a result of \textit{concrete} execution (Eg.
-return value from external function calls).
-Upon reaching the \textit{branch} instruction at Line~\ref{line:branch} in Algorithm~\ref{alg:symbex}, \textsc{KLEE} forks the current \textit{state} by making two identical copies of it and then appending to each of \textit{new} states one additional constraint encoding the \textit{true} and \textit{false} side of the branch and adds it to the \textit{execution} stack containing \textit{states} that need to be explored next.
-The process continues untill all the \textit{states} in the \textit{execution} stack are explored.
 Apart from \textit{path constraints}, the \textit{state} also contains a mapping of \textit{symbolic} variables to expressions that are either  \textit{symbolic} or \textit{concrete} (in the case of concrete execution of the program) and a list of \textit{instructions} currently getting executed as a part of the \textit{state}.
 
-	For the purpose of our implementation, we modify \textsc{KLEE} to support creation of \textit{probabilistic symbolic} variables whose values can be sampled from a distribution and dump the whole set of \textit{path} constraints that is stored in the \textit{state} corresponding to the current execution of the program at each of (1) \textit{assignment}, (2) \textit{branch}, \& (3) \textit{assume} statements.
+	During \textit{dynamic} execution, \textsc{KLEE} executes each \textit{instruction} in the program and updates the \textit{state} along with the \textit{symbolic} variables mapping ($\Delta$) depending upon \textit{type} of the \textit{instruction} it executes as described in Algorithm~\ref{alg:symbex}.
+	\textsc{KLEE} assigns values to \textit{symbolic} variables by employing an \textsc{SMT Solver} (\textsc{Z3} as in our case) for solving the current set of \textit{constraints} seen so far in the program path and also by concretizing some of the values that get evaluated as a result of \textit{concrete} execution (Eg.
+return value from external function calls).
+
+	%Upon reaching the \textit{branch} instruction at Line~\ref{line:branch} in Algorithm~\ref{alg:symbex}, based on whether the \textit{path constraints} are solvable upon adding the \textit{branch} [Line~\ref{line:branch}] condition, \textsc{KLEE} forks the current \textit{state} by making two identical copies of it and then appending to each of \textit{new} states one additional constraint encoding the \textit{true} [Line~\ref{line:true_state}] and \textit{false} [Line~\ref{line:false_state}] side of the branch and adds it to the \textit{execution} stack containing \textit{states} that need to be explored next.
+The process continues untill all the \textit{states} in the \textit{execution} stack are explored.
+
+	For the purpose of our implementation, we modify \textsc{KLEE} to support creation of \textit{probabilistic symbolic} variables whose values can be sampled from a distribution and dump the whole set of \textit{path} constraints that is stored in the \textit{state} corresponding to the current execution of the program at each of (1) \textbf{\textit{assignment}} [Algorithm~\ref{alg:symbex}, Line~\ref{line:assign}], (2) \textbf{\textit{branch}} [Algorithm~\ref{alg:symbex}, Line~\ref{line:branch}], \& (3) \textbf{\textit{assume}} [Algorithm~\ref{alg:symbex}, Line~\ref{line:assume}] statements.
 These dumps are later refined and used by the tool for further processing.

### 2021-06-24 baseline-exp/generateInputs.py

@@ -3,12 +3,19 @@ import sys
 import time
 import random
 
+# testWritter.write(
+# f"{random.randint(-2147483648, 2147483647)}\n")
+
 pwd = os.path.dirname(__file__)
 inputFilePath = os.path.join(pwd, "tests")
 
 if __name__ == "__main__":
     for index in range(int(sys.argv[1].strip())):
         with open(os.path.join(inputFilePath, f"input_{index + 1}.txt"), mode="w") as testWritter:
-            for tests in range(10):
-                testWritter.write(
-                    f"{random.randint(int(sys.argv[2].strip()), int(sys.argv[3].strip()))}\n")
+            testWritter.write(f"{int(sys.argv[1].strip())}\n")
+            testWritter.write(
+                f"{random.randint(1, 2000)}\n")
+            testWritter.write(
+                f"{random.randint(1, 100)}\n")
+            testWritter.write(
+                f"{round(random.uniform(0.000001, 1.000000), 6)}\n")

### 2021-06-24 baseline-exp/run.sh

@@ -18,7 +18,7 @@ echo "  ---- Generating Inputs for ${RUNNER} ----  "
 # do 
 #     dd if=/dev/random of=tests/input_${index}.txt bs=64 count=1
 # done
-python3 generateInputs.py 10 -500 500
+python3 generateInputs.py 250
 
 echo "  ---- Building Binary : ${RUNNER} ----  "
 cd bin/
@@ -27,9 +27,9 @@ CC=$CC CXX=$CXX cmake \
     -DCMAKE_EXPORT_COMPILE_COMMANDS=ON ../
     
 # clang-tidy -checks=* -p bin/ ../src/${RUNNER}.cpp
-make -j 12
+make -j 2
 cd ../
 
-# echo "  ---- Running Binary : ${RUNNER} ----  "
-# bin/${RUNNER} < tests/input_1.txt
-# echo "  ---- ${RUNNER} ----  "
+echo "  ---- Running Binary : ${RUNNER} ----  "
+bin/${RUNNER} < tests/input_1.txt
+echo "  ---- ${RUNNER} ----  "

### 2021-06-24 baseline-exp/src/basic_example.cpp

@@ -1,44 +1,50 @@
 #include <assert.h>
+#include <iostream>
 #include <random>
 #include <stdio.h>
 #include <vector>
 
-// int unroll = 2500;
-long long int termCount = 100000;
-
 int main() {
-  long double prob = 0.500;
-  int x = 0, n = 10, y = 10, n_start, y_start;
-  long long unsigned int win = 0, loop_run = 0, prob_runs = 0;
 
+  long double prob = 0;
+  int n = 0, y = 0, termCount = 0;
+  long long unsigned int win = 0, loop_run = 0;
+
+  // Randomly Sample the ForAlls.
+  scanf("%d", &termCount);
   scanf("%d", &n);
   scanf("%d", &y);
   scanf("%Lf", &prob);
 
-  n_start = n;
-  y_start = y;
-
+  std::cout << "ForALL Setting : n : " << n << ", y : " << y
+            << ", prob : " << prob << "\n";
+  // We read one sample of ForAlls setting
+  // and start simulation.
   while (termCount--) {
-    x = 0;
-    int n_loop = n;
+    /**
+     * @brief We simulate the sampling of
+     * probabilistic variables here.
+     *
+     * They are sampled each time from a distribution.
+     */
 
-    // program execution
+    // program execution starts
     std::default_random_engine generator;
     std::bernoulli_distribution bernoulli_rvs(prob);
+    int n_loop = n, x = 0;
 
-    while (n_loop > 0) {
+    while (n_loop--) {
+      // Sample the probabilistic variable.
       int d = bernoulli_rvs(generator);
+      // std::cout << "d : " << d << "\n";
       if (d) {
-        // This doesn't favours the "win" condition.
         x = x + y;
       }
-      n_loop -= 1;
-
-      // Iterations of the loop.
-      prob_runs++;
     }
 
     // Sample for probability. This is the assert condition.
+    // Number of times assert is HIT.
+    // std::cout << (double)x - (prob * n * y) << "\n";
     if ((double)x - (prob * n * y) <= 0)
       win++;
 
@@ -47,10 +53,7 @@ int main() {
   }
 
   auto pwin = (double)win / loop_run;
-  fprintf(stdout, "P(x - (prob * n * y) <= 0) : %.6lf\n\n", pwin);
-  if (n_start != 0)
-    fprintf(stderr,
[…]

### 2021-06-24 baseline-exp/src/bloomfilter.cpp

@@ -5,6 +5,7 @@
 #include <iostream>
 #include <math.h>
 #include <prob_hash.h>
+#include <random>
 #include <stdint.h>
 #include <stdlib.h>
 #include <string.h>
@@ -22,7 +23,10 @@ unsigned int hash(struct prob_hash *prob_hash, std::string key,
 
   // If the key is not in the map, get a random element and rehash
   if (found == prob_hash->map.end()) {
-    unsigned int x;
+    // Randomly sample PSE Variable from a given distribution.
+    std::default_random_engine generator;
+    std::uniform_int_distribution<int> int_dist(0, INT32_MAX);
+    unsigned int x = int_dist(generator);
     // make_pse_symbolic(&x, sizeof(x), "x_sym", 0, (int)max);
     prob_hash->map[key] = x;
     return x;
@@ -152,13 +156,70 @@ int bloom_reset(struct bloom *bloom) {
 const char *bloom_version() { return MAKESTRING(BLOOM_VERSION); }
 
 int main() {
-  struct bloom bloom;
-  bloom_init(&bloom, 1, 0.1);
-  bloom_add(&bloom, "Zach1");
-  if (bloom_check(&bloom, "Justin")) {
-    // klee_dump_kquery_state();
-    std::cout << "Found !\n";
+
+  /**
+   * @brief We randomly supply a set of forall values.
+   * We run the program multiple times, each time with a
+   * different setting of the ForAll variables.
+   */
+  int entries = 0, add_item = 0, search_item = 1, win = 0, loop_count = 0,
+      termCount = 0;
+  double error = 0.0454;
+  std::vector<std::string> inputs = {"Zach1",  "Zach2",     "Justin1",
+                                     "Sumit1", "Subhajit1", "Justin2"};
+
+  std::default_random_engine generator;
+  std::uniform_int_distribution<int> range_dist(0, 5);
+  std::uniform_real_distribution<double> error_dist(0.01, 0.99);
+
+  entries = 1;
+  error = error_dist(generator);
+  add_item = range_dist(generator);
+  search_item = range_dist(generator);
+  scanf("%d", &termCount);
+
+  while (termCount--) {
+
+    // For each setting of the forAlls,
+    // We run the program termCount number of times.
+    struct bloom bloom;
+    bloom_init(&bloom, entries, error);
[…]

### 2021-06-24 shared/Paper-Draft/PSE-POPL-2021.tex
WIP : POPL Paper Draft

@@
 						\Let{$I_{cur}$}{\textsc{getNextInstruction}($I_{cur}$)}	
-						\If{\textsc{isSat}($v == expr$)}
+						\If{\textsc{isSat}($v == expr$)} \algorithmiccomment{Check Satisfiablilty}
 							\Let{$S_{cur}$}{[$I_{cur}$, $\phi_{path} \wedge (v == expr)$, $\Delta$]}
+							\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
 						\Else 
-							\Let{$S_{cur}$}{[$I_{cur}$, $\phi_{path} \wedge $(\textsc{false}), $\Delta$]}
+							%\Let{$S_{cur}$}{[$I_{cur}$, $\phi_{path} \wedge $(\textsc{false}), $\Delta$]}
+							\Let {$\phi_{path}$}{$\phi$} \algorithmiccomment{Infeasible Path}
 						\EndIf
-						\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
 					\EndCase
@@
 
-	%Upon reaching the \textit{branch} instruction at Line~\ref{line:branch} in Algorithm~\ref{alg:symbex}, based on whether the \textit{path constraints} are solvable upon adding the \textit{branch} [Line~\ref{line:branch}] condition, \textsc{KLEE} forks the current \textit{state} by making two identical copies of it and then appending to each of \textit{new} states one additional constraint encoding the \textit{true} [Line~\ref{line:true_state}] and \textit{false} [Line~\ref{line:false_state}] side of the branch and adds it to the \textit{execution} stack containing \textit{states} that need to be explored next.
-The process continues untill all the \textit{states} in the \textit{execution} stack are explored.
-
 	For the purpose of our implementation, we modify \textsc{KLEE} to support creation of \textit{probabilistic symbolic} variables whose values can be sampled from a distribution and dump the whole set of \textit{path} constraints that is stored in the \textit{state} corresponding to the current execution of the program at each of (1) \textbf{\textit{assignment}} [Algorithm~\ref{alg:symbex}, Line~\ref{line:assign}], (2) \textbf{\textit{branch}} [Algorithm~\ref{alg:symbex}, Line~\ref{line:branch}], \& (3) \textbf{\textit{assume}} [Algorithm~\ref{alg:symbex}, Line~\ref{line:assume}] statements.
 These dumps are later refined and used by the tool for further processing.
+
+	{\color{blue} Upon reaching the \textit{branch} instruction at Line~\ref{line:branch} in Algorithm~\ref{alg:symbex}, based on whether the \textit{path constraints} are solvable upon adding the \textit{branch} [Line~\ref{line:branch}] condition, \textsc{KLEE} forks the current \textit{state} by making two identical copies of it and then appending to each of \textit{new} states one additional constraint encoding the \textit{true} [Line~\ref{line:true_state}] and \textit{false} [Line~\ref{line:false_state}] side of the branch and adds it to the \textit{execution} stack containing \textit{states} that need to be explored next.
+The process continues untill all the \textit{states} in the \textit{execution} stack are explored.}
+
 	\section{Case Studies}

### 2021-06-25 shared/Paper-Draft/PSE-POPL-2021.tex
WIP : Discussions

@@
 %% For final camera-ready submission, w/ required CCS and ACM Reference
-\documentclass[acmsmall]{acmart}\settopmatter{}
+\documentclass[acmsmall,review]{acmart}\settopmatter{}
 
@@
 \usepackage{algpseudocode,algorithm,algorithmicx}
-%\usepackage{amsmath, amssymb,amsthm, stmaryrd}
+\usepackage{forest}
+\usepackage{csquotes}
+\usepackage{minted}
+\usepackage{multicol}
 
@@
 
+% For the Case statements
 % Switch Statement Commands
@@
 
+	One of the goals of symbolic execution is to identify whether a ``bad'' state (e.g. an \texttt{assert} failure) is reached, signifying a bug in the program.
+	%
+	In probabilistic programs, we are often more interested in either whether a ``bad'' state is reached too often, or, conversely, whether the ``good'' states are reached often enough.
+
 	\subsection{Contributions}
@@
 	\section{Motivating Example}
-	\label{sec:example}
+	\label{sec:motiv_example}
+
+	The Monty Hall problem~\cite{selvin1975} is a classic probability puzzle based on the American television show, \textit{Let's Make a Deal}, which showcases how subtle probabilistic reasoning can be.
+	%
+	The problem itself is simple:
+	\begin{displayquote}
+		You are a contestant on a gameshow and behind one of three doors there is a car and behind the others, goats.
+		% 
+		You pick a door and the host, who knows what is behind each of the doors, opens a different door, which has a goat.
+		% 
+		The host then offers you the choice to switch to the remaining door.
+		% 
+		Should you?
+	\end{displayquote}
+	While it may seem unintuitive, regardless of the contestant's original door choice, the contestant who always switches doors will win the car $\frac{2}{3}$ of the time, as opposed to a $\frac{1}{3}$ chance.
+
+	\begin{figure}\centering
+		\begin{multicols}{2}
+			\inputminted[fontsize=\footnotesize,linenos]{c}{montyhall.c}
+		\end{multicols}
+		\caption{C code for the Monty Hall Problem}
+		\label{fig:montyhall}
+	\end{figure}
+
+	We can represent this problem as a probabilistic program, as shown in Fig.~\ref{fig:montyhall}, where $\mathtt{choice} \in [1,3]$ and is the door which is originally chosen by the contestant and $\mathtt{door\_switch}$ is \texttt{true} if the contestant wants to switch doors when asked, and \texttt{false} otherwise.
+	%
+	Supposedly if $\mathtt{door\_switch} = \mathtt{true}$, regardless of the value of \texttt{choice}, \texttt{monty\_hall} should return \texttt{true} (i.e. the car is won) $\frac{2}{3}$ of the time.
+	%
+	The problem thus becomes, given a probabilistic program with discrete sampling statements, and a program property, how do we verify that the program satisfies the property?
+
+	One typical solution would be to run a simulation on random inputs and compute the probability of winning if $\mathtt{door\_switch} = \mathtt{true}$, and the probability of winning if $\mathtt{door\_switch} = \mathtt{false}$.
+	%
+	While for this program this would work as the input space is tiny, the resulting output distributions would be absent any formal guarantees and only be an approximation.
+
+	% 1) What is the problem? Given a program, and a property we wish to check, how do we prove that property?
+	% - Introduce the program and the property
+	% 2) Given a program, how do we generate the tree with probabilities?
+	% 3) Given a tree, how do we make queries against the tree to actually verify the property?
 
@@
 	\[
-	P := \mathbf{skip} \mid \mathtt{x} \leftarrow e \mid \mathtt{x} \xleftarrow{\$} d \mid P ; P \mid \mathbf{if}~e~\mathbf{then}~P~\mathbf{else}~P \mid \mathbf{while}~e~\mathbf{do}~P 
+	S := \mathbf{skip} \mid \mathtt{x} \leftarrow e \mid \mathtt{x} \xleftarrow{\$} d \mid S_1 ; S_2 \mid \mathbf{if}~e~\mathbf{then}~S_1~\mathbf{else}~S_2 \mid \mathbf{while}~e~\mathbf{do}~S 
 	\]
@@
 	\begin{itemize}
-		\item \textit{Probabilistic symbolic variables.} We distiguish two types of symbolic variables: \textit{universally quantified} symbolic variables (identical to those in traditional symbolic execution), and \textit{probabilistic} symbolic variables.
+		\item \textit{Probabilistic symbolic variables.} We distiguish two types of symbolic variables: \textit{universal} symbolic variables (identical to those in traditional symbolic execution), and \textit{probabilistic} symbolic variables.
 		% 
@@
 		\item \textit{Distribution map.} We add a new mapping from probabilistic symbolic variables to distribution expressions, $P$, which tracks the distribution from which a probabilistic symbolic variable was originally sampled from.
-		\item \textit{Path probability.} For each path, we adjoin a path probability expression, $p$, which is parameterized by universally quantified symbolic variables.
+		\item \textit{Path probability.} For each path, we adjoin a path probability expression, $p$, which is parameterized by universal symbolic variables.
 	\end{itemize}
@@
 		\caption{PSE Assignment Algorithm}
+		\label{alg:assign}
 		\begin{algorithmic}[1]
-			\Function{PSEAssignment}{$\mathtt{x}, e, \varphi, \sigma, P, I$}
-			\Let{$e_{sym}$}{Convert $v$ into a symbolic expression using $\sigma$}
+			\Function{PSEAssignment}{$\mathtt{x}, e, \varphi, \sigma, P$}
+			\Let{$e_{sym}$}{$\sigma[e]$}
 			\State{$\sigma[\mathtt{x}] = e_{sym}$}
-			\State\Return{$(\varphi,\sigma, P, I)$}
+			\State\Return{$(\varphi,\sigma,P)$}
 			\EndFunction
@@
 	\end{algorithm}
+
+	\begin{paragraph}{Assignment}
+		For assignment statements of the form $\mathtt{x} \leftarrow e$, where $\mathtt{x}$ is a \textit{program} variable and $e$ is an expression, probabilistic symbolic execution proceeds identically to traditional symbolic execution, as detailed in Alg.~\ref{alg:assign}.
+	\end{paragraph}
 
@@
 
+	\begin{paragraph}{Sampling}
+		For sampling statements, $\mathtt{x} \xleftarrow{\$} d$, where $\mathtt{x}$ is a \textit{program} variable and $d$ is a distribution expression, Alg.~\ref{alg:sample} is used.
+		% 
+		A fresh probabilistic symbolic variable, $\delta$, is created, $\sigma$ is updated to be $\sigma[\mathtt{x}] = \delta$, and the original distribution $d$ is recorded in $P$ by setting $P[\delta] = d$.
+	\end{paragraph}
+
 	\begin{algorithm}
@@
 			\Let{$(d_1,\ldots,d_n)$}{$(P[\delta_1],\ldots,P[\delta_n])$}
-			\Let{$p_c$}{$\frac{\displaystyle\sum_{(v_1,\ldots,v_n) \in \dom{d_1} \times \cdots\times \dom{d_n}} [(c_{sym} \wedge \varphi)\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]}{\displaystyle\sum_{(v_1,\ldots,v_n) \in \dom{d_1} \times \cdots\times \dom{d_n}}[\varphi\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]}$}\\
-			\Return{$((\varphi \wedge c_{sym}, \sigma,P,p_c), (\varphi \wedge \neg c_{sym}, \sigma,P,1-p_c))$}
+			\Let{$p_c$}{$\frac{\displaystyle\sum_{(v_1,\ldots,v_n) \in \dom{d_1} \times \cdots\times \dom{d_n}} [(c_{sym} \wedge \varphi)\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]}{\displaystyle\sum_{(v_1,\ldots,v_n) \in \dom{d_1} \times \cdots\times \dom{d_n}}[\varphi\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]}$}
+			\State\Return{$((\varphi \wedge c_{sym}, \sigma,P,p_c), (\varphi \wedge \neg c_{sym}, \sigma,P,1-p_c))$}
 			\EndFunction
@@
 
+	% Symbolic Execution Algorithm.
 	\begin{algorithm}
@@
 			\EndCase
-					\Case{\textbf{assume}$(v == expr)$} \algorithmiccomment{Assume Instruction} \label{line:assume}
-						\Let{$I_{cur}$}{\textsc{getNextInstruction}($I_{cur}$)}	
-						\If{\textsc{isSat}($v == expr$)} \algorithmiccomment{Check Satisfiablilty}
-							\Let{$S_{cur}$}{[$I_{cur}$, $\phi_{path} \wedge (v == expr)$, $\Delta$]}
-							\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
-						\Else 
-							%\Let{$S_{cur}$}{[$I_{cur}$, $\phi_{path} \wedge $(\textsc{false}), $\Delta$]}
-							\Let {$\phi_{path}$}{$\phi$} \algorithmiccomment{Infeasible Path}
-						\EndIf
-					\EndCase
 			\Case{\textbf{HALT}} \algorithmiccomment{Terminate Instruction}
@@
 
-	When a sampling statement, $\mathtt{x} \xleftarrow{\$} d$, is reached, a fresh probabilistic symbolic variable, $\delta$, is created, $\sigma$ is updated to be $\sigma[\mathtt{x}] = \delta$, and the original distribution $d$ is recorded in $P$ by setting $P[\delta] = d$.
-	%
-	Note that with the inclusion of probabilistic symbolic variables we can now either branch on universally quantified or probabilistic symbolic variables (or both).
+	\begin{paragraph}{Branches}
+		Note that with the inclusion of probabilistic symbolic variables we can now either branch on universal or probabilistic symbolic variables (or both).
 		% 
@@
 		% 
-	If $c_{sym}$ is a symbolic expression which represents the guard to a branch, and $c_{sym}$ does not contain any probabilistic symbolic variables, then we define the probability of taking the ``true'' branch is $[c_{sym}]$, and the probability of taking the ``false'' branch is $[\neg c_{sym}]$, where $[\cdot]$ are Iverson brackets.
+		If $c_{sym}$ is a symbolic expression which represents the guard to a branch, and $c_{sym}$ does not contain any probabilistic symbolic variables, then we define the probability of taking the ``true'' branch is $[c_{sym}]$, and the probability of taking the ``false'' branch is $[\neg c_{sym}]$, where $[Q] = 1$ if $Q$ is true, and 0 otherwise (known as Iverson brackets).
 
@@
 		% 
-	Without loss of generality, consider a branch of the form $\mathbf{if}~c~\mathbf{then}~P_1~\mathbf{else}~P_2$ where $c$ is a probabilistic branch.
+		Without loss of generality, consider a branch of the form $\mathbf{if}~c~\mathbf{then}~S_1~\mathbf{else}~S_2$ where $c$ is a probabilistic branch.
 		% 
@@
 		% 
-	Under this interpretation, we aim to compute $\Pr[c_{sym} \mid \varphi]$ where $\varphi$ is the current path condition formula.
+		Under this interpretation, we aim to compute the conditional probability $\Pr[c_{sym} \mid \varphi] = \frac{\Pr[c_{sym}\wedge \varphi]}{\Pr[\varphi]}$, where $\varphi$ is the current path condition formula.
 
-	% Add small example 
 		We use a form of model counting in order to compute $p_c$, the probability of $c$ being true.
@@
 		% 
-	We then count the number of \textit{assignments} from $\mathcal{D}$ which satisfy $c_{sym} \wedge \varphi$ and $\varphi$, and divide these two quantities as shown on line 5 of Alg.~\ref{alg:branch}.
+		We then count the number of elements (or \textit{assignments}) from $\mathcal{D}$ which satisfy $c_{sym} \wedge \varphi$ and $\varphi$, and divide these two quantities as shown on line 5 of Alg.~\ref{alg:branch}.
 		% 
-	In Section~\ref{sec:formalization} we have a proof of correctness for this quantity, but the intuition is by applying the definition of conditional probability.
+		Note that $p_c$ is not necessarily a value, but rather a symbolic expression containing constants and universal symbolic variables.
 		% 
-	Note that $p_c$ is not necessarily a value, but rather a symbolic expression containing constants and universally quantified symbolic variables.
+		Additionally, we exploit the fact that the sum of the conditional probabilities of the branch outcomes is 1, which allows us to avoid computing the probability of taking the ``false'' branch directly.
+	\end{paragraph}
+
+	\begin{figure}[h]
+		\centering
+		\begin{subfigure}{.3\textwidth}
+			\centering
+			{\small
+				\begin{algorithmic}[1]
+					\State{$\mathtt{x}\xleftarrow{\$}\mathrm{UniformInt}(1,3)$}
+					\State{$\mathtt{y}\xleftarrow{\$}\mathrm{UniformInt}(1,3)$}
+					\If{$\mathtt{x} > 1$}
+					\If{$\mathtt{x} < \mathtt{y}$}
+					\State\Return{$\mathtt{True}$}
+					\EndIf
+					\Else
+					\State\Return{$\mathtt{False}$}
+					\EndIf
+				\end{algorithmic}
+			}
+			\caption{Program}
+			\label{fig:exam_program}
+		\end{subfigure}
+		\begin{subfigure}{.69\textwidth}
+			\centering
+			{\small
+				\begin{forest}baseline,for tree=draw,
+					[{$\varphi=\top$},align=center, base=bottom
+					[{$\varphi = \delta_1 > 1$}, align=center, base=bottom, edge label={node [midway,above] {$\frac{2}{3}$} }
+					[{$\varphi = (\delta_1 > 1) \wedge (\delta_1 < \delta_2)$}, align=center, base=bottom, edge label={node [midway,above] {$\frac{1}{6}$} }
+					[{\texttt{True}}]]
+					[{$\varphi = (\delta_1 > 1) \wedge \neg(\delta_1 < \delta_2)$}, align=center, base=bottom, edge label={node [midway,above] {$\frac{5}{6}$} }
+					[{\texttt{False}}]]]
+					[{$\varphi = \neg(\delta_1 > 1)$}, align=center, base=bottom, edge label={node [midway,above] {$\frac{1}{3}$} }
+					[{\texttt{False}}]]]
+				\end{forest}
+			}
+			\caption{Execution Tree}
+			\label{fig:exam_tree}
+
+		\end{subfigure}
+		\caption{An example program and its symbolic execution tree}
+		\label{fig:example}
+	\end{figure}
+
+	\begin{paragraph}{Example}
+		Consider the code in Fig.~\ref{fig:exam_program} and suppose you wish to calculate the probability of the program returning \texttt{True}.
 		%
-	We exploit the fact that the sum of the conditional probabilities of the branch outcomes is 1, which allows us to avoid computing the probability of taking the ``false'' branch directly.
+		Following Alg.~\ref{alg:sample} for lines 1,2, we generate fresh probabilistic symbolic variables for $\mathtt{x}$ and $\mathtt{y}$, $\delta_1$ and $\delta_2$, respectively.
+		%
+		We also store the distributions which $\delta_1$ and $\delta_2$ are samples from, namely the discrete uniform distribution $\mathcal{U}\{1,3\}$.
+		%
+		In our notation, we say that $\sigma = \{ \mathtt{x} \mapsto \delta_1, \mathtt{y} \mapsto \delta_2 \}$ and $P = \{ \delta_1,\delta_2 \mapsto \mathcal{U}\{1,3\} \}$.
+		%
+		Now following Alg.~\ref{alg:branch} to process line 4 of Fig.~\ref{fig:exam_program}, note that $\mathcal{D} = \{1,2,3\} \times \{1,2,3\}$ and
+
+		\begin{align*}
+			p_c = \Pr[\delta_1 < \delta_2 \mid \delta_1 > 1] &= \frac{\Pr[(\delta_1 < \delta_2) \wedge (\delta_1 > 1)]}{\Pr[\delta_1 > 1]}\\
+			&= \frac{\displaystyle\sum_{(v_1,v_2) \in \mathcal{D}} [(\delta_1 < \delta_2) \wedge (\delta_1 > 1)\{\delta_1 \mapsto v_1, \delta_2 \mapsto v_2\}]}{\displaystyle\sum_{(v_1,v_2) \in \mathcal{D}} [(\delta_1 > 1)\{\delta_1 \mapsto v_1\}]}\\
+			&= \frac{1}{6}
+		\end{align*}
+	\end{paragraph}
+
+	\subsection{Query Generation}
+	\label{sec:query_gen}
+
+	At this point, we have an execution tree where each branch is annotated with the probability of taking the true and false branch.
+	%
+	From this tree we construct a set of paths which are represented by a path condition and set of probabilities.
+	%
+	If there are $n$ paths, and $\varphi_i$ is the $i^\text{th}$ path condition, and $p_{i_j}$ is the probability of the $j^{\text{th}}$ branch in the $i^{\text{th}}$ path, then we have $\{ (\varphi_1, \{p_{1_1},\ldots,p_{1_{k_1}}\}), \ldots, (\varphi_n, \{p_{n_1},\ldots,p_{n_{k_n}}\})\}$.
+	%
+	To calculate the probability of an entire path, or equivalently, the probability of a path condition, $\varphi$, being true, we can simply multiple each of the branch probabilities.
+	%
+	Recall that $p_{i_j}$ is the \textit{conditional} probability of the $j^{\text{th}}$ branch condition being true along path $i$.
+	%
+	Since $\varphi_i$ is the conjunction of each of the $k_i$ branch conditions, the probability of taking the entire path can be computed using the rule $\Pr[A \wedge B] = \Pr[A \mid B]\Pr[B]$ where $A$ and $B$ are any two events.
+	%
+	In other words, since $\varphi_i = c_{i_1} \wedge \cdots \wedge c_{i_{k_i}}$, then
+	\begin{align*}
+		\Pr[\varphi_i] &= \Pr[c_{i_1} \wedge \cdots \wedge c_{i_{k_i}}]\\
+		&= \Pr[c_{i_1} (c_{i_2} \wedge \cdots \wedge c_{i_{{k_i}-1}} \wedge c_{i_{k_i}})]\\
+		&= p_{i_1} \cdot \Pr[c_{i_2} \wedge \cdots \wedge c_{i_{k_i}}]\\
+		&\vdots\\
+		&= \displaystyle\prod_{j=1}^{k_i} p_{i_j}
+	\end{align*}
+
+	So, if we let $p_i = \prod_{j=1}^{k_i} p_{i_j}$, then we can simplify our set of paths to $\Phi = \{ (\varphi_1, p_1), \ldots, (\varphi_n, p_n)\}$.
+
+	In our interpretation, the ultimate goal of probabilistic symbolic execution is to verify properties of probabilistic programs.
+	%
+	In a probabilistic setting this often equates to either proving the upper bound of reaching some ``bad'' state, or proving the lower bound of reaching some ``good'' state.
+	%
+	We achieve this through queries to an SMT solver, such as Z3~\cite{demoura2008}.
+	%
+	There are three components to our queries: 1) a universal quantification over the universal symbolic variables, 2) a filtering condition specifying what a ``good'' or ``bad'' state is, and 3) a desired upper/lower bound, potentially parameterized by universal symbolic variables.
+	%
+	\begin{enumerate}
+		\item If a program has $m$ universal symbolic variables, $\alpha_1,\ldots,\alpha_m$, we begin the query with a universal quantification, $\forall \alpha_1,\ldots,\alpha_m$, in order to reason over any setting of the non-probabilistic program variables.
+		\item A \textit{filtering condition}, $\psi$, is a predicate which determines whether a path is considered ``bad'' or ``good'', depending on the property.
+		% 
+		Some example conditions are whether: a certain value is returned, a false positive (or negative) occurred, or a hash collision occurred.
+		% 
+		Out of all the paths, $\Phi$, we keep only those which satisfy $\psi$, $\Phi'$.
+		% 
+		We then sum over all of the paths in $\Phi'$, giving us the probability of $\psi$ occuring in program $S$:
+		\[
+		\sum_{(\varphi,p) \in \Phi'} [\varphi]\cdot p.
+		\]
+		Note that the probability expression $p$ is multiplied by $[\varphi]$, as during some settings of $\alpha_1,\ldots,\alpha_m$, the path represented by $\varphi$ might not be reachable, and so we should exclude that probability from the sum.
+		% 
+		The inclusion of the Iverson brackets achieves this desired behavior.
+		\item Let $\delta$ (???) be the lower/upper bound \textit{expression} which we want to prove the $S$ does not violate.
+	\end{enumerate}
+	A general query then takes the form of
+	\[
+	\forall \alpha_1,\ldots,\alpha_m . \displaystyle \delta \sim \sum_{(\varphi,p) \in \Phi'} [\varphi]\cdot p 
+	\]
+	where $\sim$ is a binary relation (e.g. $>,<,\leq,\geq$).
+
+	{\color{blue} \textbf{TODO: Finish up once the overview section is done}\\\\
+		For example, in the Monty Hall problem as described in Section~\ref{sec:motiv_example}, we were only concerned with those paths that resulted in the contestant winning the car.
+		%
+		So, we would filter on $\psi := win = true$, restricting the set of paths to be (TODO: Add on more after writing section 2).
+		%
+		The probability of this occuring is then ... as ...
+	}
 
@@
 	\begin{itemize}
-		\item Let $Vars$ be the set of all program variables, $ForallSymVars$ be the set of all universally quantified symbolic variables, $ProbSymVars$ be the set of all probabilistic symbolic variables, $SymVars = ForallSymVars \cup ProbSymVars$ be the combined set of all symbolic variables, and $Vals$ be the set of all values.
-		\item Let $a_f: ForallSymVars \rightarrow Vals$ be an assignment of universally quantified symbolic variables to values and let $ForallAssign$ be the set of all such assignments.
+		\item Let $Vars$ be the set of all program variables, $ForallSymVars$ be the set of all universal symbolic variables, $ProbSymVars$ be the set of all probabilistic symbolic variables, $SymVars = ForallSymVars \cup ProbSymVars$ be the combined set of all symbolic variables, and $Vals$ be the set of all values.
+		\item Let $a_f: ForallSymVars \rightarrow Vals$ be an assignment of universal symbolic variables to values and let $ForallAssign$ be the set of all such assignments.
 		\item Similarly, let $a_p : ProbSymVars \rightarrow Vals$ be an assignment of probabilistic symbolic variables to values and let $ProbAssign$ be the set of all such assignments.
@@
 		\item Let $de : Mems \rightarrow (Vals \rightarrow [0,1])$ be a distribution expression parameterized by program memories, and let $DistExprs$ be the set of all distribution expressions.
-		\item Let $d : ForallAssign \times Mems \rightarrow [0,1]$ be a distribution of program memories parameterized by assignments to universally quantified symbolic variables and let $MemDists$ be the set of all parameterized distributions of program memories.
+		\item Let $d : ForallAssign \times Mems \rightarrow [0,1]$ be a distribution of program memories parameterized by assignments to universal symbolic variables and let $MemDists$ be the set of all parameterized distributions of program memories.
 	\end{itemize}
@@
 	\label{sec:case_studies}
+	In this section we will briefly explain each of the case studies that we use in our evaluation (Section~\ref{sec:eval}).
+	% 
+	For each case study, we will explain, (1) what the algorithm does, (2) which variables are concretized, universally quantified, and probabilistic, and (3) the property we aim to verify using our technique.
+	%
+	Note that we frame the queries as an existential query and hope to get ``UNSAT'' in order to reason over all the possible values for the universal symbolic variables.
+
+	\subsection{Freivalds' Algorithm}
+	\label{sec:freivalds}
+
+	Freivalds' algorithm~\cite{freivalds1977} is a randomized algorithm used to verify matrix multiplication in $\mathcal{O}(n^2)$ time.
+	%
+	Given three $n \times n$ matrices $A,B$, and $C$, Freivalds' algorithm checks whether $A \times B = C$ by generating a random $n \times 1$ vector containing 0s and 1s, $\vec{r}$ and checks whether $A \times (B\vec{r}) - C\vec{r} = (0,\ldots,0)^T$.
+	%
+	If so, the algorithm outputs ``Yes'', and ``No'' otherwise.
+	%
+	However, if $A \times B \neq C$, the probability that the algorithm returns ``Yes'' is at most $\frac{1}{2}$.
+
+	While the size of the matrices has to be concretized, the elements of the three matrices can be represented by universal symbolic variables and the elements of $r$ as probabilistic symbolic variables.
+	%
+	We want to verify the false positive error rate of $\frac{1}{2}$.
+	%
+	To do this, we can ask Z3, for a fixed $n$, whether there exist any $n \times n$ matrices $A,B$, and $C$ where $A \times B \neq C$ such that
+	\[
+	\Pr[\mathtt{freivalds}(A,B,C) = \text{Yes}] > \frac{1}{2}.
+	\]
+
+	\subsection{Randomized Response}
+	\label{sec:randomized_response}
+
+	Randomized response is a surveying technique which allows respondents to answer in a way that provides ``plausible deniability''
+	%
+	Before answering the query, a coin is flipped.
+	%
+	If ``tails'', then the respondent answers truthfully, if ``heads'', a second coin is flipped and the respondent answers ``Yes'' if ``heads'' and ``No'' if tails.
+	%
+	In fact, this method is $(\ln 3, 0)$-differentially private.
+
+	The answer the respondent would give if they answered truthfully can be represented with a universal symbolic variable, and the results of the two coin flips as probabilistic symbolic variables.
+	%
+	With this model, we can prove $(\ln 3, 0)$ differential privacy by asking our method if there exists a setting of the ``truth'' such that
+	\[
+	\frac{\Pr[\text{Response} = \text{Yes} \mid \mathtt{text} = \text{Yes}]}{\Pr[\text{Response} = \text{Yes} \mid \mathtt{text} = \text{No}]} \neq 3
+	\]
+	and
+	\[
+	\frac{\Pr[\text{Response} = \text{No} \mid \mathtt{text} = \text{No}]}{\Pr[\text{Response} = \text{No} \mid \mathtt{text} = \text{Yes}]} \neq 3.
+	\]
+
+	\subsection{Reservoir Sampling}
+	\label{sec:reservoir_sampling}
+
+	\begin{algorithm}
+		\caption{Reservoir Sampling}
+		\label{alg:reservoir_sampling}
+		\begin{algorithmic}[1]
+			\Function{ReservoirSampling}{$A[1..n], S[1..k]$}
+			\For{$i=1 \text{ to } k$}
+			\Let{$S[i]$}{$A[i]$}
+			\EndFor
+			\For{$i=k+1\text{ to }n$}
+			\Let{$j$}{$\mathrm{UniformInt}(1,i)$}
+			\If{$j <= k$}
+			\Let{$S[j]$}{$A[i]$}
+			\EndIf
+			\EndFor
+			\State\Return{$S$}
+			\EndFunction
+		\end{algorithmic}
+	\end{algorithm}
+
+	Reservoir sampling is an online, randomized algorithm to get a simple random sample of $k$ elements from a population of $n$ elements.
+	%
+	It uses uniform integer samples to maintain a set of $k$ elements drawn from the set of $n$ elements.
+	%
+	For the full algorithm, see Alg.~\ref{alg:reservoir_sampling}.
+
+	The sizes of both the population, $n$, and the sample, $k$, need to be concretized.
+	%
+	The elements from $A$, are universal symbolic variables, and each sample, $j$, are probabilistic symbolic variables.
+	%
+	The property that we want to check is whether each sample has an equal probability of being returned by Alg.~\ref{alg:reservoir_sampling}, namely $\frac{1}{\binom{n}{k}}$.
+
+	\subsection{Schwartz-Zippel Lemma}
+	\label{sec:schwartz-zippel}
+
+	The Schwartz-Zippel lemma is a probabilistic method of polynomial identity testing, that is, the problem of determining whether a given multivariate polynomial is identially equal to 0 or not.
+	%
+	Given a non-zero polynomial of total degree $d$, $P$, over a field $F$, and $r_1,\ldots,r_n$ selected at random from a subset of $F$, say $S$, then the lemma states that
+	\[
+	\Pr[P(r_1,\ldots,r_n) = 0] \leq \frac{d}{\abs{S}}.
+	\]
+
+	The number of terms in $P$, $n$, has to be concretized, the degrees of each of the terms, and the size of the subset $S$ all need to be concretized.
+	%
+	The coefficients are represented as universal symbolic variables and $r_1,\ldots,r_n$ are probabilistic symbolic variables.
+	%
+	The property that we want to check is whether there exists a non-zero polynomial, $P$, such that
+	\[
+	\Pr[P(r_1,\ldots,r_n) = 0] > \frac{d}{\abs{S}}.
+	\]
+
+	\subsection{Bloom Filter}
+	\label{sec:bloom_filter}
+
+	A Bloom filter is a space-efficient, probabilistic data structure used to rapidly determine whether an element is in a set.
+	%
+	A Bloom filter is a bit-array of $n$ bits and $k$ associated hash functions, each of which maps elements in the set to places in the bit-array.
+	%
+	To insert an element, $x$, into the filter, $x$ is hashed using each of the $k$ hash functions to get $k$ array positions.
+	%
+	All of the bits at these positions are set to 1.
+	%
+	To check whether an element $y$ is in the filter, $y$ is again hashed by each of the hash functions to get $k$ array positions.
+	%
+	The bits at each of these positions are checked and the filter reports that $y$ is in the filter if, and only if, each of the bits are set to 1.
+	%
+	Note that false positives are possible due to hash collisions, but false negatives are not.
+
+	In order to bound the false positive error rate, most implementations of Bloom filters take in the expected number of elements to be inserted as well as the desired false positive error rate.
+	%
+	From these two quantities, the optimal size of the bit-array, $n$, as well as the number of hash functions, $k$ can be computed.
+	%
+	If $m$ is the expected number of elements and $\varepsilon$ is the desired error rate, then
+	\begin{align*}
+		n &= - \frac{m\ln \varepsilon}{(\ln 2)^2}\\
+		k &= - \frac{\ln \varepsilon}{\ln 2}
+	\end{align*}
+	%
+	We want to prove that for a given $m$ and $\varepsilon$ that the actual false positive rate does not exceed $\varepsilon$.
+
+	With our method, $m$ and $\varepsilon$ first need to be concretized. 
+	%
+	Then, we insert $m$ elements $x_i$, where each $x_i$ can be represented using a universal symbolic variable.
+	%
+	We model each of the $k$ uniform hash functions using the method described in Sec. (TODO: Insert bit about hash functions).
+	%
+	We then want to check if there exist $x_1,\ldots,x_m$ such that the false positive rate exceeds $\varepsilon$.
+
+	\subsection{Quicksort}
+	\label{sec:quicksort}
+
+	Quicksort is a popular sorting algorithm which uses partitioning in order to achieve efficient sorting.
+	%
+	One way to choose a pivot element is by way of a uniform random sample.
+	%
+	Using this pivot method, the expected number of pivots required is $1.386 n \log_2(n)$ where $n$ is the length of the array.
+	%
+	If we concretize the length of the array, but represent the elements as universal symbolic variables, we can compute the expected number of pivots required to sort the array.
 
@@
 	{\color{red} Subhajit \& Sumit: If you could both start looking into related work (Mayhap, original PSE paper, Axprof, P4WN, PSI), that would be great!}
-	\begin{itemize}
-		\item Compare and Contrast with Mayhap, PSE, AxProf, P4WN \& PSI.
-		\item Explain how we differ by not using Model Counting but a Constraint Solving approach.
-		\item Support for \textsc{ForAll} variables along with \textit{probabilistic} variables. 
-	\end{itemize}
 	\section{Conclusion \& Future Work}
@@
 	%% Bibliography
-	%\bibliography{bibfile}
+	\bibliography{main}
 

### 2021-06-25 baseline-exp/src/bloomfilter.cpp

@@ -202,6 +202,7 @@ int main() {
     bloom_init(&bloom, entries, error);
     bloom_add(&bloom, inputs[add_item]);
 
+    // Different Elem.
     if (bloom_check(&bloom, inputs[search_item])) {
       // klee_dump_kquery_state();
       win++;

### 2021-06-25 baseline-exp/src/countminsketch.cpp

@@ -146,7 +146,7 @@ unsigned int CountMinSketch::hashstr(const char *str) {
 int main() {
 
   std::default_random_engine generator;
-  std::uniform_int_distribution<int> dataRange(-15000, 15000);
+  std::uniform_int_distribution<int> dataRange(INT32_MIN, INT32_MAX);
   std::uniform_real_distribution<float> ep_range(0.01, 1);
   std::uniform_real_distribution<float> gamm_range(0, 1);
 
@@ -157,20 +157,21 @@ int main() {
   scanf("%d", &termCount);
 
   while (termCount--) {
-    // CountMinSketch c(0.01, 0.1);
-    float ep = ep_range(generator);
-    float gamm = gamm_range(generator);
-    CountMinSketch c(ep, gamm);
 
-    c.update(dataSet[0].c_str(), 1);
+    // Try with concrete values as of now.
+    // We can try with Foralls later.
+    CountMinSketch c(0.01, 0.1);
+    // float ep = ep_range(generator);
+    // float gamm = gamm_range(generator);
+    // CountMinSketch c(ep, gamm);
+
+    c.update(dataSet[0].c_str(), 1); // Update number Could be foralls.
     c.update(dataRange(generator), 2);
     c.update(dataSet[0].c_str(), 1);
 
     auto ret = c.estimate(dataSet[0].c_str());
     if (ret != 2) {
       // klee_dump_kquery_state();
-      std::cout << "Estimate : " << ret << ", ep : " << ep
-                << ", gamma : " << gamm << "\n";
       win++;
     }
     loop_count++;

### 2021-06-25 baseline-exp/src/freivalds.cpp

@@ -93,12 +93,15 @@ int main() {
     unsigned char realC[n * n];
     matmul(A, B, n, realC);
 
+    // realC[] & C[] must not be
+    // identiaclly same.
     bool orAssume = false;
     for (size_t i = 0; i < n * n; i++) {
       orAssume = orAssume || (C[i] != realC[i]);
     }
 
-    // TODO : How to encode this assume?
+    // This is a condition that must hold.
+    // Need to check which ones hold.
     // klee_assume(orAssume);
     // klee_assume(C[0] != realC[0]);
 

### 2021-06-25 baseline-exp/src/freivalds_multiple.cpp

@@ -93,11 +93,15 @@ int main() {
     unsigned char realC[n * n];
     matmul(A, B, n, realC);
 
+    // realC[] & C[] must not be
+    // identiaclly same.
     bool orAssume = false;
     for (size_t i = 0; i < n * n; i++) {
       orAssume = orAssume || (C[i] != realC[i]);
     }
 
+    // This is a condition that must hold.
+    // Need to check which ones hold.
     // klee_assume(orAssume);
     // klee_assume(C[0] != realC[0]);
 

### 2021-06-25 baseline-exp/src/init.cpp

@@ -1,9 +1,16 @@
 #include <cstdio>
+#include <deque>
 #include <init.h>
 #include <iostream>
+#include <json.hpp>
+#include <list>
 #include <string>
 #include <unordered_map>
+#include <unordered_set>
 #include <vector>
+
+using json = nlohmann::json;
+// https://github.com/nlohmann/json#conversion-from-stl-containers
 
 int main() {
   /**
@@ -13,10 +20,36 @@ int main() {
   int termCount = 0, win = 0, loop_count = 0;
   scanf("%d", &termCount);
 
+  std::vector<int> c_vector{1, 2, 3, 4};
+  json j_vec(c_vector);
+  // [1, 2, 3, 4]
+
+  std::deque<double> c_deque{1.2, 2.3, 3.4, 5.6};
+  json j_deque(c_deque);
+  // [1.2, 2.3, 3.4, 5.6]
+
+  std::unordered_set<std::string> c_uset{"one", "two", "three", "four", "one"};
+  json j_uset(c_uset); // only one entry for "one" is used
+  // maybe ["two", "three", "four", "one"]
+
+  std::unordered_multiset<std::string> c_umset{"one", "two", "one", "four"};
+  json j_umset(c_umset); // both entries for "one" are used
+                         // maybe ["one", "two", "one", "four"]
+
+  std::multimap<std::string, bool> c_mmap{
+      {"one", true}, {"two", true}, {"three", false}, {"three", true}};
+  json j_mmap(c_mmap); // only one entry for key "three" is used
+  // maybe {"one": true, "two": true, "three": true}
+
+  std::unordered_multimap<std::string, bool> c_ummap{
+      {"one", true}, {"two", true}, {"three", false}, {"three", true}};
+  json j_ummap(c_ummap); // only one entry for key "three" is used
+                         // maybe {"one": true, "two": true, "three": true}
+
   while (termCount--) {
-    std::string str = "";
-    std::getline(std::cin, str);
-    std::cout << str << "\n";
+    std::cout << j_uset << "\n";
+    std::cout << j_ummap << "\n";
+    std::cout << j_mmap << "\n";
   }
 
   return 0;

### 2021-06-25 baseline-exp/src/montyhall.cpp

@@ -6,10 +6,10 @@
 #include <vector>
 
 int montyhall(int choice, int door_switch) {
-  int car_door;
+  // PSE Symbolic Variable.
   std::default_random_engine generator;
   std::uniform_int_distribution<int> value_dist(1, 3);
-  car_door = value_dist(generator);
+  int car_door = value_dist(generator);
   // make_pse_symbolic(&car_door, sizeof(car_door), "car_door_sym", 1, 3);
 
   if (choice == car_door) {
@@ -60,11 +60,14 @@ int main() {
     srand(time(0));
     std::default_random_engine generator;
     std::uniform_int_distribution<int> value_dist(1, 3);
+
+    // Forall
     choice = value_dist(generator);
     // klee_make_symbolic(&choice, sizeof(choice), "choice_sym");
     // klee_assume(1 <= choice);
     // klee_assume(choice <= 3);
 
+    // Forall
     door_switch = rand() > 1500 ? 0 : 1;
     // klee_make_symbolic(&door_switch, sizeof(door_switch), "door_switch_sym");
     // klee_assume(0 <= door_switch);

### 2021-06-25 baseline-exp/src/partition.cpp

@@ -31,6 +31,7 @@ int partition(unsigned int arr[], int left, int right) {
     }
   }
 
+  // E[outcome]
   outcome = left_count < (right_count - 1) ? (right_count - 1) : left_count;
 
   // klee_dump_kquery_state();

### 2021-06-25 baseline-exp/src/quicksort.cpp

@@ -29,11 +29,18 @@ int partition(unsigned char arr[], int p, int r, size_t *num_comps) {
 }
 
 int randomized_partition(unsigned char arr[], int p, int r, size_t *num_comps) {
-  int i;
-  auto name = "i" + to_string(p) + to_string(r);
   // printf("%s\n", name.c_str());
   // uniform_int_sample(&i, sizeof(i), name.c_str(), (int) p, (int) r, fp);
   // make_pse_symbolic(&i, sizeof(i), name.c_str(), (int)p, (int)r);
+
+  // PSE Symbolic Variable.
+  std::default_random_engine generator;
+  std::uniform_int_distribution<int> dataRange(INT32_MIN, INT32_MAX);
+  int i = dataRange(generator);
+
+  auto name = "i" + to_string(p) + to_string(r);
+  // Choose between p and r.
+
   swap(&arr[i], &arr[r]);
   return partition(arr, p, r, num_comps);
 }
@@ -56,7 +63,7 @@ int main() {
     unsigned char arr[N];
     // klee_make_symbolic(&arr, sizeof(arr), "arr");
     std::default_random_engine generator;
-    std::uniform_int_distribution<char> char_dist(0, 255);
+    std::uniform_int_distribution<int> char_dist(0, 255);
 
     for (auto i = 0; i < N; i++)
       arr[i] = char_dist(generator);

### 2021-06-25 baseline-exp/src/reservoir_sampling_syminput.cpp

@@ -24,6 +24,8 @@ int main() {
   scanf("%d", &termCount);
 
   while (termCount--) {
+
+    // Could also be a forall.
     int n = 4;
     int arr[n];
 

### 2021-06-25 baseline-exp/src/schwartz_zippel.cpp

@@ -24,6 +24,8 @@ int main() {
   scanf("%d", &termCount);
 
   while (termCount--) {
+
+    // Could also be a forall.
     size_t n = 3;
     unsigned char poly[n];
 
@@ -51,7 +53,7 @@ int main() {
 
     unsigned char d[] = {1, 1, 1};
     auto ret = schwartz_zippel(poly, r, d, n);
-    if (ret) {
+    if (ret != 0) {
       // klee_dump_kquery_state();
       win++;
     }

### 2021-06-25 baseline-exp/src/skiplist.cpp

@@ -167,11 +167,19 @@ void sl_unset(sl_entry *head, int key) {
   }
 }
 
+/**
+ * @brief Try this example out.
+ * Could add to paper.
+ *
+ * @return int
+ */
 int main() {
   int termCount = 0, win = 0, loop_count = 0;
   scanf("%d", &termCount);
 
-  while (termCount--) { // Create a list
+  while (termCount--) {
+
+    // Create a list
     std::default_random_engine generator;
     std::uniform_int_distribution<int> random_range(INT32_MIN, INT32_MAX);
 
@@ -203,6 +211,7 @@ int main() {
     // klee_dump_kquery_state();
     // klee_dump_symbolic_details(&cost, "cost");
 
+    // E[cost]
     if (cost > 0) {
       win++;
       std::cout << "cost : " << cost << "\n";

### 2021-06-25 baseline-exp/src/zp_hash.cpp

@@ -8,6 +8,8 @@ int main() {
   scanf("%d", &termCount);
 
   while (termCount--) {
+
+    // Could be a forall. Must be a large prime.
     int prime = 3;
 
     std::default_random_engine generator;

### 2021-06-30 shared/Paper-Draft/PSE-POPL-2021.tex
WIP : SymbEx Section (B)

@@
 \usepackage{mathtools}
-\usepackage{algpseudocode,algorithm,algorithmicx}
+\usepackage[noend]{algpseudocode}
+\usepackage{algorithm}
 \usepackage{forest}
@@
 \usepackage{multicol}
+\usepackage{xcolor}
+
+%%% Colors %%%
+\definecolor{darkgreen}{RGB}{0,128,0}
 
@@
 \newcommand*\Let[2]{\State #1 $\gets$ #2}
+\newcommand*\cLet[3]{\State\ColorLine{#3} #1 $\gets$ #2}
 \newcommand*\dom[1]{\mathrm{dom}\left( #1 \right)}
-
 % For the Case statements
@@
 \algtext*{EndCase}%
+
+% Highlight lines in algorithm environment
+\makeatletter
+% code borrowed from Andrew Stacey; See
+% https://tex.stackexchange.com/a/50054/3954
+\tikzset{%
+	remember picture with id/.style={%
+		remember picture,
+		overlay,
+		save picture id=#1,
+	},
+	save picture id/.code={%
+		\edef\pgf@temp{#1}%
+		\immediate\write\pgfutil@auxout{%
+			\noexpand\savepointas{\pgf@temp}{\pgfpictureid}}%
+	},
+	if picture id/.code args={#1#2#3}{%
+		\@ifundefined{save@pt@#1}{%
+			\pgfkeysalso{#3}%
+		}{
+			\pgfkeysalso{#2}%
+		}
+	}
+}
+
+\def\savepointas#1#2{%
+	\expandafter\gdef\csname save@pt@#1\endcsname{#2}%
+}
+
+\def\tmk@labeldef#1,#2\@nil{%
+	\def\tmk@label{#1}%
+	\def\tmk@def{#2}%
+}
+
+\tikzdeclarecoordinatesystem{pic}{%
+	\pgfutil@in@,{#1}%
+	\ifpgfutil@in@%
+	\tmk@labeldef#1\@nil
+	\else
+	\tmk@labeldef#1,(0pt,0pt)\@nil
+	\fi
+	\@ifundefined{save@pt@\tmk@label}{%
+		\tikz@scan@one@point\pgfutil@firstofone\tmk@def
+	}{%
+		\pgfsys@getposition{\csname save@pt@\tmk@label\endcsname}\save@orig@pic%
+		\pgfsys@getposition{\pgfpictureid}\save@this@pic%
+		\pgf@process{\pgfpointorigin\save@this@pic}%
+		\pgf@xa=\pgf@x
+		\pgf@ya=\pgf@y
+		\pgf@process{\pgfpointorigin\save@orig@pic}%
+		\advance\pgf@x by -\pgf@xa
+		\advance\pgf@y by -\pgf@ya
+	}%
+}
+
+\makeatother
+% end of Andrew's code
+
+% main command to draw the colored background
+\newcounter{mymark}
+\newcommand\ColorLine[1]{%
+	\stepcounter{mymark}%
+	\tikz[remember picture with id=mark-\themymark,overlay] {;}%
+	\begin{tikzpicture}[remember picture,overlay]%
+		\filldraw[#1]%
+		let \p1=(pic cs:mark-\themymark), 
+		\p2=(current page.east)  in 
+		([xshift=-0.3em,yshift=-0.7ex]0,\y1)  rectangle ++([xshift=-1.2cm]\x2,\baselineskip);
+	\end{tikzpicture}%
+}%
+
+% colored loops and declarations
+\makeatletter
+\algnewcommand\cRequire[1]{\item[\ColorLine{#1}\algorithmicrequire]}%
+\algnewcommand\cEnsure[1]{\item[\ColorLine{#1}\algorithmicensure]}%
+\algnewcommand\cState[1]{\State\ColorLine{#1}}%
+\algnewcommand\cStatex[1]{\Statex\ColorLine{#1}}%
+\algnewcommand\cComment[1]{\Comment\ColorLine{#1}}%
+
+\algdef{SE}[WHILE]{cWhile}{ENDWHILE}%
+[2]{\ColorLine{#2}\algorithmicwhile\ #1\ \algorithmicdo}%
+{\algorithmicend\ \algorithmicwhile}%
+\algdef{SE}[FOR]{cFor}{ENDFOR}%
+[2]{\ColorLine{#2}\algorithmicfor\ #1\ \algorithmicdo}%
+{\algorithmicend\ \algorithmicfor}%
+\algdef{S}[FOR]{cForAll}%
+[2]{\ColorLine{#2}\algorithmicforall\ #1\ \algorithmicdo}%
+\algdef{SE}[LOOP]{cLoop}{ENDLOOP}%
+[1]{\ColorLine{#1}\algorithmicloop}%
+{\algorithmicend\ \algorithmicloop}%
+\algdef{SE}[REPEAT]{cRepeat}{UNTIL}%
+[1]{\ColorLine{#1}\algorithmicrepeat}%
+[1]{\algorithmicuntil\ #1}%
+\algdef{SE}[IF]{cIf}{ENDIF}%
+[2]{\ColorLine{#2}\algorithmicif\ #1\ \algorithmicthen}%
+{\algorithmicend\ \algorithmicif}%
+\algdef{C}[IF]{IF}{cElsif}%
+[2]{\ColorLine{#2}\algorithmicelse\ \algorithmicif\ #1\ \algorithmicthen}%
+\algdef{Ce}[ELSE]{IF}{cElse}{ENDIF}%
+[1]{\ColorLine{#1}\algorithmicelse}%
+\algdef{SE}[SWITCH]{cSwitch}{EndSwitch}%
+[2]{\ColorLine{#2}\algorithmicswitch\ #1\ \algorithmicdo}%
+{\algorithmicend\ \algorithmicswitch}%
+\algdef{SE}[CASE]{cCase}{EndCase}%
+[2]{\ColorLine{#2}\algorithmiccase\ #1}%
+{\algorithmicend\ \algorithmiccase}%
+\makeatother
 
@@
 	\end{displayquote}
-	While it may seem unintuitive, regardless of the contestant's original door choice, the contestant who always switches doors will win the car $\frac{2}{3}$ of the time, as opposed to a $\frac{1}{3}$ chance.
+	While it may seem unintuitive, regardless of the contestant's original door choice, the contestant who always switches doors will win the car $\frac{2}{3}$ of the time, as opposed to a $\frac{1}{3}$ chance if the contestant sticks with their original choice.
 
 	\begin{figure}\centering
-		\begin{multicols}{2}
 		\inputminted[fontsize=\footnotesize,linenos]{c}{montyhall.c}
-		\end{multicols}
 		\caption{C code for the Monty Hall Problem}
@@
 
-	We can represent this problem as a probabilistic program, as shown in Fig.~\ref{fig:montyhall}, where $\mathtt{choice} \in [1,3]$ and is the door which is originally chosen by the contestant and $\mathtt{door\_switch}$ is \texttt{true} if the contestant wants to switch doors when asked, and \texttt{false} otherwise.
+	We can represent this problem as a probabilistic program, as shown in Fig.~\ref{fig:montyhall}, where $\mathtt{choice} \in [1,3]$ is the door which is originally chosen by the contestant and $\mathtt{door\_switch}$ is \texttt{true} if the contestant wants to switch doors when asked, and \texttt{false} otherwise.
 	%
-	Supposedly if $\mathtt{door\_switch} = \mathtt{true}$, regardless of the value of \texttt{choice}, \texttt{monty\_hall} should return \texttt{true} (i.e. the car is won) $\frac{2}{3}$ of the time.
+	If $\mathtt{door\_switch} = \mathtt{true}$, regardless of the value of \texttt{choice}, \texttt{monty\_hall} should return \texttt{true} (i.e. the car is won) $\frac{2}{3}$ of the time.
 	%
-	The problem thus becomes, given a probabilistic program with discrete sampling statements, and a program property, how do we verify that the program satisfies the property?
+	In general, the problem we aim to solve is: given a probabilistic program with discrete sampling statements, and a program property, how do we verify that the program satisfies the property?
 
-	One typical solution would be to run a simulation on random inputs and compute the probability of winning if $\mathtt{door\_switch} = \mathtt{true}$, and the probability of winning if $\mathtt{door\_switch} = \mathtt{false}$.
+	% One typical solution would be to run a simulation on random inputs and compute the probability of winning if $\mathtt{door\_switch} = \mathtt{true}$, and the probability of winning if $\mathtt{door\_switch} = \mathtt{false}$.
+	% %
+	% While for this program this would work as the input space is tiny, the resulting output distributions would be absent any formal guarantees and only be an approximation.
+	% %
+	% We instead develop a novel symbolic execution technique to provide a sound guarantee on the probability of certain events occurring.
+
+	In symbolic execution, program inputs are replaced by \textit{symbolic} variables which can take on any value.
 	%
-	While for this program this would work as the input space is tiny, the resulting output distributions would be absent any formal guarantees and only be an approximation.
+	The program is then ``run'' on these symbolic variables and when a branch is reached execution proceeds along each of these two branches and the constraint is recorded in that path's, \textit{path condition}, which is represented by $\varphi$.
+	%
+	This yields an execution tree which shows us possible paths through the program.
 
-	% 1) What is the problem? Given a program, and a property we wish to check, how do we prove that property?
-	% - Introduce the program and the property
-	% 2) Given a program, how do we generate the tree with probabilities?
-	% 3) Given a tree, how do we make queries against the tree to actually verify the property?
+	\begin{figure}
+		\label{fig:montyhall_tree}
+		\centering
+		{\footnotesize
+			\begin{forest}baseline,for tree=draw,
+				[{$\mathtt{1}: c_0=\top$},align=center, base=bottom
+				[{$\mathtt{4}: c_1 = \alpha = 1$},align=center, base=bottom
+				[{$\mathtt{5}: c_2 = \beta$},align=center, base=bottom, node options={dotted,thick}, draw=red] %loss
+				[{$\mathtt{5}: c_2 = \neg\beta$},align=center, base=bottom, node options={dashed}, draw=darkgreen]] %win
+				[{$\mathtt{4}: c_1 = \alpha \neq 1$},align=center, base=bottom
+				[{$\mathtt{10}: c_2 = \alpha \neq 2$},align=center, base=bottom
+				[{$\mathtt{12}: c_3 = \beta$},align=center, base=bottom, node options={dashed}, draw=darkgreen ] % win
+				[{$\mathtt{12}: c_3 = \neg\beta$},align=center, base=bottom, node options={dotted,thick}, draw=red]] % loss
+				[{$\mathtt{10}: c_2 = \alpha = 2$},align=center, base=bottom
+				[{$\mathtt{12}: c_3 = \beta$},align=center, base=bottom, node options={dashed}, draw=darkgreen ] % win
+				[{$\mathtt{12}: c_3 = \neg\beta$},align=center, base=bottom, node options={dotted,thick}, draw=red ]]]] % loss
+			\end{forest}
+		}
+		\caption{Execution Tree for the Monty Hall Problem if the car is behind door 1.}
+	\end{figure}
+
+	Suppose we were to run traditional symbolic execution on the program in Fig~\ref{fig:montyhall} where the car was randomly chosen to be behind door 1.
+	%
+	The two inputs, \texttt{choice} and \texttt{door\_switch}, would become the symbolic variables $\alpha$ and $\beta$, respectively.
+	%
+	The execution tree is shown in Fig.~\ref{fig:montyhall_tree}.
+	%
+	For each node in the tree the line number of the branch statement and the path condition is given.
+	%
+	Leaves which are surrounded by a dashed (\tikz{\draw[dashed,line width=1pt] (0,0) -- (0.35,0) }), {\color{darkgreen} green} line represent the contestant winning the car (the function returning \texttt{true}), and those leaves which are surrounded by a dotted (\tikz{\draw[dotted,thick,line width=1pt] (0,0) -- (0.35,0) }), {\color{red} red} line represent the contestant losing the contest (the function returning \texttt{false}).
+	%
+	Symmetric trees can be made for the cases when the car is behind door 2 and door 3.
+
+	While this tree can tell us that it is \textit{possible} to win (or lose) the car with any choice of initial door and decision to switch, it does not tell us how \textit{often} a contestant will for any initial door and decision to switch.
+	%
+	In theory, if we knew how likely it was to take one branch over another we could extend this reasoning to determine how often we would hit a winning leaf over a losing leaf.
+	%
+	\textbf{Our core idea is to represent probabilistic sampling statements also as symbolic variables.}
+	%
+	For the sake of presentation we refer to these as \textit{probabilistic} symbolic variables as opposed to, what we call, \textit{universal} symbolic variables which range over all possible values.
+	%
+	So, instead of asking for a random value, we replace the result of the sample with a probabilistic symbolic variable and record the distribution from which the sample is from.
+	%
+	We then are able to interpret a branch on a probabilistic symbolic variable as a conditioning operation on the originating distribution.
+
+	Now let us return to the Monty Hall problem from Fig.~\ref{fig:montyhall}.
+	%
+	Let \texttt{car\_door} be represented by the probabilistic symbolic variable, $\delta$ and let \texttt{choice} and \texttt{door\_switch} be $\alpha$ and $\beta$, respectively, as before.
+	%
+	Instead of branching solely on $\alpha$ and $\beta$, we additionally branch on $\delta$.
+	%
+	The execution tree is presented in Fig.~\ref{fig:montyhall_tree_prob}.
+	%
+	Note that branches are omitted from the tree if which direction to traverse can be inferred by the current path condition.
+
+	Since probabilistic symbolic variables originate from a distribution, we can determine the \textit{probability} of taking a certain branch by simply counting how many values from the distribution satisfy the guard condition.
+	%
+	For example, to figure out the probability of taking the \texttt{true} branch of the \texttt{if} condition on line 4 (denoted by \textbf{T} in Fig.~\ref{montyhall_tree_prob}), it suffices to count how many settings of $\delta$ satisfy $\alpha = \delta$ and divide by the total number of possible assignments to $\delta$ (i.e.
+3).
+	%
+	However, since $\alpha$ is a symbolic variable we can only obtain a probability expression which is in terms of universal symbolic variables.
+	%
+	Let $[\cdot]$ denote Iverson brackets, where $[Q]=1$ if formula $Q$ is true, and 0 otherwise.
+	%
+	Then, $\text{\textbf{T}} = ([\alpha = 1] + [\alpha = 2] + [\alpha = 3])/3 = \frac{1}{3}$ as $\delta \in [1,2,3]$ and each setting is equally likely.
+	%
+	Similarly, $\text{\textbf{F}} = ([\alpha \neq 1] + [\alpha \neq 2] + [\alpha \neq 3])/3 = \frac{2}{3}$.
+
+	\begin{figure}
+		\label{fig:montyhall_tree_prob}
+		\centering
+		{\footnotesize
+			\begin{forest}baseline,for tree=draw,
+				[{$\mathtt{1}: c_0=\top$},align=center, base=bottom
+				[{$\mathtt{4}: c_1 = \alpha = \delta$},align=center, base=bottom, edge label={node [midway,above] {\textbf{T}} }
+				[{$\mathtt{5}: c_2 = \beta$},align=center, base=bottom, node options={dotted,thick}, draw=red ] %loss
+				[{$\mathtt{5}: c_2 =  \neg\beta$},align=center, base=bottom, node options={dashed}, draw=darkgreen ]] %win
+				[{$\mathtt{4}: c_1 = \alpha \neq \delta$},align=center, base=bottom, edge label={node [midway,above] {\textbf{F}} }
+				[{$\mathtt{7}: c_2 = \alpha \neq 1 \wedge \delta \neq 1$},align=center, base=bottom, 
+				[{$\mathtt{12}: c_3 = \beta$},align=center, base=bottom, node options={dashed}, draw=darkgreen ] %win
+				[{$\mathtt{12}: c_3 = \neg\beta$},align=center, base=bottom, node options={dotted,thick}, draw=red ]] %loss
+				[{$\mathtt{7}: c_2 = \alpha = 1 \vee \delta = 1$},align=center, base=bottom
+				[{$\mathtt{10}: c_3 = \alpha \neq 2 \vee \delta \neq 2$},align=center, base=bottom
+				[{$\mathtt{12}: c_4 = \beta$},align=center, base=bottom, node options={dashed}, draw=darkgreen ] %win
+				[{$\mathtt{12}: c_4 = \neg\beta$},align=center, base=bottom, node options={dotted,thick}, draw=red ]] %loss
+				[{$\mathtt{10}: c_3 = \alpha = 2 \vee \delta = 2$},align=center, base=bottom
+				[{$\mathtt{12}: c_4 = \beta$},align=center, base=bottom, node options={dashed}, draw=darkgreen ]%win
+				[{$\mathtt{12}: c_4 = \neg\beta$},align=center, base=bottom, node options={dotted,thick}, draw=red ]]]]] %loss
+			\end{forest}
+		}
+		\caption{Execution tree for the Monty Hall Problem with probabilistic symbolic variables.}
+	\end{figure}
+
+	With this \textit{probabilistic} execution tree in hand, let's return to the original question we wanted to answer: if the contestant switches doors, does their chances of winning the car exceed $\frac{1}{3}$?
+	%
+	Note that each path in the tree has a probability associated with it.
+	%
+	If we want to know the probability of winning if the contestant switches versus not, we can look at solely those paths in the tree which lead to a win.
+	%
+	To then figure out the probability of winning the car if the contestant switches we then can remove those paths where $\neg\beta$ is true, and then sum up the probabilities of the remaining paths. 
+	%
+	This results in an expression in terms of $\alpha$ and constants, which we can then evaluate where $\alpha = 1$, $\alpha = 2$, and $\alpha = 3$ and compare the probabilities.
+	%
+	In the end, we get that regardless the setting of $\alpha$ (i.e. the program variable, \texttt{choice}) the probability of winning the car if the contestant switches doors is exactly $\frac{2}{3}$.
+	%
+	We formalize this intuition in Section~\ref{sec:query_gen} by expressing this query in first order logic and use automated decision procedures to automate the solving.
 
@@
 	\label{sec:trad_sym_exec}
-	{\color{red} Subhajit \& Sumit: If you could add a high-level description of symb. exec., maybe an algorithm, that would be great!\\}
+
+	% Symbolic Execution Algorithm.
+	\begin{algorithm}
+		\caption{Probabilistic Symbolic Execution Algorithm}
+		\label{alg:symbex}
+		\begin{algorithmic}[1]
+			\Function{SymbEx}{$P_{prog} : Program$}
+			\Let{$\varphi_{paths}$}{[]}, {$Ex_{stack}$} $\leftarrow$ {[]}, $\Delta \leftarrow$ {[]}, $\phi_{paths} \leftarrow \phi$, $P \leftarrow \phi$  \algorithmiccomment{Initialization}
+			\Let{$I_{0}$}{\textsc{getStartInstruction}($P_{prog}$)}
+			\Let{$S_{0}$}{[$I_{0}$, $\phi_{path}$, $\Delta$, $\phi$]} \algorithmiccomment{Empty Initial State}
+			\State {$Ex_{stack}$.\textsc{Push}({$S_{0}$})} \algorithmiccomment{Start with $S_{cur}$ in Execution Stack}
+			\While{$Ex_{stack}$ != $\phi$}
+			\Let{$S_{cur}$}{$Ex_{stack}$.\textsc{Pop}( )}, $I_{cur} \leftarrow S_{cur}[1]$ \algorithmiccomment{Start State, [$I_{0}$, $\phi_{path}$, $\Delta$]}
+			\Switch{\textsc{instType}($I_{cur}$)} \label{line:inst_case}
+			\Case{\texttt{make\_pse\_sym}} ($x_{var},  d_{dist}$) \algorithmiccomment{Create \texttt{fresh} Symbolic Variable} \label{line:make_pse}
+			\Let{$I_{cur}$}{\textsc{getNextInstruction}($I_{cur}$)}
+			\Let{$\phi_{path}, \Delta, P$}{{\textbf{PSESample}}({$x_{var},  d_{dist}$, $\phi_{path}$, $\Delta$, $P$})}
+			\Let{$S_{cur}$}{[$I_{cur}$, $\phi_{path}$, $\Delta$, $P$]}
+			\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
+			\EndCase
+			\Case{v := e} \algorithmiccomment{Assignment Instruction} \label{line:assign}
+			\Let{$I_{cur}$}{\textsc{getNextInstruction}($I_{cur}$)}
+			\Let{$\phi_{path}, \Delta, P$}{{\textbf{PSEAssignment}}({v, e, $\phi_{path}$, $\Delta$, $P$})}
+			\Let{$S_{cur}$}{[$I_{cur}$, $\phi_{path}$, $\Delta$, $P$]}
+			\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
+			\EndCase
+			\Case{\textbf{if} $(c_{sym})$ \textbf{then} $P_{1}$ \textbf{else} $P_{2}$} \algorithmiccomment{Branch Instruction}
+			\Let{$Branch_{expr}$}{{\textbf{PSEBranch}}({$c_{sym}$, $\phi_{path}$, $\Delta$, $P$})} \label{line:branch}
+			\State {$S_{true}$}, {$S_{false}$} $\leftarrow$ \textsc{ForkState} ($S_{cur}$, $I_{cur}$) \label{line:fork}
+			\Let{$I_{1}$}{\textsc{getStartInstruction}($P_{1}$)} \Let{$I_{2}$} {\textsc{getStartInstruction}($P_{2}$)}	
+			\Let{$S_{true}$}{[$I_{1}$, $\phi_{path} \wedge c_{sym}$, $\Delta$, $Branch_{expr}[0]$]} \label{line:true_state}
+			\Let{$S_{false}$}{[$I_{2}$, $\phi_{path} \wedge (\neg c_{sym})$, $\Delta$, $Branch_{expr}[1]$]} \label{line:false_state}
+			\State {$Ex_{stack}$.\textsc{Push}({$S_{false}$})}
+			\State {$Ex_{stack}$.\textsc{Push}({$S_{true}$})} \algorithmiccomment{Start with True State}
+			\EndCase
+			\Case{\textbf{HALT}} \algorithmiccomment{Terminate Instruction}
+			\Let{$\varphi_{paths}$}{$\varphi_{paths}$.\textsc{Append}($\phi_{path}$)}		
+			\EndCase
+			\EndSwitch
+			\EndWhile \\
+			\Return{$\varphi_{paths}$}
+			\EndFunction
+		\end{algorithmic}
+	\end{algorithm}
+
 	\textit{Symbolic execution} is a program analysis technique where a program is run on \textit{symbolic} inputs and all program operations are replaced with those which manipulate these symbolic variables.
 	%
-	During execution, program state is encoded symbolically in two parts: a path condition which is a conjunctive formula, $\varphi$, which records the branch conditions which are true for that particular path, and a mapping from program variables to symbolic expressions containing constants and \textit{symbolic variables}, $\sigma$.
+	We present a high-level description of how \textit{symbolic execution} works in Alg~\ref{alg:symbex}. 
 	% 
-	When execution reaches an assignment of the form $\mathtt{x} = e$, where $e$ is a constant or program variable, $\sigma[\mathtt{x}] = \sigma[e]$.
+	For each path in the program, a list of \textit{constraints} are stored that encodes the whole path as a \textit{logical}
+	formula.
 	% 
-	Similarly, if $e = e_1 \oplus e_2$, where $\oplus$ is an arbitrary binary operation, $\sigma[\mathtt{x}] = \sigma[e_1] \oplus \sigma[e_2]$. 
+	These constraints are over \textit{program} variables that have been marked \textit{symbolic} by the user and are stored in the \textit{state} data structure as \textit{metadata} during the \textit{dynamic} symbolic execution of the program.
+	% 
+	Apart from \textit{path constraints}, the \textit{state} also contains a mapping of \textit{symbolic} variables to expressions that are either  \textit{symbolic} or \textit{concrete} (in the case of concrete execution of the program) and a list of \textit{instructions} currently getting executed as a part of the \textit{state}.
+	% 
+	During symbolic execution, program state is encoded symbolically in two parts: a conjunctive formula, $\varphi$, consisting of the branch conditions which are true for that particular path, called a \textit{path condition}, and a mapping from program variables to symbolic expressions containing constants and \textit{symbolic variables}, $\sigma$.
+	% 
+	Each \textit{instruction} in the program is executed and depending upon the \textit{type} of the \textit{instruction} the \textit{state} along with the \textit{symbolic variables} mapping, ($\Delta$ in Alg~\ref{alg:symbex}) are updated as described in Algorithm~\ref{alg:symbex}.
+	% 
+	\textit{Symbolic variables} are assigned values by employing an \textsc{SMT Solver} for solving the current set of \textit{constraints} collected so far in the \textit{program path} and also by \textit{concretizing} some of the values that get evaluated as a result of \textit{concrete} execution (e.g.
+return value from external function calls).
+	%
+	When execution reaches an assignment of the form $\mathtt{x} = e$, where $e$ is a constant or program variable, $\sigma[\mathtt{x}]$ is either just the constant, $e$, or the symbolic representation of $e$, namely $\sigma[e]$.
+	% 
+	If $e$ is an expression, we recursively convert each program variable in $e$ to its corresponding symbolic expression found in $\sigma$ to construct a new symbolic execution, $e_{sym}$, and set $\sigma[\mathtt{x}] = e_{sym}$.
 	% 
@@
 	\subsection{Adding Probabilistic Sampling}
-	We now consider the problem of performing symbolic execution on a simple imperative probabilistic programming language, \textbf{pWhile}:
+	We present the formalism of our approach on \textbf{pWhile}, a core imperative probabilistic programming language, as a model for more general languages:
 	% 
@@
 
-	Above, $\mathtt{x}$ is a program variable, $e$ is an expression, and $d$ is a \textit{discrete} distribution expression. 
+	Above, $\mathtt{x}$ is a program variable, $e$ is an expression, and $d$ is a \textit{discrete} distribution expression which denotes which distribution the sample should be drawn from.
+	% 
+	We permit distribution expressions to be (optionally) parameterized by program variables.
+	% 
+	For example, $\mathsf{UniformInt}(1,\mathtt{x})$ is a uniform distribution which selects at random a value between 1 and $\mathtt{x}$ (inclusive), where $\mathtt{x} \geq 1$.
 	% 
@@
 	\begin{itemize}
-		\item \textit{Probabilistic symbolic variables.} We distiguish two types of symbolic variables: \textit{universal} symbolic variables (identical to those in traditional symbolic execution), and \textit{probabilistic} symbolic variables.
+		\item \textit{Probabilistic symbolic variables.} We distinguish two types of symbolic variables: \textit{universal} symbolic variables (identical to those in traditional symbolic execution), and \textit{probabilistic} symbolic variables.
 		% 
-		For each unique sampling instruction a new probabilistic symbolic variable is created to denote the result of sample.
+		For each sampling instruction a new probabilistic symbolic variable is created to denote the result of sample.
 		\item \textit{Distribution map.} We add a new mapping from probabilistic symbolic variables to distribution expressions, $P$, which tracks the distribution from which a probabilistic symbolic variable was originally sampled from.
+		% 
+		This is analogous to the symbolic variable map, $\sigma$, except for mapping probabilistic symbolic variables to distributions instead from program variables to symbolic expressions.
 		\item \textit{Path probability.} For each path, we adjoin a path probability expression, $p$, which is parameterized by universal symbolic variables.
+		% 
+		Now each path can be identified by both its path condition and its probability.
 	\end{itemize}
@@
 		For assignment statements of the form $\mathtt{x} \leftarrow e$, where $\mathtt{x}$ is a \textit{program} variable and $e$ is an expression, probabilistic symbolic execution proceeds identically to traditional symbolic execution, as detailed in Alg.~\ref{alg:assign}.
+		%
+		On the \textit{symbolic execution} side, the \textit{symbolic variable} mapping ($\Delta$) is updated with the result of the assignment operation is stored back in the current \textit{state} for further execution as shown in Line~\ref{line:assign} of Alg~\ref{alg:symbex}.
 	\end{paragraph}
@@
 		A fresh probabilistic symbolic variable, $\delta$, is created, $\sigma$ is updated to be $\sigma[\mathtt{x}] = \delta$, and the original distribution $d$ is recorded in $P$ by setting $P[\delta] = d$.
+		%
+		On the \textit{symbolic execution} side, the updated \textit{Distribution Map} ($P$) with the result of sampling operation is stored back in the current \textit{state} for further execution as shown in Line~\ref{line:make_pse} of Alg~\ref{alg:symbex}.
 	\end{paragraph}
@@
 
-	% Symbolic Execution Algorithm.
-	\begin{algorithm}
-		\caption{Getting Path Constraints : Symbolic Execution}
-		\label{alg:symbex}
-		\begin{algorithmic}[1]
-			\Function{SymbEx}{$P_{prog} : Program$}
-			\Let{$\varphi_{paths}$}{[]}, {$Ex_{stack}$} $\leftarrow$ {[]}, $\Delta \leftarrow$ {[]}, $\phi_{paths} \leftarrow \phi$  \algorithmiccomment{Initialization}
-			\Let{$I_{0}$}{\textsc{getStartInstruction}($P_{prog}$)}
-			\Let{$S_{0}$}{[$I_{0}$, $\phi_{path}$, $\Delta$]} \algorithmiccomment{Empty Initial State}
-			\State {$Ex_{stack}$.\textsc{Push}({$S_{0}$})} \algorithmiccomment{Start with $S_{cur}$ in Execution Stack}
-			\While{$Ex_{stack}$ != $\phi$}
-			\Let{$S_{cur}$}{$Ex_{stack}$.\textsc{Pop}( )}, $I_{cur} \leftarrow S_{cur}[1]$ \algorithmiccomment{Start State, [$I_{0}$, $\phi_{path}$, $\Delta$]}
-			\Switch{\textsc{instType}($I_{cur}$)} \label{line:inst_case}
-			\Case{v := e} \algorithmiccomment{Assignment Instruction} \label{line:assign}
-			\Let{$I_{cur}$}{\textsc{getNextInstruction}($I_{cur}$)}
-			\Let{$S_{cur}$}{[$I_{cur}$, $\phi_{path}$, $\Delta$[v $\rightarrow$ \textsc{Eval($e$, $\Delta$)}]]}
-			\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
-			\EndCase
-			\Case{\textbf{if} $(c_{sym})$ \textbf{then} $P_{1}$ \textbf{else} $P_{2}$} \algorithmiccomment{Branch Instruction} \label{line:branch}
-			\If{(\textsc{isSat}($c_{sym}$) $\wedge$ \textsc{isSat}($\neg c_{sym}$))} \algorithmiccomment{Both cases SAT}
-			\Let{$I_{1}$}{\textsc{getStartInstruction}($P_{1}$)} \Let{$I_{2}$} {\textsc{getStartInstruction}($P_{2}$)}	
-			\Let{$S_{true}$}{[$I_{1}$, $\phi_{path} \wedge c_{sym}$, $\Delta$]} \label{line:true_state}
-			\Let{$S_{false}$}{[$I_{2}$, $\phi_{path} \wedge (\neg c_{sym})$, $\Delta$]} \label{line:false_state}
-			\State {$Ex_{stack}$.\textsc{Push}({$S_{false}$})}
-			\State {$Ex_{stack}$.\textsc{Push}({$S_{true}$})} \algorithmiccomment{Start with True State}
-			\ElsIf{\textsc{isSat}($c_{sym}$)} \algorithmiccomment{True case SAT}
-			\Let{$I_{cur}$}{\textsc{getStartInstruction}($P_{1}$)}
-			\Let {$S_{cur}$}{[$I_{cur}$, $\phi_{path} \wedge c_{sym}$, $\Delta$]}
-			\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
-			\ElsIf{\textsc{isSat}($\neg c_{sym}$)} \algorithmiccomment{False case SAT}
-			\Let{$I_{cur}$}{\textsc{getStartInstruction}($P_{2}$)}
-			\Let{$S_{cur}$}{[$I_{2}$, $\phi_{path} \wedge (\neg c_{sym})$, $\Delta$]}
-			\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
-			\Else \algorithmiccomment{Unconditional Branch}
-			\Let{$I_{cur}$}{\textsc{getNextInstruction}($I_{cur}$)}
-			\Let{$S_{cur}$}{[$I_{cur}$, $\phi_{path}$, $\Delta$]}
-			\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
-			\EndIf
-			\EndCase
-			\Case{\textbf{HALT}} \algorithmiccomment{Terminate Instruction}
-			\Let{$\varphi_{paths}$}{$\varphi_{paths}$.\textsc{Append}($\phi_{path}$)}		
-			\EndCase
-			\EndSwitch
-			\EndWhile \\
-			\Return{$\varphi_{paths}$}
-			\EndFunction
-		\end{algorithmic}
-	\end{algorithm}
-
-	\begin{paragraph}{Branches}
+	\begin{paragraph}{Branches (Alg.~\ref{alg:branch})}
 		Note that with the inclusion of probabilistic symbolic variables we can now either branch on universal or probabilistic symbolic variables (or both).
 		% 
-		For guards whose symbolic version does not contain any probabilistic symbolic variables, probabilstic symbolic execution works nearly identically to traditional symbolic execution, save one detail: the probability of taking the branch.
+		Intuitively, branches are handled much the same in probabilistic symbolic execution as they are in traditional symbolic execution save for one detail: now branches have a probability associated with them.
 		% 
-		If $c_{sym}$ is a symbolic expression which represents the guard to a branch, and $c_{sym}$ does not contain any probabilistic symbolic variables, then we define the probability of taking the ``true'' branch is $[c_{sym}]$, and the probability of taking the ``false'' branch is $[\neg c_{sym}]$, where $[Q] = 1$ if $Q$ is true, and 0 otherwise (known as Iverson brackets).
+		Given a guard expression $c$, how do we compute the probability of $c$ being true?
 
-		For probabilistic branches, i.e. guards which branch on probabilistic symbolic variables, Alg.~\ref{alg:branch} is used instead of the traditional symbolic execution branch algorithm.
+		To gain intuition, for now just consider the special case where the guard condition only references universal symbolic variables.
 		% 
-		Without loss of generality, consider a branch of the form $\mathbf{if}~c~\mathbf{then}~S_1~\mathbf{else}~S_2$ where $c$ is a probabilistic branch.
+		Let $c_{sym}$ be the equivalent symbolic expression for the guard $c$ and assume that $c_{sym}$ does not reference any probabilistic symbolic variables.
 		% 
-		As before, we define $c_{sym} = \sigma[c]$.
+		Note that which side of the branch is taken is solely determined by the setting of the univeral symbolic variables.
 		% 
-		The core of Alg.~\ref{alg:branch} is computing the probability of taking each branch.
+		Therefore, one side of the branch must have a probability of 1, and the other side, 0.
 		% 
-		We interpret probabilistic branches as a conditioning operation on the distributions which are mentioned in the guard of the branch.
+		We use Iverson brackets to formalize this idea; the probability of taking the ``true'' branch is $[c_{sym}]$, and the probability of taking the ``false'' branch is $[\neg c_{sym}]$.
+
+		For probabilistic branches, i.e.
+guards which branch on probabilistic symbolic variables, computing the branch probability is trickier as given a fixed setting of the universal symbolic variables, it is unclear which branch execution will follow as this is dependent upon the sampling results.
 		% 
-		Under this interpretation, we aim to compute the conditional probability $\Pr[c_{sym} \mid \varphi] = \frac{\Pr[c_{sym}\wedge \varphi]}{\Pr[\varphi]}$, where $\varphi$ is the current path condition formula.
+		Without loss of generality, consider a branch of the form $\mathbf{if}~c~\mathbf{then}~S_1~\mathbf{else}~S_2$.
+		% 
+		As before, we define $c_{sym} = \sigma[c]$, or the symbolic expression representation of the guard expression, $c$, and we want to compute the probability of taking the ``true'' branch and the ``false'' branch, assuming execution has reached the start of the \texttt{if} condition.
+		% 
+		Since the path condition $\varphi$ records the necessary constraints on the universal and probabilistic symbolic variables which must hold in order to reach this \texttt{if} condition, we can view this probability a \textit{conditional probability}, or the probability that $c_{sym}$ holds given that $\varphi$ is satisfied.
+		% 
+		In formal notation, we aim to compute $\Pr[c_{sym} \mid \varphi] = \frac{\Pr[c_{sym}\wedge \varphi]}{\Pr[\varphi]}$.
 
-		We use a form of model counting in order to compute $p_c$, the probability of $c$ being true.
+		For now we restrict our view to uniform distributions, although we can support weighted distributions without further problems.
 		% 
@@
 		Additionally, we exploit the fact that the sum of the conditional probabilities of the branch outcomes is 1, which allows us to avoid computing the probability of taking the ``false'' branch directly.
+\\
+		% 
+		On the \textit{symbolic execution} side, upon reaching the \textit{branch} instruction at Line~\ref{line:branch} in Alg~\ref{alg:symbex}, the current \textit{state} ($S_{cur}$) is forked [Line~\ref{line:fork}] by making two identical copies of it.
+Furthermore, one additional constraint is appended to each of \textit{newly} created states ($S_{true}$ \& $S_{false}$) encoding the actual \textit{branch condition} ($c_{sym}$) [Line~\ref{line:true_state}] and it's negation ($\neg c_{sym}$) [Line~\ref{line:false_state}] representing the \textit{true} \& \textit{false} side of the \textit{branch}.
+		%
+		These states are then added to the \textit{execution} stack containing \textit{states} that need to be explored next.
+The process continues untill all the \textit{states} in the \textit{execution} stack are explored.
 	\end{paragraph}
@@
 	\begin{paragraph}{Example}
-		Consider the code in Fig.~\ref{fig:exam_program} and suppose you wish to calculate the probability of the program returning \texttt{True}.
+		Consider the code in Fig.~\ref{fig:exam_program} and suppose we wish to calculate the probability of the program returning \texttt{True}.
 		% 
@@
 		\end{align*}
+
+		This probability means that the probability of taking the ``true'' branch of the inner \texttt{if} condition is only $\frac{1}{6}$, which makes sense as \texttt{x} is restricted to be either $2$ or $3$, but \texttt{y} can be either 1,2, or 3; however, only one combination of \texttt{x} and \texttt{y} will satisfy $\mathtt{x} < \mathtt{y}$, namely $\mathtt{x} = 2$ and $\mathtt{y} = 3$.
 	\end{paragraph}
+
+	We use a robust dynamic symbolic execution engine, \textsc{KLEE} to generate the \textit{path constraints} corresponding to each path that our tool explores.
+For the purpose of our implementation, we modify \textsc{KLEE} to support creation of \textit{probabilistic symbolic} variables whose values can be sampled from a distribution and process the \textit{path} constraints that are stored in the \textit{state} corresponding to the current execution of the program at each of \textbf{\textit{assignment}} [Algorithm~\ref{alg:symbex}, Line~\ref{line:assign}], \textbf{\textit{branch}} [Algorithm~\ref{alg:symbex}, Line~\ref{line:branch}] \& \textbf{\textit{sampling}} (\texttt{make\_pse\_symbolic()}) statements.
+[Algorithm~\ref{alg:symbex}, Line~\ref{line:make_pse}].
 
@@
 	% 
-	To calculate the probability of an entire path, or equivalently, the probability of a path condition, $\varphi$, being true, we can simply multiple each of the branch probabilities.
+	To calculate the probability of an entire path, or equivalently, the probability of a path condition, $\varphi$, being true, we can simply multiply each of the branch probabilities.
 	% 
@@
 		\Pr[\varphi_i] &= \Pr[c_{i_1} \wedge \cdots \wedge c_{i_{k_i}}]\\
-		&= \Pr[c_{i_1} (c_{i_2} \wedge \cdots \wedge c_{i_{{k_i}-1}} \wedge c_{i_{k_i}})]\\
+		&= \Pr[c_{i_1} \wedge (c_{i_2} \wedge \cdots \wedge c_{i_{{k_i}-1}} \wedge c_{i_{k_i}})]\\
 		&= p_{i_1} \cdot \Pr[c_{i_2} \wedge \cdots \wedge c_{i_{k_i}}]\\
@@
 	% 
-	There are three components to our queries: 1) a universal quantification over the universal symbolic variables, 2) a filtering condition specifying what a ``good'' or ``bad'' state is, and 3) a desired upper/lower bound, potentially parameterized by universal symbolic variables.
+	There are three components to our queries: 1) a universal quantification over the universal symbolic variables, 2) a filtering condition specifying what a ``good'' or ``bad'' final state is, and 3) a desired upper/lower bound, potentially parameterized by universal symbolic variables.
 	% 
@@
 		% 
-		We then sum over all of the paths in $\Phi'$, giving us the probability of $\psi$ occuring in program $S$:
+		We then sum over all of the paths in $\Phi'$, giving us the probability of $\psi$ occurring in program $S$:
 		\[
@@
 	\[
-	\forall \alpha_1,\ldots,\alpha_m . \displaystyle \delta \sim \sum_{(\varphi,p) \in \Phi'} [\varphi]\cdot p 
+	\forall \alpha_1,\ldots,\alpha_m . \displaystyle \delta \bowtie \sum_{(\varphi,p) \in \Phi'} [\varphi]\cdot p 
 	\]
@@
 		% 
-		The probability of this occuring is then ... as ...
+		The probability of this occurring is then ... as ...
 	}
@@
 
-	In this section we present the formalization of our method. First, we will present our notation and definitions, and then provide proofs of correctness and soundness of our technique.
+	In this section we present the formalization of our method. First, we will present our notation and definitions, and then prove a soundness theorem for our technique.
+	% 
+	The goal of this section is to describe how $R=(\varphi,\sigma,P)$, the inputs to Alg.~\ref{alg:branch} is an abstraction of a \textit{distribution of program memories} before a branch guarded by a program expression $c$.
 
@@
 
-	The goal of this section is to describe how $R=(\varphi,\sigma,P)$, the inputs to Alg.~\ref{alg:branch} is an abstraction of a \textit{distribution of program memories} before a branch guarded by a program expression $c$.
-	% 
 	To begin, we will define some notation:
@@
 
-	{\color{red} Subhajit \& Sumit: Write something about KLEE and the implementation here!}
-
-	We use a robust dynamic symbolic execution engine, \textsc{KLEE} to generate the \textit{path constraints} corresponding to each path that our tool explores.
-For each path in the program, \textsc{KLEE} stores a list of \textit{constraints} that encodes the whole path.
-These constraints are over \textit{program} variables that have been marked \texttt{make\_symbolic()} by the user and are stored in \textsc{KLEE} as \textit{metadata} in the \textit{state} data structure during the \textit{dynamic} symbolic execution of the program.
-Apart from \textit{path constraints}, the \textit{state} also contains a mapping of \textit{symbolic} variables to expressions that are either  \textit{symbolic} or \textit{concrete} (in the case of concrete execution of the program) and a list of \textit{instructions} currently getting executed as a part of the \textit{state}.
-
-	During \textit{dynamic} execution, \textsc{KLEE} executes each \textit{instruction} in the program and updates the \textit{state} along with the \textit{symbolic} variables mapping ($\Delta$) depending upon \textit{type} of the \textit{instruction} it executes as described in Algorithm~\ref{alg:symbex}.
-	\textsc{KLEE} assigns values to \textit{symbolic} variables by employing an \textsc{SMT Solver} (\textsc{Z3} as in our case) for solving the current set of \textit{constraints} seen so far in the program path and also by concretizing some of the values that get evaluated as a result of \textit{concrete} execution (Eg.
-return value from external function calls).
-
-	For the purpose of our implementation, we modify \textsc{KLEE} to support creation of \textit{probabilistic symbolic} variables whose values can be sampled from a distribution and dump the whole set of \textit{path} constraints that is stored in the \textit{state} corresponding to the current execution of the program at each of (1) \textbf{\textit{assignment}} [Algorithm~\ref{alg:symbex}, Line~\ref{line:assign}], (2) \textbf{\textit{branch}} [Algorithm~\ref{alg:symbex}, Line~\ref{line:branch}], \& (3) \textbf{\textit{assume}} [Algorithm~\ref{alg:symbex}, Line~\ref{line:assume}] statements.
-These dumps are later refined and used by the tool for further processing.
-
-	{\color{blue} Upon reaching the \textit{branch} instruction at Line~\ref{line:branch} in Algorithm~\ref{alg:symbex}, based on whether the \textit{path constraints} are solvable upon adding the \textit{branch} [Line~\ref{line:branch}] condition, \textsc{KLEE} forks the current \textit{state} by making two identical copies of it and then appending to each of \textit{new} states one additional constraint encoding the \textit{true} [Line~\ref{line:true_state}] and \textit{false} [Line~\ref{line:false_state}] side of the branch and adds it to the \textit{execution} stack containing \textit{states} that need to be explored next.
-The process continues untill all the \textit{states} in the \textit{execution} stack are explored.}
+	{\color{red} KLEE Description Moved to \S\ref{sec:trad_sym_exec}} \\
+	{\color{red} KLEE Modifications Moved to \S3.2}
 
@@
 	{\color{red} Subhajit \& Sumit: If you could both start looking into related work (Mayhap, original PSE paper, Axprof, P4WN, PSI), that would be great!}
+
+	{\color{blue}
+		Write a paragraph or two about use of symbolic execution from other papers. In what ways has symbolic execution has been used and some traditional aspects.
+		Write about AxProf, Original PSE paper [ISSTA 2012], Dice [Scaling Exact Inference for Discrete Probabilistic Programs, OOPSLA'20], Quantification of Software Changes through Probabilistic Symbolic Execution [ASE 2015], P4WN [ASPLOS'21], PSI [PLDI'20], Exact Inference for Higher-order Probabilistic Programs paper [FSE'15 QCoral] etc.
+Write the central idea in these papers and contrast with differences from approach presented in this paper.
+	}
 	\section{Conclusion \& Future Work}
@@
 
+	\section{WIP Probabilistic Symbolic Execution} 
+	\input{symbolic_execution.tex}
+
 \end{document}
+% Zach: Ignore for now, might swap out trees for this one later depending on feedback.
+% \begin{figure}
+%   \label{fig:montyhall_tree_prob}
+%   \centering
+%   {\tiny
+%   \begin{forest}baseline,for tree=draw,
+%     [{$\mathtt{1}: c_0=\top$},align=center, base=bottom
+%       [{$\mathtt{4}: c_1 = \alpha = \delta$},align=center, base=bottom,edge label={node [midway,above] {$\frac{1}{3}$} }
+%         [{$\mathtt{5}: c_2 = \beta$},align=center, base=bottom, draw=red ] %loss
+%         [{$\mathtt{5}: c_2 =  \neg\beta$},align=center, base=bottom, draw=green ]] %win
+%       [{$\mathtt{4}: c_1 = \alpha \neq \delta$},align=center, base=bottom,edge label={node [midway,above] {$\frac{2}{3}$} }
+%         [{$\mathtt{7}: c_2 = \alpha \neq 1 \wedge \delta \neq 1$},align=center, base=bottom, 
+%           [{$\mathtt{12}: c_3 = \beta$},align=center, base=bottom
+%             [{$\mathtt{14}: c_4 = \alpha = 2$},align=center, base=bottom
+%               [{$\mathtt{21}: c_5 = \delta = 3$},align=center, base=bottom, draw=green ] %win
+%               [{$\mathtt{21}: c_5 = \delta \neq 3$},align=center, base=bottom, draw=red ]] % loss
+%             [{$\mathtt{14}: c_4 = \alpha \neq 2$},align=center, base=bottom
+%               [{$\mathtt{21}: c_5 = \delta = 2$},align=center, base=bottom, draw=green ] % win
+%               [{$\mathtt{21}: c_5 = \delta \neq 2$},align=center, base=bottom, draw=red ]]] % loss
+%           [{$\mathtt{12}: c_3 = \neg\beta$},align=center, base=bottom, draw=red ]] %loss
+%         [{$\mathtt{7}: c_2 = \alpha = 1 \vee \delta = 1$},align=center, base=bottom
+%           [{$\vdots$},align=center, base=bottom]]]]
+%          % [{$\mathtt{12}: c_3 = \alpha \neq 2 \wedge \delta \neq 2$},align=center, base=bottom
+%          %   [{$c_4 = \beta$},align=center, base=bottom
+%          %     [{$c_5 = \alpha = 1$},align=center, base=bottom
+%          %       [{$c_6 = \delta = 3$},align=center, base=bottom]
+%          %       [{$c_6 = \delta \neq 3$},align=center, base=bottom]]
+%          %     [{$c_5 = \alpha \neq 1$},align=center, base=bottom
+%          %       [{$c_6 = \delta = 1$},align=center, base=bottom]
+%          %       [{$c_6 = \delta \neq 1$},align=center, base=bottom]]]
+%          %   [{$c_4 = \neg\beta$},align=center, base=bottom]]
+%          % [{$\mathtt{12}: c_3 = \alpha = 2 \vee \delta = 2$},align=center, base=bottom
+%          %   [{$c_4 = \beta$},align=center, base=bottom
+%          %     [{$c_5 = \alpha = 1$},align=center, base=bottom
+%          %       [{$c_6 = \delta = 2$},align=center, base=bottom]
+%          %       [{$c_6 = \delta \neq 2$},align=center, base=bottom]]
+%          %     [{$c_5 = \alpha \neq 1$},align=center, base=bottom
+%          %       [{$c_6 = \delta = 1$},align=center, base=bottom]
+%          %       [{$c_6 = \delta \neq 1$},align=center, base=bottom]]]
+%          %   [{$c_4 = \neg\beta$},align=center, base=bottom]]]]]
+%   \end{forest}
+%   }
+%   \caption{Partial execution tree for the Monty Hall Problem with probabilistic symbolic variables.}
+% \end{figure}

### 2021-06-30 shared/Paper-Draft/symbolic_execution.tex
WIP : SymbEx Section (B)

--- 2021-06-24 shared/Paper-Draft/PSE-POPL-2021.tex
@@
-%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
-%%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
-%% For double-blind review submission, w/ CCS and ACM Reference
-%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
-%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
-%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
-%% For single-blind review submission, w/ CCS and ACM Reference
-%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
-%% For final camera-ready submission, w/ required CCS and ACM Reference
-\documentclass[acmsmall]{acmart}\settopmatter{}
+		\subsection{Background}
+\label{sec:trad_sym_exec}
 
-%% Journal information
-%% Supplied to authors by publisher for camera-ready submission;
-%% use defaults for review submission.
-\acmJournal{PACMPL}
-\acmVolume{1}
-\acmNumber{POPL} % CONF = POPL or ICFP or OOPSLA
-\acmArticle{1}
-\acmYear{2022}
-\acmMonth{1}
-\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
-\startPage{1}
-
-%% Copyright information
-%% Supplied to authors (based on authors' rights management selection;
-%% see authors.acm.org) by publisher for camera-ready submission;
-%% use 'none' for review submission.
-\setcopyright{none}
-%\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
-%\copyrightyear{2018}           %% If different from \acmYear
-
-%% Bibliography style
-\bibliographystyle{ACM-Reference-Format}
-%% Citation style
-%% Note: author/year citations are required for papers published as an
-%% issue of PACMPL.
-\citestyle{acmauthoryear}   %% For author/year citations
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Note: Authors migrating a paper from PACMPL format to traditional
-%% SIGPLAN proceedings format must update the '\documentclass' and
-%% topmatter commands above; see 'acmart-sigplanproc-template.tex'.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Some recommended packages.
-\usepackage{booktabs}   %% For formal tables:
-%% http://ctan.org/pkg/booktabs
-\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
-%% http://ctan.org/pkg/subcaption
-\usepackage{mathtools}
-\usepackage{algpseudocode,algorithm,algorithmicx}
-%\usepackage{amsmath, amssymb,amsthm, stmaryrd}
-
-%%% Macros %%%
-
-\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}
-\newcommand{\DeclareAutoPairedDelimiter}[3]{%
-	\expandafter\DeclarePairedDelimiter\csname Auto\string#1\endcsname{#2}{#3}%
-	\begingroup\edef\x{\endgroup
-		\noexpand\DeclareRobustCommand{\noexpand#1}{%
-			\expandafter\noexpand\csname Auto\string#1\endcsname*}}%
-	\x}
-\DeclareAutoPairedDelimiter{\deno}{\llbracket}{\rrbracket}
-
-\newcommand*\Let[2]{\State #1 $\gets$ #2}
-\newcommand*\dom[1]{\mathrm{dom}\left( #1 \right)}
-
-% Switch Statement Commands
-% New definitions
-\algnewcommand\algorithmicswitch{\textbf{switch}}
-\algnewcommand\algorithmiccase{\textbf{case}}
-\algnewcommand\algorithmicassert{\texttt{assert}}
-\algnewcommand\Assert[1]{\State \algorithmicassert(#1)}%
-% New "environments"
-\algdef{SE}[SWITCH]{Switch}{EndSwitch}[1]{\algorithmicswitch\ #1\ \algorithmicdo}{\algorithmicend\ \algorithmicswitch}%
-\algdef{SE}[CASE]{Case}{EndCase}[1]{\algorithmiccase\ #1}{\algorithmicend\ \algorithmiccase}%
-\algtext*{EndSwitch}%
-\algtext*{EndCase}%
-
-\begin{document}
-
-	%% Title information
-	\title[PSE]{Probabilistic Symbolic Execution}         %% [Short Title] is optional;
-	%% when present, will be used in
-	%% header instead of Full Title.
-	%\titlenote{with title note}             %% \titlenote is optional;
-	%% can be repeated if necessary;
-	%% contents suppressed with 'anonymous'
-	%\subtitle{Subtitle}                     %% \subtitle is optional
-	%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
-	%% can be repeated if necessary;
-	%% contents suppressed with 'anonymous'
-
-	%% Author information
-	%% Contents and number of authors suppressed with 'anonymous'.
-	%% Each author should be introduced by \author, followed by
-	%% \authornote (optional), \orcid (optional), \affiliation, and
-	%% \email.
-	%% An author may have multiple affiliations and/or emails; repeat the
-	%% appropriate command.
-	%% Many elements are not rendered, but should be provided for metadata
-	%% extraction tools.
-
-	%% Author with single affiliation.
-	\author{First1 Last1}
-	\authornote{with author1 note}          %% \authornote is optional;
-	%% can be repeated if necessary
-	\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
-	\affiliation{
-		\position{Position1}
-		\department{Department1}              %% \department is recommended
-		\institution{Institution1}            %% \institution is required
-		\streetaddress{Street1 Address1}
-		\city{City1}
-		\state{State1}
-		\postcode{Post-Code1}
-		\country{Country1}                    %% \country is recommended
-	}
-	\email{first1.last1@inst1.edu}          %% \email is recommended
-
-	%% Author with two affiliations and emails.
-	\author{First2 Last2}
-	\authornote{with author2 note}          %% \authornote is optional;
-	%% can be repeated if necessary
-	\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
-	\affiliation{
-		\position{Position2a}
-		\department{Department2a}             %% \department is recommended
-		\institution{Institution2a}           %% \institution is required
-		\streetaddress{Street2a Address2a}
-		\city{City2a}
-		\state{State2a}
-		\postcode{Post-Code2a}
-		\country{Country2a}                   %% \country is recommended
-	}
-	\email{first2.last2@inst2a.com}         %% \email is recommended
-	\affiliation{
-		\position{Position2b}
-		\department{Department2b}             %% \department is recommended
-		\institution{Institution2b}           %% \institution is required
-		\streetaddress{Street3b Address2b}
-		\city{City2b}
-		\state{State2b}
-		\postcode{Post-Code2b}
-		\country{Country2b}                   %% \country is recommended
-	}
-	\email{first2.last2@inst2b.org}         %% \email is recommended
-
-	%% Abstract
-	%% Note: \begin{abstract}...\end{abstract} environment must come
-	%% before \maketitle command
-	\begin{abstract}
-		TODO: Write Abstract
-	\end{abstract}
-
-	%% 2012 ACM Computing Classification System (CSS) concepts
-	%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
-	%% TODO: Get CSS Concepts
-	\begin{CCSXML}
-		<ccs2012>
-		<concept>
-		<concept_id>10011007.10011006.10011008</concept_id>
-		<concept_desc>Software and its engineering~General programming languages</concept_desc>
-		<concept_significance>500</concept_significance>
-		</concept>
-		<concept>
-		<concept_id>10003456.10003457.10003521.10003525</concept_id>
-		<concept_desc>Social and professional topics~History of programming languages</concept_desc>
-		<concept_significance>300</concept_significance>
-		</concept>
-		</ccs2012>
-	\end{CCSXML}
-
-	\ccsdesc[500]{Software and its engineering~General programming languages}
-	\ccsdesc[300]{Social and professional topics~History of programming languages}
-	%% End of generated code
-
-	%% Keywords
-	%% comma separated list
-	\keywords{keyword1, keyword2, keyword3}  %% \keywords are mandatory in final camera-ready submission
-
-	%% \maketitle
-	%% Note: \maketitle command must come after title commands, author
-	%% commands, abstract environment, Computing Classification System
-	%% environment and commands, and keywords command.
-	\maketitle
-
-	\section{Introduction}
-	\label{sec:intro}
-
-	\subsection{Contributions}
-	\label{sec:contrib}
-
-	\section{Motivating Example}
-	\label{sec:example}
-
-	\section{Probabilistic Symbolic Execution Algorithm}
 \label{sec:pse}
@@
 
-	\subsection{Background}
-	\label{sec:trad_sym_exec}
-	{\color{red} Subhajit \& Sumit: If you could add a high-level description of symb. exec., maybe an algorithm, that would be great!\\}
+% Symbolic Execution Algorithm.
+\begin{algorithm}
+	\caption{Probabilistic Symbolic Execution Algorithm}
+	\label{alg:symbex}
+	\begin{algorithmic}[1]
+		\Function{SymbEx}{$Prog : Program$}
+		\Let{$\varphi_{paths}$}{[]}, {$Ex_{stack}$} $\leftarrow$ {[]}, $\Delta \leftarrow$ {[]}, $\phi_{paths} \leftarrow \phi$, $P \leftarrow \phi$  \algorithmiccomment{Initialization}
+		\Let{$I_{0}$}{\textsc{getStartInstruction}($Prog$)}
+		\Let{$S_{0}$}{[$I_{0}$, $\phi_{path}$, $\Delta$, $\phi$]} \algorithmiccomment{Empty Initial State}
+		\State {$Ex_{stack}$.\textsc{Push}({$S_{0}$})} \algorithmiccomment{Start with $S_{cur}$ in Execution Stack}
+		\While{$Ex_{stack}$ != $\phi$}
+		\Let{$S_{cur}$}{$Ex_{stack}$.\textsc{Pop}( )}, $I_{cur} \leftarrow S_{cur}[1]$ \algorithmiccomment{Start State, [$I_{0}$, $\phi_{path}$, $\Delta$]}
+		\Switch{\textsc{instType}($I_{cur}$)} \label{line:inst_case}
+		\Case{\texttt{make\_pse\_sym}} ($x_{var},  d_{dist}$) \algorithmiccomment{Create \texttt{fresh} Symbolic Variable} \label{line:make_pse}
+		\Let{$I_{cur}$}{\textsc{getNextInstruction}($I_{cur}$)}
+		\Let{$\phi_{path}, \Delta, P$}{{\textbf{PSESample}}({$x_{var},  d_{dist}$, $\phi_{path}$, $\Delta$, $P$})}
+		\Let{$S_{cur}$}{[$I_{cur}$, $\phi_{path}$, $\Delta$, $P$]}
+		\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
+		\EndCase
+		\Case{v := e} \algorithmiccomment{Assignment Instruction} \label{line:assign}
+		\Let{$I_{cur}$}{\textsc{getNextInstruction}($I_{cur}$)}
+		\Let{$\phi_{path}, \Delta, P$}{{\textbf{PSEAssignment}}({v, e, $\phi_{path}$, $\Delta$, $P$})}
+		\Let{$S_{cur}$}{[$I_{cur}$, $\phi_{path}$, $\Delta$, $P$]}
+		\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
+		\EndCase
+		\Case{\textbf{if} $(c_{sym})$ \textbf{then} $P_{1}$ \textbf{else} $P_{2}$} \algorithmiccomment{Branch Instruction}
+		\Let{$Branch_{expr}$}{{\textbf{PSEBranch}}({$c_{sym}$, $\phi_{path}$, $\Delta$, $P$})} \label{line:branch}
+		\Let{$I_{1}$}{\textsc{getStartInstruction}($P_{1}$)} \Let{$I_{2}$} {\textsc{getStartInstruction}($P_{2}$)}	
+		\Let{$S_{true}$}{[$I_{1}$, $\phi_{path} \wedge c_{sym}$, $\Delta$, $Branch_{expr}[0]$]} \label{line:true_state}
+		\Let{$S_{false}$}{[$I_{2}$, $\phi_{path} \wedge (\neg c_{sym})$, $\Delta$, $Branch_{expr}[1]$]} \label{line:false_state}
+		\State {$Ex_{stack}$.\textsc{Push}({$S_{false}$})}
+		\State {$Ex_{stack}$.\textsc{Push}({$S_{true}$})} \algorithmiccomment{Start with True State}
+		\EndCase
+		\Case{\textbf{HALT}} \algorithmiccomment{Terminate Instruction}
+		\Let{$\varphi_{paths}$}{$\varphi_{paths}$.\textsc{Append}($\phi_{path}$)}		
+		\EndCase
+		\EndSwitch
+		\EndWhile \\
+		\Return{$\varphi_{paths}$}
+		\EndFunction
+	\end{algorithmic}
+\end{algorithm}
+
 \textit{Symbolic execution} is a program analysis technique where a program is run on \textit{symbolic} inputs and all program operations are replaced with those which manipulate these symbolic variables.
 %
-	During execution, program state is encoded symbolically in two parts: a path condition which is a conjunctive formula, $\varphi$, which records the branch conditions which are true for that particular path, and a mapping from program variables to symbolic expressions containing constants and \textit{symbolic variables}, $\sigma$.
+We present a high-level description of how \textit{symbolic execution} works in Alg~\ref{alg:symbex}. 
 % 
-	When execution reaches an assignment of the form $\mathtt{x} = e$, where $e$ is a constant or program variable, $\sigma[\mathtt{x}] = \sigma[e]$.
+For each path in the program, a list of \textit{constraints} are stored that encodes the whole path as a \textit{logical}
+formula.
 % 
-	Similarly, if $e = e_1 \oplus e_2$, where $\oplus$ is an arbitrary binary operation, $\sigma[\mathtt{x}] = \sigma[e_1] \oplus \sigma[e_2]$. 
+These constraints are over \textit{program} variables that have been marked \textit{symbolic} by the user and are stored in the \textit{state} data structure as \textit{metadata} during the \textit{dynamic} symbolic execution of the program.
+% 
+Apart from \textit{path constraints}, the \textit{state} also contains a mapping of \textit{symbolic} variables to expressions that are either  \textit{symbolic} or \textit{concrete} (in the case of concrete execution of the program) and a list of \textit{instructions} currently getting executed as a part of the \textit{state}.
+% 
+During symbolic execution, program state is encoded symbolically in two parts: a conjunctive formula, $\varphi$, consisting of the branch conditions which are true for that particular path, called a \textit{path condition}, and a mapping from program variables to symbolic expressions containing constants and \textit{symbolic variables}, $\sigma$.
+% 
+Each \textit{instruction} in the program is executed and depending upon the \textit{type} of the \textit{instruction} the \textit{state} along with the \textit{symbolic variables} mapping, ($\Delta$ in Alg~\ref{alg:symbex}) are updated as described in Algorithm~\ref{alg:symbex}.
+% 
+\textit{Symbolic variables} are assigned values by employing an \textsc{SMT Solver} for solving the current set of \textit{constraints} collected so far in the \textit{program path} and also by \textit{concretizing} some of the values that get evaluated as a result of \textit{concrete} execution (e.g.
+return value from external function calls).
+%
+When execution reaches an assignment of the form $\mathtt{x} = e$, where $e$ is a constant or program variable, $\sigma[\mathtt{x}]$ is either just the constant, $e$, or the symbolic representation of $e$, namely $\sigma[e]$.
+% 
+If $e$ is an expression, we recursively convert each program variable in $e$ to its corresponding symbolic expression found in $\sigma$ to construct a new symbolic execution, $e_{sym}$, and set $\sigma[\mathtt{x}] = e_{sym}$.
 % 
@@
 \subsection{Adding Probabilistic Sampling}
-	We now consider the problem of performing symbolic execution on a simple imperative probabilistic programming language, \textbf{pWhile}:
+We present the formalism of our approach on \textbf{pWhile}, a core imperative probabilistic programming language, as a model for more general languages:
 % 
 \[
-	P := \mathbf{skip} \mid \mathtt{x} \leftarrow e \mid \mathtt{x} \xleftarrow{\$} d \mid P ; P \mid \mathbf{if}~e~\mathbf{then}~P~\mathbf{else}~P \mid \mathbf{while}~e~\mathbf{do}~P 
+S := \mathbf{skip} \mid \mathtt{x} \leftarrow e \mid \mathtt{x} \xleftarrow{\$} d \mid S_1 ; S_2 \mid \mathbf{if}~e~\mathbf{then}~S_1~\mathbf{else}~S_2 \mid \mathbf{while}~e~\mathbf{do}~S 
 \]
 
-	Above, $\mathtt{x}$ is a program variable, $e$ is an expression, and $d$ is a \textit{discrete} distribution expression. 
+Above, $\mathtt{x}$ is a program variable, $e$ is an expression, and $d$ is a \textit{discrete} distribution expression which denotes which distribution the sample should be drawn from.
+% 
+We permit distribution expressions to be (optionally) parameterized by program variables.
+% 
+For example, $\mathsf{UniformInt}(1,\mathtt{x})$ is a uniform distribution which selects at random a value between 1 and $\mathtt{x}$ (inclusive), where $\mathtt{x} \geq 1$.
 % 
@@
 \begin{itemize}
-		\item \textit{Probabilistic symbolic variables.} We distiguish two types of symbolic variables: \textit{universally quantified} symbolic variables (identical to those in traditional symbolic execution), and \textit{probabilistic} symbolic variables.
+	\item \textit{Probabilistic symbolic variables.} We distinguish two types of symbolic variables: \textit{universal} symbolic variables (identical to those in traditional symbolic execution), and \textit{probabilistic} symbolic variables.
 	% 
-		For each unique sampling instruction a new probabilistic symbolic variable is created to denote the result of sample.
+	For each sampling instruction a new probabilistic symbolic variable is created to denote the result of sample.
 	\item \textit{Distribution map.} We add a new mapping from probabilistic symbolic variables to distribution expressions, $P$, which tracks the distribution from which a probabilistic symbolic variable was originally sampled from.
-		\item \textit{Path probability.} For each path, we adjoin a path probability expression, $p$, which is parameterized by universally quantified symbolic variables.
+	% 
+	This is analogous to the symbolic variable map, $\sigma$, except for mapping probabilistic symbolic variables to distributions instead from program variables to symbolic expressions.
+	\item \textit{Path probability.} For each path, we adjoin a path probability expression, $p$, which is parameterized by universal symbolic variables.
+	% 
+	Now each path can be identified by both its path condition and its probability.
 \end{itemize}
@@
 	\caption{PSE Assignment Algorithm}
+	\label{alg:assign}
 	\begin{algorithmic}[1]
-			\Function{PSEAssignment}{$\mathtt{x}, e, \varphi, \sigma, P, I$}
-			\Let{$e_{sym}$}{Convert $v$ into a symbolic expression using $\sigma$}
+		\Function{PSEAssignment}{$\mathtt{x}, e, \varphi, \sigma, P$}
+		\Let{$e_{sym}$}{$\sigma[e]$}
 		\State{$\sigma[\mathtt{x}] = e_{sym}$}
-			\State\Return{$(\varphi,\sigma, P, I)$}
+		\State\Return{$(\varphi,\sigma,P)$}
 		\EndFunction
@@
 \end{algorithm}
+
+\begin{paragraph}{Assignment}
+	For assignment statements of the form $\mathtt{x} \leftarrow e$, where $\mathtt{x}$ is a \textit{program} variable and $e$ is an expression, probabilistic symbolic execution proceeds identically to traditional symbolic execution, as detailed in Alg.~\ref{alg:assign}.
+	%
+	On the \textit{symbolic execution} side, the \textit{symbolic variable} mapping ($\Delta$) is updated with the result of the assignment operation is stored back in the current \textit{state} for further execution as shown in Line~\ref{line:assign} of Alg~\ref{alg:symbex}.
+\end{paragraph}
 
@@
 
+\begin{paragraph}{Sampling}
+	For sampling statements, $\mathtt{x} \xleftarrow{\$} d$, where $\mathtt{x}$ is a \textit{program} variable and $d$ is a distribution expression, Alg.~\ref{alg:sample} is used.
+	% 
+	A fresh probabilistic symbolic variable, $\delta$, is created, $\sigma$ is updated to be $\sigma[\mathtt{x}] = \delta$, and the original distribution $d$ is recorded in $P$ by setting $P[\delta] = d$.
+	%
+	On the \textit{symbolic execution} side, the updated \textit{Distribution Map} ($P$) with the result of sampling operation is stored back in the current \textit{state} for further execution as shown in Line~\ref{line:make_pse} of Alg~\ref{alg:symbex}.
+\end{paragraph}
+
 \begin{algorithm}
@@
 		\Let{$(d_1,\ldots,d_n)$}{$(P[\delta_1],\ldots,P[\delta_n])$}
-			\Let{$p_c$}{$\frac{\displaystyle\sum_{(v_1,\ldots,v_n) \in \dom{d_1} \times \cdots\times \dom{d_n}} [(c_{sym} \wedge \varphi)\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]}{\displaystyle\sum_{(v_1,\ldots,v_n) \in \dom{d_1} \times \cdots\times \dom{d_n}}[\varphi\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]}$}\\
-			\Return{$((\varphi \wedge c_{sym}, \sigma,P,p_c), (\varphi \wedge \neg c_{sym}, \sigma,P,1-p_c))$}
+		\Let{$p_c$}{$\frac{\displaystyle\sum_{(v_1,\ldots,v_n) \in \dom{d_1} \times \cdots\times \dom{d_n}} [(c_{sym} \wedge \varphi)\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]}{\displaystyle\sum_{(v_1,\ldots,v_n) \in \dom{d_1} \times \cdots\times \dom{d_n}}[\varphi\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]}$}
+		\State\Return{$((\varphi \wedge c_{sym}, \sigma,P,p_c), (\varphi \wedge \neg c_{sym}, \sigma,P,1-p_c))$}
 		\EndFunction
@@
 
-	\begin{algorithm}
-		\caption{Getting Path Constraints : Symbolic Execution}
-		\label{alg:symbex}
-		\begin{algorithmic}[1]
-			\Function{SymbEx}{$P_{prog} : Program$}
-				\Let{$\varphi_{paths}$}{[]}, {$Ex_{stack}$} $\leftarrow$ {[]}, $\Delta \leftarrow$ {[]}, $\phi_{paths} \leftarrow \phi$  \algorithmiccomment{Initialization}
-				\Let{$I_{0}$}{\textsc{getStartInstruction}($P_{prog}$)}
-				\Let{$S_{0}$}{[$I_{0}$, $\phi_{path}$, $\Delta$]} \algorithmiccomment{Empty Initial State}
-				\State {$Ex_{stack}$.\textsc{Push}({$S_{0}$})} \algorithmiccomment{Start with $S_{cur}$ in Execution Stack}
-				\While{$Ex_{stack}$ != $\phi$}
-					\Let{$S_{cur}$}{$Ex_{stack}$.\textsc{Pop}( )}, $I_{cur} \leftarrow S_{cur}[1]$ \algorithmiccomment{Start State, [$I_{0}$, $\phi_{path}$, $\Delta$]}
-					\Switch{\textsc{instType}($I_{cur}$)} \label{line:inst_case}
-					\Case{v := e} \algorithmiccomment{Assignment Instruction} \label{line:assign}
-						\Let{$I_{cur}$}{\textsc{getNextInstruction}($I_{cur}$)}
-						\Let{$S_{cur}$}{[$I_{cur}$, $\phi_{path}$, $\Delta$[v $\rightarrow$ \textsc{Eval($e$, $\Delta$)}]]}
-						\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
-					\EndCase
-					\Case{\textbf{if} $(c_{sym})$ \textbf{then} $P_{1}$ \textbf{else} $P_{2}$} \algorithmiccomment{Branch Instruction} \label{line:branch}
-						\If{(\textsc{isSat}($c_{sym}$) $\wedge$ \textsc{isSat}($\neg c_{sym}$))} \algorithmiccomment{Both cases SAT}
-							\Let{$I_{1}$}{\textsc{getStartInstruction}($P_{1}$)} \Let{$I_{2}$} {\textsc{getStartInstruction}($P_{2}$)}	
-							\Let{$S_{true}$}{[$I_{1}$, $\phi_{path} \wedge c_{sym}$, $\Delta$]} \label{line:true_state}
-							\Let{$S_{false}$}{[$I_{2}$, $\phi_{path} \wedge (\neg c_{sym})$, $\Delta$]} \label{line:false_state}
-							\State {$Ex_{stack}$.\textsc{Push}({$S_{false}$})}
-							\State {$Ex_{stack}$.\textsc{Push}({$S_{true}$})} \algorithmiccomment{Start with True State}
-						\ElsIf{\textsc{isSat}($c_{sym}$)} \algorithmiccomment{True case SAT}
-							\Let{$I_{cur}$}{\textsc{getStartInstruction}($P_{1}$)}
-							\Let {$S_{cur}$}{[$I_{cur}$, $\phi_{path} \wedge c_{sym}$, $\Delta$]}
-							\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
-						\ElsIf{\textsc{isSat}($\neg c_{sym}$)} \algorithmiccomment{False case SAT}
-							\Let{$I_{cur}$}{\textsc{getStartInstruction}($P_{2}$)}
-							\Let{$S_{cur}$}{[$I_{2}$, $\phi_{path} \wedge (\neg c_{sym})$, $\Delta$]}
-							\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
-						\Else \algorithmiccomment{Unconditional Branch}
-							\Let{$I_{cur}$}{\textsc{getNextInstruction}($I_{cur}$)}
-							\Let{$S_{cur}$}{[$I_{cur}$, $\phi_{path}$, $\Delta$]}
-							\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
-						\EndIf
-					\EndCase
-					\Case{\textbf{assume}$(v == expr)$} \algorithmiccomment{Assume Instruction} \label{line:assume}
-						\Let{$I_{cur}$}{\textsc{getNextInstruction}($I_{cur}$)}	
-						\If{\textsc{isSat}($v == expr$)} \algorithmiccomment{Check Satisfiablilty}
-							\Let{$S_{cur}$}{[$I_{cur}$, $\phi_{path} \wedge (v == expr)$, $\Delta$]}
-							\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
-						\Else 
-							%\Let{$S_{cur}$}{[$I_{cur}$, $\phi_{path} \wedge $(\textsc{false}), $\Delta$]}
-							\Let {$\phi_{path}$}{$\phi$} \algorithmiccomment{Infeasible Path}
-						\EndIf
-					\EndCase
-					\Case{\textbf{HALT}} \algorithmiccomment{Terminate Instruction}
-						\Let{$\varphi_{paths}$}{$\varphi_{paths}$.\textsc{Append}($\phi_{path}$)}		
-					\EndCase
-					\EndSwitch
-				\EndWhile \\
-				\Return{$\varphi_{paths}$}
-			\EndFunction
-		\end{algorithmic}
-	\end{algorithm}
+\begin{paragraph}{Branches (Alg.~\ref{alg:branch})}
+	Note that with the inclusion of probabilistic symbolic variables we can now either branch on universal or probabilistic symbolic variables (or both).
+	% 
+	Intuitively, branches are handled much the same in probabilistic symbolic execution as they are in traditional symbolic execution save for one detail: now branches have a probability associated with them.
+	% 
+	Given a guard expression $c$, how do we compute the probability of $c$ being true?
 
-	When a sampling statement, $\mathtt{x} \xleftarrow{\$} d$, is reached, a fresh probabilistic symbolic variable, $\delta$, is created, $\sigma$ is updated to be $\sigma[\mathtt{x}] = \delta$, and the original distribution $d$ is recorded in $P$ by setting $P[\delta] = d$.
+	To gain intuition, for now just consider the special case where the guard condition only references universal symbolic variables.
 	% 
-	Note that with the inclusion of probabilistic symbolic variables we can now either branch on universally quantified or probabilistic symbolic variables (or both).
+	Let $c_{sym}$ be the equivalent symbolic expression for the guard $c$ and assume that $c_{sym}$ does not reference any probabilistic symbolic variables.
 	% 
-	For guards whose symbolic version does not contain any probabilistic symbolic variables, probabilstic symbolic execution works nearly identically to traditional symbolic execution, save one detail: the probability of taking the branch.
+	Note that which side of the branch is taken is solely determined by the setting of the univeral symbolic variables.
 	% 
-	If $c_{sym}$ is a symbolic expression which represents the guard to a branch, and $c_{sym}$ does not contain any probabilistic symbolic variables, then we define the probability of taking the ``true'' branch is $[c_{sym}]$, and the probability of taking the ``false'' branch is $[\neg c_{sym}]$, where $[\cdot]$ are Iverson brackets.
+	Therefore, one side of the branch must have a probability of 1, and the other side, 0.
+	% 
+	We use Iverson brackets to formalize this idea; the probability of taking the ``true'' branch is $[c_{sym}]$, and the probability of taking the ``false'' branch is $[\neg c_{sym}]$.
 
-	For probabilistic branches, i.e. guards which branch on probabilistic symbolic variables, Alg.~\ref{alg:branch} is used instead of the traditional symbolic execution branch algorithm.
+	For probabilistic branches, i.e.
+guards which branch on probabilistic symbolic variables, computing the branch probability is trickier as given a fixed setting of the universal symbolic variables, it is unclear which branch execution will follow as this is dependent upon the sampling results.
 	% 
-	Without loss of generality, consider a branch of the form $\mathbf{if}~c~\mathbf{then}~P_1~\mathbf{else}~P_2$ where $c$ is a probabilistic branch.
+	Without loss of generality, consider a branch of the form $\mathbf{if}~c~\mathbf{then}~S_1~\mathbf{else}~S_2$.
 	% 
-	As before, we define $c_{sym} = \sigma[c]$.
+	As before, we define $c_{sym} = \sigma[c]$, or the symbolic expression representation of the guard expression, $c$, and we want to compute the probability of taking the ``true'' branch and the ``false'' branch, assuming execution has reached the start of the \texttt{if} condition.
 	% 
-	The core of Alg.~\ref{alg:branch} is computing the probability of taking each branch.
+	Since the path condition $\varphi$ records the necessary constraints on the universal and probabilistic symbolic variables which must hold in order to reach this \texttt{if} condition, we can view this probability a \textit{conditional probability}, or the probability that $c_{sym}$ holds given that $\varphi$ is satisfied.
 	% 
-	We interpret probabilistic branches as a conditioning operation on the distributions which are mentioned in the guard of the branch.
-	%
-	Under this interpretation, we aim to compute $\Pr[c_{sym} \mid \varphi]$ where $\varphi$ is the current path condition formula.
+	In formal notation, we aim to compute $\Pr[c_{sym} \mid \varphi] = \frac{\Pr[c_{sym}\wedge \varphi]}{\Pr[\varphi]}$.
 
-	% Add small example 
-	We use a form of model counting in order to compute $p_c$, the probability of $c$ being true.
+	For now we restrict our view to uniform distributions, although we can support weighted distributions without further problems.
 	% 
@@
 	% 
-	We then count the number of \textit{assignments} from $\mathcal{D}$ which satisfy $c_{sym} \wedge \varphi$ and $\varphi$, and divide these two quantities as shown on line 5 of Alg.~\ref{alg:branch}.
+	We then count the number of elements (or \textit{assignments}) from $\mathcal{D}$ which satisfy $c_{sym} \wedge \varphi$ and $\varphi$, and divide these two quantities as shown on line 5 of Alg.~\ref{alg:branch}.
 	% 
-	In Section~\ref{sec:formalization} we have a proof of correctness for this quantity, but the intuition is by applying the definition of conditional probability.
+	Note that $p_c$ is not necessarily a value, but rather a symbolic expression containing constants and universal symbolic variables.
 	% 
-	Note that $p_c$ is not necessarily a value, but rather a symbolic expression containing constants and universally quantified symbolic variables.
+	Additionally, we exploit the fact that the sum of the conditional probabilities of the branch outcomes is 1, which allows us to avoid computing the probability of taking the ``false'' branch directly.
+\\
 	% 
-	We exploit the fact that the sum of the conditional probabilities of the branch outcomes is 1, which allows us to avoid computing the probability of taking the ``false'' branch directly.
+	On the \textit{symbolic execution} side, upon reaching the \textit{branch} instruction at Line~\ref{line:branch} in Alg~\ref{alg:symbex}, two new \textit{states} are created ($S_{true}$ \& $S_{false}$) and the constraint encoding the actual \textit{branch condition} ($c_{sym}$) [Line~\ref{line:true_state}] and it's negation ($\neg c_{sym}$)  [Line~\ref{line:false_state}] are appended to them representing the \textit{true} \& \textit{false} side of the \textit{branch}.
+	%
+	These states are then added to the \textit{execution} stack containing \textit{states} that need to be explored next.
+The process continues untill all the \textit{states} in the \textit{execution} stack are explored.
+\end{paragraph}
 
-	\subsection{Formalization}
-	\label{sec:formalization}
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}{.3\textwidth}
+		\centering
+		{\small
+			\begin{algorithmic}[1]
+				\State{$\mathtt{x}\xleftarrow{\$}\mathrm{UniformInt}(1,3)$}
+				\State{$\mathtt{y}\xleftarrow{\$}\mathrm{UniformInt}(1,3)$}
+				\If{$\mathtt{x} > 1$}
+				\If{$\mathtt{x} < \mathtt{y}$}
+				\State\Return{$\mathtt{True}$}
+				\EndIf
+				\Else
+				\State\Return{$\mathtt{False}$}
+				\EndIf
+			\end{algorithmic}
+		}
+		\caption{Program}
+		\label{fig:exam_program}
+	\end{subfigure}
+	\begin{subfigure}{.69\textwidth}
+		\centering
+		{\small
+			\begin{forest}baseline,for tree=draw,
+				[{$\varphi=\top$},align=center, base=bottom
+				[{$\varphi = \delta_1 > 1$}, align=center, base=bottom, edge label={node [midway,above] {$\frac{2}{3}$} }
+				[{$\varphi = (\delta_1 > 1) \wedge (\delta_1 < \delta_2)$}, align=center, base=bottom, edge label={node [midway,above] {$\frac{1}{6}$} }
+				[{\texttt{True}}]]
+				[{$\varphi = (\delta_1 > 1) \wedge \neg(\delta_1 < \delta_2)$}, align=center, base=bottom, edge label={node [midway,above] {$\frac{5}{6}$} }
+				[{\texttt{False}}]]]
+				[{$\varphi = \neg(\delta_1 > 1)$}, align=center, base=bottom, edge label={node [midway,above] {$\frac{1}{3}$} }
+				[{\texttt{False}}]]]
+			\end{forest}
+		}
+		\caption{Execution Tree}
+		\label{fig:exam_tree}
 
-	In this section we present the formalization of our method. First, we will present our notation and definitions, and then provide proofs of correctness and soundness of our technique.
+	\end{subfigure}
+	\caption{An example program and its symbolic execution tree}
+	\label{fig:example}
+\end{figure}
 
-	\subsubsection{Notation \& Definitions}
-	\label{sec:notation}
+\begin{paragraph}{Example}
+	Consider the code in Fig.~\ref{fig:exam_program} and suppose we wish to calculate the probability of the program returning \texttt{True}.
+	% 
+	Following Alg.~\ref{alg:sample} for lines 1,2, we generate fresh probabilistic symbolic variables for $\mathtt{x}$ and $\mathtt{y}$, $\delta_1$ and $\delta_2$, respectively.
+	% 
+	We also store the distributions which $\delta_1$ and $\delta_2$ are samples from, namely the discrete uniform distribution $\mathcal{U}\{1,3\}$.
+	% 
+	In our notation, we say that $\sigma = \{ \mathtt{x} \mapsto \delta_1, \mathtt{y} \mapsto \delta_2 \}$ and $P = \{ \delta_1,\delta_2 \mapsto \mathcal{U}\{1,3\} \}$.
+	% 
+	Now following Alg.~\ref{alg:branch} to process line 4 of Fig.~\ref{fig:exam_program}, note that $\mathcal{D} = \{1,2,3\} \times \{1,2,3\}$ and
 
-	The goal of this section is to describe how $R=(\varphi,\sigma,P)$, the inputs to Alg.~\ref{alg:branch} is an abstraction of a \textit{distribution of program memories} before a branch guarded by a program expression $c$.
-	% 
-	To begin, we will define some notation:
-	\begin{itemize}
-		\item Let $Vars$ be the set of all program variables, $ForallSymVars$ be the set of all universally quantified symbolic variables, $ProbSymVars$ be the set of all probabilistic symbolic variables, $SymVars = ForallSymVars \cup ProbSymVars$ be the combined set of all symbolic variables, and $Vals$ be the set of all values.
-		\item Let $a_f: ForallSymVars \rightarrow Vals$ be an assignment of universally quantified symbolic variables to values and let $ForallAssign$ be the set of all such assignments.
-		\item Similarly, let $a_p : ProbSymVars \rightarrow Vals$ be an assignment of probabilistic symbolic variables to values and let $ProbAssign$ be the set of all such assignments.
-		\item Let $m : Vars \rightarrow Vals$ be a program memory which translates program variables into values, and let $Mems$ be the set of all program memories.
-		\item Let $de : Mems \rightarrow (Vals \rightarrow [0,1])$ be a distribution expression parameterized by program memories, and let $DistExprs$ be the set of all distribution expressions.
-		\item Let $d : ForallAssign \times Mems \rightarrow [0,1]$ be a distribution of program memories parameterized by assignments to universally quantified symbolic variables and let $MemDists$ be the set of all parameterized distributions of program memories.
-	\end{itemize}
+	\begin{align*}
+		p_c = \Pr[\delta_1 < \delta_2 \mid \delta_1 > 1] &= \frac{\Pr[(\delta_1 < \delta_2) \wedge (\delta_1 > 1)]}{\Pr[\delta_1 > 1]}\\
+		&= \frac{\displaystyle\sum_{(v_1,v_2) \in \mathcal{D}} [(\delta_1 < \delta_2) \wedge (\delta_1 > 1)\{\delta_1 \mapsto v_1, \delta_2 \mapsto v_2\}]}{\displaystyle\sum_{(v_1,v_2) \in \mathcal{D}} [(\delta_1 > 1)\{\delta_1 \mapsto v_1\}]}\\
+		&= \frac{1}{6}
+	\end{align*}
 
-	Additionally, we will use emphatic brackets for two purposes:
-	\begin{itemize}
-		\item If $e \in ProgExprs$ is a \textit{program} expression containing the program variables $\mathtt{x}_1,\ldots,\mathtt{x}_n \in Vars$, and $m \in Mems$, then
-		\[
-		\deno{e}m = \text{eval}(e[\mathtt{x}_1 \mapsto m(\mathtt{x}_1),\ldots,\mathtt{x}_n \mapsto m(\mathtt{x}_n)])
-		\]
-		\item If $e \in SymExprs$ is a \textit{symbolic} expression containing the symbolic variables $\alpha_1,\ldots,\alpha_n \in ForallSymVars$ and $\delta_1,\ldots,\delta_m \in ProbSymVars$, and $a_f \in ForallAssign$ and $a_p \in ProbAssign$, then
-		\[
-		\deno{e}a_fa_p = \text{eval}(e[\alpha_1\mapsto a_f(\alpha_1),\ldots,\alpha_n \mapsto a_f(\alpha_n), \delta_1 \mapsto a_p(\delta_1), \ldots, \delta_m \mapsto a_p(\delta_m)])
-		\]
-	\end{itemize}
-
-	With this notation in hand, we can now define what it means for $R$ to be an abstraction of a distribution of programs memories.
-
-	\begin{definition}
-		\label{def:combined}
-		Let $R = (\varphi, \sigma, P)$ be the abstraction generated by the symbolic execution algorithm where $\varphi: ForallAssign \times ProbAssign \rightarrow \{0,1\}$ denotes whether the path condition is true or false under the given assignments, $\sigma : Vars \rightarrow SymExprs$ is the mapping from program variables to symbolic expressions generated through symbolic execution, and $P : ForallAssign \rightarrow ProbSymVars \rightharpoonup (Vals \rightarrow [0,1])$  is the mapping from probabilistic symbolic variables to the distribution it is sampled from parameterized by assignments of forall symbolic variables.
-		% 
-		Additionally, for every assignment of forall symbolic variables, $a_f \in ForallAssign$, $\mathrm{domain}(P(a_f)) = \{\delta_1,\ldots,\delta_k\}$.
-		% 
-		Let $\alpha_1,\ldots,\alpha_l \in ForallSymVars$ be the forall symbolic variables which correspond to the $l$ parameters to the program.
-		% 
-		For every assignment of probabilistic and forall symbolic variables, $a_f \in ForallAssign, a_p \in ProbAssign$, let $\nu : ForallAssign \rightarrow (ProbAssign \rightarrow [0,1])$ be a distribution of assignments of probabilistic symbolic variables parameterized by assignments of forall symbolic variables, defined as
-		\[
-		\nu(a_f,a_p) \triangleq \prod_{i=1}^k \Pr_{v \sim P(a_f,\delta_i)}[v = a_p(\delta_i)].
-		\]
-		% 
-		We say that a distribution $d$ satisfies our abstraction $R$ if, for all assignments of forall symbolic variables, $a_f \in ForallAssign$, $\displaystyle\Pr_{a_p' \sim \nu(a_f)}[\varphi(a_f,a_p') = 1] > 0$, and if $\mu : ForallAssign \rightarrow (ProbAssign \rightarrow [0,1])$ is defined as
-		\[
-		\mu(a_f,a_p) = \cfrac{\Pr_{a_p' \sim \nu(a_f)}[a_p' = a_p \land \varphi(a_f,a_p') = 1]}{\Pr_{a_p' \sim \nu(a_f)}[\varphi(a_f,a_p')=1]}.
-		\]
-		Additionally, define $\text{convertToMem} : (Vars \rightarrow SymExprs) \rightarrow ForallAssign \rightarrow ProbAssign \rightarrow Mem$ as
-		\begin{equation*}
-			\text{convertToMem}(\sigma,a_f,a_p) \triangleq \lambda (\mathtt{x}: Vars)~.~\deno{\sigma(\mathtt{x})}a_fa_p,
-		\end{equation*}
-		and let $\text{convertFromMem}(\sigma,a_f,m) = (\text{convertToMem}(\sigma,a_f))^{-1}(m)$.
-		% 
-		Then,
-		\[
-		d(a_f,m) = \sum_{a_p \in \text{convertFromMem}(\sigma,a_f,m)} \mu(a_f,a_p).
-		\]
-	\end{definition}
-
-	We additionally define the semantics for the three main types of statements which concerns probabilistic symbolic execution: assignments, probabilistic samples, and branches.
-
-	\begin{definition}[Assignment Semantics]
-		Let $d \in MemDists$ be a distribution of program memories parameterized by assignments to forall symbolic variables.
-Let $\mathtt{x} = e$ be an arbitrary assignment of the program variable $\mathtt{x} \in Vars$ to the program expression $e \in ProgExprs$.
-Let $\text{assign}_{\mathtt{x}=e} : Mems \rightarrow Mems$ is defined as
-		\[
-		\text{assign}_{\mathtt{x}=e}(m) = \lambda(\mathtt{y} : Vars)
-		\begin{cases}
-			\deno{e}m & \text{if $\mathtt{x} = \mathtt{y}$}\\
-			m(\mathtt{y}) & \text{otherwise}
-		\end{cases}
-		\]
-		and let $\text{unassign}_{\mathtt{x}=e} = \text{assign}_{\mathtt{x}=e}^{-1}$.
-Then we define $d_{\mathtt{x}=e}$ to be the distribution over program memories parameterized by assignments to forall symbolic variables after executing the assignment statement $\mathtt{x}=e$ to be
-		\[
-		d_{\mathtt{x}=e}(a_f,m) = \sum_{m' \in \text{unassign}_{\mathtt{x}=e}(m)} d(a_f,m').
-		\]
-	\end{definition}
-
-	\begin{definition}[Sampling Semantics]
-		Let $d \in MemDists$ be a distribution of program memories parameterized by assignments to forall symbolic variables.
-Let $\mathtt{x} \sim de$ be an arbitrary sampling instruction which assigns the program variable $\mathtt{x} \in Vars$ to a random element from the distribution of values parameterized by a memory, represented as a distribution expression $de \in DistExprs$.
-Let $\text{desample} : Vars \times Mems \rightarrow \mathcal{P}(Mems)$ be defined as
-		\[
-		\text{desample}(\mathtt{x},m) = \{ m'\in Mems \mid \forall (\mathtt{y} \in Vars)~.~(\mathtt{y} \neq \mathtt{x} \wedge m'(\mathtt{y}) = m(\mathtt{y}))\}.
-		\]
-		Then, we define $d_{\mathtt{x} \sim de}$ to be the distribution over program memories parameterized by assignments to forall symbolic variables after executing the sampling statement $\mathtt{x} \sim de$ to be
-		\[
-		d_{\mathtt{x} \sim de}(a_f,m) = \sum_{m' \in \text{desample}(m)} (\deno{de}a_f)(m(\mathtt{x})) \cdot d(a_f,m').
-		\]
-	\end{definition}
-
-	\begin{definition}[Conditional Distribution of Program Memories]
-		\label{def:cond}
-		Let $a_f \in ForallAssign$ be an arbitrary assignment of forall symbolic variables, $c$ be a guard of an \texttt{if} condition, $d \in MemDists$ be a distribution of program memories parameterized by assignments to forall symbolic variables, and $\mathtt{x}_1,\ldots,\mathtt{x}_n \in Vars$ be all of the program variables in $c$.
-Then for all program memories $m \in Mems$, $d$ conditioned on a guard $c$ being true, represented as $d_c$ is defined as
-		\[
-		d_c(a_f,m) = \frac{\Pr_{m' \sim d(a_f)}\left[ m' = m \land \deno{c}m' = \mathtt{true} \right]}{\Pr_{m' \sim d(a_f)}\left[ \deno{c}m' = \mathtt{true} \right]}
-		\]
-		Similarly, for all program memories $m \in Mems$, $d$ conditioned on a guard $c$ being false, represented as $d_{\neg c}$ is defined as
-		\[
-		d_{\neg c}(a_f,m) = \frac{\Pr_{m' \sim d(a_f)}\left[ m' = m \land \deno{c}m' = \mathtt{false} \right]}{\Pr_{m' \sim d(a_f)}\left[ \deno{c}m' = \mathtt{false} \right]}
-		\]
-	\end{definition}
-
-	\subsubsection{Proofs}
-	\label{sec:proofs}
-
-	\section{Implementation}
-	\label{sec:implementation}
-
-	{\color{red} Subhajit \& Sumit: Write something about KLEE and the implementation here!}
+	This probability means that the probability of taking the ``true'' branch of the inner \texttt{if} condition is only $\frac{1}{6}$, which makes sense as \texttt{x} is restricted to be either $2$ or $3$, but \texttt{y} can be either 1,2, or 3; however, only one combination of \texttt{x} and \texttt{y} will satisfy $\mathtt{x} < \mathtt{y}$, namely $\mathtt{x} = 2$ and $\mathtt{y} = 3$.
+\end{paragraph}
 
 We use a robust dynamic symbolic execution engine, \textsc{KLEE} to generate the \textit{path constraints} corresponding to each path that our tool explores.
-For each path in the program, \textsc{KLEE} stores a list of \textit{constraints} that encodes the whole path.
-These constraints are over \textit{program} variables that have been marked \texttt{make\_symbolic()} by the user and are stored in \textsc{KLEE} as \textit{metadata} in the \textit{state} data structure during the \textit{dynamic} symbolic execution of the program.
-Apart from \textit{path constraints}, the \textit{state} also contains a mapping of \textit{symbolic} variables to expressions that are either  \textit{symbolic} or \textit{concrete} (in the case of concrete execution of the program) and a list of \textit{instructions} currently getting executed as a part of the \textit{state}.
-
-	During \textit{dynamic} execution, \textsc{KLEE} executes each \textit{instruction} in the program and updates the \textit{state} along with the \textit{symbolic} variables mapping ($\Delta$) depending upon \textit{type} of the \textit{instruction} it executes as described in Algorithm~\ref{alg:symbex}.
-	\textsc{KLEE} assigns values to \textit{symbolic} variables by employing an \textsc{SMT Solver} (\textsc{Z3} as in our case) for solving the current set of \textit{constraints} seen so far in the program path and also by concretizing some of the values that get evaluated as a result of \textit{concrete} execution (Eg.
-return value from external function calls).
-
-	For the purpose of our implementation, we modify \textsc{KLEE} to support creation of \textit{probabilistic symbolic} variables whose values can be sampled from a distribution and dump the whole set of \textit{path} constraints that is stored in the \textit{state} corresponding to the current execution of the program at each of (1) \textbf{\textit{assignment}} [Algorithm~\ref{alg:symbex}, Line~\ref{line:assign}], (2) \textbf{\textit{branch}} [Algorithm~\ref{alg:symbex}, Line~\ref{line:branch}], \& (3) \textbf{\textit{assume}} [Algorithm~\ref{alg:symbex}, Line~\ref{line:assume}] statements.
-These dumps are later refined and used by the tool for further processing.
-
-	{\color{blue} Upon reaching the \textit{branch} instruction at Line~\ref{line:branch} in Algorithm~\ref{alg:symbex}, based on whether the \textit{path constraints} are solvable upon adding the \textit{branch} [Line~\ref{line:branch}] condition, \textsc{KLEE} forks the current \textit{state} by making two identical copies of it and then appending to each of \textit{new} states one additional constraint encoding the \textit{true} [Line~\ref{line:true_state}] and \textit{false} [Line~\ref{line:false_state}] side of the branch and adds it to the \textit{execution} stack containing \textit{states} that need to be explored next.
-The process continues untill all the \textit{states} in the \textit{execution} stack are explored.}
-
-	\section{Case Studies}
-	\label{sec:case_studies}
-
-	\section{Evaluation}
-	\label{sec:eval}
-
-	\section{Related Work}
-	\label{sec:related}
-	{\color{red} Subhajit \& Sumit: If you could both start looking into related work (Mayhap, original PSE paper, Axprof, P4WN, PSI), that would be great!}
-	\begin{itemize}
-		\item Compare and Contrast with Mayhap, PSE, AxProf, P4WN \& PSI.
-		\item Explain how we differ by not using Model Counting but a Constraint Solving approach.
-		\item Support for \textsc{ForAll} variables along with \textit{probabilistic} variables. 
-	\end{itemize}
-	\section{Conclusion \& Future Work}
-	\label{sec:conclusion}
-
-	%% Acknowledgments
-	\begin{acks}                            %% acks environment is optional
-		%% contents suppressed with 'anonymous'
-		%% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
-		%% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
-		%% acknowledge financial support and will be used by metadata
-		%% extraction tools.
-		% This material is based upon work supported by the
-		% \grantsponsor{GS100000001}{National Science
-		%   Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
-		% No.~\grantnum{GS100000001}{nnnnnnn} and Grant
-		% No.~\grantnum{GS100000001}{mmmmmmm}.  Any opinions, findings, and
-		% conclusions or recommendations expressed in this material are those
-		% of the author and do not necessarily reflect the views of the
-		% National Science Foundation.
-	\end{acks}
-
-	%% Bibliography
-	%\bibliography{bibfile}
-
-	%% Appendix
-	\appendix
-	\section{Appendix}
-
-	Text of appendix \ldots
-
-\end{document}
+For the purpose of our implementation, we modify \textsc{KLEE} to support creation of \textit{probabilistic symbolic} variables whose values can be sampled from a distribution and process the \textit{path} constraints that are stored in the \textit{state} corresponding to the current execution of the program at each of \textbf{\textit{assignment}} [Algorithm~\ref{alg:symbex}, Line~\ref{line:assign}], \textbf{\textit{branch}} [Algorithm~\ref{alg:symbex}, Line~\ref{line:branch}] \& \textbf{\textit{sampling}} (\texttt{make\_pse\_symbolic()}) statements.
+[Algorithm~\ref{alg:symbex}, Line~\ref{line:make_pse}].

### 2021-06-30 baseline-exp/run.sh

@@ -9,7 +9,7 @@ export RUNNER=$1
 
 rm -rf bin/* 
 rm -rf output/*
-rm -rf tests/*
+# rm -rf tests/*
 
 # TODO : Replace with custom test generator (dummy-baseline) 
 # These are inputs for the ForAll variables.
@@ -18,7 +18,7 @@ echo "  ---- Generating Inputs for ${RUNNER} ----  "
 # do 
 #     dd if=/dev/random of=tests/input_${index}.txt bs=64 count=1
 # done
-python3 generateInputs.py 250
+# python3 generateInputs.py 250
 
 echo "  ---- Building Binary : ${RUNNER} ----  "
 cd bin/

### 2021-06-30 baseline-exp/src/bloomfilter.cpp

@@ -14,6 +14,7 @@
 #include <cstdio>
 #include <fcntl.h>
 #include <iostream>
+#include <limits>
 #include <math.h>
 #include <prob_hash.h>
 #include <random>
@@ -118,8 +119,8 @@ int bloom_init(struct bloom *bloom, int entries, double error) {
   }
 
   bloom->hashes = (int)ceil(0.693147180559945 * bloom->bpe); // ln(2)
-  printf("Hashes = %d\n", bloom->hashes);
-  printf("Bits = %d\n", bloom->bits);
+  // printf("Hashes = %d\n", bloom->hashes);
+  // printf("Bits = %d\n", bloom->bits);
 
   bloom->bf = (unsigned char *)malloc(bloom->bytes * sizeof(unsigned char));
   if (bloom->bf == NULL) { // LCOV_EXCL_START
@@ -178,66 +179,44 @@ int main() {
    * We run the program multiple times, each time with a
    * different setting of the ForAll variables.
    */
-  int entries = 0, add_item = 0, search_item = 1, win = 0, loop_count = 0,
-      termCount = 0;
-  double error = 0.00;
-  std::vector<std::string> inputs = {"Zach1",  "Zach2",     "Justin1",
-                                     "Sumit1", "Subhajit1", "Justin2"};
+  int entries = 0, add_item = 0, search_item = 0, N = 0;
+  long double error = 0.00;
 
-  std::default_random_engine generator;
-  std::uniform_int_distribution<int> range_dist(0, 5);
-  std::uniform_real_distribution<double> error_dist(0.01, 0.99);
+  // For each setting of the forAlls,
+  // We run the program termCount number of times.
 
-  entries = 1;
-  error = error_dist(generator);
-  add_item = range_dist(generator);
-  search_item = range_dist(generator);
-  scanf("%d", &termCount);
+  scanf("%d", &N);
+  scanf("%d", &entries);
+  scanf("%Lf", &error);
+  scanf("%d", &add_item);
+  scanf("%d", &search_item);
 
-  while (termCount--) {
+  std::vector<std::string> inputs;
 
-    // For each setting of the forAlls,
-    // We run the program termCount number of times.
-    struct bloom bloom;
-    bloom_init(&bloom, entries, error);
-    bloom_add(&bloom, inputs[add_item]);
+  assert(add_item < N && add_item >= 0);
[…]

### 2021-06-30 shared/Paper-Draft/montyhall.c

@@ -1,0 +1,37 @@
+int monty_hall(int choice, bool door_switch) {
+	int car_door = uniform_int(1,3);
+	int host_door;
+	if (choice != 1 && car_door != 1) {
+		host_door = 1;
+	} else if (choice != 2 && car_door != 2) {
+		host_door = 2;
+	} else {
+		host_door = 3;
+	}
+	if (door_switch) {
+		if (host_door == 1) {
+			if (choice == 2) {
+				choice = 3;
+			} else {
+				choice = 2;
+			}
+		} else if (host_door == 2) {
+			if (choice == 1) {
+				choice = 3;
+			} else {
+				choice = 1;
+			}
+		} else {
+			if (choice == 1) {
+				choice = 2;
+			} else {
+				choice = 1;
+			}
+		}
+	}
+	if (choice == car_door) {
+		return true;
+	} else {
+		return false;
+	}
+}

### 2021-06-30 shared/Paper-Draft/symbolic_execution.tex
WIP : SymbEx Algorithm

@@
 	\begin{algorithmic}[1]
-		\Function{SymbEx}{$Prog : Program$}
-		\Let{$\varphi_{paths}$}{[]}, {$Ex_{stack}$} $\leftarrow$ {[]}, $\Delta \leftarrow$ {[]}, $\phi_{paths} \leftarrow \phi$, $P \leftarrow \phi$  \algorithmiccomment{Initialization}
-		\Let{$I_{0}$}{\textsc{getStartInstruction}($Prog$)}
-		\Let{$S_{0}$}{[$I_{0}$, $\phi_{path}$, $\Delta$, $\phi$]} \algorithmiccomment{Empty Initial State}
-		\State {$Ex_{stack}$.\textsc{Push}({$S_{0}$})} \algorithmiccomment{Start with $S_{cur}$ in Execution Stack}
-		\While{$Ex_{stack}$ != $\phi$}
-		\Let{$S_{cur}$}{$Ex_{stack}$.\textsc{Pop}( )}, $I_{cur} \leftarrow S_{cur}[1]$ \algorithmiccomment{Start State, [$I_{0}$, $\phi_{path}$, $\Delta$]}
-		\Switch{\textsc{instType}($I_{cur}$)} \label{line:inst_case}
-		\Case{\texttt{make\_pse\_sym}} ($x_{var},  d_{dist}$) \algorithmiccomment{Create \texttt{fresh} Symbolic Variable} \label{line:make_pse}
-		\Let{$I_{cur}$}{\textsc{getNextInstruction}($I_{cur}$)}
-		\Let{$\phi_{path}, \Delta, P$}{{\textbf{PSESample}}({$x_{var},  d_{dist}$, $\phi_{path}$, $\Delta$, $P$})}
-		\Let{$S_{cur}$}{[$I_{cur}$, $\phi_{path}$, $\Delta$, $P$]}
-		\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
+		\Function{SymbEx}{$S : Program$}
+		\Let{$\varphi_{paths}$}{[]}, {$E_{s}$} $\leftarrow$ {[]}, $\sigma \leftarrow$ {[]}, $\varphi \leftarrow \emptyset$, $P \leftarrow \{ \}$  \algorithmiccomment{Initialization}
+		\Let{$I_{0}$}{\textsc{getStartInstruction}($S$)}
+		\State {$E_{s} \leftarrow$  \{[$I_{0}$, $\varphi$, $\sigma$, $P$]\}} \algorithmiccomment{Start State [$I_{0}$, $\varphi$, $\sigma$, $P$]}
+		\While{$E_{s} \neq \emptyset$}
+		\Let{$\Delta_{c}$}{\textsc{GetNext}($E_{s}$)}, $\Delta_{c}$ $\rightarrow$ [$I_{c}$, $\varphi$, $\sigma$, $P$]  \algorithmiccomment{Get Next state from $E_{s}$}
+		\Switch{\textsc{instType}($I_{c}$)} \label{line:inst_case}
+		\Case{$\mathtt{x} \xleftarrow{\$} d$} \algorithmiccomment{Create \texttt{fresh} Symbolic Variable} \label{line:make_pse}
+		\Let{$I_{s}$}{\textsc{getNextInstruction}($I_{c}$)}
+		\Let{$\varphi, \sigma, P$}{{\textbf{PSESample}}({$x,  d$, $\varphi$, $\sigma$, $P$})}
+		\State {$E_{s} \leftarrow E_{s} \cup$ \{[$I_{c}$, $\varphi$, $\sigma$, $P$]\} }
 		\EndCase
-		\Case{v := e} \algorithmiccomment{Assignment Instruction} \label{line:assign}
-		\Let{$I_{cur}$}{\textsc{getNextInstruction}($I_{cur}$)}
-		\Let{$\phi_{path}, \Delta, P$}{{\textbf{PSEAssignment}}({v, e, $\phi_{path}$, $\Delta$, $P$})}
-		\Let{$S_{cur}$}{[$I_{cur}$, $\phi_{path}$, $\Delta$, $P$]}
-		\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
+		\Case{$\mathtt{x} \leftarrow e$} \algorithmiccomment{Assignment Instruction} \label{line:assign}
+		\Let{$I_{s}$}{\textsc{getNextInstruction}($I_{c}$)}
+		\Let{$\varphi, \sigma, P$}{{\textbf{PSEAssignment}}({v, e, $\varphi$, $\sigma$, $P$})}
+		\State {$E_{s} \leftarrow E_{s} \cup$ \{[$I_{c}$, $\varphi$, $\sigma$, $P$]\} }
 		\EndCase
-		\Case{\textbf{if} $(c_{sym})$ \textbf{then} $P_{1}$ \textbf{else} $P_{2}$} \algorithmiccomment{Branch Instruction}
-		\Let{$Branch_{expr}$}{{\textbf{PSEBranch}}({$c_{sym}$, $\phi_{path}$, $\Delta$, $P$})} \label{line:branch}
-		\Let{$I_{1}$}{\textsc{getStartInstruction}($P_{1}$)} \Let{$I_{2}$} {\textsc{getStartInstruction}($P_{2}$)}	
-		\Let{$S_{true}$}{[$I_{1}$, $\phi_{path} \wedge c_{sym}$, $\Delta$, $Branch_{expr}[0]$]} \label{line:true_state}
-		\Let{$S_{false}$}{[$I_{2}$, $\phi_{path} \wedge (\neg c_{sym})$, $\Delta$, $Branch_{expr}[1]$]} \label{line:false_state}
-		\State {$Ex_{stack}$.\textsc{Push}({$S_{false}$})}
-		\State {$Ex_{stack}$.\textsc{Push}({$S_{true}$})} \algorithmiccomment{Start with True State}
+		\Case{\textbf{if} $(c_{sym})$ \textbf{then} $S_{1}$ \textbf{else} $S_{2}$} \algorithmiccomment{Branch Instruction}
+		\Let{$((\varphi \wedge c_{sym}, \sigma,P,p_c), (\varphi \wedge \neg c_{sym}, \sigma,P,1-p_c))$}{{\textbf{PSEBranch}}({$c_{sym}$, $\varphi$, $\sigma$, $P$})} \label{line:branch}
+		\Let{$I_{t}$}{\textsc{getStartInstruction}($P_{1}$)} \Let{$I_{f}$} {\textsc{getStartInstruction}($P_{2}$)}	
+		\State {$E_{s} \leftarrow E_{s} \cup$ \{[$I_{t}$, $\varphi \wedge c_{sym}$, $\sigma$, $P$]\} }
+		\State {$E_{s} \leftarrow E_{s} \cup$ \{[$I_{f}$, $\varphi \wedge \neg c_{sym}$, $\sigma$, $P$]\} }
 		\EndCase
 		\Case{\textbf{HALT}} \algorithmiccomment{Terminate Instruction}
-		\Let{$\varphi_{paths}$}{$\varphi_{paths}$.\textsc{Append}($\phi_{path}$)}		
+		\Let{$\varphi_{paths}$}{$\varphi_{paths}$.\textsc{Append}($\varphi$)}		
 		\EndCase
@@
 % 
-Each \textit{instruction} in the program is executed and depending upon the \textit{type} of the \textit{instruction} the \textit{state} along with the \textit{symbolic variables} mapping, ($\Delta$ in Alg~\ref{alg:symbex}) are updated as described in Algorithm~\ref{alg:symbex}.
+Each \textit{instruction} in the program is executed and depending upon the \textit{type} of the \textit{instruction} the \textit{state} along with the \textit{symbolic variables} mapping, ($\sigma$ in Alg~\ref{alg:symbex}) are updated as described in Algorithm~\ref{alg:symbex}.
 % 
@@
 \[
-S := \mathbf{skip} \mid \mathtt{x} \leftarrow e \mid \mathtt{x} \xleftarrow{\$} d \mid S_1 ; S_2 \mid \mathbf{if}~e~\mathbf{then}~S_1~\mathbf{else}~S_2 \mid \mathbf{while}~e~\mathbf{do}~S 
+S := \mathbf{skip} \mid \mathtt{x} \leftarrow e \mid \mathtt{x} \xleftarrow{\$} d \mid \Delta_1 ; \Delta_2 \mid \mathbf{if}~e~\mathbf{then}~\Delta_1~\mathbf{else}~\Delta_2 \mid \mathbf{while}~e~\mathbf{do}~S
 \]
@@
 	%
-	On the \textit{symbolic execution} side, the \textit{symbolic variable} mapping ($\Delta$) is updated with the result of the assignment operation is stored back in the current \textit{state} for further execution as shown in Line~\ref{line:assign} of Alg~\ref{alg:symbex}.
+	On the \textit{symbolic execution} side, the \textit{symbolic variable} mapping ($\sigma$) is updated with the result of the assignment operation is stored back in the current \textit{state} for further execution as shown in Line~\ref{line:assign} of Alg~\ref{alg:symbex}.
 \end{paragraph}
@@
 		\Function{PSESample}{$\mathtt{x}, d, \varphi, \sigma, P$}
-		\Let{$\delta$}{Generate a fresh probabilistic symbolic variable}
-		\State{$\sigma[\mathtt{x}] = \delta$}
-		\State{$P[\delta] = d$}
+		\Let{$\sigma$}{Generate a fresh probabilistic symbolic variable}
+		\State{$\sigma[\mathtt{x}] = \sigma$}
+		\State{$P[\sigma] = d$}
 		\State\Return{$(\varphi,\sigma,P)$}
@@
 	% 
-	A fresh probabilistic symbolic variable, $\delta$, is created, $\sigma$ is updated to be $\sigma[\mathtt{x}] = \delta$, and the original distribution $d$ is recorded in $P$ by setting $P[\delta] = d$.
+	A fresh probabilistic symbolic variable, $\sigma$, is created, $\sigma$ is updated to be $\sigma[\mathtt{x}] = \sigma$, and the original distribution $d$ is recorded in $P$ by setting $P[\sigma] = d$.
 	%
@@
 		\Let{$c_{sym}$}{$\sigma[c]$}
-		\Let{$(\delta_1,\ldots,\delta_n)$}{$\dom{P}$}
-		\Let{$(d_1,\ldots,d_n)$}{$(P[\delta_1],\ldots,P[\delta_n])$}
-		\Let{$p_c$}{$\frac{\displaystyle\sum_{(v_1,\ldots,v_n) \in \dom{d_1} \times \cdots\times \dom{d_n}} [(c_{sym} \wedge \varphi)\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]}{\displaystyle\sum_{(v_1,\ldots,v_n) \in \dom{d_1} \times \cdots\times \dom{d_n}}[\varphi\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]}$}
+		\Let{$(\sigma_1,\ldots,\sigma_n)$}{$\dom{P}$}
+		\Let{$(d_1,\ldots,d_n)$}{$(P[\sigma_1],\ldots,P[\sigma_n])$}
+		\Let{$p_c$}{$\frac{\displaystyle\sum_{(v_1,\ldots,v_n) \in \dom{d_1} \times \cdots\times \dom{d_n}} [(c_{sym} \wedge \varphi)\{\sigma_1 \mapsto v_1,\ldots,\sigma_n \mapsto v_n\}]}{\displaystyle\sum_{(v_1,\ldots,v_n) \in \dom{d_1} \times \cdots\times \dom{d_n}}[\varphi\{\sigma_1 \mapsto v_1,\ldots,\sigma_n \mapsto v_n\}]}$}
 		\State\Return{$((\varphi \wedge c_{sym}, \sigma,P,p_c), (\varphi \wedge \neg c_{sym}, \sigma,P,1-p_c))$}
@@
 	% 
-	Without loss of generality, consider a branch of the form $\mathbf{if}~c~\mathbf{then}~S_1~\mathbf{else}~S_2$.
+	Without loss of generality, consider a branch of the form $\mathbf{if}~c~\mathbf{then}~\Delta_1~\mathbf{else}~\Delta_2$.
 	% 
@@
 	% 
-	Note that each probabilistic symbolic variable, $\delta$, is mapped to exactly one distribution, $d$, and therefore, $\delta \in \dom{d}$.
+	Note that each probabilistic symbolic variable, $\sigma$, is mapped to exactly one distribution, $d$, and therefore, $\sigma \in \dom{d}$.
 	% 
-	So, assuming there are $n$ probabilistic symbolic variables, $\delta_1,\ldots,\delta_n$, and so $n$ distributions, $d_1,\ldots,d_n$, the set of all possible values $\delta_1,\ldots,\delta_n$ be is $\mathcal{D} = \dom{d_1} \times \cdots \times \dom{d_n}$.
+	So, assuming there are $n$ probabilistic symbolic variables, $\sigma_1,\ldots,\sigma_n$, and so $n$ distributions, $d_1,\ldots,d_n$, the set of all possible values $\sigma_1,\ldots,\sigma_n$ be is $\mathcal{D} = \dom{d_1} \times \cdots \times \dom{d_n}$.
 	% 
@@
 	% 
-	On the \textit{symbolic execution} side, upon reaching the \textit{branch} instruction at Line~\ref{line:branch} in Alg~\ref{alg:symbex}, two new \textit{states} are created ($S_{true}$ \& $S_{false}$) and the constraint encoding the actual \textit{branch condition} ($c_{sym}$) [Line~\ref{line:true_state}] and it's negation ($\neg c_{sym}$)  [Line~\ref{line:false_state}] are appended to them representing the \textit{true} \& \textit{false} side of the \textit{branch}.
+	On the \textit{symbolic execution} side, upon reaching the \textit{branch} instruction at Line~\ref{line:branch} in Alg~\ref{alg:symbex}, two new \textit{states} are created ($\Delta_{true}$ \& $\Delta_{false}$) and the constraint encoding the actual \textit{branch condition} ($c_{sym}$) [Line~\ref{line:true_state}] and it's negation ($\neg c_{sym}$)  [Line~\ref{line:false_state}] are appended to them representing the \textit{true} \& \textit{false} side of the \textit{branch}.
 	%
@@
 				[{$\varphi=\top$},align=center, base=bottom
-				[{$\varphi = \delta_1 > 1$}, align=center, base=bottom, edge label={node [midway,above] {$\frac{2}{3}$} }
-				[{$\varphi = (\delta_1 > 1) \wedge (\delta_1 < \delta_2)$}, align=center, base=bottom, edge label={node [midway,above] {$\frac{1}{6}$} }
+				[{$\varphi = \sigma_1 > 1$}, align=center, base=bottom, edge label={node [midway,above] {$\frac{2}{3}$} }
+				[{$\varphi = (\sigma_1 > 1) \wedge (\sigma_1 < \sigma_2)$}, align=center, base=bottom, edge label={node [midway,above] {$\frac{1}{6}$} }
 				[{\texttt{True}}]]
-				[{$\varphi = (\delta_1 > 1) \wedge \neg(\delta_1 < \delta_2)$}, align=center, base=bottom, edge label={node [midway,above] {$\frac{5}{6}$} }
+				[{$\varphi = (\sigma_1 > 1) \wedge \neg(\sigma_1 < \sigma_2)$}, align=center, base=bottom, edge label={node [midway,above] {$\frac{5}{6}$} }
 				[{\texttt{False}}]]]
-				[{$\varphi = \neg(\delta_1 > 1)$}, align=center, base=bottom, edge label={node [midway,above] {$\frac{1}{3}$} }
+				[{$\varphi = \neg(\sigma_1 > 1)$}, align=center, base=bottom, edge label={node [midway,above] {$\frac{1}{3}$} }
 				[{\texttt{False}}]]]
@@
 	% 
-	Following Alg.~\ref{alg:sample} for lines 1,2, we generate fresh probabilistic symbolic variables for $\mathtt{x}$ and $\mathtt{y}$, $\delta_1$ and $\delta_2$, respectively.
+	Following Alg.~\ref{alg:sample} for lines 1,2, we generate fresh probabilistic symbolic variables for $\mathtt{x}$ and $\mathtt{y}$, $\sigma_1$ and $\sigma_2$, respectively.
 	% 
-	We also store the distributions which $\delta_1$ and $\delta_2$ are samples from, namely the discrete uniform distribution $\mathcal{U}\{1,3\}$.
+	We also store the distributions which $\sigma_1$ and $\sigma_2$ are samples from, namely the discrete uniform distribution $\mathcal{U}\{1,3\}$.
 	% 
-	In our notation, we say that $\sigma = \{ \mathtt{x} \mapsto \delta_1, \mathtt{y} \mapsto \delta_2 \}$ and $P = \{ \delta_1,\delta_2 \mapsto \mathcal{U}\{1,3\} \}$.
+	In our notation, we say that $\sigma = \{ \mathtt{x} \mapsto \sigma_1, \mathtt{y} \mapsto \sigma_2 \}$ and $P = \{ \sigma_1,\sigma_2 \mapsto \mathcal{U}\{1,3\} \}$.
 	% 
@@
 	\begin{align*}
-		p_c = \Pr[\delta_1 < \delta_2 \mid \delta_1 > 1] &= \frac{\Pr[(\delta_1 < \delta_2) \wedge (\delta_1 > 1)]}{\Pr[\delta_1 > 1]}\\
-		&= \frac{\displaystyle\sum_{(v_1,v_2) \in \mathcal{D}} [(\delta_1 < \delta_2) \wedge (\delta_1 > 1)\{\delta_1 \mapsto v_1, \delta_2 \mapsto v_2\}]}{\displaystyle\sum_{(v_1,v_2) \in \mathcal{D}} [(\delta_1 > 1)\{\delta_1 \mapsto v_1\}]}\\
+		p_c = \Pr[\sigma_1 < \sigma_2 \mid \sigma_1 > 1] &= \frac{\Pr[(\sigma_1 < \sigma_2) \wedge (\sigma_1 > 1)]}{\Pr[\sigma_1 > 1]}\\
+		&= \frac{\displaystyle\sum_{(v_1,v_2) \in \mathcal{D}} [(\sigma_1 < \sigma_2) \wedge (\sigma_1 > 1)\{\sigma_1 \mapsto v_1, \sigma_2 \mapsto v_2\}]}{\displaystyle\sum_{(v_1,v_2) \in \mathcal{D}} [(\sigma_1 > 1)\{\sigma_1 \mapsto v_1\}]}\\
 		&= \frac{1}{6}

### 2021-06-30 shared/Paper-Draft/symbolic_execution.tex
WIP : Algorithm Section (B)

--- 2021-06-30 shared/Paper-Draft/symbolic_execution.tex
@@
-		\subsection{Background}
-\label{sec:trad_sym_exec}
-
 \label{sec:pse}
@@
 	\begin{algorithmic}[1]
-		\Function{SymbEx}{$Prog : Program$}
-		\Let{$\varphi_{paths}$}{[]}, {$Ex_{stack}$} $\leftarrow$ {[]}, $\Delta \leftarrow$ {[]}, $\phi_{paths} \leftarrow \phi$, $P \leftarrow \phi$  \algorithmiccomment{Initialization}
+		\Function{SymbEx}{Prog : Program}
+		\Let{$\varphi_{paths}$}{[]}, {$L$} $\leftarrow$ {[]}, $Enc_t \gets \bot, Enc_a \gets \bot$  \algorithmiccomment{Initialization}
 		\Let{$I_{0}$}{\textsc{getStartInstruction}($Prog$)}
-		\Let{$S_{0}$}{[$I_{0}$, $\phi_{path}$, $\Delta$, $\phi$]} \algorithmiccomment{Empty Initial State}
-		\State {$Ex_{stack}$.\textsc{Push}({$S_{0}$})} \algorithmiccomment{Start with $S_{cur}$ in Execution Stack}
-		\While{$Ex_{stack}$ != $\phi$}
-		\Let{$S_{cur}$}{$Ex_{stack}$.\textsc{Pop}( )}, $I_{cur} \leftarrow S_{cur}[1]$ \algorithmiccomment{Start State, [$I_{0}$, $\phi_{path}$, $\Delta$]}
+		\Let{$S_{0}$}{($I_{0}$, $\phi$, $\phi$, $\phi$, 1.0)} \algorithmiccomment{Empty Initial State}
+		\State {$L$.\textsc{Append}({$S_{0}$})} \algorithmiccomment{Start with $S_{cur}$ in Execution Stack}
+		\While{$L \neq \phi$}
+		\Let{($I_{cur}, \varphi, \sigma, P, p)$}{$L$.\textsc{Remove}( )}
+		\If{\textsc{UNSAT}($\varphi$) $\lor p = 0.0$}
+		\State \textbf{continue}
+		\EndIf
 		\Switch{\textsc{instType}($I_{cur}$)} \label{line:inst_case}
-		\Case{\texttt{make\_pse\_sym}} ($x_{var},  d_{dist}$) \algorithmiccomment{Create \texttt{fresh} Symbolic Variable} \label{line:make_pse}
-		\Let{$I_{cur}$}{\textsc{getNextInstruction}($I_{cur}$)}
-		\Let{$\phi_{path}, \Delta, P$}{{\textbf{PSESample}}({$x_{var},  d_{dist}$, $\phi_{path}$, $\Delta$, $P$})}
-		\Let{$S_{cur}$}{[$I_{cur}$, $\phi_{path}$, $\Delta$, $P$]}
-		\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
+		\Case{$x \gets d$} \algorithmiccomment{Create \texttt{fresh} Symbolic Variable} \label{line:make_pse}
+		\Let{$I_1$}{\textsc{getNextInstruction}($I_{cur}$)}
+		\Let{$P_1$}{{\textbf{PSESample}}({$x,  d, P$})}
+		\Let{$S_1$}{($I_{cur}, \varphi, \sigma, P_1, p$)}
+		\State {$L$.\textsc{Append}({$S_1$})}
 		\EndCase
-		\Case{v := e} \algorithmiccomment{Assignment Instruction} \label{line:assign}
-		\Let{$I_{cur}$}{\textsc{getNextInstruction}($I_{cur}$)}
-		\Let{$\phi_{path}, \Delta, P$}{{\textbf{PSEAssignment}}({v, e, $\phi_{path}$, $\Delta$, $P$})}
-		\Let{$S_{cur}$}{[$I_{cur}$, $\phi_{path}$, $\Delta$, $P$]}
-		\State {$Ex_{stack}$.\textsc{Push}({$S_{cur}$})}
+		\Case{$v \gets e$} \algorithmiccomment{Assignment Instruction} \label{line:assign}
+		\Let{$I_1$}{\textsc{getNextInstruction}($I_{cur}$)}
+		%\Let{$e_{sym}$}{$\sigma[e]$}
+		%\Let{$\varphi, \sigma, P$}{{\textbf{PSEAssignment}}({v, e, $\varphi$, $\sigma$, $P$})}
+		\Let{$\sigma[x]$}{$\sigma[e]$}
+		\Let{$S_{cur}$}{($I_{cur}$, $\varphi$, $\sigma$, $P$)}
+		\State {$L$.\textsc{Append}({$S_{cur}$})}
 		\EndCase
-		\Case{\textbf{if} $(c_{sym})$ \textbf{then} $P_{1}$ \textbf{else} $P_{2}$} \algorithmiccomment{Branch Instruction}
-		\Let{$Branch_{expr}$}{{\textbf{PSEBranch}}({$c_{sym}$, $\phi_{path}$, $\Delta$, $P$})} \label{line:branch}
-		\Let{$I_{1}$}{\textsc{getStartInstruction}($P_{1}$)} \Let{$I_{2}$} {\textsc{getStartInstruction}($P_{2}$)}	
-		\Let{$S_{true}$}{[$I_{1}$, $\phi_{path} \wedge c_{sym}$, $\Delta$, $Branch_{expr}[0]$]} \label{line:true_state}
-		\Let{$S_{false}$}{[$I_{2}$, $\phi_{path} \wedge (\neg c_{sym})$, $\Delta$, $Branch_{expr}[1]$]} \label{line:false_state}
-		\State {$Ex_{stack}$.\textsc{Push}({$S_{false}$})}
-		\State {$Ex_{stack}$.\textsc{Push}({$S_{true}$})} \algorithmiccomment{Start with True State}
+		\Case{\textbf{if} $(c)$ \textbf{then goto} $T_{1}$} \algorithmiccomment{Branch Instruction}
+		\Let{$c_{sym}$}{$\sigma[c]$}
+		\Let{$p_t, p_f$}{{\textbf{PSEBranch}}({$c_{sym}$, $\sigma$, $P$})} \label{line:branch}
+		\Let{$I_{1}$}{\textsc{getInstruction}($T_{1}$)} 
+		\Let{$I_{2}$} {\textsc{getNextInstruction}(I)}	
+		\Let{$S_{true}$}{($I_{1}$, $\varphi \wedge c_{sym}$, $\sigma$, $p_t$)} \label{line:true_state}
+		\Let{$S_{false}$}{($I_{2}$, $\varphi \wedge \neg c_{sym}$, $\sigma$, $p_f$)} \label{line:false_state}
+		\State {$L$.\textsc{Append}({$S_{false}$})}
+		\State {$L$.\textsc{Append}({$S_{true}$})} \algorithmiccomment{Start with True State}
 		\EndCase
-		\Case{\textbf{HALT}} \algorithmiccomment{Terminate Instruction}
-		\Let{$\varphi_{paths}$}{$\varphi_{paths}$.\textsc{Append}($\phi_{path}$)}		
+		\Case{\textbf{halt(c)}} \algorithmiccomment{Terminate Instruction}
+		\Let{$c_{sym}$}{$\sigma[c]$}
+		\If{\textsc{SAT}($c_{sym}$)}
+		\State {$Enc_t$.\textsc{AddEncoding}($\varphi, p$)}		
+		\EndIf
+		\State {$Enc_a$.\textsc{AddEncoding}($\varphi, p$)}		
 		\EndCase
 		\EndSwitch
-		\EndWhile \\
-		\Return{$\varphi_{paths}$}
+		\EndWhile 
+		\Let{$r$}{\textsc{Solve}($Enc_t, Enc_a$)} \\
+		\Return{$r$}
 		\EndFunction
@@
 \[
-S := \mathbf{skip} \mid \mathtt{x} \leftarrow e \mid \mathtt{x} \xleftarrow{\$} d \mid S_1 ; S_2 \mid \mathbf{if}~e~\mathbf{then}~S_1~\mathbf{else}~S_2 \mid \mathbf{while}~e~\mathbf{do}~S 
+%S := \mathbf{skip} \mid \mathtt{x} \leftarrow e \mid \mathtt{x} \xleftarrow{\$} d \mid S_1 ; S_2 \mid \mathbf{if}~e~\mathbf{then}~S_1~\mathbf{else}~S_2 \mid \mathbf{while}~e~\mathbf{do}~S 
+S := \mathtt{x} \leftarrow e \mid \mathtt{x} \xleftarrow{\$} d \mid S_1 ; S_2 \mid \mathbf{if}~e~\textbf{then goto} T \mid \textbf{halt}(e)
 \]
@@
 		\Function{PSEBranch}{$c, \varphi, \sigma, P$}
-		\Let{$c_{sym}$}{$\sigma[c]$}
 		\Let{$(\delta_1,\ldots,\delta_n)$}{$\dom{P}$}

### 2021-06-30 shared/Paper-Draft/symbolic_execution.tex
WIP : Appendix Section (B)

@@
 	\caption{Probabilistic Symbolic Execution Algorithm}
-	\label{alg:symbex}
+	\label{alg:symb_ex}
 	\begin{algorithmic}[1]
 		\Function{SymbEx}{Prog : Program}
-		\Let{$\varphi_{paths}$}{[]}, {$L$} $\leftarrow$ {[]}, $Enc_t \gets \bot, Enc_a \gets \bot$  \algorithmiccomment{Initialization}
+		\Let{$\varphi_{paths}$}{[]}, {$E_s$} $\leftarrow$ {[]}, $Enc_t \gets \bot, Enc_a \gets \bot$  \algorithmiccomment{Initialization}
 		\Let{$I_{0}$}{\textsc{getStartInstruction}($Prog$)}
 		\Let{$S_{0}$}{($I_{0}$, $\phi$, $\phi$, $\phi$, 1.0)} \algorithmiccomment{Empty Initial State}
-		\State {$L$.\textsc{Append}({$S_{0}$})} \algorithmiccomment{Start with $S_{cur}$ in Execution Stack}
+		\State {$E_s$.\textsc{Append}({$S_{0}$})} \algorithmiccomment{Start with $S_{0}$ in Execution Stack}
 		\While{$L \neq \phi$}
-		\Let{($I_{cur}, \varphi, \sigma, P, p)$}{$L$.\textsc{Remove}( )}
-		\If{\textsc{UNSAT}($\varphi$) $\lor p = 0.0$}
+		\Let{($I_{c}, \varphi, \sigma, P, p)$}{$E_s$.\textsc{Remove}( )}
+		\If{\textsc{UNSAT}($\varphi$) $\lor (p = 0.0)$}
 		\State \textbf{continue}
 		\EndIf
-		\Switch{\textsc{instType}($I_{cur}$)} \label{line:inst_case}
-		\Case{$x \gets d$} \algorithmiccomment{Create \texttt{fresh} Symbolic Variable} \label{line:make_pse}
-		\Let{$I_1$}{\textsc{getNextInstruction}($I_{cur}$)}
-		\Let{$P_1$}{{\textbf{PSESample}}({$x,  d, P$})}
-		\Let{$S_1$}{($I_{cur}, \varphi, \sigma, P_1, p$)}
-		\State {$L$.\textsc{Append}({$S_1$})}
+		\Switch{\textsc{instType}($I_{c}$)} \label{line:inst_type}
+		\Case{\fbox{$\mathtt{x} \xleftarrow{\$} d$}} \algorithmiccomment{Create \texttt{New} Symbolic Variable} \label{line:pse_sampling}
+		\Let{$I_1$}{\textsc{getNextInstruction}($I_{c}$)}
+		\State{\colorbox[RGB]{200, 200, 200}{$\sigma,~P_1 \leftarrow~${\textbf{PSESample}}~({$x,~d,~P$})}}
+		\Let{$S_1$}{($I_{c}, \varphi, \sigma, P_1, p$)}
+		\State {$E_s$.\textsc{Append}({$S_1$})}
 		\EndCase
-		\Case{$v \gets e$} \algorithmiccomment{Assignment Instruction} \label{line:assign}
-		\Let{$I_1$}{\textsc{getNextInstruction}($I_{cur}$)}
+		\Case{\fbox{$x \gets e$}} \algorithmiccomment{Assignment Instruction} \label{line:symbex_assign}
+		\Let{$I_1$}{\textsc{getNextInstruction}($I_{c}$)}
 		%\Let{$e_{sym}$}{$\sigma[e]$}
@@
 		\Let{$\sigma[x]$}{$\sigma[e]$}
-		\Let{$S_{cur}$}{($I_{cur}$, $\varphi$, $\sigma$, $P$)}
-		\State {$L$.\textsc{Append}({$S_{cur}$})}
+		\Let{$S_{1}$}{($I_{1}$, $\varphi$, $\sigma$, $P$, $p$)}
+		\State {$E_s$.\textsc{Append}({$S_{1}$})}
 		\EndCase
-		\Case{\textbf{if} $(c)$ \textbf{then goto} $T_{1}$} \algorithmiccomment{Branch Instruction}
+		\Case{\fbox{\textbf{if} $(c)$ \textbf{then goto} $T_{1}$}} \algorithmiccomment{Branch Instruction}
 		\Let{$c_{sym}$}{$\sigma[c]$}
-		\Let{$p_t, p_f$}{{\textbf{PSEBranch}}({$c_{sym}$, $\sigma$, $P$})} \label{line:branch}
+		\State{\colorbox[RGB]{200, 200, 200}{$p_t,~p_f \leftarrow~${\textbf{PSEBranch}}~({$c_{sym},~\sigma,~P$})}}
 		\Let{$I_{1}$}{\textsc{getInstruction}($T_{1}$)} 
 		\Let{$I_{2}$} {\textsc{getNextInstruction}(I)}	
-		\Let{$S_{true}$}{($I_{1}$, $\varphi \wedge c_{sym}$, $\sigma$, $p_t$)} \label{line:true_state}
-		\Let{$S_{false}$}{($I_{2}$, $\varphi \wedge \neg c_{sym}$, $\sigma$, $p_f$)} \label{line:false_state}
-		\State {$L$.\textsc{Append}({$S_{false}$})}
-		\State {$L$.\textsc{Append}({$S_{true}$})} \algorithmiccomment{Start with True State}
+		\Let{$S_{t}$}{($I_{1}$, $\varphi \wedge c_{sym}$, $\sigma$, $P$, $p * p_t$)} \label{line:symbex_true_state} \algorithmiccomment{Multiply with previous \textit{probability} value.}
+		\Let{$S_{f}$}{($I_{2}$, $\varphi \wedge \neg c_{sym}$, $\sigma$, $P$, $p * p_f$)} \label{line:symbex_false_state}
+		\State {$E_s$.\textsc{Append}({$S_{f}$})}
+		\State {$E_s$.\textsc{Append}({$S_{t}$})} \algorithmiccomment{Start with True State}
 		\EndCase
-		\Case{\textbf{halt(c)}} \algorithmiccomment{Terminate Instruction}
+		\Case{\fbox{\textbf{halt(c)}}} \algorithmiccomment{Terminate Instruction}
 		\Let{$c_{sym}$}{$\sigma[c]$}
 		\If{\textsc{SAT}($c_{sym}$)}
-		\State {$Enc_t$.\textsc{AddEncoding}($\varphi, p$)}		
+		\State {\colorbox[RGB]{200, 200, 200}{$Enc_t$.\textsc{AddEncoding}~($\varphi,~p$)}}		
 		\EndIf
-		\State {$Enc_a$.\textsc{AddEncoding}($\varphi, p$)}		
+		\State {\colorbox[RGB]{200, 200, 200}{$Enc_a$.\textsc{AddEncoding}~($\varphi,~p$)}}		
 		\EndCase
@@
 		\EndWhile 
-		\Let{$r$}{\textsc{Solve}($Enc_t, Enc_a$)} \\
+		\Let{$r$}{\colorbox[RGB]{200, 200, 200}{\textsc{Solve}~($Enc_t,~Enc_a$)}} \\
 		\Return{$r$} 
@@
 %S := \mathbf{skip} \mid \mathtt{x} \leftarrow e \mid \mathtt{x} \xleftarrow{\$} d \mid S_1 ; S_2 \mid \mathbf{if}~e~\mathbf{then}~S_1~\mathbf{else}~S_2 \mid \mathbf{while}~e~\mathbf{do}~S 
-S := \mathtt{x} \leftarrow e \mid \mathtt{x} \xleftarrow{\$} d \mid S_1 ; S_2 \mid \mathbf{if}~e~\textbf{then goto} T \mid \textbf{halt}(e)
+S := \mathtt{x} \leftarrow e \mid \mathtt{x} \xleftarrow{\$} d \mid S_1 ; S_2 \mid \mathbf{if}~e~\textbf{then goto}~T \mid \textbf{halt}(e)
 \]
@@
 
-\begin{algorithm}[H]
-	\caption{PSE Assignment Algorithm}
-	\label{alg:assign}
-	\begin{algorithmic}[1]
-		\Function{PSEAssignment}{$\mathtt{x}, e, \varphi, \sigma, P$}
-		\Let{$e_{sym}$}{$\sigma[e]$}
-		\State{$\sigma[\mathtt{x}] = e_{sym}$}
-		\State\Return{$(\varphi,\sigma,P)$}
-		\EndFunction
-	\end{algorithmic}
-\end{algorithm}
-
 \begin{paragraph}{Assignment}
@@
 	\begin{algorithmic}[1]
-		\Function{PSESample}{$\mathtt{x}, d, \varphi, \sigma, P$}
+		\Function{PSESample}{$\mathtt{x}, d, \sigma, P$}
 		\Let{$\delta$}{Generate a fresh probabilistic symbolic variable}
@@
 		\State{$P[\delta] = d$}
-		\State\Return{$(\varphi,\sigma,P)$}
+		\State\Return{$(\sigma, P)$}
 		\EndFunction
@@
 	\begin{algorithmic}[1]
-		\Function{PSEBranch}{$c, \varphi, \sigma, P$}
+		\Function{PSEBranch}{$c, \sigma, P$}
 		\Let{$(\delta_1,\ldots,\delta_n)$}{$\dom{P}$}
@@
 		\Let{$p_c$}{$\frac{\displaystyle\sum_{(v_1,\ldots,v_n) \in \dom{d_1} \times \cdots\times \dom{d_n}} [(c_{sym} \wedge \varphi)\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]}{\displaystyle\sum_{(v_1,\ldots,v_n) \in \dom{d_1} \times \cdots\times \dom{d_n}}[\varphi\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]}$}
-		\State\Return{$((\varphi \wedge c_{sym}, \sigma,P,p_c), (\varphi \wedge \neg c_{sym}, \sigma,P,1-p_c))$}
+		\State\Return{$(p_c, 1 - p_c)$}
 		\EndFunction

### 2021-06-30 baseline-exp/src/bloomfilter.cpp

@@ -214,7 +214,7 @@ int main() {
     std::cout << "1"
               << "\n";
   } else {
-    std::cout << "-1"
+    std::cout << "0"
               << "\n";
   }
 

### 2021-07-02 analysis/analysis.tex
Updates

--- 2021-05-27 shared/analysis.tex
@@
 \usepackage{mathtools}
-
-\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
+\usepackage[ruled,lined,linesnumbered]{algorithm2e}
 \usepackage{amsmath}
@@
 The probability mass associated with the $i_{th}$ random run as is given below considering each $pivot$ selection being an independent selection.
+The variable $count_i$ denotes the number of comparisions made in $t^{th}$ random run.
 
 \begin{equation}
-	w_i = (1 / n) * \prod_{j=1}^{k} 1 / l_j  * \prod_{j=1}^{k} 1 / r_j \quad \mid \quad for \enspace k-partitons
+	w_i = (1 / n) * \prod_{j=1}^{k} 1 / (\#size_{partition_{j}}) \quad \mid \quad for \enspace k-partitons
 \end{equation}
@@
 \begin{equation}
-	where \enspace l_j = count(l_{terms}), \enspace r_j = count(r_{terms}) \quad \mid \quad in \enspace j^{th} \enspace partition. 
+	E[comparisions] = \sum_{i=1}^{r} (w_i * count_i) \quad \mid \quad for \enspace r-runs
 \end{equation}
 
+\section{PSE Approach}
+\begin{itemize}
+	\item Get the path contraints from KLEE, encoding each one into a \textsc{SMT} formula.
+	\item \ A single \textit{abstract} path may have multiple \textit{randomized} runs, each corresponding to a different \textit{setting} of the \textit{probabilistic} variables.
+	\item For each of the path $\in$ \textit{abstract program paths}, 
+	\begin{itemize}
+		\item We treat the \textit{probabilistic} variables as \textit{nondet} vars.
+		\item Find the estimated \textsc{Expected} value of the \textit{probabilistic} variable.
+		\item For each of the \textit{probabilistic} run record the setting of for the \textit{forall} variable. 
+		\item We use these as \textit{forall} inputs later for the \textit{concrete} runs.
+		\item The constraints for each run is encoded into a \textit{smt} formula. We make one call to \textsc{Z3} at the end to get the value for all the randomized runs. 
+		\item The \textsc{Expected} value will be an estimation here, we choose say the top \textit{k} candidates only, reposnsible for  \textit{maximizing} $\sum_{1}^{k} w_{i}$ (Total Mass Probability).
+	\end{itemize}
+	\item Now we do concrete runs of the program multiple times using the \textit{forall} variable values from \textit{randomized} runs.
+	\item We use a \textit{path} selection heuristic using a \textit{maximizing} value of the \textsc{forall} setting that leads to a \textit{violation}.	
+\end{itemize}
+
 \end{document}

### 2021-07-02 benchmark/ex10.py

@@ -1,31 +1,0 @@
-import random
-import numpy as np
-from scipy.stats import bernoulli
-
-
-def ex10(inpt):
-    x = 0
-    n = 30  # N
-    y = 0
-    prob = inpt[0]
-    while(n > 0):
-        d = bernoulli.rvs(size=1, p=prob)[0]
-        if(d):
-            x = x + 1
-        else:
-            y = y + 1
-        n = n - 1
-    return x*y
-
-
-'''
-Simulation of fair coin
-Prinsys Paper
-Lst 7
-I = [x = 0 ∧ y − 1 = 0] − [x − 1 = 0 ∧ y = 0]  #as per prinsys template
-'''
-'''
-x -> [0,1],    y -> [0,1]
-
-Guess: True
-'''

### 2021-07-02 benchmark/ex18.py

@@ -1,41 +1,0 @@
-import random
-import numpy as np
-from scipy.stats import bernoulli
-
-'''
-src: http://www-i2.informatik.rwth-aachen.de/pub/index.php?type=download&pub_id=1274
-pg-120
-Fig 5.9
-
-I = [x ≥ 0 and x − n ≤ 0 and n − M ≤ 0] * (x/M - p*n/M + p) 
-
-'''
-'''
-x -> [0,0], n -> [0,0]               recheck
-guess: [x ≥ 0 and x − n ≤ 0 and n − M ≤ 0]
-x -> [0,4], n -> [0,4]
-'''
-
-
-def ex18(inpt):
-    x = 0
-    n = 0
-    prob = inpt[0]
-    M = 5
-    while n - M + 1 <= 0:
-        d = bernoulli.rvs(size=1, p=prob)[0]
-        if d:
-            x = x + 1
-        n = n + 1
-    return n
-
-
-'''
-src: https://moves.rwth-aachen.de/wp-content/uploads/WS1819/probprog/prob-prog-2018-lec89.pdf
-Joost-Pieter Katoen
-I = [t = A ∧ c = 0]+ [t = A ∧ c = 1] * (p1/(p1 + p2 - p1 * p2))+ \
- [t = B ∧ c = 1] * ((1 - p2)/(p1 + p2 - p1 * p2))
-'''
-'''
-c -> [0,1],   t -> ['A','B'],  n -> [0,+inf]
-'''

### 2021-07-02 benchmark/ex20.py

@@ -1,57 +1,0 @@
-import random
-import numpy as np
-from scipy.stats import bernoulli
-
-'''
-Max 3SAT problem
-Theorem 2.1 in http://timroughgarden.org/w16/l/l18.pdf
-
-I= [n<=10] + [n>10] * (n*(7/8)*m)
-
-Post=n*(7/8)*m
-'''
-
-
-def ex20(inpt):
-    prob1, prob2 = inpt
-    n = 0
-    x1, x2, x3 = 0, 0, 0
-    z = 0
-    while(n <= 10):
-        d1 = bernoulli.rvs(size=1, p=prob1)[0]
-        if(d1):
-            x1 = 1
-        else:
-            x1 = 0
-        d2 = bernoulli.rvs(size=1, p=prob2)[0]
-        if(d2):
-            x2 = 1
-        else:
-            x2 = 0
-        d3 = bernoulli.rvs(size=1, p=prob2)[0]
-        if(d3):
-            x3 = 1
-        else:
-            x3 = 0
-
-        c1 = x1 + x2 + x3  # c1 = "x1 or x2 or x3"
-        if c1 >= 1:
-            c1 = 1
-        c2 = x1 + (1-x2) + x3  # c2 = "not x1 or x2 or x3"
-        if c2 >= 1:
-            c2 = 1
-        c3 = (1-x1) + x2 + x3  # c3 = "not x2 or x1 or x3"
-        if c3 >= 1:
-            c3 = 1
-        n = n + 1
-        z = c1 + c2 + c3
-    return z
-
-
-'''
-Kaminski pg 125
-I = [x-1 >= 0] + [x-1 < 0] * z
-'''
-'''
-x -> [-1,20],  z -> [0,+inf]
-'''

### 2021-07-02 benchmark/ex25.py

@@ -1,34 +1,0 @@
-import random
-import numpy as np
-from scipy.stats import bernoulli
-
-'''
-product.v2
-
-Pre-expectation:	n*n
-Post-expectation:	4*x*y
-
-Lagrange Interpolation output:
-
-Invariant:		n^2 + 2*n*y + 2*n*x + 4*x*y 
-
-'''
-'''
-x -> [1,+inf], n->[0,N],  y->[1,1]
-'''
-
-
-def ex25(inpt):
-    n = N
-    x = 1  # random
-    y = 1  # random
-    prob1, prob2 = inpt
-    while(n > 0):
-        d1 = bernoulli.rvs(size=1, p=prob1)[0]
-        if(d1):
-            x = x + 1
-        d2 = bernoulli.rvs(size=1, p=prob2)[0]
-        if(d2):
-            y = y + 1
-        n = n - 1
-    return (4 * x * y)

### 2021-07-02 benchmark/ex7.py

@@ -1,37 +1,0 @@
-import random
-import numpy as np
-from scipy.stats import bernoulli
-
-'''
-Lagrange Interpolation paper
-Binomial Distribution
-I=[y >= 0 and n − 1 >= 0] * (x + p * n * y)
-'''
-'''
-x -> [0,+inf],    n -> [0,10]
-'''
-
-
-def ex7(inpt):
-    x = 0
-    n = 10  # N
-    y = 10  # N
-    prob = inpt[0]
-    while(n > 0):
-        d = bernoulli.rvs(size=1, p=prob)[0]
-        if(d):
-            x = x + y
-        n = n-1
-    return x
-
-
-'''
-Lagrange Interpolation paper
-Binomial Distribution 2 (bin2)
-I = [y >= 0 and n − 1 >= 0] * (x + (0.125)* n * n + 0.125 * n − 0.75 * n * y)
-
-p=0.25
-'''
-'''
-x -> [0,+inf],    n -> [0,10],   [n-x <= 10]
-'''

### 2021-07-02 benchmark/ex8.py

@@ -1,28 +1,0 @@
-import random
-import numpy as np
-from scipy.stats import bernoulli
-
-
-def ex8(inpt):
-    x = 0
-    n = 10  # N
-    y = 10  # N
-    prob = inpt[0]
-    while(n > 0):
-        d = bernoulli.rvs(size=1, p=prob)[0]
-        if(d):
-            x = x + n
-        else:
-            x = x + y
-        n = n - 1
-    return x
-
-
-'''
-Lagrange Interpolation paper
-Sum of Random Series
-I= [n − 1 >= 0] * (x + (1/4) * n * n + (1/4) * n)
-'''
-'''
-x -> [0,+inf],    n -> [0,10],  [n - x <= 10]
-'''

### 2021-07-02 benchmark/ex9.py

@@ -1,32 +1,0 @@
-import random
-import numpy as np
-from scipy.stats import bernoulli
-
-
-def ex9(inpt):
-    x = 0
-    n = 10  # N
-    prob = inpt[0]
-    while(n > 0):
-        d = bernoulli.rvs(size=1, p=prob)[0]
-        if(d):
-            x = x + n
-        n = n - 1
-    return x
-
-
-'''
-Lagrange Interpolation paper
-Product of dependent random variables
-I = -(1/4) * n + x * y + (1/2) * x * n + (1/2) * y * n + \
-(1/4) * n^2 
-
-Lagrange output:
-
-pre=n(n-1) 
-post=xy 
-invariant = n^2 + 2nx + 2ny + 4xy - n
-'''
-'''
-x -> [0,+inf],    n -> [0,30],    y -> [0,+inf]
-'''

### 2021-07-02 benchmark/example_bloomfilter.cpp

@@ -1,22 +1,0 @@
-#include <bf/all.hpp>
-#include <iostream>
-
-int main() {
-  bf::basic_bloom_filter b(0.8, 100);
-
-  // Add two elements.
-  b.add("foo");
-  b.add(42);
-
-  // Test set membership
-  std::cout << b.lookup("foo") << std::endl; // 1
-  std::cout << b.lookup("bar") << std::endl; // 0
-  std::cout << b.lookup(42) << std::endl;    // 1
-
-  // Remove all elements.
-  b.clear();
-  std::cout << b.lookup("foo") << std::endl; // 0
-  std::cout << b.lookup(42) << std::endl;    // 0
-
-  return 0;
-}

### 2021-07-02 benchmark/example_hyperloglog.cpp

@@ -1,62 +1,0 @@
-#include <fstream>
-#include <iostream>
-
-// DataSketches/
-#include <DataSketches/hll.hpp>
-
-// simplified file operations and no error handling for clarity
-int main(int argc, char **argv) {
-  const int lg_k = 11;
-  const auto type = datasketches::HLL_4; // this is the default, but explicit
-                                         // here for illustration
-
-  // this section generates two sketches with some overlap and serializes them
-  // into files
-  {
-    // 100000 distinct keys
-    datasketches::hll_sketch sketch1(
-        lg_k, type); // type is optional, defaults to HLL_4
-    for (int key = 0; key < 100000; key++)
-      sketch1.update(key);
-    std::ofstream os1("hll_sketch1.bin");
-    sketch1.serialize_compact(os1);
-
-    // 100000 distinct keys
-    datasketches::hll_sketch sketch2(
-        lg_k, type); // type is optional, defaults to HLL_4
-    for (int key = 50000; key < 150000; key++)
-      sketch2.update(key);
-    std::ofstream os2("hll_sketch2.bin");
-    sketch2.serialize_compact(os2);
-  }
-
-  // this section deserializes the sketches, produces union and prints the
-  // result
-  {
-    std::ifstream is1("hll_sketch1.bin");
-    datasketches::hll_sketch sketch1 =
-        datasketches::hll_sketch::deserialize(is1);
-
-    std::ifstream is2("hll_sketch2.bin");
-    datasketches::hll_sketch sketch2 =
-        datasketches::hll_sketch::deserialize(is2);
-
-    datasketches::hll_union u(lg_k);
-    u.update(sketch1);
-    u.update(sketch2);
-    datasketches::hll_sketch sketch =
-        u.get_result(type); // type is optional, defaults to HLL_4
-
-    // debug summary of the union result sketch
-    sketch.to_string(std::cout);
-
-    std::cout << "Distinct count estimate: " << sketch.get_estimate()
-              << std::endl;
-    std::cout << "Distinct count lower bound 95% confidence: "
-              << sketch.get_lower_bound(2) << std::endl;
-    std::cout << "Distinct count upper bound 95% confidence: "
-              << sketch.get_upper_bound(2) << std::endl;
-  }
-
-  return 0;
-}

### 2021-07-02 run_foralls.sh

@@ -1,18 +1,0 @@
-#!/usr/bin/bash
-
-rm -rf $1/inputs/*
-rm -rf $1/outputs/*
-rm -rf $1/foralls/*
-
-rm -rf $1/pathprobs.txt
-rm -rf $1/results.txt
-
-python3 $1/candidates.py  
-python3 $1/executeCV.py foralls
-
-# python3 estimate_example5/candidates.py 15
-# python3 estimate_example5/executeCV.py inputs
-# cd estimate_example5/outputs/
-# cat *txt | sort 
-# cd ../../
-# python3 postprocess/z3write.py example5_processed/example5_paths.json > estimate_example5/paths.py

### 2021-07-02 shared/Paper-Draft/montyhall.c

@@ -1,37 +1,0 @@
-int monty_hall(int choice, bool door_switch) {
-	int car_door = uniform_int(1,3);
-	int host_door;
-	if (choice != 1 && car_door != 1) {
-		host_door = 1;
-	} else if (choice != 2 && car_door != 2) {
-		host_door = 2;
-	} else {
-		host_door = 3;
-	}
-	if (door_switch) {
-		if (host_door == 1) {
-			if (choice == 2) {
-				choice = 3;
-			} else {
-				choice = 2;
-			}
-		} else if (host_door == 2) {
-			if (choice == 1) {
-				choice = 3;
-			} else {
-				choice = 1;
-			}
-		} else {
-			if (choice == 1) {
-				choice = 2;
-			} else {
-				choice = 1;
-			}
-		}
-	}
-	if (choice == car_door) {
-		return true;
-	} else {
-		return false;
-	}
-}

### 2021-07-02 clean.sh
Repository Clean-Up

@@ -1,0 +1,4 @@
+#!/usr/bin/bash
+
+rm -rf *_klee_out *.out *.bc *.logs *_processed
+

### 2021-07-02 run.sh

@@ -1,9 +1,10 @@
-export RUNFILE=$1.cpp
-clang++-10 -I $HOME/klee/include -c -emit-llvm -std=c++17 -g -O0 -fPIC -fno-rtti -Xclang -disable-O0-optnone $1.cpp
+#!/usr/bin/bash
+
+clang++-10 -I $HOME/klee/include -c -emit-llvm -std=c++17 -g -O0 -fPIC -fno-rtti -Xclang -disable-O0-optnone src/$1.cpp
 klee --libc=klee --exit-on-error --optimize --disable-inlining --search=nurs:depth --use-cex-cache --write-kqueries $1.bc --set-ptree-dump 
 
 ktest-tool klee-last/test000001.ktest
-g++ -std=c++17 -march=native -I $HOME/klee/include/ -L $HOME/klee/lib/ $1.cpp -lkleeRuntest
+g++ -std=c++17 -march=native -I $HOME/klee/include/ -L $HOME/klee/lib/ src/$1.cpp -lkleeRuntest
 KTEST_FILE=klee-last/test000001.ktest ./a.out
 
 rm -rf $1_klee_out/

### 2021-09-04 draft/evaluation.tex
Reviews

\section{Evaluation}
\label{sec:eval}
We use \textsc{KLEE}\cite{cadar2008}, a robust symbolic execution engine, to implement the \textit{probabilistic symbolic} execution algorithm as described in Alg~\ref{alg:symb_ex}. For the purpose of our implementation, we modify \textsc{KLEE} to support creation of \textit{probabilistic symbolic} variables as described in \S~\ref{sec:pse_intro} whose values can be sampled from a distribution ($\delta$) by invoking \textsc{PSESample} as shown in the \textbf{\textit{sampling}} statement [Alg~\ref{alg:symb_ex}, Line~\ref{line:pse_sampling}]. We use the  \textit{path constraints} ($\varphi$)  from the \textit{state} data-structure (maintained by \textsc{KLEE}) at each of the \textbf{\textit{assignment}} [Alg~\ref{alg:symb_ex}, Line~\ref{line:pse_assignment}] and \textbf{\textit{branch}} [Alg~\ref{alg:symb_ex}, Line~\ref{line:symbex_branch}] statements to get the final encoding ($Enc_a, Enc_t$)  which we solve later. [{\color{red} Zach can describe more on how the actual solving and P-map updates happen on the implementation side}]

### 2021-09-04 draft/main.tex
Reviews

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
% \documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
% \documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
% \documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
% \documentclass[acmsmall]{acmart}\settopmatter{}

%% Journal information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{POPL} % CONF = POPL or ICFP or OOPSLA
\acmArticle{1}
\acmYear{2022}
\acmMonth{1}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

%% Copyright information
%% Supplied to authors (based on authors' rights management selection;
%% see authors.acm.org) by publisher for camera-ready submission;
%% use 'none' for review submission.
\setcopyright{none}
% \setcopyright{acmcopyright}
% \setcopyright{acmlicensed}
% \setcopyright{rightsretained}
% \copyrightyear{2018}           %% If different from \acmYear

%% Bibliography style
\bibliographystyle{ACM-Reference-Format}
%% Citation style
%% Note: author/year citations are required for papers published as an
%% issue of PACMPL.
\citestyle{acmauthoryear}   %% For author/year citations

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%% Note: Authors migrating a paper from PACMPL format to traditional
%% SIGPLAN proceedings format must update the '\documentclass' and
%% topmatter commands above; see 'acmart-sigplanproc-template.tex'.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
%% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
%% http://ctan.org/pkg/subcaption
\usepackage{mathtools}
\usepackage{thm-restate}
\usepackage[noend]{algpseudocode}
\usepackage{algorithm}
\usepackage{forest}
\usepackage{minted}
\usepackage{multicol}
\usepackage{xspace}
\usepackage{xcolor, soul}
\usepackage{wrapfig}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{cleveref}

%%% cleveref %%%
% \crefname{section}{§}{§}
% \Crefname{section}{§}{§}
\crefname{section}{\S}{\S}
\Crefname{section}{\S}{\S}

%%% Colors %%%
\definecolor{darkgreen}{RGB}{0,128,0}
\definecolor{gray}{RGB}{200,200,200}

%%% Comments %%%
\newcommand{\zach}[1]{\textcolor{red}{ZS: #1}}
\newcommand{\sumit}[1]{\textcolor{brown}{SL: #1}}
\newcommand{\jh}[1]{\textcolor{blue}{JH: #1}}
\newcommand{\sr}[1]{\textcolor{green}{SR: #1}}

%%% Macros %%%
\newcommand{\SYSTEM}{\textsc{Plinko}\xspace}
\newcommand{\Q}[1]{(\textit{\textbf{Q#1}})}

\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}
\newcommand{\DeclareAutoPairedDelimiter}[3]{%
	\expandafter\DeclarePairedDelimiter\csname Auto\string#1\endcsname{#2}{#3}%
	\begingroup\edef\x{\endgroup
		\noexpand\DeclareRobustCommand{\noexpand#1}{%
			\expandafter\noexpand\csname Auto\string#1\endcsname*}}%
	\x}
\DeclareAutoPairedDelimiter{\deno}{\llbracket}{\rrbracket}

\newcommand*\Let[2]{\State #1 $\gets$ #2}
\newcommand*\cLet[3]{\State\ColorLine{#3} #1 $\gets$ #2}
\newcommand*\dom[1]{\mathrm{dom}\left( #1 \right)}
\newcommand*\E[1]{\mathbb{E}\left[ #1 \right]}

% For the Case statements
% Switch Statement Commands
% New definitions
\algnewcommand\algorithmicswitch{\textbf{switch}}
\algnewcommand\algorithmiccase{\textbf{case}}
\algnewcommand\algorithmicassert{\texttt{assert}}
\algnewcommand\Assert[1]{\State \algorithmicassert(#1)}%

% New "environments"
\algdef{SE}[SWITCH]{Switch}{EndSwitch}[1]{\algorithmicswitch\ #1\ \algorithmicdo}{\algorithmicend\ \algorithmicswitch}%
\algdef{Se}[CASE]{Case}{EndCase}[1]{\algorithmiccase\ #1}%
\algtext*{EndSwitch}%
\algtext*{EndCase}%

% Highlight lines in algorithm environment
\makeatletter
% code borrowed from Andrew Stacey; See
% https://tex.stackexchange.com/a/50054/3954
\tikzset{%
	remember picture with id/.style={%
		remember picture,
		overlay,
		save picture id=#1,
	},
	save picture id/.code={%
		\edef\pgf@temp{#1}%
		\immediate\write\pgfutil@auxout{%
			\noexpand\savepointas{\pgf@temp}{\pgfpictureid}}%
	},
	if picture id/.code args={#1#2#3}{%
		\@ifundefined{save@pt@#1}{%
			\pgfkeysalso{#3}%
		}{
			\pgfkeysalso{#2}%
		}
	}
}

\def\savepointas#1#2{%
	\expandafter\gdef\csname save@pt@#1\endcsname{#2}%
}

\def\tmk@labeldef#1,#2\@nil{%
	\def\tmk@label{#1}%
	\def\tmk@def{#2}%
}

\tikzdeclarecoordinatesystem{pic}{%
	\pgfutil@in@,{#1}%
	\ifpgfutil@in@%
	\tmk@labeldef#1\@nil
	\else
	\tmk@labeldef#1,(0pt,0pt)\@nil
	\fi
	\@ifundefined{save@pt@\tmk@label}{%
		\tikz@scan@one@point\pgfutil@firstofone\tmk@def
	}{%
		\pgfsys@getposition{\csname save@pt@\tmk@label\endcsname}\save@orig@pic%
		\pgfsys@getposition{\pgfpictureid}\save@this@pic%
		\pgf@process{\pgfpointorigin\save@this@pic}%
		\pgf@xa=\pgf@x
		\pgf@ya=\pgf@y
		\pgf@process{\pgfpointorigin\save@orig@pic}%
		\advance\pgf@x by -\pgf@xa
		\advance\pgf@y by -\pgf@ya
	}%
}

\makeatother
% end of Andrew's code
\newlength\AlgIndent
\setlength\AlgIndent{0pt}
% main command to draw the colored background
\newcounter{mymark}
\newcommand\ColorLine[1]{%
	\stepcounter{mymark}%
	\tikz[remember picture with id=mark-\themymark,overlay] {;}%
	\begin{tikzpicture}[remember picture,overlay]%
		\filldraw[#1]%
		let \p1=(pic cs:mark-\themymark), 
		\p2=(current page.east)  in 
    ([xshift=-0.05em,yshift=-0.75ex]0,\y1)  rectangle ++([xshift=-7.7cm]\x2,\baselineskip);
    % ([xshift=-\ALG@thistlm-0.3em,yshift=-0.7ex]0,\y1)  rectangle ++(\linewidth+\AlgIndent,\baselineskip);
	\end{tikzpicture}%
}%

\makeatletter
% colored loops and declarations
\algnewcommand\cRequire[1]{\item[\ColorLine{#1}\algorithmicrequire]}%
\algnewcommand\cEnsure[1]{\item[\ColorLine{#1}\algorithmicensure]}%
\algnewcommand\cState[1]{\State\ColorLine{#1}}%
\algnewcommand\cStatex[1]{\Statex\ColorLine{#1}}%
\algnewcommand\cComment[1]{\Comment\ColorLine{#1}}%

\algdef{SE}[WHILE]{cWhile}{ENDWHILE}%
[2]{\ColorLine{#2}\algorithmicwhile\ #1\ \algorithmicdo}%
{\algorithmicend\ \algorithmicwhile}%
\algdef{SE}[FOR]{cFor}{ENDFOR}%
[2]{\ColorLine{#2}\algorithmicfor\ #1\ \algorithmicdo}%
{\algorithmicend\ \algorithmicfor}%
\algdef{S}[FOR]{cForAll}%
[2]{\ColorLine{#2}\algorithmicforall\ #1\ \algorithmicdo}%
\algdef{SE}[LOOP]{cLoop}{ENDLOOP}%
[1]{\ColorLine{#1}\algorithmicloop}%
{\algorithmicend\ \algorithmicloop}%
\algdef{SE}[REPEAT]{cRepeat}{UNTIL}%
[1]{\ColorLine{#1}\algorithmicrepeat}%
[1]{\algorithmicuntil\ #1}%
\algdef{SE}[IF]{cIf}{cEndIf}%
[2]{\ColorLine{#2}\algorithmicif\ #1\ \algorithmicthen}%
[1]{\ColorLine{#1}\algorithmicend\ \algorithmicif}%
\algdef{C}[IF]{IF}{cElsif}%
[2]{\ColorLine{#2}\algorithmicelse\ \algorithmicif\ #1\ \algorithmicthen}%
\algdef{Ce}[ELSE]{IF}{cElse}{ENDIF}%
[1]{\ColorLine{#1}\algorithmicelse}%
\algdef{SE}[SWITCH]{cSwitch}{cEndSwitch}%
[2]{\ColorLine{#2}\algorithmicswitch\ #1\ \algorithmicdo}%
{\algorithmicend\ \algorithmicswitch}%
\algdef{SE}[CASE]{cCase}{cEndCase}%
[2]{\ColorLine{#2}\algorithmiccase\ #1}%
[1]{\ColorLine{#1}\algorithmicend\ \algorithmiccase}%
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%% TODO: REMOVE THIS BEFORE SUBMISSION %%%%%%%%%%%%%%%%%%
% \hypersetup{draft}
%%%%%%%%%%%%%%%%%%%%%%%%% TODO: REMOVE THIS BEFORE SUBMISSION %%%%%%%%%%%%%%%%%%

\begin{document}

%% Title information
\title{Symbolic Execution for Randomized Programs}         %% [Short Title] is optional;
% \title[PSE]{Probabilistic Symbolic Execution}         %% [Short Title] is optional;
%% when present, will be used in
%% header instead of Full Title.
% \titlenote{with title note}             %% \titlenote is optional;
%% can be repeated if necessary;
%% contents suppressed with 'anonymous'
% \subtitle{Subtitle}                     %% \subtitle is optional
% \subtitlenote{with subtitle note}       %% \subtitlenote is optional;
%% can be repeated if necessary;
%% contents suppressed with 'anonymous'

%% Author information
%% Contents and number of authors suppressed with 'anonymous'.
%% Each author should be introduced by \author, followed by
%% \authornote (optional), \orcid (optional), \affiliation, and
%% \email.
%% An author may have multiple affiliations and/or emails; repeat the
%% appropriate command.
%% Many elements are not rendered, but should be provided for metadata
%% extraction tools.

%% Author with single affiliation.
% \author{First Last}
% \authornote{with author1 note}          %% \authornote is optional;
%                                         %% can be repeated if necessary
% \orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
% \affiliation{
% \position{Position1}
% \department{Department1}              %% \department is recommended
% \institution{Institution1}            %% \institution is required
% \streetaddress{Street1 Address1}
% \city{City1}
% \state{State1}
% \postcode{Post-Code1}
% \country{Country1}                    %% \country is recommended
% }
%   \email{first1.last1@inst1.edu}          %% \email is recommended

\author{Zachary Susag}
% \authornote{with author1 note}          %% \authornote is optional;
%% can be repeated if necessary
% \orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  % \position{Position1}
  % \department{Department1}              %% \department is recommended
  \institution{University of Wisconsin--Madison}            %% \institution is required
  % \streetaddress{Street1 Address1}
  % \city{City1}
  % \state{State1}
  % \postcode{Post-Code1}
  \country{USA}                    %% \country is recommended
}
% \email{first1.last1@inst1.edu}          %% \email is recommended

\author{Sumit Lahiri}
% \authornote{with author1 note}          %% \authornote is optional;
%% can be repeated if necessary
% \orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  % \position{Position1}
  % \department{Department1}              %% \department is recommended
  \institution{IIT Kanpur}            %% \institution is required
  % \streetaddress{Street1 Address1}
  % \city{City1}
  % \state{State1}
  % \postcode{Post-Code1}
  \country{India}                    %% \country is recommended
}
% \email{first1.last1@inst1.edu}          %% \email is recommended

\author{Justin Hsu}
% \authornote{with author1 note}          %% \authornote is optional;
%% can be repeated if necessary
% \orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  % \position{Position1}
  % \department{Department1}              %% \department is recommended
  \institution{University of Wisconsin--Madison}            %% \institution is required
  % \streetaddress{Street1 Address1}
  % \city{City1}
  % \state{State1}
  % \postcode{Post-Code1}
  \country{USA}                    %% \country is recommended
}
% \email{first1.last1@inst1.edu}          %% \email is recommended

\author{Subhajit Roy}
% \authornote{with author1 note}          %% \authornote is optional;
%% can be repeated if necessary
% \orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  % \position{Position1}
  % \department{Department1}              %% \department is recommended
  \institution{IIT Kanpur}            %% \institution is required
  % \streetaddress{Street1 Address1}
  % \city{City1}
  % \state{State1}
  % \postcode{Post-Code1}
  \country{India}                    %% \country is recommended
}
% \email{first1.last1@inst1.edu}          %% \email is recommended

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  We propose a symbolic execution method for programs that can draw random
  samples. Crucially, and in contrast to existing work, our method can handle
  randomized programs with unknown inputs and can prove probabilistic properties
  that universally quantify over all possible inputs. Our technique augments
  standard symbolic execution with a new class of \emph{probabilistic symbolic
    variables}, which represent the results of random draws, and data structures
  for tracking the distribution of random samples. Our approach computes
  symbolic expressions representing the probability of taking individual paths.
  We implement our method on top of the KLEE symbolic execution engine, and use
  it to prove properties about probabilities and expected values for a range of
  challenging case studies written in C++, including Freivalds' matrix
  multiplication verification algorithm, randomized quicksort, and a randomized
  property-testing algorithm for monotonicity.
\end{abstract}

%% 2012 ACM Computing Classification System (CSS) concepts
%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
%% TODO: Get CSS Concepts
% \begin{CCSXML}
%   <ccs2012>
%   <concept>
%   <concept_id>10011007.10011006.10011008</concept_id>
%   <concept_desc>Software and its engineering~General programming languages</concept_desc>
%   <concept_significance>500</concept_significance>
%   </concept>
%   <concept>
%   <concept_id>10003456.10003457.10003521.10003525</concept_id>
%   <concept_desc>Social and professional topics~History of programming languages</concept_desc>
%   <concept_significance>300</concept_significance>
%   </concept>
%   </ccs2012>
% \end{CCSXML}

% \ccsdesc[500]{Software and its engineering~General programming languages}
% \ccsdesc[300]{Social and professional topics~History of programming languages}
%% End of generated code

%% Keywords
%% comma separated list
\keywords{Probabilistic programs, symbolic execution}  %% \keywords are mandatory in final camera-ready submission

%% \maketitle
%% Note: \maketitle command must come after title commands, author
%% commands, abstract environment, Computing Classification System
%% environment and commands, and keywords command.
\maketitle

\section{Introduction}
\label{sec:intro}

Symbolic execution (SE)~\citep{king1976} is a highly successful method to
automatically find bugs in programs. In a nutshell, SE iteratively explores the
space of possible program paths, while treating program states as
\emph{symbolic functions} of program inputs (symbolic parameters). Whenever SE discovers a path to an error state, SE checks
to see if there is a setting of the symbolic parameters that can execute along
this path, thereby triggering an error. This basic bug-finding strategy has
proved to be a powerful technique, supporting some of the most effective tools
for analyzing large codebases~\citep{bessey_2010}.

Aiming to expand the reach of SE, researchers have proposed many domain-specific
extensions of SE~(e.g.,~\citet{geldenhuys_2012, filieri_2013, borges_2014,
  p4wn_2021, farina_2019, raimondas_2010, raimondas_2011, adam_2012}). In this
vein, we consider how to perform SE for \emph{randomized} programs, which can
draw random samples from built-in distributions. These programs play a critical
role in many leading applications today, from machine learning to security and
privacy. Randomized programs, like all programs, are susceptible to
bugs~\citep{axprof_2019}.  Correctness properties are difficult to formally
verify; existing methods typically require substantial manual effort and target
highly specific properties. Moreover, these programs are highly difficult to
test: the desired behavior is not deterministic, and it is hard to tell if a
program is producing the wrong distribution of outputs just by observing
executions.

\paragraph*{Challenges and prior work.} 
Accordingly, randomized programs are an attractive target for general-purpose,
automated verification methods, like SE. However, there are numerous challenges
in developing an SE procedure for probabilistic programs:
% 
\begin{itemize}
\item \textbf{Quantitative properties.} In standard SE, the goal is to
  identify whether a bad program state (e.g., an assertion failure) is
  reachable or not---if so, the program has a bug. In randomized programs, we
  are often more interested in whether a bad state is reached \emph{too
    often}, or whether a good state is reached \emph{often enough}. Accordingly,
  a useful SE procedure must be able to analyze the quantitative probability
  of reaching certain program states.
\item \textbf{Computing branch probabilities.} A concrete execution of a
  non-probabilistic program takes a single branch at each branching
  instruction, since the branch condition is either true or false in any
  program state. When reasoning about probabilistic behavior, it is more
  useful to model the program as transforming a distribution over program
  states. Then, a branch condition has some probability of being true, and
  some probability of being false, in every probabilistic program state. A SE
  procedure for probabilistic programs should be able to compute probabilities
  of branches; by combining these probabilities along a path, the SE procedure
  can then reason about the probabilities of paths.
\item \textbf{Handling program inputs.} Like standard programs, randomized
  programs often have input parameters. These unknown values are qualitatively
  different from the unknown results of random sampling commands: there is
  often no sensible probability one can assign to different settings of the
  program inputs, and the target correctness property usually universally
  quantifies over all possible inputs.

  Prior work has considered SE for probabilistic programs~\citep{geldenhuys_2012,sampson_2014},
  but unlike traditional SE, these methods do not treat the program inputs as
  unknown values. Instead, existing methods consider probabilistic programs
  without inputs~\citep{sampson_2014}, or assume that the inputs are
  probabilistically drawn from a known distribution~\citep{geldenhuys_2012}. This
  simplification allows SE to compute probabilities exactly using techniques
  like model counting, or approximately using statistical sampling. However,
  it significantly limits the kinds of programs that can be analyzed, and the
  kinds of properties that can be proved.
\end{itemize}

\paragraph*{Our work: symbolic execution for randomized programs.}
We propose a symbolic execution method for randomized programs, where programs
may have unknown inputs. These programs can be thought of as producing a family
of output distributions, one for each concrete input, and inputs can range over
a large, conceptually infinite set. We consider two kinds of properties:
% 
\begin{itemize}
\item \textbf{Probability bounds.} For all inputs, the \emph{probability of
    reaching a program state} is at most/at least/exactly equal to some
  quantity, which may depend on the inputs. This class of properties is the
  probabilistic analogue of the reachability properties typically considered
  by SE.
\item \textbf{Expectation bounds.} For all inputs, the \emph{expected value of
    a program expression} in the output is at most/at least/exactly equal to
  some quantity, which may depend on the inputs. This class of properties is
  more general than probability bounds, and is useful for reasoning about
  quantitative properties like expected resource usage.
\end{itemize}
% 
There are two key technical ingredients in our approach:
% 
\begin{itemize}
\item \textbf{Distinguish between regular and probabilistic symbolic
    variables.} We model probabilistic sampling statements by introducing a new kind of symbolic variable, referred as \textit{probabilistic symbolic variable}. While regular symbolic variables represent unknown inputs, 
  probabilistic symbolic variables represent the result from sampling from a
  known distribution. Prior work only supports one or the other kind of
  symbolic variable; our method supports both simultaneously.
\item \textbf{Compute symbolic branch probabilities.} In the presence of
  program inputs, the probability of taking a branch may depend on unknown
  values. Accordingly, it is not possible to use approaches like model
  counting to compute the branch probabilities, since the probabilities are
  not constant numbers. Instead, we compute the branch probability expressions
  symbolically.
\end{itemize}

\paragraph*{Contributions and outline.}
After illustrating our method on a motivating example (\cref{sec:overview}), we
present our main contributions:
% 
\begin{itemize}
\item A symbolic execution method for probabilistic programs with unknown
  input parameters, along with a formal proof of soundness for the extensions
  to the probabilistic case (\cref{sec:pse}).
\item A broad collection of case studies drawn from the randomized algorithms
  literature (\cref{sec:case_studies}). All case studies have unknown input
  parameters, and none of the examples can be handled using existing automated
  methods. Some example properties include bounding the soundness probability of
  Freivalds' algorithm~\citep{freivalds1977}, a randomized algorithm to check
  matrix multiplication; the expected number of comparisons for randomized
  quicksort; and the correctness probability of a randomized property-testing
  algorithm for checking monotonicity~\citep{goldreich_2017}.
\item An implementation of our approach called \SYSTEM, building on the KLEE
  execution engine~\citep{cadar2008}, and an evaluation on our case studies
  (\cref{sec:impl_and_eval}). By building on KLEE,~\SYSTEM is able to
  perform symbolic execution on real implementations of probabilistic programs
  with natural code written in a wide variety of mainstream languages (e.g.,
  anything targeting LLVM), while faithfully models realistic program states
  (e.g., with overflowing arithmetic, arrays, etc.).
\end{itemize}
% 
We discuss related work in \cref{sec:related}, and future directions in
\cref{sec:conclusion}. \emph{An extended version of the paper that includes all the detailed proofs (in the appendix) is provided as supplemental material.}

\section{Overview}
\label{sec:overview}

The Monty Hall problem~\citep{selvin1975} is a classic probability puzzle based on the American television show, \textit{Let's Make a Deal}, which showcases how subtle probabilistic reasoning can be.
% 
\begin{wrapfigure}[27]{r}{0.5\textwidth}
  \centering
  \vspace{-1em}
	\inputminted[numbersep=3pt,xleftmargin=10pt,tabsize=2,fontsize=\footnotesize,linenos,escapeinside=||]{c}{montyhall.c}
	\caption{C code for the Monty Hall problem.}
	\label{fig:montyhall}
\end{wrapfigure}
The problem itself is simple:
\begingroup
\addtolength\leftmargini{-0.21in}
\begin{quote}
	You are a contestant on a game show and behind one of three doors there is a car and behind the others, goats.
	% 
	You pick a door and the host, who knows what is behind each of the doors, opens a different door, which has a goat.
	% 
	The host then offers you the choice to switch to the remaining door.
	% 
	Should you?
\end{quote}
\endgroup
\noindent{}While it may seem unintuitive, regardless of the contestant's original door choice, the contestant who always switches doors will win the car $\frac{2}{3}$ of the time, as opposed to a $\frac{1}{3}$ chance if the contestant sticks with their original choice.

We can represent this problem as a probabilistic program, as shown in \Cref{fig:montyhall}, where $\mathtt{choice} \in [1,3]$ is the door which is originally chosen by the contestant and $\mathtt{door\_switch}$ is \texttt{true} if the contestant wants to switch doors when asked, and \texttt{false} otherwise.
% 
If $\mathtt{door\_switch} = \mathtt{true}$, regardless of the value of \texttt{choice}, \texttt{monty\_hall} should return \texttt{true} (i.e., the car is won) $\frac{2}{3}$ of the time.
% 
In general, the problem we aim to solve is: given a probabilistic program with discrete sampling statements, and a target probability bound, how do we verify that the program satisfies the bound?
% 
For this particular program, the property is not so hard to verify with existing
methods---the input space is tiny, so it
is feasible to try all possible inputs and verify the probability bound on each
output distribution. However, we use this example to illustrate our symbolic
execution technique, which will scale to the more complex examples we will see
in \cref{sec:case_studies}.

In symbolic execution, program inputs are replaced by \textit{symbolic} variables which can take on any value.
% 
The program is then ``run'' on these symbolic variables and when a branch is reached execution proceeds along each of these two branches and the constraint is recorded in that path's, \textit{path condition}, which is represented by $\varphi$.
% 
This yields a \textit{symbolic execution tree} that represents the possible paths through the program.
\begin{figure}
	\centering
	{\footnotesize
		\begin{forest}baseline,for tree=draw,
			[{$\mathtt{\ref{line:monty_beg}}: c_0=\top$},align=center, base=bottom, line width=1.5pt
			[{$\mathtt{\ref{line:monty_choice_!=_car}}: c_1 = \alpha = 1$},align=center, base=bottom
			[{$\mathtt{\ref{line:monty_not_switch}}: c_2 = \beta$},align=center, base=bottom, node options={dotted,thick}, draw=red] %loss
			[{$\mathtt{\ref{line:monty_not_switch}}: c_2 = \neg\beta$},align=center, base=bottom, node options={dashed}, draw=darkgreen]] %win
			[{$\mathtt{\ref{line:monty_choice_!=_car}}: c_1 = \alpha \neq 1$},align=center, base=bottom, line width=1.5pt, edge={line width=1.5pt}
			[{$\mathtt{\ref{line:monty_choice_!=_2}}: c_2 = \alpha \neq 2$},align=center, base=bottom, line width=1.5pt, edge={line width=1.5pt}
			[{$\mathtt{\ref{line:monty_switch}}: c_3 = \beta$},align=center, base=bottom, node options={dashed}, draw=darkgreen ] % win
			[{$\mathtt{\ref{line:monty_switch}}: c_3 = \neg\beta$},align=center, base=bottom, edge={line width=1.5pt}, node options={dotted,thick}, draw=red, line width=1.5pt]] % loss
			[{$\mathtt{\ref{line:monty_choice_!=_2}}: c_2 = \alpha = 2$},align=center, base=bottom
			[{$\mathtt{\ref{line:monty_switch}}: c_3 = \beta$},align=center, base=bottom, node options={dashed}, draw=darkgreen ] % win
			[{$\mathtt{\ref{line:monty_switch}}: c_3 = \neg\beta$},align=center, base=bottom, node options={dotted,thick}, draw=red ]]]] % loss
		\end{forest}
	}
	\caption{Execution Tree for the Monty Hall Problem if the car is behind door 1.}
	\label{fig:montyhall_tree}
\end{figure}
Suppose we were to run traditional symbolic execution on the program in \Cref{fig:montyhall} where the car was randomly chosen to be behind door 1.
% 
The two inputs, \texttt{choice} and \texttt{door\_switch}, would become the symbolic variables $\alpha$ and $\beta$, respectively.
% 
The execution tree is shown in \Cref{fig:montyhall_tree}.
% 
Symmetric trees can be made for the cases when the car is behind door 2 and door 3.
% 
For each node in the tree the line number of the branch statement and the branch condition is given.
% 
Leaves which are surrounded by a dashed (\tikz{\draw[dashed, line width=1pt] (0,0) -- (0.35,0) }), {\color{darkgreen} green} line represent the contestant winning the car (the function returning \texttt{true}), and those leaves which are surrounded by a dotted (\tikz{\draw[dotted, thick, line width=1pt] (0,0) -- (0.35,0) }), {\color{red} red} line represent the contestant losing the contest (the function returning \texttt{false}).
% 
Each path condition, $\varphi$, can then be written as a conjunction of the $c_i$s along a path from the root of the tree to a leaf.

For example, consider the \textbf{bolded} path through the tree.
% 
The execution begins on line~\ref{line:monty_beg} with an empty path condition, $c_0 = \top$.
% 
Execution then reaches the first \textbf{if} condition on line~\ref{line:monty_choice_!=_car} and takes false branch which jumps to line~\ref{line:monty_choice_!=_1}; however, the guard, \texttt{choice != 1 \&\& car\_door != 1} is always \texttt{false} as \texttt{car\_door == 1}.
% 
We then skip this branch and instead branch again on line~\ref{line:monty_choice_!=_2}, and take the true branch to get to the third node in the bolded path.
% 
Lastly, execution jumps to line~\ref{line:monty_switch} where the contestant's choice to switch doors is checked.
% 
This branch actually determines whether the car is won along this path as we already have determined that the contestant did not choose the door which hides the car on line~\ref{line:monty_choice_!=_car}.
% 
If the contestant doesn't switch, they will lose, and since at this stage the host has revealed a door which has a goat behind it, the remaining door \textit{must} have the car.
% 
Therefore, switching will win the contestant the car and so this path ends in a loss.
% 
The entire path condition, $\varphi$, can then be written as $\varphi = \bigwedge_i c_i = \alpha \neq 1 \wedge \alpha \neq 2 \wedge \neg\beta$.

While this tree can tell us that it is \textit{possible} to win (or lose) the car with any choice of initial door and decision to switch, it does not tell us how \textit{often} a contestant will win for any initial door and decision to switch.
% 
In theory, if we knew how likely it was to take one branch over another we could extend this reasoning to determine how often we would hit a winning leaf over a losing leaf.
% 
\textbf{Our core idea is to represent probabilistic sampling statements as a new class of symbolic variables.}
% 
For the sake of presentation we refer to these as \textit{probabilistic} symbolic variables as opposed to, what we call, \textit{universal} symbolic variables which range over all possible values.
% 
So, instead of asking for a random value, we replace the result of the sample with a probabilistic symbolic variable and record the distribution from which the sample is from.
% 
Using this information, we can then compute the probabilities of taking branches.

Now let us return to the Monty Hall problem from~\Cref{fig:montyhall}.
% 
Let \texttt{car\_door} be represented by the probabilistic symbolic variable, $\delta$ and let \texttt{choice} and \texttt{door\_switch} be $\alpha$ and $\beta$, respectively, as before.
% 
Instead of branching solely on $\alpha$ and $\beta$, we additionally branch on $\delta$.
% 
The execution tree is presented in~\Cref{fig:montyhall_tree_prob}.
% 
Note that branches are omitted from the tree if the direction to traverse can be inferred by the current path condition.

Since probabilistic symbolic variables originate from a distribution, we can determine the \textit{probability} of taking a certain branch by simply counting how many values from the distribution satisfy the guard condition.
% 
For example, to figure out the probability of taking the \texttt{true} branch of the \texttt{if} condition on line 4 (denoted by $p_t$ in~\Cref{fig:montyhall_tree_prob}), it suffices to count how many settings of $\delta$ satisfy $\alpha = \delta$ and divide by the total number of possible assignments to $\delta$ (i.e., 3).
% 
However, since $\alpha$ is a symbolic variable we can only obtain a probability expression which is in terms of universal symbolic variables.
% 
Let $[\cdot]$ denote Iverson brackets, where $[Q]=1$ if formula $Q$ is true, and 0 otherwise.
% 
Then, $p_t = ([\alpha = 1] + [\alpha = 2] + [\alpha = 3])/3 = \frac{1}{3}$ as $\delta \in [1,2,3]$ and each setting is equally likely.
% 
Similarly, $p_f = ([\alpha \neq 1] + [\alpha \neq 2] + [\alpha \neq 3])/3 = \frac{2}{3}$.
% 
We stress that these probabilities are \emph{symbolic expressions}: they may
depend on the universal symbolic variables. This feature is one of the key
advantages of our technique over existing methods for probabilistic symbolic
execution---it makes reasoning about the probabilities much more complex, but it
also enables proving properties for programs with unknown inputs. (We defer
further comparison with related work to \cref{sec:related}.)

\begin{figure}
	\centering
	{\footnotesize
		\begin{forest}baseline,for tree=draw,
			[{$\mathtt{\ref{line:monty_beg}}: c_0=\top$},align=center, base=bottom
			[{$\mathtt{\ref{line:monty_choice_!=_car}}: c_1 = \alpha = \delta$},align=center, base=bottom, edge label={node [midway,above] {$p_t$} }
      [{$\mathtt{\ref{line:monty_not_switch}}: c_2 = \beta$},align=center, base=bottom, node options={dotted,thick}, draw=red ] %loss
      [{$\mathtt{\ref{line:monty_not_switch}}: c_2 =  \neg\beta$},align=center, base=bottom, node options={dashed}, draw=darkgreen ]] %win
			[{$\mathtt{\ref{line:monty_choice_!=_car}}: c_1 = \alpha \neq \delta$},align=center, base=bottom, edge label={node [midway,above] {$p_f$} }
			[{$\mathtt{\ref{line:monty_choice_!=_1}}: c_2 = \alpha \neq 1 \wedge \delta \neq 1$},align=center, base=bottom,
			[{$\mathtt{\ref{line:monty_switch}}: c_3 = \beta$},align=center, base=bottom, node options={dashed}, draw=darkgreen ] %win
      [{$\mathtt{\ref{line:monty_switch}}: c_3 = \neg\beta$},align=center, base=bottom, node options={dotted,thick}, draw=red ]] %loss
			[{$\mathtt{\ref{line:monty_choice_!=_1}}: c_2 = \alpha = 1 \vee \delta = 1$},align=center, base=bottom
			[{$\mathtt{\ref{line:monty_choice_!=_2}}: c_3 = \alpha \neq 2 \vee \delta \neq 2$},align=center, base=bottom
			[{$\mathtt{\ref{line:monty_switch}}: c_4 = \beta$},align=center, base=bottom, node options={dashed}, draw=darkgreen ] %win
			[{$\mathtt{\ref{line:monty_switch}}: c_4 = \neg\beta$},align=center, base=bottom, node options={dotted,thick}, draw=red ]] %loss
			[{$\mathtt{\ref{line:monty_choice_!=_2}}: c_3 = \alpha = 2 \vee \delta = 2$},align=center, base=bottom
			[{$\mathtt{\ref{line:monty_switch}}: c_4 = \beta$},align=center, base=bottom, node options={dashed}, draw=darkgreen ]%win
			[{$\mathtt{\ref{line:monty_switch}}: c_4 = \neg\beta$},align=center, base=bottom, node options={dotted,thick}, draw=red ]]]]] %loss
		\end{forest}
	}
	\caption{Execution tree for the Monty Hall Problem with probabilistic symbolic variables.}
	\label{fig:montyhall_tree_prob}
\end{figure}

With this \textit{probabilistic} execution tree in hand, let's return to the original question we wanted to answer: if the contestant switches doors, does their chances of winning the car exceed $\frac{1}{3}$?
% 
Note that each path in the tree has a probability associated with it.
% 
If we want to know the probability of winning if the contestant switches versus not, we can look at solely those paths in the tree which lead to a win.
% 
To then figure out the probability of winning the car if the contestant switches we then can remove those paths where $\neg\beta$ is true, and then sum up the probabilities of the remaining paths.
% 
This results in an expression in terms of $\alpha$ and constants, which we can then evaluate where $\alpha = 1$, $\alpha = 2$, and $\alpha = 3$ and compare the probabilities.
% 
In the end, we get that regardless the setting of $\alpha$ (i.e., the program variable, \texttt{choice}) the probability of winning the car if the contestant switches doors is exactly $\frac{2}{3}$.
% 
We formalize this intuition in Section~\ref{sec:query_gen} by expressing this query in first order logic, which can then be dispatched to automated solvers.

\section{Probabilistic Symbolic Execution Algorithm}
\label{sec:pse}

We present the formalism of our approach on \textbf{pWhile}, a core imperative
probabilistic programming language, as a model for more general probabilistic
languages. The statements of \textbf{pWhile} are described by the following
grammar:
% 
\[
  S := \mathtt{x} \gets e \mid \mathtt{x} \sim d \mid S_1 ; S_2 \mid \mathbf{if}~c~\mathbf{then~goto}~T \mid \mathbf{halt} 
\]
% 
Intuitively, the assignment statement $\mathtt{x} \leftarrow e$ assigns the
result of evaluating the expression $e$ to the program variable \texttt{x},
while the sampling statement $x \sim d$ draws a random sample from a primitive
distribution $d$ and assigns the result to the program variable \texttt{x}.
% 
Here, $d$ is a \textit{discrete} distribution expression which denotes which distribution the sample should be drawn from.
% 
We interpret distributions as functions from values to the range $[0,1]$, which denotes the probability of the value occurring in the distribution.
% 
For example, $\mathsf{UniformInt}(\mathtt{1},\mathtt{6})$ is a uniform distribution which selects at random a value between 1 and $6$ (inclusive).

Control flow is implemented by $S_1 ; S_2$, which sequences two statements $S_1$
and $S_2$, and conditional branching $\mathbf{if}~c~\mathbf{then~goto}~T$, which
jumps execution to statement $T$ if the guard $c$ holds, otherwise falling
through to the next instruction. We assume that high-level constructs like loops
and regular conditionals are compiled down to conditional branches. Finally,
$\mathbf{halt}$ marks the end of execution.

Our probabilistic symbolic execution algorithm will aim to answer the following question: What is the maximum (or minimum) probability that a program, \textsf{Prog}, terminates in a state where a predicate $\psi$ holds?
% 
Formally, we are interested in computing
\[
  \text{max}_{\vec{x}}\ \{ \Pr_\mu[\psi] \mid \mu = \mathsf{Prog}(\vec{x}, \psi)\}
\]
where $\mu$ is the distribution on outputs obtained by running $\mathsf{Prog}$ on inputs $\vec{x}$.
% 
Since this quantity is difficult to compute in general, we will also be interested in computing bounds on this quantity:
\[
  \text{max}_{\vec{x}}\ \{ \Pr_\mu[\psi] \mid \mu = \mathsf{Prog}(\vec{x}, \psi)\}
  \bowtie f(\vec{x})
\]
where $\bowtie~\in\{ \leq, \geq, =, \ldots \}$ is a comparison operator and $f$ is some given function of the program inputs.

We begin with an overview of standard symbolic execution for non-probabilistic
programs~(\Cref{sec:symex}). Then, we present our symbolic execution approach
for probabilistic programs. Our approach has two steps: first, we augment
standard symbolic execution to track probabilistic information as paths are
explored~(\Cref{sec:pse_intro}). Then, we convert program paths into a logical
query encoding a probabilistic property~(\Cref{sec:query_gen}).
% 
Finally, we formalize the semantics of our approach and prove its soundness~(\Cref{sec:formalization}).

\subsection{Symbolic Execution}
\label{sec:symex}

\begin{algorithm}
	\caption{Probabilistic Symbolic Execution Algorithm}
	\label{alg:symb_ex}
	\begin{algorithmic}[1]
		\Procedure{SymbEx} {\textsf{Prog} : \textit{Program}, $\vec{x}$ : \textit{Program Inputs}, \colorbox[RGB]{200, 200, 200}{$\psi$ : \textit{Predicate}}}
		\State{$E_s$} $\leftarrow$ {[]}, $\sigma \gets $ \textsc{BindToSymbolic}($\vec{x}$), \colorbox[RGB]{200, 200, 200}{$Enc_\psi \gets 0.0, Enc_a \gets 0.0$} \label{line:initialization} \algorithmiccomment{Initialization}
		\Let{$I_{0}$}{\textsc{getStartInstruction}(\textsf{Prog})} \label{line:first_inst}
		\Let{$S_{0}$}{($I_{0}$, $\top$, $\emptyset$, \colorbox[RGB]{200, 200, 200}{$\emptyset$, 1.0})} \label{line:init_state} \algorithmiccomment{Empty Initial State}
		\State {$E_s$.\textsc{Append}({$S_{0}$})} \algorithmiccomment{Start with $S_{0}$ in Execution Stack}
		\While{$E_s \neq \emptyset$} \label{line:execution_loop}
		\Let{($I_{c}, \varphi, \sigma, P, p)$}{$E_s$.\textsc{Remove}( )} \label{line:select_state}
		\If{\textsc{UNSAT}($\varphi$)}
		\State \textbf{continue}
		\EndIf
		\Switch{\textsc{instType}($I_{c}$)} \label{line:inst_type}
		\Case{\fbox{$\mathtt{x} \gets e$}} \label{line:pse_assignment} \algorithmiccomment{Assignment Instruction} \label{line:symbex_assign}
		\Let{$I_1$}{\textsc{getNextInstruction}($I_{c}$)}
		\Let{$\sigma[\mathtt{x}]$}{$\sigma[e]$} \label{line:beg_raw_assign}
		\Let{$S_{1}$}{($I_{1}$, $\varphi$, $\sigma$, \colorbox[RGB]{200, 200, 200}{$P$, $p$})} \label{line:end_raw_assign}
		\State {$E_s$.\textsc{Append}({$S_{1}$})}
		\EndCase
		\cCase{\fbox{$\mathtt{x} \sim d$}}{gray} \algorithmiccomment \colorbox[RGB]{200, 200, 200}{Sampling Instruction} \label{line:pse_sampling}
		\cState{gray} $I_1$ $\gets$ \textsc{getNextInstruction}($I_{c}$)
		\cState{gray} {$\sigma_1,~P_1 \leftarrow~${\textbf{PSESample}}~({$\mathtt{x},~d,~\sigma,~P$})} \label{line:pse_sym_sample}
		\cState{gray} $S_1 \gets (I_{c}, \varphi, \sigma_1, P_1, p)$ \label{line:end_raw_sample}
		\cState{gray} $E_s$.\textsc{Append}({$S_1$})
    \cEndCase{gray} \label{line:end_pse_sampling}
		\Case{\fbox{\textbf{if} $c$ \textbf{then goto} $T$}} \label{line:symbex_branch} \algorithmiccomment{Branch Instruction}
		\Let{$c_{sym}$}{$\sigma[c]$} \label{line:guard_convert}
		\State \colorbox[RGB]{200, 200, 200}{$p_t,~p_f \leftarrow~\mathbf{PSEBranch}~(c_{sym},~\varphi,~P)$} \label{line:pse_sym_branch}
		\Let{$I_{1}$}{\textsc{getInstruction}($T$)} 
		\Let{$I_{2}$} {\textsc{getNextInstruction}($I_c$)}	
		\Let{$S_{t}$}{($I_{1}$, $\varphi \wedge c_{sym}$, $\sigma$,\colorbox[RGB]{200, 200, 200}{$P$, $p \cdot p_t$})} \label{line:symbex_true_state} \algorithmiccomment \colorbox[RGB]{200, 200, 200}{Multiply with current \textit{path} probability}
		\Let{$S_{f}$}{($I_{2}$, $\varphi \wedge \neg c_{sym}$, $\sigma$,\colorbox[RGB]{200, 200, 200}{$P$, $p \cdot p_f$})} \label{line:symbex_false_state}
		\State {$E_s$.\textsc{Append}({$S_{f}$})}
		\State {$E_s$.\textsc{Append}({$S_{t}$})}% \algorithmiccomment{Start with True State}
		\EndCase \label{line:end_symbex_branch}
		\Case{\fbox{\textbf{halt}}} \algorithmiccomment{Terminate Instruction}
		\cState{gray} $\psi_{sym}\gets\sigma[\psi]$ \label{line:beg_enc}
		\cIf {\textsc{SAT}($\psi_{sym}$)}{gray}
		\cState{gray} $Enc_\psi \gets Enc_\psi + p$	\label{line:encoding_t}	 
		\cEndIf{gray}
		\cState{gray} $Enc_a \gets \textsc{AddEncoding}(Enc_a,p,\sigma)$ \label{line:encoding_a}
		\EndCase
		\EndSwitch \label{line:end_execution_loop}
		\EndWhile 
		\cState{gray} $r \gets\textsc{Solve}~(Enc_\psi,~Enc_a)$ \label{line:solve_encoding}
		\cState{gray}\Return{$r$}
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

\textit{Symbolic execution}~\citep{king1976} is a program analysis technique that iteratively explores the set of paths through a given program.
% 
Since program paths may depend on input variables, which are not known, symbolic execution treats each input as a \emph{symbolic} variable.
% 
All program operations are then redefined to manipulate these symbolic variables.
% 
We present a high-level description of symbolic execution in \Cref{alg:symb_ex}.
% 
The reader should ignore portions in \colorbox{gray}{shaded boxes} for now; these are our extensions to handle probabilistic programs, which we will discuss in the next section.

The symbolic execution algorithm tracks information about program states using the following key data-structures: the next instruction to be executed, $I_c$, a conjunctive formula, $\varphi$, consisting of the symbolic branch constraints that are true for a particular path, called a \textit{path condition}, and a mapping from program variables to symbolic expressions over constants and symbolic variables, $\sigma$, called an \textit{expression map}.
% 
To begin, \Cref{alg:symb_ex} initializes the execution stack, $E_s$, with an empty list, and the expression map, $\sigma$ with fresh symbolic variables for each \textit{program input} in the input vector, $\vec{x}$ by calling \textsc{BindToSymbolic} as shown in \cref{line:initialization}.
% 
$I_0$ is then initialized with the first instruction of the program at \cref{line:first_inst} and the initial state tuple $S_0$ is created on \cref{line:init_state} and appended to $E_s$.

The core of \Cref{alg:symb_ex} is presented on \crefrange{line:execution_loop}{line:end_execution_loop} as a loop which iterates through all reachable states until $E_s$ is exhausted.
% 
For each iteration we pop a state from $E_s$ (\cref{line:select_state}) and, if the selected path condition $\varphi$ is feasible, the target instruction is analyzed based on the instruction's form: \cref{line:pse_assignment} for assignment statements and \cref{line:symbex_branch} for branch statements.

For an assignment statement, $\mathtt{x} \leftarrow e$, where $e$ is a program expression, we first convert $e$ into a \textit{symbolic} expression using the expression map, $\sigma$. %$\sigma[\mathtt{x}]$ is either just the constant, $e$, or the symbolic representation of $e$, namely $\sigma[e]$.
% 
We use the notation $\sigma[e]$ to denote the symbolic expression $e_{sym}$ constructed by replacing each program variable in $e$ with its corresponding symbolic expression in $\sigma$.
% 
% This symbolic expression is then stored in $\sigma$.
% 
For a branch statement, \textbf{if} $e$ \textbf{then goto} $T$, the symbolic execution algorithm \textit{forks} by constructing the corresponding path conditions for both branches, appending the symbolic branch guard $c_{sym}$ in the positive or negative form (for the true and false directions, respectively).
% 
Finally, symbolic execution along a path terminates at a \textbf{halt} instruction, and the terminating states may be appended to an encoding for subsequent analysis.

\subsection{Probabilistic Symbolic Execution}
\label{sec:pse_intro}

Our key idea is to enable symbolic execution over probabilistic constructs using a new category of symbolic variables, which we refer to as \textit{probabilistic symbolic variables}.
% 
Accordingly, our algorithm distinguishes between two categories of symbolic variables:

\begin{itemize}
\item \textit{Universal symbolic variables}: These are identical to those in traditional symbolic execution, and are used to model arbitrary program inputs.
\item \textit{Probabilistic symbolic variables}: Probabilistic symbolic variables model a known distribution over a set of values.
  % 
  In our algorithm, a new probabilistic symbolic variable is created for each sampling statement to denote the sampling operation.
\end{itemize}

Symbolic execution becomes quite challenging when both universal and probabilistic variables are present, as now program branches are taken with some quantitative probability.
% 
To track information about probabilistic states, we add the following data-structures:
\begin{itemize}
\item \textit{Distribution map} ($P$). This map from probabilistic symbolic variables to distribution expressions tracks the distribution from which a probabilistic symbolic variable was originally sampled from.
  % 
	This is analogous to the symbolic variable map, $\sigma$, except for mapping probabilistic symbolic variables to distributions instead from program variables to symbolic expressions.
  % 
\item \textit{Path probability} ($p$). For each path, we adjoin a path probability expression, $p$, which may be parameterized by universal symbolic variables.
	% 
	Now each path has an associated path condition and path probability.
\end{itemize}

With this new infrastructure, we can now define how symbolic execution proceeds when execution reaches a sampling statement, and demonstrate how we compute the probability of taking either side of a branch statement. 
\begin{algorithm}
	\caption{PSE Sampling Algorithm}
	\label{alg:sample}
	\begin{algorithmic}[1]
		\Function{PSESample}{$\mathtt{x}, d, \sigma, P$}
		\Let{$\delta$}{Generate a fresh probabilistic symbolic variable} \label{line:fresh_psv}
		\State{$\sigma[\mathtt{x}] = \delta$}
		\State{$P[\delta] = d$} \label{line:update_P}
		\State\Return{$(\sigma, P)$}
		\EndFunction
	\end{algorithmic}
\end{algorithm}
\begin{paragraph}{Sampling (\Crefrange{line:pse_sampling}{line:end_pse_sampling})}
	On encountering a sampling statement, $\mathtt{x} \sim d$, at \cref{line:pse_sampling} of \Cref{alg:symb_ex}, we call \textsc{PSESample} to get the updated distribution map, $P$, and expression map, $\sigma$.
	% 
  The function~\textsc{PSESample} (\Cref{alg:sample}) takes four inputs: a program variable, \texttt{x}, a distribution expression, $d$, which determines the distribution the value of \texttt{x} is sampled from, the current expression map, $\sigma$, and the current distribution map, $P$, and returns updated expression and distribution maps.
  % 
  To model the random value returned from the distribution expression $d$, a fresh probabilistic symbolic variable, $\delta$, is created and \texttt{x} is mapped to $\delta$ under $\sigma$.
  % 
  Additionally, the distribution map is updated to reflect that $\delta$ is ``drawn'' from $d$.
\end{paragraph}
\begin{algorithm}
	\caption{PSE Branch Algorithm}
	\label{alg:branch}
	\begin{algorithmic}[1]
		\Function{PSEBranch}{$c_{sym}, \varphi, P$}
		\Let{$(\delta_1,\ldots,\delta_n)$}{$\dom{P}$}
		\Let{$(d_1,\ldots,d_n)$}{$(P[\delta_1],\ldots,P[\delta_n])$} \Comment{Retrieve all distribution expressions}
		\Let{$p_c$}{$\frac{\displaystyle\sum_{(v_1,\ldots,v_n) \in \dom{d_1} \times \cdots\times \dom{d_n}} [(c_{sym} \wedge \varphi)\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]}{\displaystyle\sum_{(v_1,\ldots,v_n) \in \dom{d_1} \times \cdots\times \dom{d_n}}[\varphi\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]}$}\label{line:branch_prob_compute}
		\State\Return{$(p_c, 1 - p_c)$}
		\EndFunction
	\end{algorithmic}
\end{algorithm}
\begin{paragraph}{Branches (\Crefrange{line:symbex_branch}{line:end_symbex_branch})}
  Since probabilistic programs can branch on random values, each branch has a probability of being taken.
  % 
	Note that with the addition of probabilistic symbolic variables we can now either branch on universal or probabilistic symbolic variables (or both).

	Upon reaching a branch statement, similar to traditional symbolic execution, the symbolic states corresponding to the true and false branches are added to $E_s$.
  % 
  Then, \textsc{PSEBranch} (\Cref{alg:branch}) computes probability \textit{expressions} for the true and false branches.
  % 
  \textsc{PSEBranch} takes as input a symbolic expression, $c_{sym}$, which is equivalent to the guard expression $c$, the current path condition, $\varphi$, and the current distribution map, $P$, and returns two probability expressions: $p_c$, which is denotes the probability of taking the true branch, and $1-p_c$, which denotes taking the false branch.
  % 
  For simplicity, we present this subroutine in the simplified setting where all
  sampling instructions are from the uniform distribution over a finite set;
  handling general weighted distributions is not much more complicated.

	To gain intuition on the computation of path probabilities, for now just consider the special case where the guard condition only involves universal symbolic variables.
	% 
  Let $c_{sym} = \sigma[c]$ be the equivalent symbolic expression for the guard $c$ and assume that $c_{sym}$ does not mention any probabilistic symbolic variables.
	% 
  In this case, the branch that is taken is entirely determined by the universal symbolic variables. 
	% 
	Therefore, for a fixed setting of the universal symbolic variables, one side of the branch must have a probability of 1, and the other side, 0.
  % 
  Put another way, either $c_{sym}$ can be satisfiable or $\neg c_{sym}$, but never both.
	% 
	We use Iverson brackets to formalize this idea; the probability of taking the ``true'' branch is $[c_{sym}]$, and the probability of taking the ``false'' branch is $[\neg c_{sym}]$.

	For probabilistic branches (i.e., guards which branch on probabilistic symbolic variables), computing the branch probability is more involved.
  % 
  We give an intuitive justification here, and defer the formal proof of correctness to \Cref{sec:formalization}.
	% 
  When symbolic execution is at the start of a conditional branch statement, the path condition $\varphi$ records the necessary constraints on the universal and probabilistic symbolic variables which must hold in order to reach this conditional branch. 
  % 
  Then, we can view the probability of taking either branch as a \textit{conditional probability}: the probability that $c_{sym}$ holds assuming that $\varphi$ is satisfied.
	% 
	In more formal notation, we aim to compute $\Pr[c_{sym} \mid \varphi] = {\Pr[c_{sym}\wedge \varphi]}/{\Pr[\varphi]}$.

  \Cref{alg:branch} builds an expression which computes this conditional probability.
	% 
	Note that each probabilistic symbolic variable, $\delta$, is mapped to exactly one distribution, $d$, and therefore, $\delta \in \dom{d}$.
	% 
	So, assuming there are $n$ probabilistic symbolic variables, $\delta_1,\ldots,\delta_n$, and so $n$ distributions, $d_1,\ldots,d_n$, the set of all possible values for $\delta_1,\ldots,\delta_n$ is $\mathcal{D} = \dom{d_1} \times \cdots \times \dom{d_n}$.
  % 
  Using our simplifying assumption that all probabilistic symbolic variables are drawn from a uniform distribution, each assignment $v_1, \dots, v_n$ to $\delta_1, \dots, \delta_n$ has equal probability.
  % 
  Thus, instead of computing the conditional probability as a ratio of probabilities, we can compute the ratio of the number of assignments from $\mathcal{D}$ which satisfy $c_{sym} \wedge \varphi$ and $\varphi$, as shown on \cref{line:branch_prob_compute} of \Cref{alg:branch}.
	% 
	Note that $p_c$ is not necessarily a value, but rather a symbolic expression containing constants and universal symbolic variables.
	% 
	Finally, we use the fact that the sum of the conditional probabilities of the branch outcomes is 1, which allows us to avoid computing the probability of taking the false branch directly.

  Now that we know the probability of taking a branch, we can compute the probability of traversing the entire path, or equivalently, the probability of $\varphi \wedge c_{sym}$ (or $\varphi \wedge \neg c_{sym}$) being satisfied.
  % 
  Note that $p_t$ is the \textit{conditional} probability of taking the true branch and $p_f$ is the conditional probability of taking the false branch on \cref{line:pse_sym_branch}, or $p_t = \Pr[c_{sym} \mid \varphi]$ and $p_f = \Pr[\neg c_{sym} \mid \varphi]$.
  % 
  Since $p$ is the probability of $\varphi$, to the probability of $\varphi \wedge c_{sym}$, we can simply multiply $p \cdot p_t$ according to the standard rule $\Pr[A \wedge B] = \Pr[A \mid B]\Pr[B]$ where $A$ and $B$ are any two events.
  % 
  The same can be done for $\varphi \wedge \neg c_{sym}$, as shown on \cref{line:symbex_true_state,line:symbex_false_state}.
\end{paragraph}

\begin{figure}[h]
	\centering
	\begin{subfigure}{.3\textwidth}
		\centering
		{\small
			\begin{algorithmic}[1]
				\State{$\mathtt{x}\sim\mathsf{UniformInt}(\mathtt{1},\mathtt{3})$}
				\State{$\mathtt{y}\sim\mathsf{UniformInt}(\mathtt{1},\mathtt{3})$}
				\If{$\mathtt{x} > \mathtt{1}$}\label{line:first_cond}
				\If{$\mathtt{x} < \mathtt{y}$}
				\State\Return{$\mathtt{True}$}
				\EndIf
				\Else
				\State\Return{$\mathtt{False}$}
				\EndIf
			\end{algorithmic}
		}
		\caption{Program with random sampling.}
		\label{fig:exam_program}
	\end{subfigure}
	\begin{subfigure}{.69\textwidth}
		\centering
		{\small
			\begin{forest}baseline,for tree=draw,
				[{$\varphi=\top$},align=center, base=bottom
				[{$\varphi = \delta_1 > 1$}, align=center, base=bottom, edge label={node [midway,above] {$\frac{2}{3}$} }
				[{$\varphi = (\delta_1 > 1) \wedge (\delta_1 < \delta_2)$}, align=center, base=bottom, edge label={node [midway,above] {$\frac{1}{6}$} }
				[{\texttt{True}}]]
				[{$\varphi = (\delta_1 > 1) \wedge \neg(\delta_1 < \delta_2)$}, align=center, base=bottom, edge label={node [midway,above] {$\frac{5}{6}$} }
				[{\texttt{False}}]]]
				[{$\varphi = \neg(\delta_1 > 1)$}, align=center, base=bottom, edge label={node [midway,above] {$\frac{1}{3}$} }
				[{\texttt{False}}]]]
			\end{forest}
		}
		\caption{Symbolic execution tree.}
		\label{fig:exam_tree}

	\end{subfigure}
	\caption{A sample, randomized program and its associated symbolic execution tree annotated with probabilities.}
	\label{fig:example}
\end{figure}
\begin{paragraph}{Example}
	Consider the code in \Cref{fig:exam_program} and suppose we wish to calculate the probability of the program returning \texttt{True}.
	% 
	Following~\Cref{alg:sample}, we generate fresh probabilistic symbolic variables for $\mathtt{x}$ and $\mathtt{y}$, $\delta_1$ and $\delta_2$, respectively.
	% 
	We also store the distributions which $\delta_1$ and $\delta_2$ are samples from, namely the discrete uniform distribution $\mathcal{U}\{1,3\}$.
	% 
	In our notation, we say that $\sigma = \{ \mathtt{x} \mapsto \delta_1, \mathtt{y} \mapsto \delta_2 \}$ and $P = \{ \delta_1,\delta_2 \mapsto \mathcal{U}\{1,3\} \}$.
	% 
	Now following \Cref{alg:branch} to process \cref{line:first_cond} of \Cref{fig:exam_program}, note that $\mathcal{D} = \{1,2,3\} \times \{1,2,3\}$ and

	\begin{align*}
		p_c = \Pr[\delta_1 < \delta_2 \mid \delta_1 > 1] &= \frac{\Pr[(\delta_1 < \delta_2) \wedge (\delta_1 > 1)]}{\Pr[\delta_1 > 1]}\\
                                   &= \frac{\displaystyle\sum_{(v_1,v_2) \in \mathcal{D}} [(\delta_1 < \delta_2) \wedge (\delta_1 > 1)\{\delta_1 \mapsto v_1, \delta_2 \mapsto v_2\}]}{\displaystyle\sum_{(v_1,v_2) \in \mathcal{D}} [(\delta_1 > 1)\{\delta_1 \mapsto v_1\}]} = \frac{1}{6}\\
	\end{align*}
  This probability means that the probability of taking the true branch of the inner \textbf{if} condition is only $\frac{1}{6}$, which makes sense as \texttt{x} is restricted to be either $2$ or $3$, but \texttt{y} can be either 1,2, or 3; however, only one combination of \texttt{x} and \texttt{y} will satisfy $\mathtt{x} < \mathtt{y}$, namely $\mathtt{x} = 2$ and $\mathtt{y} = 3$.
\end{paragraph}

\subsection{Query Generation}
\label{sec:query_gen}

Recall that our original goal is to find the maximum (or minimum) probability that a program, \textsf{Prog}, terminates in a state where a predicate $\psi$ holds.
% 
We frame this question as a logical query using the symbolic state found in the execution tree.
% 
In general, our queries are of the following form:
% 
\begin{equation}
  \label{eq:query}
	\forall \alpha_1,\ldots,\alpha_n~.~Enc_\psi \bowtie f(\alpha_1,\ldots,\alpha_n)
\end{equation}
% 
where $\alpha_1,\ldots,\alpha_n$ are \textit{all} the universal symbolic variables found in \textsf{Prog}, $Enc_\psi$ is an expression representing the probability that $\psi$ holds in \textsf{Prog}, $\bowtie$ is a binary relation (e.g., $>,<,\geq,\leq$), and $f$ is some function of the universal symbolic variables denoting the desired bound to check.
% 
There are three main components to our queries: 1) a universal quantification over the universal symbolic variables, 2) $Enc_\psi$, or the probability that $\psi$ holds in \textsf{Prog}, and 3) a desired upper/lower bound expression, potentially parameterized by universal symbolic variables, $e$
% 
\begin{enumerate}
\item If a program has $n$ universal symbolic variables, $\alpha_1,\ldots,\alpha_n$, we begin the query with a universal quantification, $\forall \alpha_1,\ldots,\alpha_n$, in order to reason over any setting of the non-probabilistic program variables.

\item We construct $Enc_\psi$ on~\crefrange{line:beg_enc}{line:encoding_a} of~\Cref{alg:symb_ex}.
  % 
  Once a path reaches a \textbf{halt} statement, $\psi$ is converted into a symbolic expression using the expression map, $\sigma$, called $\psi_{sym}$.
  % 
  If $\psi_{sym}$ is satisfiable, then we add $p$ to the current $Enc_\psi$ as this path's probability should be included in our query.
  % 
  Note that during some settings of $\alpha_1,\ldots,\alpha_n$, the path represented by $\varphi$ might not be reachable, and so we should exclude that probability from the sum.
  % 
  However, since we use $\varphi$ in the construction of $p$, if $\varphi$ is unsatisfiable, then $p$ will be 0 as each summand in the numerator of $p_c$, as defined on~\cref{line:branch_prob_compute} of~\Cref{alg:branch} will be 0. 
  % 
  For example, recall the Monty Hall program in~\Cref{fig:montyhall} and consider the left-most two paths in~\Cref{fig:montyhall_tree_prob}, namely $\varphi_1 := \alpha = \delta \wedge \beta$ and $\varphi_2 := \alpha = \delta \wedge \neg \beta$. 
  % 
  Note that $p_1 = [\alpha = 1 \wedge \beta] + [\alpha = 2 \wedge \beta] + [\alpha = 3 \wedge \beta]/3$ and $p_2 = [\alpha = 1 \wedge \neg\beta] + [\alpha = 2 \wedge \neg\beta] + [\alpha = 3 \wedge \neg\beta]/3$.
  % 
  If $\beta$ is true, then $p_2 = 0$ regardless of the setting of $\alpha$, as $\varphi_2$ is unsatisfiable.
  % 
  Once we have exhausted all reachable states in $E_s$, $Enc_\psi$ represents the probability that $\psi$ holds for all reachable paths in \textsf{Prog}.
\item Let $f$ be the lower/upper bound function of universal symbolic variables which we want to prove \textsf{Prog} does not violate.
  % 
  Another way of interpreting $f$ is a function which computes the \textit{desired} probability of $\psi$ occurring in \textsf{Prog} (e.g., a maximum acceptable error rate) given a setting of the universal symbolic variables.
  % 
  We should note, however, that symbolic execution is not complete, meaning not all possible paths necessarily will be reached.
  % 
  Therefore, we can only find violations on upper bounds, but not lower bounds, since it is possible that some missing paths might violate the lower bound, but if we find a violation on an upper bound, more paths will only make that violation more egregious.
\end{enumerate}

Once probabilistic symbolic execution terminates, \textsc{Solve} is called on \cref{line:solve_encoding} which takes in $Enc_\psi$, constructs formula \ref{eq:query}, and calls an automated decision procedure, such as an SMT solver, to answer the query.
% 
The meaning of this query depends on the termination condition of symbolic execution.
% 
If all reachable paths are explored, then $Enc_\psi$ represents the true probability that $\psi$ holds in the output distribution, parameterized by the unknown input variables.
% 
However, in most realistic settings, symbolic execution will not be able to explore all paths due to resource and time limitations.
% 
In this case, $Enc_\psi$ may not be equal to the true probability of $\psi$; however, it is always a sound \emph{lower bound} of this probability.
% 
This information is enough for our approach to refute upper bounds on
probability: if we want to verify that the probability of $\psi$ is at most $f(\alpha_1,\ldots,\alpha_n)$
for all settings of the input variables, and symbolic execution produces a
probability mass $Enc_\psi$ that exceeds $f(\alpha_1,\ldots,f_n)$ for some setting of the input
variables, then the original upper bound cannot hold.
\begin{paragraph}{Example}
  In~\Cref{sec:overview} we introduced the Monty Hall problem, and we wanted to prove that if a contestant always switched doors their probability of winning the car is $\frac{2}{3}$.
  % 
  With can frame this question as a query of the form defined in~\Cref{eq:query}.
  % 
  If $\alpha$ is the universal symbolic variable corresponding to \texttt{choice}, and $\beta$ is the universal symbolic variable corresponding to \texttt{door\_switch}, $\psi := \beta \wedge \mathsf{win}$ where \textsf{win} means the car is won (determined by the return value of \texttt{monty\_hall}), $\bowtie~:=~=$, and $f := \frac{2}{3}$, then our full query is: $\forall \alpha,\beta~.~Enc_\psi = \frac{2}{3}$.
  % 
  \Cref{alg:symb_ex} then constructs the tree found in~\Cref{fig:montyhall_tree_prob} and constructs the probability expression for each path.
  % 
  If $\varphi_i$ is path condition for the path ending in the $i^{\text{th}}$ left-most leaf of~\Cref{fig:montyhall_tree_prob}, and $p_i$ is the probability expression for $\varphi_i$, as created by~\Cref{alg:symb_ex}, then $Enc_\psi = p_3 + p_5 + p_7$.
  % 
  \textsc{Solve} then takes the query $\forall \alpha,\beta~.~p_3 + p_5 + p_7 = \frac{2}{3}$ and uses an external automated decision procedure to prove for each possible setting of $\alpha$ and $\beta$ that $p_3 + p_5 + p_7 = \frac{2}{3}$.
\end{paragraph}

\subsubsection{Expected Value Queries}
\label{sec:expected_value}

\begin{algorithm}
  \caption{\textsc{AddEncoding} for computing $\E{\mathtt{v}}$}
  \label{alg:expected_val_encoding}
  \begin{algorithmic}[1]
    \Function{AddEncoding}{$Enc_a,p,\sigma$}
    \State\Return $Enc_a + p \cdot \sigma[\mathtt{v}]$
    \EndFunction
  \end{algorithmic}
\end{algorithm}

In addition to normal probability bound queries, our technique can also be used to compute the expected value of any variable with only a slight modification.
% 
Suppose that we want to compute the expected value of a program variable \texttt{v}, denoted $\E{\mathtt{v}}$.
% 
Since each path has a probability, $p_i$, and an expression map, $\sigma_i$, we can construct a symbolic expression which computes $\E{\mathtt{v}}$, namely $\sum_{i=1}^n p_i \cdot \sigma_i[\mathtt{v}]$, as $\sigma_i[\mathtt{v}]$ is the symbolic expression which is the value of $\mathtt{v}$ along $i^\text{th}$ path.
% 
In terms of~\Cref{alg:symb_ex}, we use~\Cref{alg:expected_val_encoding} for \textsc{AddEncoding} on~\cref{line:encoding_a}.
% 
Then, for \textsc{Solve}, on~\cref{line:solve_encoding}, we use an automated decision procedure to solve the query
\[
	\forall \alpha_1,\ldots,\alpha_n~.~Enc_a \bowtie f(\alpha_1,\ldots,\alpha_n)
\]
where, as before, $\alpha_1,\ldots,\alpha_n$ are the universal symbolic variables representing the input variables of \textsf{Prog}.

\subsection{Formalization}
\label{sec:formalization}

In this section we present the formalization of our method. First, we will present our notation and definitions (\Cref{sec:notation}), and then state a series of soundness theorems for our technique (\Cref{sec:proofs}).
% 
The goal of this section is to describe how the symbolic state used by~\Cref{alg:symb_ex}, $R=(\sigma,\varphi,P)$, is an abstraction of a \textit{distribution of program memories}.

\subsubsection{Notation \& Definitions}
\label{sec:notation}

To begin, we will define some notation: 
\begin{itemize}
\item Let $\mathcal{V}$ be the set of all values, $\mathcal{X}$ be the set of all program variables, $\mathcal{Z}_U$ be the set of all universal symbolic variables, $\mathcal{Z}_P$ be the set of all probabilistic symbolic variables, and $\mathcal{Z} = \mathcal{Z}_U \cup \mathcal{Z}_P$ be the combined set of all symbolic variables.
\item Let $a_{\forall}: \mathcal{Z}_U \rightarrow \mathcal{V}$ be an assignment of universal symbolic variables to values and let $\mathit{A}_{\forall}$ be the set of all such assignments.
\item Similarly, let $a_p : \mathcal{Z}_P \rightarrow \mathcal{V}$ be an assignment of probabilistic symbolic variables to values and let $\mathit{A}_p$ be the set of all such assignments.
\item Let $m : \mathcal{X} \rightarrow \mathcal{V}$ be a program memory which translates program variables into values, and let $\mathit{M}$ be the set of all program memories.
\item Let $d : \mathit{M} \rightarrow (\mathcal{V} \rightarrow [0,1])$ be a distribution expression parameterized by program memories, and let $\mathit{Dists}$ be the set of all distribution expressions.
\item Let $\mu : \mathit{A}_{\forall} \times \mathit{M} \rightarrow [0,1]$ be a distribution of program memories parameterized by assignments to universal symbolic variables and let $\mathit{Dists_M}$ be the set of all parameterized distributions of program memories.
\end{itemize}

Additionally, we will use emphatic brackets ($\deno{\cdot}$) for two purposes:
\begin{itemize}
\item If $e$ is a \textit{program} expression containing the program variables $\mathtt{x}_1,\ldots,\mathtt{x}_n \in \mathcal{X}$, and $m \in \mathit{M}$, then
  \[
    \deno{e}m = \mathsf{eval}(e[\mathtt{x}_1 \mapsto m(\mathtt{x}_1),\ldots,\mathtt{x}_n \mapsto m(\mathtt{x}_n)])
  \]
\item If $e$ is a \textit{symbolic} expression containing the symbolic variables $\alpha_1,\ldots,\alpha_n \in \mathcal{Z}_U$ and $\delta_1,\ldots,\delta_m \in \mathcal{Z}_P$, and $a_{\forall} \in \mathit{A}_{\forall}$ and $a_p \in \mathit{A}_p$, then
  \[
    \deno{e}a_{\forall}a_p = \mathsf{eval}(e[\alpha_1\mapsto a_{\forall}(\alpha_1),\ldots,\alpha_n \mapsto a_{\forall}(\alpha_n), \delta_1 \mapsto a_p(\delta_1), \ldots, \delta_m \mapsto a_p(\delta_m)])
  \]
\end{itemize}

With this notation in hand, we can now define what it means for $R$ to be an abstraction of a distribution of programs memories.
\begin{definition}
  \label{def:main}
  Let $R = (\sigma,\varphi,P)$ be the abstraction generated by~\Cref{alg:symb_ex} where $\varphi: \mathit{A}_{\forall} \times \mathit{A}_p \rightarrow \{0,1\}$ denotes whether a path condition is true or false under the given assignments, $\sigma : \mathcal{X} \rightarrow SymExprs$ is a mapping from program variables to symbolic expressions generated through symbolic execution, and $P : \mathit{A}_{\forall} \rightarrow \mathcal{Z}_P \rightharpoonup (\mathcal{V} \rightarrow [0,1])$ is a mapping from probabilistic symbolic variables to the distribution it is sampled from, parameterized by assignments to universal symbolic variables.
  % 
  Additionally, for every assignment of universal symbolic variables, $a_{\forall} \in \mathit{A}_{\forall}$, $\dom{P(a_{\forall})} = \{\delta_1,\ldots,\delta_k\}$.
  % 
  Let $\alpha_1,\ldots,\alpha_l \in \mathcal{Z}_U$ be the universal symbolic variables which correspond to the $l$ parameters to the program.
  % 
  For every assignment of probabilistic and universal symbolic variables, $a_{\forall} \in \mathit{A}_{\forall}, a_p \in \mathit{A}_p$, let $\nu : \mathit{A}_{\forall} \rightarrow (\mathit{A}_p \rightarrow [0,1])$ be a distribution of assignments to probabilistic symbolic variables parameterized by assignments to universal symbolic variables, defined as
  \[
    \nu(a_{\forall},a_p) \triangleq \prod_{i=1}^k \Pr_{v \sim P(a_{\forall},\delta_i)}[v = a_p(\delta_i)].
  \]
  % 
  We say that a distribution $\mu$ satisfies our abstraction $R$ if, for all assignments to universal symbolic variables, $a_{\forall} \in \mathit{A}_{\forall}$, $\Pr_{a_p' \sim \nu(a_{\forall})}[\varphi(a_{\forall},a_p') = 1] > 0$, and if $\nu_{\varphi} : \mathit{A}_{\forall} \rightarrow (\mathit{A}_p \rightarrow [0,1])$ is defined as
  \[
    \nu_\varphi(a_{\forall},a_p) \triangleq \cfrac{\displaystyle\Pr_{a_p' \sim \nu(a_{\forall})}[a_p' = a_p \land \varphi(a_{\forall},a_p') = 1]}{\displaystyle\Pr_{a_p' \sim \nu(a_{\forall})}[\varphi(a_{\forall},a_p')=1]}.
  \]
  Additionally, define $\mathsf{toMem} : (\mathcal{X} \rightarrow SymExprs) \rightarrow \mathit{A}_{\forall} \rightarrow \mathit{A}_p \rightarrow M$ as
  \begin{equation*}
    \mathsf{toMem}(\sigma,a_{\forall},a_p) \triangleq \lambda (\mathtt{x}: \mathcal{X})~.~\deno{\sigma(\mathtt{x})}a_{\forall}a_p,
  \end{equation*}
  and let $\mathsf{fromMem}(\sigma,a_{\forall},m) = (\mathsf{toMem}(\sigma,a_{\forall}))^{-1}(m)$.
  % 
  Then,
  \[
    \mu(a_{\forall},m) \triangleq \sum_{a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m)} \nu_{\varphi}(a_{\forall},a_p).
  \]
\end{definition}

\subsubsection{Soundness Theorems}
\label{sec:proofs}

Note that in \Cref{alg:symb_ex} we represent the symbolic program state as a five-tuple, namely $S = (I, \varphi, \sigma, P, p)$; however, in our abstraction $R$, we omit $I$ and $p$.
% 
$I$ represents the current executing instruction which we remove as we prove soundness locally for each type of statement in \textbf{pWhile}, rather than prove soundness for the entirety of \Cref{alg:symb_ex}.
% 
Therefore, there is no need to track what the current instruction is.
% 
For $p$, we will begin by proving that $p$ can be completely reconstructed using $\varphi$ and $P$ and so there is no need to track it separately.
\begin{restatable}[Equivalency between $p$ and $(\varphi,P)$]{theorem}{equivpthm}
  For all program statements, $S$ in \textbf{pWhile}, \Cref{alg:symb_ex} maintains
  \[
    p = \frac{\displaystyle\sum_{v_1,\ldots,v_n \in \mathcal{D}} [ \varphi\{\delta_1 \mapsto v_1, \ldots, \delta_n \mapsto v_n\} ]}{\abs{\mathcal{D}}}
  \]
  where $\{\delta_1,\ldots,\delta_n\} = \dom{P}$, or all the probabilistic symbolic variables in the program, and $\mathcal{D} = \dom{P[\delta_1]} \times \cdots \times \dom{P[\delta_n]}$, or all the assignments to the probabilistic symbolic variables $\delta_1,\ldots,\delta_n$.
\end{restatable}

We will now prove soundness for \Cref{alg:symb_ex} by showing that our abstraction $R$ respects the semantics defined in the supplemental material for each of the three main types of statements in \textbf{pWhile}, namely \textit{assignment}, \textit{sampling}, and \textit{branching}. A proof for each theorem can be found in the supplemental material.

\begin{restatable}[Correctness of Assignment (\Crefrange{line:beg_raw_assign}{line:end_raw_assign})]{theorem}{soundnessAssignment}
  If a distribution $\mu$ satisfies $R=(\varphi,\sigma,P)$, and~\Cref{alg:symb_ex} reaches an assignment statement of the form $\mathtt{x} \gets e$, then $\mu_{\mathtt{x}\gets e}$, the distribution of program memories after executing $\mathtt{x} \gets e$, as defined in the supplemental material, satisfies $R'=(\varphi,\sigma',P)$, which is produced by~\Cref{alg:symb_ex}.
\end{restatable}

\begin{restatable}[Correctness of Sampling (\Crefrange{line:pse_sym_sample}{line:end_raw_sample})]{theorem}{soundnessSampling}
  If a distribution $\mu$ satisfies $R = (\varphi,\sigma,P)$ and~\Cref{alg:symb_ex} reaches a sampling statement of the form $\mathtt{x} \sim d$, then $\mu_{\mathtt{x} \sim d}$, the distribution of program memories after executing $\mathtt{x} \sim d$, as defined in the supplemental material, satisfies $R'=(\varphi,\sigma',P')$, which is produced by~\Cref{alg:symb_ex}.
\end{restatable}

\begin{restatable}[Correctness of Branching (\Cref{line:pse_sym_branch,line:symbex_true_state,line:symbex_false_state})]{theorem}{soundnessBranching}\label{thm:branch}
  If a distribution $\mu$ satisfies $R=(\varphi,\sigma,P)$, and~\Cref{alg:symb_ex} encounters a branching statement of the form $\mathbf{if}~c~\mathbf{then~goto}~T$, then $\mu_c$ satisfies $R_{true} = (\varphi \wedge c_{sym}, \sigma, P)$ and $\mu_{\neg c}$, the distribution of program memories after executing $\mathbf{if}~c~\mathbf{then~goto}~T$, as defined in the supplemental material, satisfies $R_{false} = (\varphi \wedge \neg c_{sym}, \sigma, P)$. Additionally, for all $a_{\forall} \in \mathit{A}_{\forall}$,
  \[
    \sum_{m \in \{m \in \mathit{M} \mid \deno{c}m = 1\}}\mu(a_{\forall},m) = \deno{p_c} a_{\forall}\quad\text{and}\quad\sum_{m \in \{m \in \mathit{M} \mid \deno{c}m = 0\}}\mu(a_{\forall},m) = \deno{p_c'} a_{\forall}.
  \]
\end{restatable}

\section{Case Studies}
\label{sec:case_studies}
In this section we will briefly explain each of the case studies that we use in our evaluation (\Cref{sec:impl_and_eval}).
% 
For each case study, we will explain, (1) the algorithm, (2) the property we aim to verify using our technique, and (3) any variants to the core algorithm we consider.
% 
For the sake of presentation, we present the queries using the program variable names instead of the equivalent symbolic variable representations.

\subsection{Freivalds' Algorithm}
\label{sec:freivalds}

\begin{algorithm}[h]
  \caption{Freivalds' Algorithm}
  \label{alg:freivalds}
  \begin{algorithmic}[1]
    \Require $A,B$, and $C$ are $n \times n$ matrices
    \Function{Freivalds}{$A,B,C,n$}
    \Let{$\vec{r}$}{An empty $n \times 1$ vector}
    \For{$i\gets1,n$}
    \State{$\vec{r}[i] \sim \mathsf{UniformInt}(0,1)$} 
    \EndFor
    \Let{$\vec{D}$}{$A \times (B\vec{r}) - C\vec{r}$}
    \State\Return{$\vec{D} = \begin{pmatrix} 0 & \cdots & 0 \end{pmatrix}^{\text{T}}$}
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\paragraph*{Background.}
Freivalds' algorithm~\citep{freivalds1977} is a randomized algorithm used to verify matrix multiplication in $\mathcal{O}(n^2)$ time.
% 
Given three $n \times n$ matrices $A, B$, and $C$, Freivalds' algorithm checks whether $A \times B = C$ by generating a random $n \times 1$ vector containing 0s and 1s, $\vec{r}$ and checks whether $A \times (B\vec{r}) - C\vec{r} = (0,\ldots,0)^T$.
% 
If so, the algorithm returns \texttt{true}, and \texttt{false} otherwise.
% 
If $A \times B = C$, the algorithm returns \texttt{true} with probability $1$ (always).
% 
However, if $A \times B \neq C$, the probability that the algorithm returns \texttt{true} is at most $\frac{1}{2}$.
% 
Pseudocode for the algorithm is presented in \Cref{alg:freivalds}.

\paragraph*{Target queries.}
We want to verify that the false-positive error rate does not exceed $\frac{1}{2}$.
% 
Letting $\psi := A \times B \neq C \wedge \textsc{Freivalds}(A,B,C,n) = \texttt{true}$, our query is

\begin{equation}
	\forall A,B,C,n~.~Enc_\psi \leq \frac{1}{2}.\label{eq:freivalds}
\end{equation}

\begin{algorithm}[h]
  \caption{Freivalds' Algorithm (Multiple)}
  \label{alg:mult_freivalds}
  \begin{algorithmic}[1]
    \Function{MultFreivalds}{$A,B,C,n,k$}
    \For{$i\gets1,k$}
    \If{\Call{Freivalds}{$A,B,C,n$} $= \mathtt{false}$}
    \State\Return{\texttt{false}}
    \EndIf
    \EndFor
    \State\Return{\texttt{true}}
    \EndFunction
  \end{algorithmic}
\end{algorithm}

To reduce the probability of false-positive in~\Cref{alg:freivalds} can be run $k$ times and returns \texttt{true} only if each call to Freivalds' algorithm returns \texttt{true}, and \texttt{false} otherwise.
% 
The pseudocode for this variant is presented in~\Cref{alg:mult_freivalds}.
% 
Since each trial is independent, the probability of a false-positive given that $A \times B \neq C$ is at most $\left(\frac{1}{2}\right)^k$.
% 
Thus, letting $\psi := A \times B \neq C \wedge \textsc{MultFreivalds}(A,B,C,n,k) = \texttt{true}$, our query becomes:
% 
\begin{equation*}
	\forall A,B,C,n,k~.~Enc_\psi \leq \left(\frac{1}{2}\right)^k.
\end{equation*}

% \subsection{Randomized Response}
% \label{sec:randomized_response}

% \begin{algorithm}[H]
%   \caption{Randomized Response (Fair)}
%   \label{alg:rand_resposne}
%   \begin{algorithmic}[1]
%     \Function{RandomizedResponse}{$truth$}
%     \Let{$flip_1$}{$\mathsf{UniformInt}(0,1)$}
%     \If{$\neg flip_1$}
%     \State\Return{$truth$}
%     \Else
%     \Let{$flip_2$}{$\mathsf{UniformInt}(0,1)$}
%     \State\Return{$flip_2$}
%     \EndIf
%     \EndFunction
%   \end{algorithmic}
% \end{algorithm}

% \paragraph*{Background.}
% Randomized response is a surveying technique which allows respondents to answer in a way that provides plausible deniability.
% % 
% Before answering the query, a coin is flipped.
% % 
% If ``tails'', then the respondent answers truthfully, if ``heads'', a second coin is flipped and the respondent answers ``Yes'' if ``heads'' and ``No'' if tails.
% % 
% In fact, this method satisfies the $(\ln 3, 0)$-differentially privacy guarantee~\citep{DMNS06}.

% \paragraph*{Target query.}
% To prove this fact, we have to show that
% \[
%   \frac{\Pr[\textsc{RandomizedResponse}(\text{Yes}) = \text{Yes}]}{\Pr[\textsc{RandomizedResponse}(\text{No}) = \text{Yes}]} = \frac{3/4}{1/4} = \frac{\Pr[\textsc{RandomizedResponse}(\text{No}) = \text{No}]}{\Pr[\textsc{RandomizedResponse}(\text{Yes}) = \text{No}]} = 3.
% \]
% Using our method, we can make four separate queries to compute the four different quantities.
% % 
% For example, to prove that $\Pr[\textsc{RandomizedResponse}(\text{Yes}) = \text{Yes}] = \frac{3}{4}$, let $\psi_1 := \mathit{truth} = \text{Yes} \wedge \textsc{RandomizedResponse}(\mathit{truth}) = \text{Yes}$ and take the following query:
% % 
% \begin{equation}
%   \label{eq:ranomized_response_yes_yes}
%   \forall \mathit{truth}~.~Enc_{\psi_1} = \frac{3}{4}.
% \end{equation}
% % 
% For the other three (Input, Output) combinations, we ask similar queries.
% % 
% We additionally consider variants where the coin flips are weighted.

\subsection{Reservoir Sampling}
\label{sec:reservoir_sampling}

\begin{algorithm}
	\caption{Reservoir Sampling}
	\label{alg:reservoir_sampling}
	\begin{algorithmic}[1]
    \Require $1 \leq k \leq n$
		\Function{ReservoirSampling}{$A[1..n], k$}
    \Let{$S$}{An empty list of size $k$}
		\For{$i\gets1,k$}
		\Let{$S[i]$}{$A[i]$}
		\EndFor
		\For{$i\gets k+1,n$}
		\Let{$j$}{$\mathsf{UniformInt}(1,i)$}
		\If{$j \leq k$}
		\Let{$S[j]$}{$A[i]$}
		\EndIf
		\EndFor
		\State\Return{$S$}
		\EndFunction
	\end{algorithmic}
\end{algorithm}

\paragraph*{Background.}
Reservoir sampling \citep{vitter_1985} is an online, randomized algorithm to get a simple random sample of $k$ elements from a population of $n$ elements.
% 
It uses uniform integer samples to constantly maintain a set of $k$ elements drawn from the set of $n$ elements.
% 
For the full algorithm, see~\Cref{alg:reservoir_sampling}.
% 
We want to verify that each possible sample is returned with equal probability, namely $1/\binom{n}{k}$ or, in other words, the output distribution of samples is uniform.
% 
To do this, we instead prove an equivalent property that if all elements of $A$ are distinct then the probability that any element of $A$ appears in $S$ is $k/n$.

\paragraph*{Target query.}
One way of framing the query is to ask the probability of the first element of $A$ appearing in $S$.
% 
If all elements of $A$ are distinct, then this probability will be the same for all elements in $A$.
% 
Therefore, let $\psi := A[1] \neq \cdots \neq A[n] \wedge A[1] \in \textsc{ReservoirSampling}(A,k)$. Then we can take the following query:
\begin{equation*}
  \forall A,n,k~.~Enc_\psi = \frac{k}{n}.
\end{equation*}

% \subsection{Schwartz-Zippel Lemma}
% \label{sec:schwartz-zippel}

% \begin{algorithm}
%   \caption{Schwartz-Zippel Lemma}
%   \label{alg:schwartz-zippel}
%   \begin{algorithmic}[1]
%     \Function{SchwartzZippel}{$P,D,S,n$}
%     \Let{$R$}{An empty list of size $n$}
%     \For{$i\gets1,n$}
%     \Let{$R[i]$}{$\mathsf{Uniform}(S)$} \Comment{Uniformly sample from a set $S$}
%     \EndFor
%     \Let{$\mathit{sum}$}{$0$}
%     \For{$i\gets1,n$}
%     \Let{$\mathit{sum}$}{$\mathit{sum} + P[i] \cdot R[i]^{D[i]}$}
%     \EndFor
%     \State\Return{$\mathit{sum} = 0$}
%     \EndFunction
%   \end{algorithmic}
% \end{algorithm}

% \paragraph*{Background.}
% The Schwartz-Zippel lemma is a probabilistic method of polynomial identity
% testing, that is, the problem of determining whether a given multivariate
% polynomial is identically equal to 0 or not.
% % 
% Given a non-zero polynomial of total degree $d$, $P$, over a field $F$, and $r_1,\ldots,r_n$ selected at random from a subset of $F$, say $S$, the lemma states that
% \[
%   \Pr[P(r_1,\ldots,r_n) = 0] \leq \frac{d}{\abs{S}}
% \]
% if the polynomial is not identically 0; if the polynomial is identically equal
% to zero, then the probability is equal to $1$.

% We model this lemma using~\Cref{alg:schwartz-zippel} which takes as input a list of $n$ coefficients from $F$, $P$, a list of $n$ degrees, $D$, a subset $S \subseteq F$, and the number of terms in the polynomial, $n$.
% % 
% \Cref{alg:schwartz-zippel} then picks $n$ random elements from $S$ and plugs them into the polynomial represented by $P$ and $D$.
% % 
% If the results from evaluating the polynomial are all equal to zero, then the
% algorithm returns \texttt{true}; otherwise, it returns \texttt{false}.

% \paragraph*{Target query.}
% To check the property, we let $\psi := (P[1] \neq 0 \vee \cdots \vee P[n] \neq 0) \wedge \textsc{SchwartzZippel}(P,D,S,n) = \texttt{true}$ and take the query be
% \begin{equation}
%   \label{eq:schwartz-zippel}
%   \forall P,D,S,n~.~Enc_\psi \leq \frac{\max(D)}{\abs{S}}.
% \end{equation}

\subsection{Randomized Monotonicity Testing}
\label{sec:monotone_testing}

\begin{algorithm}
  \caption{Randomized Monotonicity Testing~\citep{goldreich_2017}}
  \label{alg:monotone_testing}
  \begin{algorithmic}[1]
    \Function{MonotoneTest}{$f,n$}
    \State $l \gets \lceil \log_2 n \rceil, a \gets 1, b \gets n$ \label{line:monotone_l}
    \Let{$i$}{$\mathsf{UniformInt}(1,n)$}
    \For{$t\gets1,l$}
    \Let{$p$}{$\lceil a+b/2 \rceil$}
    \If{$i \leq p$}
    \If{$f[i] > f[p]$}
    \State\Return \texttt{false}
    \EndIf
    \Let{$b$}{$p$}
    \Else
    \If{$f[i] < f[p]$}
    \State\Return \texttt{false}
    \EndIf
    \Let{$a$}{$p+1$}
    \EndIf
    \EndFor
    \State\Return \texttt{true}
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\paragraph*{Background.}
Property testing is a subfield of computer science which aims to develop algorithms to determine whether a mathematical object has some property.
% 
For example, given a function $f: [n] \rightarrow R_n$ where $[n] = \{1,\ldots,n\}$ and $R$ is some ordered set, how can we determine whether $f$ is monotone?
% 
That is, can we check that $f(i) \leq f(j)$ whenever $i \leq j$?
% 
\Cref{alg:monotone_testing} is a randomized algorithm inspired by the binary
search algorithm to rapidly determine how ``far'' from monotone $f$ is~\citep{goldreich_2017}.

To get an intuitive understanding of this algorithm suppose that $f$ is an array of size $n$ where each element is distinct.
% 
~\Cref{alg:monotone_testing} selects an element $i \in [1,n]$ at random and attempts to find the value $f(i)$ in the array using binary search.
% 
If $f$ is actually (strictly) monotone, then it will find $f(i)$ at location $i$, and will accept if and only if $f(i)$ is found during this search at all.
% 
However, if $f$ is not monotone, specifically \textit{$\delta$-far} from
monotone, it will reject with probability greater than $\delta$~\citep{goldreich_2017}, where $\delta$-far means that $\delta\cdot n$ points need to be changed in $f$ in order to make $f$ monotone.
% 
This is the property that we want to check.

Let $\mathsf{DistToMono}(f)$ be a function which returns the number of elements whose order needs to be changed in order to make $f$ monotone.
% 
Letting $\psi := \mathsf{DistToMono}(f) = k \wedge \textsc{MonotoneTest}(f,n) = \texttt{false}$, we take the query
% 
\begin{equation*}
  \forall f,n~.~Enc_\psi > \frac{k}{n}.
\end{equation*}

\subsection{Randomized Quicksort}
\label{sec:quicksort}

\begin{algorithm}
  \caption{QuickSort}
  \label{alg:quicksort}  
  \begin{algorithmic}[1]
    \Function{QuickSort}{$A,p,r$}
    \If{$p < r$} \label{line:quicksort_comp1}
    \Let{$q$}{\Call{Partition}{$A,p,r$}}
    \State\Call{QuickSort}{$A,p,q-1$}
    \State\Call{QuickSort}{$A,q+1,r$}
    \EndIf
    \EndFunction
    \Statex
    \Function{Partition}{$A,p,r$}
    \Let{$i$}{$\mathsf{UniformInt}(p,r)$}
    \State exchange $A[r]$ with $A[i]$
    \Let{$x$}{$A[r]$}
    \Let{$i$}{$p-1$}
    \For{$j\gets p, r-1$}
    \If{$A[j] \leq x$} \label{line:quicksort_comp2}
    \Let{$i$}{$i + 1$}
    \State exchange $A[i]$ with $A[j]$
    \EndIf
    \EndFor
    \State exchange $A[i+1]$ with $A[r]$
    \State\Return $i+1$
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\paragraph*{Background.}
Quicksort is a popular sorting algorithm which uses partitioning in order to achieve efficient sorting.
% 
While there are many ways of choosing a pivot element, one way is through a uniform random sample.
% 
Using this pivot method, the \textit{expected} number of comparisons required is $1.386 n \log_2(n)$ where $n$ is the length of the array.

\paragraph*{Target query.}
We use the method described in~\Cref{sec:expected_value} to compute $\E{\mathtt{num\_comps}}$, where \texttt{num\_comps} is a program variable which is initially set to 0 and is incremented on~\cref{line:quicksort_comp1,line:quicksort_comp2}.
% 
Intuitively, \texttt{num\_comps} counts the number of comparisons performed on a given run of \textsc{QuickSort}.

\subsection{Interlude: Hash Functions}
\label{sec:hash_function}

\begin{algorithm}
  \caption{Uniform Hash Function}
  \label{alg:hash_function}
  \begin{algorithmic}[1]
    \Function{HashCreate}{$\mathit{min},\mathit{max}$} \label{line:hashfns}
    \Let{$H$}{An empty, uninitialized hash function}
    \Let{$H.Map$}{An empty map}
    \Let{$H.min$}{$\mathit{min}$}
    \Let{$H.max$}{$\mathit{max}$}
    \State\Return{$H$}
    \EndFunction
    \Statex
    \Function{Hash}{$H,x$}
    \If{$x \in H.Map$}
    \State\Return{$H.Map[x]$}
    \Else
    \Let{$i$}{$\mathsf{UniformInt}(H.min,H.max)$}
    \Let{$H.Map[x]$}{$i$}
    \State\Return{$i$}
    \EndIf
    \EndFunction
  \end{algorithmic}
\end{algorithm}

The remaining case-studies make use of \textit{hash functions} in order to achieve their guarantees.
% 
For non-cryptographic purposes, hash functions allow for rapid indexing into data structures and in many cases allow for constant time data retrieval.
% 
Formally, hash functions take elements from some universe and map them to a fixed range, often between $[1,n]$ where $n$ is the length of an array.
% 
Ideally, these functions distribute elements from the universe \textit{uniformly} across the range, so distinct elements hash to the same target with low probability.
% 
If $h$ is a hash function, and $x,y$ are arbitrary elements, we define a \textit{hash collision} to be when $h(x) = h(y)$ where $x \neq y$.
% 
In the upcoming examples, the probability of a certain number of hash collisions occurring is directly connected to the error rate of the examples.

To properly analyze programs which employ hashing we consider ideal, \textit{uniform} hash functions.
% 
Therefore, we model hash functions through uniform random samples.
% 
Pseudocode for how we model hash functions is provided in the function \textsc{HashCreate} in~\Cref{alg:hash_function}, Line~\ref{line:hashfns}
% 
Essentially, to hash an unseen element, $x$, we randomly sample an integer between $H.min$ and $H.max$.
% 
We then record that sample in $H.Map$ in order to maintain determinism.
% 
To hash $x$ again in the future, we simply retrieve the sample from the mapping.
% 
This ensures that each element is hashed uniformly and independently the first time, while subsequent hashes of an element always return the same result.

\subsection{Bloom Filter}
\label{sec:bloom_filter}
\begin{algorithm}
  \caption{Bloom Filter}
  \label{alg:bloom_filter}
  \begin{algorithmic}[1]
    \Function{BloomCreate}{$m,\epsilon$}
    \Let{$B$}{An empty, uninitialized Bloom Filter}
    \Let{$B.Arr$}{A bit-array of size $-\frac{m\ln \varepsilon}{(\ln 2)^2}$}
    \Let{$B.H$}{A list of $-\frac{\ln \epsilon}{\ln 2}$ independent hash functions}
    \State\Return{$B$}
    \EndFunction
    \Statex
    \Function{BloomInsert}{$B,x$}
    \ForAll{$h \in B.H$}
    \Let{$B.Arr[h(x)]$}{$1$}
    \EndFor
    \State\Return{$B$}
    \EndFunction
    \Statex
    \Function{BloomCheck}{$B,x$}
    \ForAll{$h \in B.H$}
    \If{$\neg B.Arr[h(x)]$}
    \State\Return{\texttt{false}}
    \EndIf
    \EndFor
    \State\Return{\texttt{true}}
    \EndFunction
    \Statex
    \Require $X[1] \neq \cdots \neq X[m] \neq y$
    \Function{Main}{$X,y,m,\epsilon$}\label{line:bloom_filter_main}
    \Let{$B$}{\Call{BloomCreate}{$m,\epsilon$}}
    \For{$i\gets1,m$}
    \Let{$B$}{\Call{BloomInsert}{$B,X[i]$}}
    \EndFor
    \State\Return{\Call{BloomCheck}{$B,y$}}
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\paragraph*{Background.}
A Bloom filter~\citep{bloom_1970} is a space-efficient, probabilistic data structure used to rapidly determine whether an element is in a set.
% 
Fundamentally, it is a bit-array of $n$ bits and $k$ associated hash functions, each of which maps elements in the set to places in the bit-array.
% 
To insert an element, $x$, into the filter, $x$ is hashed using each of the $k$ hash functions to get $k$ array positions.
% 
All of the bits at these positions are set to 1.
% 
To check whether an element $y$ is in the filter, $y$ is again hashed by each of the hash functions to get $k$ array positions.
% 
The bits at each of these positions are checked and the filter reports that $y$ is in the filter if, and only if, each of the bits are set to 1.
% 
Note that false-positives are possible due to hash collisions, but false negatives are not.
% 
Pseudocode for a Bloom filter is provided in~\Cref{alg:bloom_filter}.

\paragraph*{Target query.}
In order to bound the false-positive error rate, most implementations of Bloom filters take in the expected number of elements to be inserted as well as the \textit{desired} false-positive error rate.
% 
From these two quantities, the optimal size of the bit-array, $n$, as well as the number of hash functions, $k$ can be computed.
% 
If $m$ is the expected number of elements and $\varepsilon$ is the desired error rate, then the optimal settings of $n$ and $k$ are
\begin{equation}
  n = - \frac{m\ln \varepsilon}{(\ln 2)^2}\quad\text{and}\quad k = - \frac{\ln \varepsilon}{\ln 2}\label{eq:bloom_n_and_k}
\end{equation}
% 
We want to prove that for a given $m$ and $\varepsilon$ that the actual false-positive rate does not exceed $\varepsilon$.
% 
In other words, we want to show that the probability that \textsc{Main} (on~\cref{line:bloom_filter_main} of~\Cref{alg:bloom_filter}) returns \texttt{true} does not exceed $\epsilon$.

To capture this property, we let $\psi := X[1] \neq \cdots \neq X[m] \neq y \wedge \textsc{Main}(X,y,m,\epsilon) = \texttt{true}$ and take the query:
% 
\begin{equation*}
  \forall X,y,m,\epsilon~.~Enc_\psi \leq \epsilon
\end{equation*}

As we show later, setting $n$ and $k$ based on the number of expected elements $m$ and desired false-positive error rate, $\epsilon$, as in~\Cref{eq:bloom_n_and_k} does \textit{not} guarantee that the actual false-positive error rate is $\epsilon$.
% 
In actuality, $\epsilon$ will only be a lower bound for the actual false-positive error rate.

\subsection{Count-min Sketch}
\label{sec:countminsketch}

\begin{algorithm}
  \caption{Count-min Sketch}
  \label{alg:countminsketch}
  \begin{algorithmic}[1]
    \Function{SketchCreate}{$\epsilon,\gamma$}
    \Let{$w$}{$\lceil \frac{e}{\epsilon} \rceil$}
    \Let{$d$}{$\lceil \ln \frac{1}{\gamma} \rceil$}
    \Let{$C$}{An empty, uninitialized count-min sketch}
    \Let{$C.\mathit{sketch}$}{An empty $w \times d$ array}
    \Let{$C.H$}{A list of $d$ independent hash functions}
    \State\Return $C$
    \EndFunction
    \Statex
    \Function{SketchUpdate}{$C,x$}
    \For{$j\gets1,d$}
    \Let{$C.\mathit{sketch}[j,C.H[j](x)]$}{$C.\mathit{sketch}[j,C.H[j](x)] + 1$}
    \EndFor
    \State\Return $C$
    \EndFunction
    \Statex
    \Function{SketchEstimate}{$C,x$}
    \Let{$\hat{a}_x$}{$\infty$}
    \For{$j\gets1,d$}
    \Let{$\hat{a}_x$}{$\min(\hat{a}_x,C.\mathit{sketch}[j,C.H[j](x)])$}
    \EndFor
    \State\Return $\hat{a}_x$
    \EndFunction
    \Statex
    \Function{Main}{$\epsilon,\gamma,X,n$} \label{line:countminsketch_main}
    \Let{$C$}{\Call{SketchCreate}{$\epsilon,\gamma$}}
    \For{$i\gets1,n$}
    \Let{$C$}{\Call{SketchUpdate}{$C,X[i]$}}
    \EndFor
    \State\Return \Call{SketchEstimate}{$C,X[1]$}~$> 1+\epsilon n$
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\paragraph*{Background.}
A Count-min Sketch~\citep{graham_2005} is another space-efficient, probabilistic data structure which is used as a frequency table for a stream of data.
% 
It constantly maintains an estimate for the number of times an element $x$ has been seen while using sub-linear space.
% 
Behind the scenes, the data structure is a 2D array of $w$ columns and $d$ rows, and $d$ pairwise independent hash functions, one per row.
% 
To create a new count-min sketch, $\epsilon$ and $\gamma$ are taken as arguments representing the additive factor for the count to be off and the probability of error occurring, respectively.
% 
Most commonly, $w = \lceil \frac{e}{\epsilon} \rceil$ and $d = \lceil \ln \frac{1}{\gamma} \rceil$.
% 
To update the count for an element $x$, for each row $j$, $x$ is hashed using $j$'s hash function, $h_j$, to get the column index $k$.
% 
That is, $k = h_j(x)$.
% 
The value at row $j$ and column $k$ is then updated.
% 
Let $\mathit{sketch}$ be the 2D array.
% 
Then, to get the count for $x$, $\hat{a}_x$, $x$ is hashed using each row's associated hash function to index into $\mathit{sketch}$ and the minimum element among each of the $d$ counts is chosen as the estimate, or, in other words, $\hat{a}_x = \min_j \mathit{sketch}[j,h_j(x)]$.
% 
This count has the property that $\hat{a}_x \leq a_x + \epsilon N$ with probability $1-\gamma$, where $a_x$ is the ``true'' count for $x$ and $N = \sum_x a_x$, or the total number of elements seen by the sketch.
% 
This is the property we wish to verify.
% 
Pseudocode for count-min sketch is provided in~\Cref{alg:countminsketch}.

\paragraph*{Target query.}
We want to prove that for all $\epsilon$ and $\gamma$, the probability of \textsc{Main} (\cref{line:countminsketch_main} of~\Cref{alg:countminsketch}) returning \texttt{true} does not exceed $\gamma$.
% 
To capture this property, we let $\psi := X[1] \neq \cdots \neq X[n] \wedge \textsc{Main}(\epsilon,\gamma,X,n)$ and take the following query:
\begin{equation*}
  \forall \epsilon,\gamma,X,n~.~Enc_\psi \leq \gamma
\end{equation*}

\section{Implementation and Evaluation}
\label{sec:impl_and_eval}

\subsection{Implementation}
\label{sec:implementation}

We have implemented a prototype of our tool, \SYSTEM, on top of \textsc{KLEE}~\citep{cadar2008}, a robust symbolic execution engine.  \SYSTEM implements the \textit{probabilistic symbolic} execution algorithm as described in~\Cref{alg:symb_ex}. For the purpose of our implementation, we modify \textsc{KLEE} to support creation of \textit{probabilistic symbolic} variables as described in~\Cref{sec:pse_intro} whose values can be sampled from a distribution ($\delta$) by invoking \textsc{PSESample} as shown in the \textbf{\textit{sampling}} statement [\Cref{alg:symb_ex},~\Cref{line:pse_sampling}]. We use the  \textit{path constraints} ($\varphi$)  from the \textit{state} data-structure (maintained by \textsc{KLEE}) at each of the \textbf{\textit{assignment}} [\Cref{alg:symb_ex}, \Cref{line:pse_assignment}] and \textbf{\textit{branch}} [\Cref{alg:symb_ex}, \Cref{line:symbex_branch}] statements to get the final encodings $Enc_\psi$ and $Enc_a$.

For solving, \SYSTEM uses Z3~\citep{demoura2008}, a popular SMT solver, to either prove or refute our queries.
% 
Depending on the type of query, whether it be a probability bound query or an
expected value computation, we construct the query in the SMTLIB2~\citep{smtlib}.
% 
All the universal symbolic variables are then universally quantified in the query and $Enc_\psi$ is converted into the SMTLIB language.
% 
We then pass the converted query to Z3 which either verifies the query or generates a counterexample which disproves the claim.

\subsection{Evaluation}
\label{sec:eval}

To evaluate \SYSTEM, we answer the following questions:
%
\begin{itemize}
  \item \Q{1} How efficiently can \SYSTEM prove probabilistic properties on complex programs?
  \item \Q{2} How does the form of the query affect performance?
  \item \Q{3} How does the domain of the universal symbolic variables affect performance?
  \item \Q{4} Can~\SYSTEM find bugs in probabilistic programs?
\end{itemize}
%
To answer \Q{1}, we implement, or collect open-source implementations, for each of the case studies presented in~\Cref{sec:case_studies} in C++, run them on \SYSTEM, and record a variety of performance metrics, such as timing, number of paths explored, etc.
% 
We note that we used publicly available implementations for both of the data structures we present, namely Bloom Filter\footnote{\url{https://github.com/jvirkki/libbloom}} and Count-min Sketch\footnote{\url{https://github.com/alabid/countminsketch}} and adapted them to be analyzed by~\SYSTEM and to use our idealized hash functions as presented in~\Cref{sec:hash_function}.
% 
In certain cases, we ``concretize'' some input parameters, often the sizes of the input arrays, in order to constrain the paths explored by the symbolic execution engine.
% 
It was required in our setting, as contrary to most applications of symbolic execution that attempt to test the program, we attempt to \textit{verify} these examples in our evaluation.
% 
This necessitates exhaustive path enumeration within a reasonable time.
%
We selected our parameter settings (\cref{tab:q1}, last column) such that a complete path enumeration, and query verification, could be carried out within 10 minutes.
%
Note that when an array length is concretized, the array contents still remain symbolic. For example, for Quicksort, if the array length is concretized to 4, {\SYSTEM} searches over all possible arrays of size 4.
%
There is no conceptual obstacle to using our method without concretization if we are interested in bug-finding; {\SYSTEM} produces a sound lower-bound on exploring a subset of paths (see \cref{sec:query_gen}). However, implementation difficulties exist; for instance, there is currently limited support for running KLEE without concretizing array lengths.

To answer~\Q{2} and~\Q{3}, we analyze how changes to the query for Freivalds' Algorithm (\Cref{sec:freivalds}) affect performance.
% 
In general, these changes narrow the domain of possible assignments to the universal symbolic variables that Z3 must consider, thus allowing Z3 to arrive at a conclusion faster.
%
We also discuss how narrowing this space weakens the guarantees that~\SYSTEM can provide.
%

For~\Q{4}, we consider two types of bugs: implementation bugs where programmer errors result in the query being falsified, and specification bugs, where the specification is incorrect.
%
We find that we can effectively find, and address, both of these bugs using the results~\SYSTEM provides.

We conduct our experiments a machine equipped with an Intel Core i7-5820K running at 3.3 GHz and 32 GB of RAM running Arch Linux with kernel 5.12.14.
% 
For each experiment, we report the following metrics: the amount of time taken by \SYSTEM to explore the paths of the program and to generate the query, the amount of time Z3 takes to solve the query, the total amount of time taken, the number of lines in the C++ code, the number of paths \SYSTEM  explored, the number of random samples, and the maximum value ``concretized'' universal symbolic variables could take such that the query could be proven (or disproven) in the time allotted.

\paragraph*{\Q{1} Discussion.}
\begin{table}
  \centering
  \caption{Performance metrics for each of the case studies presented in~\Cref{sec:case_studies}.}
  \label{tab:q1}
  \begin{tabular}{@{}llllllll@{}}
    \toprule
    & \multicolumn{3}{c}{Timing (sec.)} &&\\ \cmidrule{2-4}
    \textbf{Case Study} & \textbf{KLEE} & \textbf{Z3} & \textbf{Total} & \textbf{Lines} & \textbf{Paths} & \textbf{Samples} & \textbf{Concretizations}\\ \midrule
    Freivalds' & 5 & 70 & \textbf{75} & 97 & 8 & 2 & $n=2$ \\
    Freivalds' (Multiple) & 44 & 255 & \textbf{299} & 96 & 8 & 21 & $(n, k) = (3, 7)$ \\
    % Randomized Response (Numer.) & 1.24 & 0.02 & 35 & 3 & 2 & --- \\
    % Randomized Response (Denom.) & 1.21 & 0.02 & 35 & 3 & 2 & --- \\
    Reservoir Sampling & 49 & 79 & \textbf{128} & 52 & 63 & 5 & $(n, k) = (10, 5)$ \\
    Monotone Testing & 4 & 352 & \textbf{356} & 69 & 30 & 1 & $n=23$ \\
    QuickSort & 95 & 489 & \textbf{584} & 65 & 120 & 10 & $n=5$ \\
    Bloom Filter & 256 & 231 & \textbf{487} & 386 & 83 & 8 & $(m, \epsilon) = (3, 0.4)$ \\
    Count-min Sketch & 108 & 206 & \textbf{314} & 245 & 2 & 8 & $(n, \epsilon, \gamma) = (4, 0.5, 0.25)$ \\

    % Freivalds' & 5.04 & 70.26 & \textbf{75.30} & 97 & 8 & 2 & $n=2$ \\
    % Freivalds' (Multiple) & 44.91 & 255.01 & \textbf{299.92} & 96 & 8 & 21 & $(n, k) = (3, 7)$ \\
    % % Randomized Response (Numer.) & 1.24 & 0.02 & 35 & 3 & 2 & --- \\
    % % Randomized Response (Denom.) & 1.21 & 0.02 & 35 & 3 & 2 & --- \\
    % Reservoir Sampling & 49.36 & 79.74 & \textbf{129.10} & 52 & 63 & 5 & $(n, k) = (10, 5)$ \\
    % Monotone Testing & 4.77 & 352.46 & \textbf{357.23} & 69 & 30 & 1 & $n=23$ \\
    % QuickSort & 95.15 & 489.09 & \textbf{584.24} & 65 & 120 & 10 & $n=5$ \\
    % Bloom Filter & 256.86 & 231.18 & \textbf{488.04} & 386 & 83 & 8 & $(m, \epsilon) = (3, 0.4)$ \\
    % Count-min Sketch & 108.11 & 206.21 & \textbf{314.32} & 245 & 2 & 8 & $(n, \epsilon, \gamma) = (4, 0.5, 0.25)$ \\
    % \begin{tabular}{@{}c@{}}$n=4,\epsilon=0.5$,\\$\gamma=0.25$\end{tabular}\\
    \bottomrule
  \end{tabular}
\end{table}
\Cref{tab:q1} summarizes our experimental results from running standard versions for each of the case studies presented in~\Cref{sec:case_studies}.
% 
All queries, except for the one for Bloom filter, which we will discuss later, were proven to be true within ten minutes.
%
As far as we know, \emph{none} of these examples can be verified by existing
automated tools; our method is the first to handle these examples fully
automatically.

We begin by making a few general observations.
% 
First, the presented examples showcase a range of path counts and number of random samples.
% 
For instance, even when we restricted the array to be of length 5, we still explored and reasoned over 120 paths and 10 probabilistic symbolic variables when analyzine QuickSort.
% 
Second, the time~\SYSTEM takes to execute~\Cref{alg:symb_ex} is usually much shorter than the time it takes for Z3 to solve the query; this suggests that constraint solving is the main bottleneck in our approach, not path exploration.

\paragraph*{\Q{2} Discussion.}
\begin{table}
  \centering
  \caption{Performance metrics of four different ways of specifying $A \times B \neq C$ in the query for Freivalds' Algorithm (\Cref{sec:freivalds}). Here, $n=2$ and all elements of the matrices are C++ \texttt{int}s.}
  \label{tab:q2}
  \begin{tabular}{@{}lllll@{}}
    \toprule
    & \multicolumn{3}{c}{Timing (sec.)} &\\ \cmidrule{2-4}
    \textbf{Spec. for $A \times B \neq C$} & \textbf{KLEE} & \textbf{Z3} & \textbf{Total} & \textbf{Paths}\\ \midrule
    \textsc{AllOff} & 2 & 1 & \textbf{3} & 2\\
    \textsc{SomeOff}& 5 & 70 & \textbf{75} & 8\\
    \textsc{FirstOff}& 1 & 5 & \textbf{6} & 2\\
    \textsc{OneOff} & 2 & 17 & \textbf{19} & 2\\
    \bottomrule
  \end{tabular}
\end{table}
To better understand~\SYSTEM's performance we consider how changes to the phrasing of the query for Freivalds' Algorithm affects performance.
% 
Recall that Freivalds' Algorithm efficiently determines whether $A \times B = C$, where $A,B$, and $C$ are $n \times n$ matrices; however, it has a false-positive error rate of at most $\frac{1}{2}$.
% 
In~\Cref{eq:freivalds} we set $\psi := A \times B \neq C \wedge \textsc{Freivalds}(A,B,C,n) = \mathtt{true}$ but did not state exactly how $A \times B$ must differ from $C$.

We consider four different ways of specifying that $A \times B \neq C$:
\begin{align}
  \textsc{AllOff} &= \bigwedge_{i=1}^n\bigwedge_{j=1}^n (A\times B)_{i,j} \neq C_{i,j}&
  \textsc{SomeOff} &= \bigvee_{i=1}^n\bigvee_{j=1}^n (A\times B)_{i,j} \neq C_{i,j}\label{eq:someoff}\\
  \textsc{FirstOff} &= (A\times B)_{0,0} \neq C_{0,0}\nonumber&
  \textsc{OneOff} &= \exists i,j~.~(A\times B)_{i,j} \neq C_{i,j}\nonumber
\end{align}
\textsc{AllOff} states that \textit{every} element of $A \times B$ must be different from the corresponding element in $C$, whereas \textsc{SomeOff} only states that \textit{at least one} element be deifferent between $A \times B$ and $C$. Similarly, \textsc{FirstOff} states that the first element of each matrix be different and \textsc{OneOff} states that \textit{an} element of $A \times B$ must differ from $C$. For \textsc{OneOff}, we represent $i$ and $j$ as universal symbolic variables and universally quantify them in~\Cref{eq:freivalds}.
% 
In all four cases, we only consider $2 \times 2$ matrices which contain C++ \texttt{int}s and present the performance results in~\Cref{tab:q2}.
%
We quickly note that~\SYSTEM explored eight paths for the \textsc{SomeOff} specifcation compared to the two paths for each of the other three variants.
%
Since specifications are written in the source program itself the complexity of said program can increase or decrease depending on the definition of $\psi$.
%
In the case of \textsc{SomeOff},~\SYSTEM explores more paths than the other variants as \textsc{SomeOff} is the only variant which does not provide a concrete number for the number of differing elements between the two matrices.

In general, the results in~\Cref{tab:q2} suggest that simpler and more specific settings of $\psi$ result in increased performance.
%
The strongest, and best performing specification was \textsc{AllOff}, whereas the most general, and the least performing specification was \textsc{SomeOff}.
% 
Additionally, \textsc{FirstOff} performed considerably better than \textsc{OneOff}, while being similar.
% 
Intuitively, this makes sense as \textsc{AllOff} drastically limits the amount of possible matrices that Z3 has to consider, whereas \textsc{SomeOff} requires Z3 to reason about \textit{all} matrices $A,B$, and $C$ such that $A \times B \neq C$.
%
The same reasoning can be applied to the relationship between \textsc{FirstOff} and \textsc{OneOff}; \textsc{OneOff} already considers whether \textsc{FirstOff} holds.
% 
Therefore, while performing the worst, \textsc{SomeOff} provides the strongest guarantee out of all the other variants, followed by \textsc{OneOff}, then \textsc{FirstOff}, and then finally, \textsc{AllOff}.

\paragraph*{\Q{3} Discussion.}
% \label{sec:eval_q3}

\begin{table}
  \centering
  \caption{Performance metrics for four different domains from which the elements of $A,B$, and $C$ are drawn from in the implementation for Freivalds' Algorithm (\Cref{sec:freivalds}). We only consider $2 \times 2$ matrices for each data type and use \textsc{SomeOff} (\Cref{eq:someoff}) to specify that $A \times B \neq C$. In each variant,~\SYSTEM explored 8 paths.}
  \label{tab:q3}
  \begin{tabular}{@{}llll@{}}
    \toprule
    & \multicolumn{3}{c}{Timing (sec.)}\\ \cmidrule{2-4}
    \textbf{Data Type} & \textbf{KLEE} & \textbf{Z3} & \textbf{Total}\\ \midrule
    \texttt{long int} & 11 & 1,589 & \textbf{1,600}\\
    \texttt{int} & 5 & 70 & \textbf{75}\\
    \texttt{short int} & 3 & 7 & \textbf{10}\\
    \texttt{char} & 2 & 1 & \textbf{3}\\
    \bottomrule
  \end{tabular}
\end{table}
%
We additionally consider how the size of the domain that Z3 has to reason over impacts performance.
%
This domain is primarily determined by the declared datatype of the C++ variables.
% 
We test four variants of Freivalds' Algorithm where we change the data type for the elements of the three matrices.
% 
For each data type, we restrict ourselves to $2 \times 2$ matrices and specify that $A \times B \neq C$ using \textsc{SomeOff} (\Cref{eq:someoff}).
% 
The performance results are presented in~\Cref{tab:q3}.
% 
On the evaluating machine, \texttt{long int}s are eight bytes, \texttt{int}s are four bytes, \texttt{short int}s are two bytes, and \texttt{char}s are a single byte.

As suspected, matrices containing \texttt{char}s performed the best, completing the verification in only 3.53 seconds whereas matrices containing \texttt{long int}s took over 26 minutes to complete.
% 
On the other hand, using \texttt{char}s provides the weakest guarantee whereas \texttt{long int}s provide the strongest.
% 
For many applications, however, analyzing variants of the program with smaller data types might provide sufficient proof of correctness, or already be able to surface bugs.

\paragraph*{\Q{4} Discussion}
%\label{sec:eval_q4}

We were able to find two bugs: one which we seeded in our implementation of Randomized Monotonicity Testing (\Cref{sec:monotone_testing}), and one which we found in our reference implementation of Bloom Filter (\Cref{sec:bloom_filter}).
% 
For randomized monotonicity testing, the source material which provides the
algorithm and guarantee~\citep{goldreich_2017} presents the algorithm using 1-based indexing.
% 
To mimic a common off-by-one error, we did not perform the proper translation during the initialization of $l$ on~\Cref{line:monotone_l} of~\Cref{alg:monotone_testing}.
% 
Specifically, we set $l \gets \lceil \log_2 n \rceil$ instead of $l \gets \lceil \log_2 (n-1) \rceil$, which is the proper 0-indexed value.
% 
This bug increased the probability that a function $f$ would be rejected by~\Cref{line:monotone_l}, and so made our queries fail.
% 
We found this bug setting $n = 4$.
% 
While this was a simple (yet common) off-by-one error, it is a prime example of both how subtle probabilistic reasoning can be and how potentially effective~\SYSTEM can be as not only a verification, but also a debugging tool.

The second error we found was in our reference Bloom filter implementation.
% 
If we set $m=3$, or the number of expected elements to be inserted into the Bloom filter, and $\epsilon = 0.4$, or the \textit{desired} false-positive rate,~\SYSTEM computes the actual false-positive rate to be $\approx45.03\%$.
% 
Upon closer inspection, we were able to conclude that because approximations must be used in order to compute the number of hash functions and the number of bits needed to achieve $\epsilon$, $\epsilon$ can only be a lower bound for the actual false-positive rate.
% 
This confirms an observation by~\citet{DBLP:journals/ipl/BoseGKMMMST08}, who showed that the commonly reported false-positive rate for the Bloom filter is slightly incorrect.

\input{related_work.tex}
\section{Conclusion and Future Directions}
\label{sec:conclusion}

We have presented a symbolic execution method for randomized programs, with
symbolic variables for modeling unknown inputs and random samples. Going
forward, we see two promising directions for further investigation.

\paragraph*{Optimizing probabilistic symbolic execution.}
In this work, we have made little effort to optimize our symbolic execution
method. One natural direction is to develop heuristics for exploring paths. It
would be interesting to apply techniques from the literature on path
prioritization in symbolic execution~\citep{bihuan_2016, p4wn_2021}, but perhaps there are other
heuristics in the probabilistic setting. For instance, since our method computes
path probabilities incrementally, perhaps paths with higher probability mass
should be explored first. Another possibility is to develop methods to simplify
the path probability expressons; while our method can compute them, the
expressions are rather complicated.

\paragraph*{Analyzing more complex probabilistic programs.}
We have evaluated our implementation on relatively standard randomized programs
so far, and both KLEE and Z3 support richer programs and hardware features. For
instance, Z3 has support for reasoning about floating-point arithmetic; perhaps
our symbolic execution method could also be used to validate randomized programs
that use floating-point computations. In another direction, recent work develops
an extension of KLEE that works on unbounded integers~\citep{kapus_2019}; it
could be interesting to see if this technique gives better performance or
stronger guarantees when verifying randomized algorithms, which often work with
mathematical integers.

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
	%% contents suppressed with 'anonymous'
	%% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
	%% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
	%% acknowledge financial support and will be used by metadata
	%% extraction tools.
	% This material is based upon work supported by the
	% \grantsponsor{GS100000001}{National Science
	% Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
	% No.~\grantnum{GS100000001}{nnnnnnn} and Grant
	% No.~\grantnum{GS100000001}{mmmmmmm}.  Any opinions, findings, and
	% conclusions or recommendations expressed in this material are those
	% of the author and do not necessarily reflect the views of the
	% National Science Foundation.
\end{acks}

%% Bibliography
\bibliography{header,main}
\end{document}

### 2021-09-04 draft/rebuttal/parts/detailed_responses.tex
Reviews

\section{Detailed Comments}

\subsection{Reviewer 1}

\subsection{Reviewer 2}

\subsection{Reviewer 3}

While you do state that you made little effort to optimize your symbolic
execution, the "optimization" direction of future work seems to convey that 
you believe it's just a matter of developing heuristics. While I whole-heartedly agree 
that a solid foundation, like the one presented, should be at the core of 
any reasonable symbolic executor, can you give any intuition as to why you 
expect your approach to scale, when the computation of path probabilities 
and solving them with Z3 seems to already dominate the execution time?

### 2021-09-04 draft/related_work.tex
Reviews

\section{Related Work}
\label{sec:related}

% In this section, we present our work in light of other closely related
% techniques that have been proposed for Probabilistic Symbolic Execution and also
% contrast on where our work differs.

\paragraph*{Probabilistic Symbolic Execution.}
\citet{geldenhuys_2012} was the first to propose a method for probabilistic
symbolic execution. Given a standard, non-probabilistic program, their
technique treats all inputs as drawn from a uniform distribution, and then
computes the probabilities of taking particular program paths by using model
counting. Later works build on this idea for different applications: analyzing
software reliability~\citep{filieri_2013, borges_2014}, quantifying software
changes~\citep{filieri_2015}, generating performance
distribution~\citep{bihuan_2016}, and evaluating worst-case input distributions
in network programs~\citep{p4wn_2021}. More sophisticated schemes apply
volume-bound computations instead of model counting, which is a performance
bottleneck~\citep{sankaranarayanan_2013,DBLP:journals/pacmpl/AlbarghouthiDDN17}.

These methods all focus on probabilistic programs where all the program inputs
are either known constants, or sampled from a known distribution (often the
uniform distribution). In contrast, our technique works for inputs that are
unknown values, and not drawn from a known distribution. Applying existing
methods for probabilistic symbolic execution to our setting would be
prohibitively expensive, since each possible input would need to be considered,
and input may range over a very large domain (e.g., integers ranging from
$-2^{63}$ to $2^{63}-1$).

\paragraph*{Symbolic inference in probabilistic programs.}
\emph{Probabilistic programming languages} are languages enriched with both
\emph{sampling} and \emph{conditioning} operations. The combination of these two
features allows a probabilistic program to encode a complex distribution; many
models of interest in machine learning can be implemented in this way. A recent
line of research considers how to perform \emph{inference} on such programs:
given an assertion $P$, what is the probability that $P$ holds in the
distribution described by the program? Researchers have considered a variety of
approaches, from weighted model counting~\citep{holtzen_2020}, to analyzing
Bayesian networks~\citep{sampson_2014}, to applying computer algebra
systems~\citep{claret_2013, psi_2016, lambda_psi_2020}.

Most existing work on probabilistic programming languages assumes that all
quantities in the program are drawn from known distributions---while we consider
a family of output distributions, probabilistic programming languages typically
consider a single distribution. It would be interesting to extend our work to
handle conditioning, but it would likely be quite challenging since conditioning
can transform our symbolic branch probabilities in highly complex ways.

\paragraph*{Other automated techniques for probabilistic programs.}
Automated verification of probabilistic programs is an active area of research.
We briefly survey some of the most relevant lines of work.

\textsc{AxProf}~\citep{axprof_2019} is a \emph{statistical testing} approach to
analyzing probabilistic programs, which runs the target program multiple times
on concrete inputs in order to estimate probabilities and expected values in the
output distribution. \textsc{AxProf} is highly efficient, and supports programs
with unknown inputs. However, it can only explore a small subset of the input
space and cannot provide logical guarantees over all possible inputs.

\emph{Probabilistic model checking} is a well-studied method for checking
logical formulas on probabilistic transition
systems~\citep{DBLP:conf/icalp/BaierCHKR97, DBLP:reference/mc/BaierAFK18,
kwiatkowska2011prism, dehnert_2017}. However, probabilistic model checking
targets finite state systems, and performance degrades rapidly as the number of
states grows. Our technique applies to infinite state systems; our examples,
which are finite state, are far too large to encode in existing model checking
tools.

\emph{Abstract interpretation} and \emph{algebraic program analysis} methods
have been developed for probabilistic programs~\citep{CousotM12,
DBLP:conf/pldi/WangHR18}. These methods abstract the probabilistic state, losing
information in exchange for better performance.  In contrast, our method
computes path probabilities exactly, in symbolic form.

Finally, there are many \emph{domain-specific} automated analysis for specific
probabilistic properties: termination and resource
analysis~\citep{Chatterjee:2016:AAQ:2837614.2837639, wang_2021,
DBLP:conf/esop/MoosbruggerBKK21}, accuracy~\citep{Chakarov-martingale, SHA18},
reliability~\citep{DBLP:conf/pldi/CarbinKMR12}, differential
privacy~\citep{DBLP:journals/pacmpl/BartheCKS021} and other relational
properties~\citep{AH17, AH18, DBLP:conf/esop/FarinaCG21}, and long-run
properties of probabilistic loops~\citep{DBLP:conf/atva/BartocciKS19,
DBLP:conf/tacas/BartocciKS20}. Our approach aims at a general-purpose analysis.

### 2021-09-04 draft/supplemental.tex
Reviews

--- 2021-09-04 draft/main.tex
@@
 We discuss related work in \cref{sec:related}, and future directions in
-\cref{sec:conclusion}. \emph{An extended version of the paper that includes all the detailed proofs (in the appendix) is provided as supplemental material.}
+\cref{sec:conclusion}.
 
@@
 
-We will now prove soundness for \Cref{alg:symb_ex} by showing that our abstraction $R$ respects the semantics defined in the supplemental material for each of the three main types of statements in \textbf{pWhile}, namely \textit{assignment}, \textit{sampling}, and \textit{branching}.
-A proof for each theorem can be found in the supplemental material.
+We will now prove soundness for \Cref{alg:symb_ex} by showing that our abstraction $R$ respects the semantics defined in \Cref{sec:semantics} for each of the three main types of statements in \textbf{pWhile}, namely \textit{assignment}, \textit{sampling}, and \textit{branching}.
+A proof for each theorem can be found in~\Cref{sec:omitted_proofs}.
 
 \begin{restatable}[Correctness of Assignment (\Crefrange{line:beg_raw_assign}{line:end_raw_assign})]{theorem}{soundnessAssignment}
-  If a distribution $\mu$ satisfies $R=(\varphi,\sigma,P)$, and~\Cref{alg:symb_ex} reaches an assignment statement of the form $\mathtt{x} \gets e$, then $\mu_{\mathtt{x}\gets e}$, the distribution of program memories after executing $\mathtt{x} \gets e$, as defined in the supplemental material, satisfies $R'=(\varphi,\sigma',P)$, which is produced by~\Cref{alg:symb_ex}.
+  If a distribution $\mu$ satisfies $R=(\varphi,\sigma,P)$, and~\Cref{alg:symb_ex} reaches an assignment statement of the form $\mathtt{x} \gets e$, then $\mu_{\mathtt{x}\gets e}$, the distribution of program memories after executing $\mathtt{x} \gets e$, as defined in~\Cref{sec:semantics},  satisfies $R'=(\varphi,\sigma',P)$, which is produced by~\Cref{alg:symb_ex}.
 \end{restatable}
@@
 \begin{restatable}[Correctness of Sampling (\Crefrange{line:pse_sym_sample}{line:end_raw_sample})]{theorem}{soundnessSampling}
-  If a distribution $\mu$ satisfies $R = (\varphi,\sigma,P)$ and~\Cref{alg:symb_ex} reaches a sampling statement of the form $\mathtt{x} \sim d$, then $\mu_{\mathtt{x} \sim d}$, the distribution of program memories after executing $\mathtt{x} \sim d$, as defined in the supplemental material, satisfies $R'=(\varphi,\sigma',P')$, which is produced by~\Cref{alg:symb_ex}.
+  If a distribution $\mu$ satisfies $R = (\varphi,\sigma,P)$ and~\Cref{alg:symb_ex} reaches a sampling statement of the form $\mathtt{x} \sim d$, then $\mu_{\mathtt{x} \sim d}$, the distribution of program memories after executing $\mathtt{x} \sim d$, as defined in~\Cref{sec:semantics}, satisfies $R'=(\varphi,\sigma',P')$, which is produced by~\Cref{alg:symb_ex}.
 \end{restatable}
@@
 \begin{restatable}[Correctness of Branching (\Cref{line:pse_sym_branch,line:symbex_true_state,line:symbex_false_state})]{theorem}{soundnessBranching}\label{thm:branch}
-  If a distribution $\mu$ satisfies $R=(\varphi,\sigma,P)$, and~\Cref{alg:symb_ex} encounters a branching statement of the form $\mathbf{if}~c~\mathbf{then~goto}~T$, then $\mu_c$ satisfies $R_{true} = (\varphi \wedge c_{sym}, \sigma, P)$ and $\mu_{\neg c}$, the distribution of program memories after executing $\mathbf{if}~c~\mathbf{then~goto}~T$, as defined in the supplemental material, satisfies $R_{false} = (\varphi \wedge \neg c_{sym}, \sigma, P)$.
+  If a distribution $\mu$ satisfies $R=(\varphi,\sigma,P)$, and~\Cref{alg:symb_ex} encounters a branching statement of the form $\mathbf{if}~c~\mathbf{then~goto}~T$, then $\mu_c$ satisfies $R_{true} = (\varphi \wedge c_{sym}, \sigma, P)$ and $\mu_{\neg c}$, the distribution of program memories after executing $\mathbf{if}~c~\mathbf{then~goto}~T$, as defined in~\Cref{sec:semantics}, satisfies $R_{false} = (\varphi \wedge \neg c_{sym}, \sigma, P)$.
 Additionally, for all $a_{\forall} \in \mathit{A}_{\forall}$,
@@
 \paragraph*{\Q{1} Discussion.}
+% \label{sec:eval_q1}
+
 \begin{table}
@@
 \paragraph*{\Q{2} Discussion.}
+% \label{sec:eval_q2}
+
 \begin{table}
@@
 \bibliography{header,main}
+
+%% Appendix
+\appendix
+\allowdisplaybreaks
+
+\section{Program Semantics}
+\label{sec:semantics}
+Here we define the semantics for the three main types of statements which concerns probabilistic symbolic execution: assignments, probabilistic sampling, and branching.
+
+\begin{definition}[Assignment Semantics]
+  \label{def:assignment}
+  Let $\mu \in \mathit{Dists_M}$ be a distribution of program memories parameterized by assignments to universal symbolic variables.
+Let $\mathtt{x} \gets e$ be an arbitrary assignment statement where $\mathtt{x} \in \mathcal{X}$ is assigned to the program expression $e$.
+Let $\mathsf{assign}_{\mathtt{x}\gets e} : \mathit{M} \rightarrow \mathit{M}$ is defined as
+  \[
+    \mathsf{assign}_{\mathtt{x}\gets e}(m) = \lambda(\mathtt{y} : \mathcal{X})
+    \begin{cases}
+      \deno{e}m     & \text{if $\mathtt{x} = \mathtt{y}$} \\
+      m(\mathtt{y}) & \text{otherwise}
+    \end{cases}
+  \]
+  and let $\mathsf{unassign}_{\mathtt{x}\gets e} = \mathsf{assign}_{\mathtt{x}\gets e}^{-1}$.
+Define $\mu_{\mathtt{x}\gets e}$ to be the distribution over program memories parameterized by assignments to universal symbolic variables after executing the assignment statement $\mathtt{x}\gets e$ to be
+  \[
+    \mu_{\mathtt{x}\gets e}(a_{\forall},m) = \sum_{m' \in \mathsf{unassign}_{\mathtt{x}\gets e}(m)} \mu(a_{\forall},m').
+  \]
+\end{definition}
+
+\begin{definition}[Sampling Semantics]
+  \label{def:sampling}
+  Let $\mu \in \mathit{Dists_M}$ be a distribution of program memories parameterized by assignments to universal symbolic variables.
+Let $\mathtt{x} \sim d$ be an arbitrary sampling instruction which assigns the program variable $\mathtt{x} \in \mathcal{X}$ to a random element from the distribution of values parameterized by a memory, represented as a distribution expression $d \in \mathit{Dists}$.
+Let $\mathsf{desample} : \mathcal{X} \times \mathit{M} \rightarrow \mathcal{P}(\mathit{M})$ be defined as
+  \[
+    \mathsf{desample}(\mathtt{x},m) = \{ m'\in \mathit{M} \mid \forall (\mathtt{y} \in \mathcal{X})~.~(\mathtt{y} \neq \mathtt{x} \wedge m'(\mathtt{y}) = m(\mathtt{y}))\}.
+  \]
+  Define $\mu_{\mathtt{x} \sim d}$ to be the distribution over program memories parameterized by assignments to universal symbolic variables after executing the sampling statement $\mathtt{x} \sim d$ to be
+  \[
+    \mu_{\mathtt{x} \sim d}(a_{\forall},m) = \sum_{m' \in \mathsf{desample}(m)} (\deno{d}a_{\forall})(m(\mathtt{x})) \cdot \mu(a_{\forall},m').
+  \]
+\end{definition}
+
+\begin{definition}[Branching Semantics]
+  \label{def:branching}
+  Let $a_{\forall} \in \mathit{A}_{\forall}$ be an arbitrary assignment of universal symbolic variables, $c$ be a guard of an \textbf{if-goto} statement, $\mu \in \mathit{Dists_M}$ be a distribution of program memories parameterized by assignments to universal symbolic variables, and $\mathtt{x}_1,\ldots,\mathtt{x}_n \in \mathcal{X}$ be all the program variables in $c$.
+Then for all program memories $m \in \mathit{M}$, $\mu$ conditioned on a guard $c$ being true, represented as $\mu_c$ is defined as
+  \[
+    \mu_c(a_{\forall},m) = \frac{\displaystyle\Pr_{m' \sim \mu(a_{\forall})}\left[ m' = m \land \deno{c}m' = \mathtt{true} \right]}{\displaystyle\Pr_{m' \sim \mu(a_{\forall})}\left[ \deno{c}m' = \mathtt{true} \right]}
+  \]
+  Similarly, for all program memories $m \in \mathit{M}$, $\mu$ conditioned on a guard $c$ being false, represented as $\mu_{\neg c}$ is defined as
+  \[
+    \mu_{\neg c}(a_{\forall},m) = \frac{\displaystyle\Pr_{m' \sim \mu(a_{\forall})}\left[ m' = m \land \deno{c}m' = \mathtt{false} \right]}{\displaystyle\Pr_{m' \sim \mu(a_{\forall})}\left[ \deno{c}m' = \mathtt{false} \right]}
+  \]
+\end{definition}
+
+\section{Omitted Proofs}
+\label{sec:omitted_proofs}
+\equivpthm*
+\begin{proof}
+  Let $S$ be an arbitrary \textbf{pWhile} program statement, $\varphi$ be the current path condition, $P$ be the current distribution map, and $p$ be the current path probability before executing $S$.
+  % 
+  Assume that
+  \[
+    p = \frac{\displaystyle\sum_{v_1,\ldots,v_n \in \mathcal{D}} [ \varphi\{\delta_1 \mapsto v_1, \ldots, \delta_n \mapsto v_n\} ]}{\abs{\mathcal{D}}}.
+  \]
+  We will proceed with a case analysis on $S$:
+  \begin{itemize}
+  \item \textit{Assignment (\Crefrange{line:beg_raw_assign}{line:end_raw_assign})}.
+Suppose $S$ is an assignment statement of the form $\mathtt{x} \gets e$, where \texttt{x} is an arbitrary program variable and $e$ is an arbitrary program expression.
+    % 
+    Note that $\varphi$, $P$, and $p$ do not change after executing $\mathtt{x} \gets e$ and so the statement trivially holds.
+  \item \textit{Sampling (\Crefrange{line:pse_sym_sample}{line:end_raw_sample})}.
+Suppose $S$ is a sampling statement of the form $\mathtt{x} \sim d$, where \texttt{x} is an arbitrary program variable and $d$ is an arbitrary distribution expression.
+    % 
+    Additionally assume that there are $n$ probabilistic symbolic variables in $P$, namely $\delta_1,\ldots,\delta_n$, and $\delta_{n+1}$ is the fresh probabilistic symbolic variable created on \cref{line:fresh_psv} in \Cref{alg:sample}.
+    % 
+    Then, $P_1 = P \cup \{\delta_{n+1} \mapsto d\}$, according to \cref{line:update_P} where $P_1$ is the updated distribution map returned by \textbf{PSESample} on \cref{line:pse_sym_sample}.
+    % 
+    If $\mathcal{D}_1 = \dom{P_1[\delta_1]} \times \cdots \times \dom{P_1[\delta_{n+1}]}$, then
+    \begin{align*}
+      \frac{\displaystyle\sum_{v_1,\ldots,v_{n+1} \in \mathcal{D}_1} [ \varphi\{\delta_1 \mapsto v_1, \ldots, \delta_{n+1} \mapsto v_{n+1}\}]}{\abs{\mathcal{D}_1}} &= \frac{\abs{\dom{P_1[\delta_{n+1}]}} \cdot \displaystyle\sum_{v_1,\ldots,v_{n} \in \mathcal{D}} [ \varphi\{\delta_1 \mapsto v_1, \ldots, \delta_{n} \mapsto v_{n}\}]}{\abs{\mathcal{D}_1}} \\
+                                                                                                                         &= \frac{\abs{\dom{P_1[\delta_{n+1}]}} \cdot \displaystyle\sum_{v_1,\ldots,v_{n} \in \mathcal{D}} [ \varphi\{\delta_1 \mapsto v_1, \ldots, \delta_{n} \mapsto v_{n}\}]}{\abs{\dom{P_1[\delta_{n+1}]}} \cdot \abs{\mathcal{D}}} \\
+                                                                                                                         &= \frac{\displaystyle\sum_{v_1,\ldots,v_{n} \in \mathcal{D}} [ \varphi\{\delta_1 \mapsto v_1, \ldots, \delta_{n} \mapsto v_{n}\}]}{\abs{\mathcal{D}}} \\
+                                                                                                                         &= p
+    \end{align*}
+    where the first line follows from the fact that $\delta_{n+1}$ cannot appear in $\varphi$ as $\delta_{n+1}$ is a \textit{fresh} probabilistic symbolic variable.
+  \item \textit{Branching (\Cref{line:pse_sym_branch,line:symbex_true_state,line:symbex_false_state})}.
+Suppose $S$ is a branching statement of the form $\mathbf{if}~c~\mathbf{then~goto}~T$ where $c$ is an arbitrary program guard.
+    % 
+    Additionally assume that there are $n$ probabilistic symbolic variables in $P$, namely $\delta_1,\ldots,\delta_n$.
+    % 
+    Then, according to \cref{line:branch_prob_compute} of \Cref{alg:branch},
+    \[
+      p_c = \frac{\displaystyle\sum_{(v_1,\ldots,v_n) \in \mathcal{D}} [(c_{sym} \wedge \varphi)\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]}{\displaystyle\sum_{(v_1,\ldots,v_n) \in \mathcal{D}}[\varphi\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]}
+    \]
+    and so $p_t = p_c$ and $p_f = 1-p_c$.
+    % 
+    If $p'_t = p \cdot p_t$ and $p'_f = p \cdot p_f$, as on lines \cref{line:symbex_true_state,line:symbex_false_state}, and $\varphi'_t = \varphi \wedge c_{sym}$ and $\varphi'_f = \varphi \wedge \neg c_{sym}$, then we claim that
+    \[
+      p'_t = \frac{\displaystyle\sum_{v_1,\ldots,v_n \in \mathcal{D}} [ \varphi'_t\{\delta_1 \mapsto v_1, \ldots, \delta_n \mapsto v_n\} ]}{\abs{\mathcal{D}}}
+    \]
+    and similarly
+    \[
+      p'_f = \frac{\displaystyle\sum_{v_1,\ldots,v_n \in \mathcal{D}} [ \varphi'_f\{\delta_1 \mapsto v_1, \ldots, \delta_n \mapsto v_n\} ]}{\abs{\mathcal{D}}}.
+    \]
+
+    We will prove the claim for $p'_t$ as the proof for $p'_f$ is symmetric.
+    % 
+    Note that,
+    \begin{align*}
+      p'_t &= p \cdot p_t \\
+           &= \frac{\displaystyle\sum_{v_1,\ldots,v_n \in \mathcal{D}} [ \varphi\{\delta_1 \mapsto v_1, \ldots, \delta_n \mapsto v_n\} ]}{\abs{\mathcal{D}}} \cdot \frac{\displaystyle\sum_{(v_1,\ldots,v_n) \in \mathcal{D}} [(c_{sym} \wedge \varphi)\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]}{\displaystyle\sum_{(v_1,\ldots,v_n) \in \mathcal{D}}[\varphi\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]} \\
+           &= \frac{\displaystyle\sum_{(v_1,\ldots,v_n) \in \mathcal{D}} [(c_{sym} \wedge \varphi)\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]}{\abs{\mathcal{D}}}\\
+           &= \frac{\displaystyle\sum_{(v_1,\ldots,v_n) \in \mathcal{D}} [\varphi'_t\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]}{\abs{\mathcal{D}}}
+    \end{align*}
+  \end{itemize}
+  Since no state changes if $S$ is a \textbf{halt} statement, the theorem is trivially true for this case.
+\end{proof}
+
+\soundnessAssignment*
+\begin{proof}
+  First assume that $\mu$ satisfies the input abstraction $R=(\varphi,\sigma,P)$. Note that by~\Cref{def:assignment},
+  \[
+    \mu_{\mathtt{x}\gets e}(a_{\forall},m) = \displaystyle\sum_{m' \in \mathsf{unassign}_{\mathtt{x}\gets e}(m)} \mu(a_{\forall},m')
+  \]
+  for all $a_{\forall} \in \mathit{A}_{\forall}$ and $m \in \mathit{M}$. Also note that by~\Cref{def:main},
+  \[
+    \mu(a_{\forall},m) = \displaystyle\sum_{a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m)} \nu_{\varphi}(a_{\forall},a_p).
+  \]
+  So,
+  \begin{align*}
+    \mu_{\mathtt{x}\gets e}(a_{\forall},m) &= \sum_{m' \in \mathsf{unassign}_{\mathtt{x}\gets e}(m)} \mu(a_{\forall},m')\\
+                                           &= \sum_{m' \in \mathsf{unassign}_{\mathtt{x}\gets e}(m)} \sum_{a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m')} \nu_{\varphi}(a_{\forall},a_p).
+  \end{align*}
+
+  Thus, in order to satisfy~\Cref{def:main} it suffices to show that
+  \[
+    \sum_{a_p \in \mathsf{fromMem}(\sigma',a_{\forall},m)} \nu_{\varphi}(a_{\forall},a_p) = \sum_{m' \in \mathsf{unassign}_{\mathtt{x}\gets e}(m)} \sum_{a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m')} \nu_{\varphi}(a_{\forall},a_p).
+  \]
+
+  Note that if $m_1,m_2 \in \mathit{M}$ where $m_1 \neq m_2$, then for all $a_{\forall} \in \mathit{A}_{\forall}$ and $\sigma$, $\mathsf{fromMem}(\sigma,a_{\forall},m_1)$ and $\mathsf{fromMem}(\sigma,a_{\forall},m_2)$ are disjoint.
+Hence, it suffices to show that
+  \[
+    \mathsf{fromMem}(\sigma',a_{\forall},m) = \bigcup_{m' \in \mathsf{unassign}_{\mathtt{x}\gets e}(m)} \mathsf{fromMem}(\sigma,a_{\forall},m').
+  \]
+  to prove the theorem. We will show this through double containment.
+
+  First, let $a_p \in \bigcup_{m' \in \mathsf{unassign}_{\mathtt{x}\gets e}(m)} \mathsf{fromMem}(\sigma,a_{\forall},m')$ be arbitrary.
+This means that for some $m' \in \mathsf{unassign}_{\mathtt{x}\gets e}(m)$, $m' = \lambda (\mathtt{y} : \mathcal{X}) .
+\deno{\sigma(\mathtt{y})}a_{\forall}a_p$.
+Furthermore, since $m' \in \mathsf{unassign}_{\mathtt{x}\gets e}(m)$,
+  \[
+    m = \lambda (\mathtt{y} : \mathcal{X})
+    \begin{cases}
+      \deno{e}m' & \text{if $\mathtt{x}=\mathtt{y}$}\\
+      m'(\mathtt{y}) & \text{otherwise}
+    \end{cases}
+  \]
+  Note that we need to show that $a_p \in \mathsf{fromMem}(\sigma',a_{\forall},m)$.
+This is equivalent to showing that $m =\mathsf{toMem}(\sigma',a_{\forall},a_p)$.
+Thus, it is sufficient to prove that
+  \[
+    \lambda (\mathtt{y} : \mathcal{X}) . \deno{\sigma'(\mathtt{y})}a_{\forall}a_p = \lambda (\mathtt{y} : \mathcal{X})
+    \begin{cases}
+      \deno{e}m' & \text{if $\mathtt{x}=\mathtt{y}$}\\
+      m'(\mathtt{y}) & \text{otherwise}
+    \end{cases}.
+  \]
+  Note that the domains of each of these functions are equal, namely the set of all program variables present within the program.
+Now we need to show that for every $\mathtt{z} \in \mathcal{X}$, the two functions compute the same result.
+We have two cases:
+  \begin{enumerate}
+  \item \textbf{Case 1:} Assume that $\mathtt{z} = \mathtt{x}$.
+Then we have to show that $\deno{e}m' = \deno{\sigma'(\mathtt{x})}a_{\forall}a_p$.
+However, note that by~\Crefrange{line:beg_raw_assign}{line:end_raw_assign}, $\sigma'(\mathtt{x}) = e_{sym}$.
+Recall that $m' = \lambda (\mathtt{y} : \mathcal{X}) .
+\deno{\sigma(x)}a_{\forall}a_p$.
+If $\mathtt{x}_1,\ldots,\mathtt{x}_k \in \mathcal{X}$ are all the program variables present, then
+    \begin{align*}
+      \deno{e}m' &= \mathsf{eval}(e[\mathtt{x}_1 \mapsto \deno{\sigma(\mathtt{x}_1)}a_{\forall}a_p, \ldots, \mathtt{x}_k \mapsto \deno{\sigma(\mathtt{x}_k)}a_{\forall}a_p])
+    \end{align*}
+    However, note that $e_{sym} = e[\mathtt{x}_1 \mapsto \sigma(\mathtt{x}_1),\ldots,\mathtt{x}_k \mapsto \sigma(\mathtt{x}_k)]$ and so,
+    \begin{align*}
+      \deno{e_{sym}}a_{\forall}a_p &= \deno{e[\mathtt{x}_1 \mapsto \sigma(\mathtt{x}_1),\ldots,\mathtt{x}_k \mapsto \sigma(\mathtt{x}_k)]}a_{\forall}a_p\\
+                             &= \mathsf{eval}(e[\mathtt{x}_1 \mapsto \deno{\sigma(\mathtt{x}_1)}a_{\forall}a_p, \ldots, \mathtt{x}_k \mapsto \deno{\sigma(\mathtt{x}_k)}a_{\forall}a_p]).
+    \end{align*}
+    Hence, $\deno{e}m' = \deno{\sigma'(\mathtt{x})}a_{\forall}a_p$.
+  \item \textbf{Case 2:} Now assume that $\mathtt{z} \neq \mathtt{x}$.
+We claim that $m'(\mathtt{z}) = \deno{\sigma'(\mathtt{z})}a_{\forall}a_p$.
+Note that $m'(\mathtt{z}) = \deno{\sigma(\mathtt{z})}a_{\forall}a_p$.
+Since $\mathtt{z}\neq\mathtt{x}$, then $\sigma(\mathtt{z}) = \sigma'(\mathtt{z})$ and we are done.
+  \end{enumerate}
+  Therefore,
+  \[
+    \lambda (\mathtt{y} : \mathcal{X}) . \deno{\sigma'(\mathtt{y})}a_{\forall}a_p = \lambda (\mathtt{y} : \mathcal{X})
+    \begin{cases}
+      \deno{e}m' & \text{if $\mathtt{x}=\mathtt{y}$}\\
+      m'(\mathtt{y}) & \text{otherwise}
+    \end{cases}
+  \] and so $a_p \in \mathsf{fromMem}(\sigma',a_{\forall},m)$.
+
+  For the forward direction of the double containment, assume that $a_p \in \mathsf{fromMem}(\sigma',a_{\forall},m)$ be arbitrary.
+This implies that $m = \mathsf{toMem}(\sigma',a_{\forall},a_p) = \lambda (\mathtt{y} : \mathcal{X}) .
+\deno{\sigma'(\mathtt{y})}a_{\forall}a_p$.
+We need to show that $a_p \in  \bigcup_{m' \in \mathsf{unassign}_{\mathtt{x}\gets e}(m)} \mathsf{fromMem}(\sigma,a_{\forall},m')$ which is equivalent to showing that for some $m'$, $a_p = \mathsf{fromMem}(\sigma,a_{\forall},m')$.
+We claim that $m' = \lambda (\mathtt{y} : \mathcal{X}) .
+\deno{\sigma(\mathtt{y})}a_{\forall}a_p \in \mathsf{unassign}_{\mathtt{x}\gets e}(m)$.
+We can prove this by showing that $\mathsf{assign}_{\mathtt{x}\gets e}(m') = m$.
+Note that
+  \[
+    \mathsf{assign}_{\mathtt{x}\gets e}(m') = \lambda (\mathtt{y} : \mathcal{X}) .
+    \begin{cases}
+      \deno{e}m' & \text{if $\mathtt{x} = \mathtt{y}$}\\
+      m'(\mathtt{y}) & \text{otherwise}
+    \end{cases}
+  \]
+  Both functions have the same domain, namely the program variables present in the program.
+We will show that both functions give the same output on the arbitrary input $\mathtt{z} \in \mathcal{X}$.
+There are two cases:
+  \begin{enumerate}
+  \item \textbf{Case 1:} Assume that $\mathtt{z} = \mathtt{x}$. Then, we need to show $\deno{e}m' = \deno{\sigma'(\mathtt{y})}a_{\forall}a_p$.
+    However, note that by~\Crefrange{line:beg_raw_assign}{line:end_raw_assign}, $\sigma'(\mathtt{x}) = e_{sym}$.
+Recall that $m' = \lambda (\mathtt{y} : \mathcal{X}) .
+\deno{\sigma(x)}a_{\forall}a_p$.
+If $\mathtt{x}_1,\ldots,\mathtt{x}_k \in \mathcal{X}$ are all the program variables present, then $\deno{e}m' = \mathsf{eval}(e[\mathtt{x}_1 \mapsto \deno{\sigma(\mathtt{x}_1)}a_{\forall}a_p, \ldots, \mathtt{x}_k \mapsto \deno{\sigma(\mathtt{x}_k)}a_{\forall}a_p])$.
+    However, note that $e_{sym} = e[\mathtt{x}_1 \mapsto \sigma(\mathtt{x}_1),\ldots,\mathtt{x}_k \mapsto \sigma(\mathtt{x}_k)]$.
+    and so,
+    \begin{align*}
+      \deno{e_{sym}}a_{\forall}a_p &= \deno{e[\mathtt{x}_1 \mapsto \sigma(\mathtt{x}_1),\ldots,\mathtt{x}_k \mapsto \sigma(\mathtt{x}_k)]}a_{\forall}a_p\\
+                             &= \mathsf{eval}(e[\mathtt{x}_1 \mapsto \deno{\sigma(\mathtt{x}_1)}a_{\forall}a_p, \ldots, \mathtt{x}_k \mapsto \deno{\sigma(\mathtt{x}_k)}a_{\forall}a_p]).
+    \end{align*}
+    Hence, $\deno{e}m' = \deno{\sigma'(\mathtt{x})}a_{\forall}a_p$.
+  \item \textbf{Case 2:} Now assume that $\mathtt{z} \neq \mathtt{x}$.
+Then we have to show that $m'(\mathtt{z}) = \deno{\sigma'(\mathtt{z})}a_{\forall}a_p$.
+Since $m'(\mathtt{z}) = \deno{\sigma(\mathtt{z})}a_{\forall}a_p$ and $\mathtt{z}\neq\mathtt{x}$, then $\sigma(\mathtt{z}) = \sigma'(\mathtt{z})$ and we are done.
+  \end{enumerate}
+  Therefore, $m' \in \mathsf{unassign}_{\mathtt{x}\gets e}(m)$.
+Since $m' = \mathsf{toMem}(\sigma,a_{\forall},a_p)$, we have that $a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m')$ which implies that $a_p \in  \bigcup_{m' \in \mathsf{unassign}_{\mathtt{x}\gets e}(m)} \mathsf{fromMem}(\sigma,a_{\forall},m')$.
+By double containment,
+  \[
+    \mathsf{fromMem}(\sigma',a_{\forall},m) = \bigcup_{m' \in \mathsf{unassign}_{\mathtt{x}\gets e}(m)} \mathsf{fromMem}(\sigma,a_{\forall},m')
+  \]
+  and so
+  \[
+    \mu_{\mathtt{x}\gets e}(a_{\forall},m) = \sum_{a_p \in \mathsf{fromMem}(\sigma',a_{\forall},m)} \nu_{\varphi}(a_{\forall},a_p).
+  \]
+  Since $\nu_{\varphi}$ is unchanged, $\mu_{\mathtt{x}\gets e}$ satisfies $(\varphi,\sigma',P)$.
+\end{proof}
+
+\soundnessSampling*
+\begin{proof}
+  First assume that $\mu$ satisfies the input abstraction $R = (\varphi,\sigma,P)$.
+We want to show that $\mu_{\mathtt{x} \sim d}$ satisfies the output abstraction $(\varphi,\sigma',P')$.
+To do this, we need to define $\nu'$ and $\nu_{\varphi}'$ in terms of $\sigma'$ and $P'$ and show that $\nu_{\varphi}$ satisfies~\Cref{def:main}.
+Let $\delta_{k+1}$ be the fresh probabilistic symbolic variable allocated on~\cref{line:fresh_psv} of~\Cref{alg:sample}.
+
+  Note according to~\Cref{def:main},
+  \[
+    \nu'(a_{\forall},a_p) = \prod_{i=1}^{k+1} \Pr_{v \sim P'(a_{\forall},\delta_i)}[v = a_p(\delta_i)].
+  \]
+
+  However, we want
+  \[
+    \nu(a_{\forall},a_p) = \prod_{i=1}^{k} \Pr_{v \sim P(a_{\forall},\delta_i)}[v = a_p(\delta_i)]
+  \]
+  by definition. Since for all $1 \leq i \leq k$, $P(\delta_i) = P'(\delta_i)$,
+  \begin{align*}
+    \nu'(a_{\forall},a_p) &= \prod_{i=1}^{k+1} \Pr_{v \sim P'(a_{\forall},\delta_i)}[v = a_p(\delta_i)]\\
+                  &= \left( \prod_{i=1}^{k} \Pr_{v \sim P'(a_{\forall},\delta_i)}[v = a_p(\delta_i)] \right) \cdot \Pr_{v \sim P'(a_{\forall},\delta_{k+1})}[v = a_p(\delta_{k+1})] \\
+                  &= \left( \prod_{i=1}^{k} \Pr_{v \sim P(a_{\forall},\delta_i)}[v = a_p(\delta_i)] \right) \cdot \Pr_{v \sim P'(a_{\forall},\delta_{k+1})}[v = a_p(\delta_{k+1})] 
+  \end{align*}
+  Note that the domain of $\nu$ is $\{\delta_1,\ldots,\delta_k\}$. So, if we let $a_p = a_p' \cup \{\delta_{k+1} \mapsto v\}$ where $v \in \mathcal{V}$ is arbitrary,
+  \[
+    \left( \prod_{i=1}^{k} \Pr_{v \sim P(a_{\forall},\delta_i)}[v = a_p(\delta_i)] \right) \cdot \Pr_{v \sim P'(a_{\forall},\delta_{k+1})}[v = a_p(\delta_{k+1})] = \nu(a_{\forall},a_p') \cdot \Pr_{v' \sim P'(a_{\forall},\delta_{k+1})}[v' = v]
+  \]
+  By definition
+  \[
+    \Pr_{v' \sim P'(a_{\forall},\delta_{k+1})}[v' = v] = \sum_{v' \in \{v' \in \mathcal{V} \mid v' = v\}} P'(a_{\forall},\delta_{k+1})(v') = P'(a_{\forall},\delta_{k+1})(v).
+  \]
+  According to \textsc{PSESample} on \cref{line:update_P}, $P'(a_{\forall},\delta_{k+1}) = \deno{d} a_{\forall}$, which is a distribution of values. Thus,
+  \[
+    \nu'(a_{\forall},a_p) = (a_p' \cup \{\delta_{k+1} \mapsto v) = \nu(a_{\forall},a_p') \cdot (\deno{d} a_{\forall})(v).
+  \]
+
+  Now, we can define $\nu_{\varphi}'$ as
+  \[
+    \nu_{\varphi}' = \frac{\Pr_{a_p' \sim \nu'(a_{\forall})}[a_p' = a_p \wedge \varphi(a_{\forall},a_p') = 1]}{\Pr_{a_p' \sim \nu'(a_{\forall})}[\varphi(a_{\forall},a_p') = 1]}.
+  \]
+
+  Before moving onto the main result, we will prove a lemma.
+  \begin{lemma}
+    \label{lem:split}
+    For all $a_{\forall} \in \mathit{A}_{\forall}, a_p \in \mathit{A}_p$ where the domain of $a_p$ is $\{\delta_1,\ldots,\delta_k\}$ and $\delta_{k+1} \in \mathcal{Z}_P$ is a newly allocated probabilistic symbolic variable created by~\Cref{alg:sample}.
+Also let $v \in \mathcal{V}$ be arbitrary.
+Then,
+    \[
+      \nu_{\varphi}'(a_{\forall},a_p \cup \{\delta_{k+1} \mapsto v\}) = \nu_{\varphi}(a_{\forall},a_p) \cdot (\deno{d} a_{\forall})(v).
+    \]
+  \end{lemma}
+  \begin{proof}
+    Let $a = a_p \cup \{\delta_{k+1} \mapsto v\}$. By definition,
+    \begin{align*}
+      \nu_{\varphi}'(a_{\forall}, a) = \frac{\Pr_{a_p' \sim \nu'(a_{\forall})}[a_p' = a \wedge \varphi(a_{\forall},a_p') = 1]}{\Pr_{a_p' \sim \nu'(a_{\forall})}[\varphi(a_{\forall},a_p') = 1]}
+      &= \frac{\displaystyle \smashoperator[r]{\sum_{a_p' \in \{a_p' \in \mathit{A}_p \mid a_p' = a \wedge \varphi(a_{\forall},a_p') = 1\}}} \nu'_{\mathtt{x}\sim d}(a_{\forall},a_p')}{\displaystyle \smashoperator[r]{\sum_{a_p' \in \{a_p' \in \mathit{A}_p \mid \varphi(a_{\forall},a_p') = 1\}}} \nu'_{\mathtt{x}\sim d}(a_{\forall},a_p')}\\
+      &= \frac{\displaystyle \smashoperator[r]{\sum_{a_p' \in \{a_p' \in \mathit{A}_p \mid a_p' = a \wedge \varphi(a_{\forall},a_p') = 1\}}} \nu(a_{\forall},a_p)\cdot(\deno{d}a_{\forall})(v)}{\displaystyle \smashoperator[r]{\sum_{a_p' \cup \{\delta_{k+1} \mapsto v'\} \in \{a_p' \in \mathit{A}_p \mid \varphi(a_{\forall},a_p') = 1\}}} \nu(a_{\forall},a_p')\cdot(\deno{d}a_{\forall})(v')}
+    \end{align*}
+    Note that the set being summed over in the numerator is $\{a_p' \in \mathit{A}_p \mid a_p' = a \wedge \varphi(a_{\forall},a_p') = 1\} = \{a\}$ as $\varphi$ does not reference $\delta_{k+1}$ so, as long as $\varphi(a_{\forall},a_p)=1$, $\varphi(a_{\forall},a)=1$.
+Therefore, we can remove the summation to get:
+    \[
+      \frac{\displaystyle \smashoperator[r]{\sum_{a_p' \in \{a_p' \in \mathit{A}_p \mid a_p' = a \wedge \varphi(a_{\forall},a_p') = 1\}}} \nu(a_{\forall},a_p)\cdot(\deno{d}a_{\forall})(v)}{\displaystyle \smashoperator[r]{\sum_{a_p' \cup \{\delta_{k+1} \mapsto v'\} \in \{a_p' \in \mathit{A}_p \mid \varphi(a_{\forall},a_p') = 1\}}}\nu(a_{\forall},a_p')\cdot(\deno{d}a_{\forall})(v')} = \frac{\nu(a_{\forall},a_p)\cdot(\deno{d}a_{\forall})(v)}{\displaystyle \smashoperator[r]{\sum_{a_p' \cup \{\delta_{k+1} \mapsto v'\} \in \{a_p'' \in \mathit{A}_p \mid \varphi(a_{\forall},a_p'') = 1\}}}\nu(a_{\forall},a_p')\cdot(\deno{d}a_{\forall})(v')}.
+    \]
+    Now, $\{a_p' \in \mathit{A}_p \mid \varphi(a_{\forall},a_p') = 1\}$ is the set of all probabilistic assignments which satisfy the path condition $\varphi$ with the assignment to universal symbolic variables, $a_{\forall}$.
+Since $\delta_{k+1}$ does not appear in $\varphi$, whatever value $a_p'$ assigns to $\delta_{k+1}$ will not affect whether $\varphi$ is satisfied.
+Therefore, for each value $v'$ in the domain of $\deno{d}a_{\forall}$, $a_p' \cup \{\delta_{k+1} = v'\} \in \{a_p'' \in \mathit{A}_p \mid \varphi(a_{\forall},a_p'') = 1\}$, where $a_p' \in \mathit{A}_p$ is some probabilistic assignment such that $\varphi(a_{\forall},a_p')=1$.
+Hence,
+    \[
+      \smashoperator[r]{\sum_{a_p' \cup \{\delta_{k+1} \mapsto v'\} \in \{a_p'' \in \mathit{A}_p \mid \varphi(a_{\forall},a_p'') = 1\}}} \nu(a_{\forall},a_p')\cdot(\deno{d}a_{\forall})(v')= \smashoperator[r]{\sum_{a_p' \cup \{\delta_{k+1} \mapsto v'\} \in \{a_p'' \in \mathit{A}_p \mid \varphi(a_{\forall},a_p'') = 1\}}} \nu(a_{\forall},a_p').
+    \]
+    Combining this all together, we have
+    \begin{align*}
+      \nu_{\varphi}'(a_{\forall}, a) &= \frac{\nu(a_{\forall},a_p)\cdot(\deno{d}a_{\forall})(v)}{\displaystyle \smashoperator[r]{\sum_{a_p' \cup \{\delta_{k+1} \mapsto v'\} \in \{a_p'' \in \mathit{A}_p \mid \varphi(a_{\forall},a_p'') = 1\}}}\nu(a_{\forall},a_p')\cdot(\deno{d}a_{\forall})(v')} = \frac{\nu(a_{\forall},a_p)\cdot(\deno{d}a_{\forall})(v)}{\displaystyle \smashoperator[r]{\sum_{a_p' \in \{a_p' \in \mathit{A}_p \mid \varphi(a_{\forall},a_p') = 1\}}} \nu(a_{\forall},a_p')}\\
+                       &= (\deno{d}a_{\forall})(v) \cdot \frac{\displaystyle \smashoperator[r]{\sum_{a_p' \in \{a_p' \in \mathit{A}_p \mid a_p' = a_p \wedge \varphi(a_{\forall},a_p') = 1\}}}\nu(a_{\forall},a_p' )}{\displaystyle \smashoperator[r]{\sum_{a_p' \in \{a_p' \in \mathit{A}_p \mid \varphi(a_{\forall},a_p') = 1\}}} \nu(a_{\forall},a_p')}
+                         = (\deno{d}a_{\forall})(v) \cdot \frac{\displaystyle\Pr_{a_p' \sim \nu(a_{\forall})}[a_p' = a_p \wedge \varphi(a_{\forall},a_p') = 1]}{\displaystyle\Pr_{a_p' \sim \nu(a_{\forall})}[\varphi(a_{\forall},a_p') = 1]}\\
+                       &= (\deno{d}a_{\forall})(v) \cdot \nu_{\varphi}(a_{\forall},a_p)
+    \end{align*}
+  \end{proof}
+  We can now prove that $R'$ satisfies~\Cref{def:main}. Note that by~\Cref{def:sampling}, 
+  \[
+    \mu_{\mathtt{x} \sim d}(a_{\forall},m) = \sum_{m' \in \mathsf{desample}(m)} (\deno{d}a_{\forall})(m(\mathtt{x})) \cdot \mu(a_{\forall},m').
+  \]
+  for all $a_{\forall} \in \mathit{A}_{\forall}$ and $m \in \mathit{M}$. Also, by~\Cref{def:main},
+  \[
+    \mu(a_{\forall},m) = \sum_{a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m)} \nu_{\varphi}(a_{\forall},a_p).
+  \]
+  and so,
+  \begin{align*}
+    \mu_{\mathtt{x} \sim d} &= \sum_{m' \in \mathsf{desample}(m)} (\deno{d}a_{\forall})(m(\mathtt{x})) \cdot \mu(a_{\forall},m')\\
+                            &= \sum_{m' \in \mathsf{desample}(m)} (\deno{d}a_{\forall})(m(\mathtt{x})) \cdot \left( \sum_{a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m')} \nu_{\varphi}(a_{\forall},a_p) \right)\\
+                            &= \sum_{m' \in \mathsf{desample}(m)} \sum_{a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m')} (\deno{d}a_{\forall})(m(\mathtt{x})) \cdot \nu_{\varphi}(a_{\forall},a_p).
+  \end{align*}
+  Now it suffices to show the following:
+  \begin{enumerate}
+  \item For all $a_{\forall}\in \mathit{A}_{\forall}$ and $a_p \in \mathit{A}_p$,
+    \[
+      \nu_{\varphi}''(a_{\forall},a_p) = (\deno{d}a_{\forall})(v) \cdot \nu_{\varphi}(a_{\forall},a_p')
+    \]
+    where $\nu_{\varphi}''$ is defined as in~\Cref{def:main} but with $R'$ and $a_p = a_p' \cup \{\delta_{k+1} \mapsto v\}$. This immediately follows from~\Cref{lem:split}.
+  \item Note that if $m_1,m_2 \in \mathit{M}$ where $m_1\neq m_2$ then for all $a_{\forall} \in \mathit{A}_{\forall}$ and $\sigma$, $\mathsf{fromMem}(\sigma,a_{\forall},m_1)$ and $\mathsf{fromMem}(\sigma,a_{\forall},m_2)$ are disjoint.
+Thus, it suffices to show that
+    \[
+      \mathsf{fromMem}(\sigma',a_{\forall},m) = \bigcup_{m' \in \mathsf{desample}(m)} \mathsf{fromMem}(\sigma,a_{\forall},m').
+    \]
+  \end{enumerate}
+  For (2), we will show this through double containment. First, let $a_p \in \mathsf{fromMem}(\sigma',a_{\forall},m)$ be arbitrary. By definition,
+  $m = \mathsf{toMem}(\sigma',a_{\forall},a_p) = \lambda (\mathtt{y} : \mathcal{X}) .
+\deno{\sigma'(\mathtt{y})}a_{\forall}a_p$.
+Since $\sigma'(\mathtt{x}) = \delta_{k+1}$, where $\delta_{k+1}$ is a fresh probabilistic symbolic variable.
+Therefore, $a_p(\delta_{k+1}) = m(\mathtt{x})$.
+We need to show that $a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m')$ for some $m' \in \mathsf{desample}(m)$.
+Note that $m \in \mathsf{desample}(m)$.
+Furthermore, for every program variable $\mathtt{y} \in \mathcal{X}$, $\delta_{k+1}$ does not appear in $\sigma(\mathtt{y})$.
+Therefore, $a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m)$ as
+  \[
+    \mathsf{fromMem}(\sigma,a_{\forall},m) = \{ a_p' \in \mathit{A}_p \mid \forall (\mathtt{y} : \mathcal{X})~.~(\mathtt{y} \neq \mathtt{x} \wedge a_p'(\mathtt{y}) = a_p(\mathtt{y}))\}.
+  \]
+  Since $a_p$ was arbitrary, we have proven the forward direction of the containment.
+
+  Now, let $a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m')$ for some $m' \in \mathsf{desample}(m)$.
+Since for all $\mathtt{y} \in \mathcal{X}$, $\delta_{k+1}$ does not appear in $\sigma(\mathtt{y})$, $a_p(\delta_{k+1})$ can be any value.
+To prove the reverse containment, it suffices to show that $m = \mathsf{toMem}(\sigma',a_{\forall},a_p)$.
+Note that for every $a_p' \in \mathit{A}_p$ where $n = \mathsf{toMem}(\sigma',a_{\forall},a_p')$, $n(\mathtt{x}) = a_p'(\delta_{k+1})$.
+Furthermore, for every $\mathtt{y} \in \mathcal{X}$ where $\mathtt{y} \neq \mathtt{x}$, $m(\mathtt{y}) = m'(\mathtt{y})$ and $\sigma'(\mathtt{y}) = \sigma(\mathtt{y})$.
+This implies that $\mathsf{toMem}(\sigma,a_{\forall},a_p)(\mathtt{y}) = m'(\mathtt{y}) = m(\mathtt{y}) = \mathsf{toMem}(\sigma',a_{\forall},a_p)$.
+
+  Without loss of generality, assume that $m(\mathtt{x}) = z$.
+Since $a_p(\mathtt{x})$ can be any value, let this particular value be $z$.
+Thus, $m(\mathtt{x}) = a_p(\delta_{k+1})$.
+Therefore, $m = \mathsf{toMem}(\sigma',a_{\forall},a_p)$ for all program variables.
+This completes the double containment.
+\end{proof}
+
+\soundnessBranching*
+Before proving~\Cref{thm:branch}, we will prove a lemma.
+\begin{lemma}
+  \label{lem:condition}
+  Let $a_{\forall} \in \mathit{A}_{\forall}$ and $a_p \in \mathit{A}_p$ be arbitrary. Then,
+  \[
+    \nu_{\varphi}(a_{\forall},a_p) = \Pr_{a_p' \sim \nu(a_{\forall})}[ a_p' = a_p \mid \varphi(a_{\forall},a_p') = 1 \mid \deno{c_{sym}} a_{\forall} a_p'= 1 ]
+  \]
+  and
+  \[
+    \nu_{\varphi}^{\neg}(a_{\forall},a_p) = \Pr_{a_p' \sim \nu(a_{\forall})}[ a_p' = a_p \mid \varphi(a_{\forall},a_p') = 1 \mid \deno{c_{sym}} a_{\forall} a_p' = 0 ].
+  \]
+\end{lemma}
+
+\begin{proof}
+  Let $a_{\forall} \in \mathit{A}_{\forall}$ and $a_p \in \mathit{A}_p$ be arbitrary. Consider the quantity
+  \[
+    \Pr_{a_p' \sim \nu(a_{\forall})}[ a_p' = a_p \mid \varphi(a_{\forall},a_p') = 1 \mid \deno{c_{sym}} a_{\forall} a_p'= 1 ].
+  \]
+  By definition of conditional probability,
+  \begin{align*}
+    \Pr_{a_p' \sim \nu(a_{\forall})}[ a_p' = a_p &\mid \varphi(a_{\forall},a_p') = 1 \mid \deno{c_{sym}} a_{\forall} a_p'= 1 ]\\&= \frac{\displaystyle\Pr_{a_p' \sim \nu(a_{\forall})}[a_p' = a_p \wedge \varphi(a_{\forall},a_p') = 1 \mid \deno{c_{sym}} a_{\forall} a_p' = 1 ]}{\displaystyle\Pr_{a_p' \sim \nu(a_{\forall})}[\varphi(a_{\forall},a_p') = 1 \mid \deno{c_{sym}} a_{\forall} a_p' = 1]} \\
+                                                                                           &= \frac{\frac{\displaystyle\Pr_{a_p' \sim \nu(a_{\forall})}[a_p' = a_p \wedge \varphi(a_{\forall},a_p') = 1 \wedge \deno{c_{sym}} a_{\forall} a_p' = 1 ]}{\displaystyle\Pr_{a_p' \sim \nu(a_{\forall})}[ \deno{c_{sym}} a_{\forall} a_p' = 1]}}{\frac{\displaystyle\Pr_{a_p' \sim \nu(a_{\forall})}[\varphi(a_{\forall},a_p') = 1 \wedge \deno{c_{sym}} a_{\forall} a_p' = 1 ]}{\displaystyle\Pr_{a_p' \sim \nu(a_{\forall})}[ \deno{c_{sym}} a_{\forall} a_p' = 1]}} \\
+                                                                                           &= \frac{\displaystyle\Pr_{a_p' \sim \nu(a_{\forall})}[a_p' = a_p \wedge \varphi(a_{\forall},a_p') = 1 \wedge \deno{c_{sym}} a_{\forall} a_p' = 1 ]}{\displaystyle\Pr_{a_p' \sim \nu(a_{\forall})}[\varphi(a_{\forall},a_p') = 1 \wedge \deno{c_{sym}} a_{\forall} a_p' = 1 ]} \\
+                                                                                           &= \nu_{\varphi}(a_{\forall},a_p).
+  \end{align*}
+  The proof of the second quantity, $\nu_{\varphi}^{\neg}$, follows identically as above.
+\end{proof}
+Now we can prove~\Cref{thm:branch}.
+\begin{proof}
+  First assume that $\mu$ satisfies the input abstraction $R=(\varphi,\sigma,P)$.
+Note that by definition, for all program memories $m \in \mathit{M}$, and assignments to universal symbolic variables $a_{\forall} \in \mathit{A}_{\forall}$,
+  \[
+    \mu_c(a_{\forall},m) = \frac{\displaystyle\Pr_{m' \sim \mu(a_{\forall})}\left[ m' = m \land \deno{c}m' = 1 \right]}{\displaystyle\Pr_{m' \sim \mu(a_{\forall})}\left[ \deno{c}m' = 1 \right]}\quad\text{and}\quad \mu_{\neg c}(a_{\forall},m) = \frac{\displaystyle\Pr_{m' \sim \mu(a_{\forall})}\left[ m' = m \land \deno{c}m' = 0 \right]}{\displaystyle\Pr_{m' \sim \mu(a_{\forall})}\left[ \deno{c}m' = 0 \right]}.
+  \]
+  Also note that by definition, $\mu(a_{\forall},m) = \sum_{a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m)} \nu_{\varphi}(a_{\forall},a_p)$. Combining together, we get,
+  \begin{align*}
+    \mu_c(a_{\forall},m) &= \frac{\displaystyle\Pr_{m' \sim \mu(a_{\forall})}\left[ m' = m \land \deno{c}m' = 1 \right]}{\displaystyle\Pr_{m' \sim \mu(a_{\forall})}\left[ \deno{c}m' = 1 \right]} \\
+                 &= \frac{\displaystyle\sum_{m' \in \{m' \in \mathit{M} \mid m' = m \wedge \deno{c}m' = 1\}}\mu(a_{\forall},m')}{\displaystyle\sum_{m' \in \{m' \in \mathit{M} \mid \deno{c}m' = 1\}}\mu(a_{\forall},m')}\\
+                 &= \frac{\displaystyle\sum_{m' \in \{m' \in \mathit{M} \mid m' = m \wedge \deno{c}m' = 1\}}\sum_{a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m')} \nu_{\varphi}(a_{\forall},a_p)}{\displaystyle\sum_{m' \in \{m' \in \mathit{M} \mid \deno{c}m' = 1\}}\sum_{a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m')} \nu_{\varphi}(a_{\forall},a_p)}\\
+                 &= \frac{\displaystyle\sum_{m' \in \{m' \in \mathit{M} \mid m' = m \wedge \deno{c}m' = 1\}}\sum_{a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m')} \frac{\displaystyle\Pr_{a_p' \sim \nu(a_{\forall})}[a_p' = a_p \wedge \varphi(a_{\forall},a_p')=1]}{\displaystyle\Pr_{a_p' \sim \nu(a_{\forall})}[\varphi(a_{\forall},a_p')=1]}}{\displaystyle\sum_{m' \in \{m' \in \mathit{M} \mid \deno{c}m' = 1\}}\sum_{a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m')} \frac{\displaystyle\Pr_{a_p' \sim \nu(a_{\forall})}[a_p' = a_p \wedge \varphi(a_{\forall},a_p')=1]}{\displaystyle\Pr_{a_p' \sim \nu(a_{\forall})}[\varphi(a_{\forall},a_p')=1]}}\\
+                 &= \frac{\displaystyle\sum_{m' \in \{m' \in \mathit{M} \mid m' = m \wedge \deno{c}m' = 1\}}\sum_{a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m')} \Pr_{a_p' \sim \nu(a_{\forall})}[a_p' = a_p \wedge \varphi(a_{\forall},a_p')=1]}{\displaystyle\sum_{m' \in \{m' \in \mathit{M} \mid \deno{c}m' = 1\}}\sum_{a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m')} \Pr_{a_p' \sim \nu(a_{\forall})}[a_p' = a_p \wedge \varphi(a_{\forall},a_p')=1]}
+  \end{align*}
+  Now consider the denominator of the above expression.
+The left-most summation is collecting all the memories which satisfy the guard, $c$.
+From these memories, an associated assignment to probabilistic variables is created using $\sigma$.
+Since $c_{sym} = \deno{c} \sigma$, it must be that $\deno{c_{sym}} a_{\forall} a_p = 1$.
+Therefore, the denominator is simply computing $\Pr_{a_p \sim \nu(a_{\forall})}[\varphi(a_{\forall},a_p) = 1 \wedge \deno{c_{sym}} a_{\forall} a_p = 1]$.
+As for the numerator, we can apply a similar argument to conclude that\begin{multline*}
+    \sum_{m' \in \{m' \in \mathit{M} \mid m' = m \wedge \deno{c}m' = 1\}}\sum_{a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m')} \Pr_{a_p' \sim \nu(a_{\forall})}[a_p' = a_p \wedge \varphi(a_{\forall},a_p')=1] \\= \sum_{a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m)}\Pr_{a_p' \sim \nu(a_{\forall})}[a_p' = a_p \wedge \varphi(a_{\forall},a_p') = 1 \wedge \deno{c_{sym}} a_{\forall} a_p' = 1].
+  \end{multline*}
+  Thus, we have
+  \begin{equation*}
+    \begin{split}
+      &\frac{\displaystyle\sum_{m' \in \{m' \in \mathit{M} \mid m' = m \wedge \deno{c}m' = 1\}}\sum_{a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m')} \Pr_{a_p' \sim \nu(a_{\forall})}[a_p' = a_p \wedge \varphi(a_{\forall},a_p')=1]}{\displaystyle\sum_{m' \in \{m' \in \mathit{M} \mid \deno{c}m' = 1\}}\sum_{a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m')} \Pr_{a_p' \sim \nu(a_{\forall})}[a_p' = a_p \wedge \varphi(a_{\forall},a_p')=1]}\\
+      &= \sum_{a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m)}\frac{\displaystyle\Pr_{a_p' \sim \nu(a_{\forall})}[a_p' = a_p \wedge \varphi(a_{\forall},a_p') = 1 \wedge \deno{c_{sym}} a_{\forall} a_p' = 1]}{\displaystyle\Pr_{a_p' \sim \nu(a_{\forall})}[\varphi(a_{\forall},a_p') = 1 \wedge \deno{c_{sym}} a_{\forall} a_p' = 1]}\\
+      &= \sum_{a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m)} \nu_{\varphi}(a_{\forall},a_p)
+    \end{split}
+  \end{equation*}
+  We have thus proven condition 2 for $\mu_c$. An symmetric argument would apply to $\mu_{\neg c}$. Therefore, $\mu_c$ satisfies $R_{true}$ and $\mu_{\neg c}$ satisfies $R_{false}$.
+
+  We will now prove the added condition that for all $a_{\forall} \in \mathit{A}_{\forall}$, 
+  \[
+    \sum_{m \in \{m \in \mathit{M} \mid \deno{c}m = 1\}}\mu(a_{\forall},m) = \deno{p_c} a_{\forall}
+  \]
+  and
+  \[
+    \sum_{m \in \{m \in \mathit{M} \mid \deno{c}m = 0\}}\mu(a_{\forall},m) = \deno{p_c'} a_{\forall}.
+  \]
+
+  Consider the left-hand side of the proposed equality. By~\Cref{def:main},
+  \begin{align*}
+    \sum_{m \in \{m \in \mathit{M} \mid \deno{c}m = 1\}}\mu(a_{\forall},m) &= \sum_{m \in \{m \in \mathit{M} \mid \deno{c}m = 1\}} \sum_{a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m)} \nu_{\varphi}(a_{\forall},a_p)\\
+                                                         &= \sum_{m \in \{m \in \mathit{M} \mid \deno{c}m = 1\}} \sum_{a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m)} \Pr_{a_p' \sim \nu(a_{\forall})}[a_p' = a_p \mid \varphi(a_{\forall},a_p') = 1]
+  \end{align*}
+  Note that by~\Cref{line:guard_convert} of~\Cref{alg:symb_ex}, $c_{sym} = \deno{c} \sigma$.
+Note that for every $a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m)$, $m = \lambda(\mathtt{x} : \mathcal{X}) .
+\deno{\sigma(\mathtt{x})} a_{\forall} a_p$.
+Therefore, since $\deno{c} m = 1$, and $\deno{c} (\lambda(\mathtt{x} : \mathcal{X}) .
+\deno{\sigma(\mathtt{x})} a_{\forall} a_p) = \deno{c_{sym}} a_{\forall} a_p$,
+  then $\deno{c_{sym}} a_{\forall} a_p = 1$. Hence,
+  \begin{multline*}
+    \sum_{m \in \{m \in \mathit{M} \mid \deno{c}m = 1\}} \sum_{a_p \in \mathsf{fromMem}(\sigma,a_{\forall},m)} \Pr_{a_p' \sim \nu(a_{\forall})}[a_p' = a_p \mid \varphi(a_{\forall},a_p') = 1]\\
+    = \Pr_{a_p \sim \nu(a_{\forall})}[\deno{c_{sym}} a_{\forall} a_p \mid \varphi(a_{\forall},a_p') = 1].
+  \end{multline*}
+  Now, using standard transformations, we have
+  \begin{align*}
+    \Pr_{a_p \sim \nu(a_{\forall})}[\deno{c_{sym}} a_{\forall} a_p \mid \varphi(a_{\forall},a_p') = 1] &= \frac{\Pr_{a_p \sim \nu(a_{\forall})}[\deno{c_{sym}} a_{\forall} a_p = 1 \wedge \varphi(a_{\forall},a_p) = 1]}{\Pr_{a_p \sim \nu(a_{\forall})}[\varphi(a_{\forall},a_p) = 1]}\\
+                                                                       &= \frac{\sum_{a_p \in \{a_p \mid \deno{c_{sym}} a_{\forall} a_p = 1 \wedge \varphi(a_{\forall},a_p) = 1\}}\nu(a_{\forall},a_p)}{\sum_{a_p \in \{a_p \mid \varphi(a_{\forall},a_p) = 1\}}\nu(a_{\forall},a_p)}\\
+                                                                       &= \frac{\sum_{a_p \in \{a_p \mid \deno{c_{sym}} a_{\forall} a_p = 1 \wedge \varphi(a_{\forall},a_p) = 1\}}\nu(a_{\forall},a_p)}{\sum_{a_p \in \{a_p \mid \varphi(a_{\forall},a_p) = 1\}}\nu(a_{\forall},a_p)}
+  \end{align*}
+  Now consider the right-hand side of the proposed equality. By Algorithm~\ref{alg:branch},
+  \[
+    p_c = \frac{\displaystyle\sum_{(v_1,\ldots,v_n) \in \mathrm{domain}(D_1) \times \cdots\times \mathrm{domain}(D_n)} [(c_{sym} \wedge \varphi)\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]}{\displaystyle\sum_{(v_1,\ldots,v_n) \in \mathrm{domain}(D_1) \times \cdots\times \mathrm{domain}(D_n)}[\varphi\{\delta_1 \mapsto v_1,\ldots,\delta_n \mapsto v_n\}]}.
+  \]
+  Note that the substitution of the probabilistic symbolic variables $\delta_1,\ldots,\delta_n$, along with the assignment of universal symbolic variables, $a_{\forall}$, represents an assignment of probabilistic symbolic variables, $a_p$.
+Therefore,
+  \[
+    \frac{\sum_{a_p \in \{a_p \mid \deno{c_{sym}} a_{\forall} a_p = 1 \wedge \varphi(a_{\forall},a_p) = 1\}}\nu(a_{\forall},a_p)}{\sum_{a_p \in \{a_p \mid \varphi(a_{\forall},a_p) = 1\}}\nu(a_{\forall},a_p)} = \deno{p_c} a_{\forall}.
+  \]
+  Thus,
+  \[
+    \sum_{m \in \{m \in \mathit{M} \mid \deno{c}m = 1\}}\mu(a_{\forall},m) = \deno{p_c} a_{\forall}.
+  \]
+  A symmetric argument as above can be applied to the equality
+  \[
+    \sum_{m \in \{m \in \mathit{M} \mid \deno{c}m = 0\}}\mu(a_{\forall},m) = \deno{p_{c}'} a_{\forall}.
+  \]
+\end{proof}
 \end{document}

### 2021-09-04 draft/rebuttal/montyhall.c

@@ -1,0 +1,29 @@
+int monty_hall(int choice, bool door_switch) { |\label{line:monty_beg}|
+  int car_door = uniform_int(1,3);
+  int host_door;
+  if (choice == car_door) |\label{line:monty_choice_!=_car}|
+    return !door_switch; |\label{line:monty_not_switch}|
+  if (choice != 1 && car_door != 1) |\label{line:monty_choice_!=_1}|
+    host_door = 1;
+  else if (choice != 2 && car_door != 2) |\label{line:monty_choice_!=_2}|
+    host_door = 2;
+	else |\label{line:monty_choice_==_3}|
+		host_door = 3;
+	if (door_switch) |\label{line:monty_switch}|
+    if (host_door == 1)  |\label{line:monty_host_==_1}|
+      if (choice == 2) |\label{line:monty_choice_==_2}|
+				choice = 3;
+			else 
+				choice = 2;
+    else if (host_door == 2) |\label{line:monty_host_==_2}|
+      if (choice == 1) |\label{line:monty_choice_==_1}|
+				choice = 3;
+			else 
+				choice = 1;
+    else |\label{line:monty_host_==_3}|
+			if (choice == 1) |\label{line:monty_choice_==_1_2}|
+				choice = 2;
+			else 
+				choice = 1;
+  return choice == car_door;
+}

### 2021-09-07 paper/parts/experiments.tex
Examples

\section{Experimental Evalutaion}
\label{sec:experiments}

\sumit{What experiments and examples to work on?}
\sumit{In 4 pages}

\begin{itemize}
	\item (RQ1) Experiments
	\item (RQ2) Additional Examples
\end{itemize}

### 2021-09-09 draft/rebuttal.md
Changes

We thank the reviewers for their thoughtful comments.

Our paper proposes a symbolic execution method for randomized programs, which
can verify the correctness of programs on all possible inputs. As far as we are
aware, no prior automated method is able to analyze our case studies, which are
all randomized programs with unknown inputs. Our KLEE-based prototype
implementation works on LLVM bytecode, enabling us to analyze real-world
programs, rather than idealized mathematical models.

# Unknown inputs, comparison with PPLs (Reviewers A and C)

We emphasize that we are considering a different setting than probabilistic
programming languages (PPLs). In PPLs, inputs are described by some known
distribution and programs encode a *single* distribution. In our setting, inputs
are universally quantified and not drawn from a distribution, and programs
represent a *family* of output distributions, one for each possible input. We
verify properties of the entire family of distributions, while PPLs to reason
about a single distribution. None of the approaches mentioned on
L1171---including Hakaru---can handle universally quantified inputs, like our
approach does.

Reviewer C points out that our method does not handle conditioning operations,
which are common in PPLs. This is correct, but our targets---executable
randomized programs---do not make use of conditioning, because it is not
computationally tractable.

# Exhaustive search (Reviewer A)

We do not expect exhaustive search to scale beyond what we have shown, but even
with this method, we were able to verify complex programs beyond the reach of
prior work. Additionally, even with our relatively small concretizations, we
could find subtle bugs (Section 5.2).

For programs that are too large to allow for full path exploration, our method
can prove lower-bounds on the probability of some predicate $\Psi$ being
satisfied by exploring a subset of the paths (L535).

# Language of symbolic formula (Reviewer A)

Formulas use the binary operator "+" to create a single expression. While the
reviewer is correct that these expressions can be quite large, this encoding
seems tractable for programs that don't have long sequences of sampling
instructions, like our case studies. We will be more explicit about the form of
these symbolic formulae; exploring compact encodings of sums is future work.

# Model checking (Reviewers A & B)

We could not compare our work with model checkers as we are not aware of any
existing tools that can handle our examples:

1) Probabilistic model checkers work with probabilistic automata, but our
imperative programs lead to automata with enormous state spaces. It is also not
trivial to faithfully model details of our machine model.
2) We universally quantify over inputs, rather than fixing inputs to be specific
constants. We are not aware of any probabilistic model checker that has direct
support for this kind of system.
3) One indirect way to leverage existing tools would be to encode programs as
MDPs, with a non-deterministic choice over all possible inputs.  However, we are
not aware of tools that can handle such a wide non-deterministic choice.

# Similarity to traditional symbolic execution (Reviewer B)

Our method is an extension of symbolic execution, but one that we believe seems
obvious only in retrospect. Building firmly on symbolic execution is a strength,
as it allows us to adapt existing symbolic execution methods (e.g., KLEE).

# Potential optimizations (Reviewer C)

We are optimistic about improving scalability (via optimizations like state merging~[Kuznetsov et al. PLDI'12] and better encodings of sums as formulas), but we do not make any concrete
claims at this time. We keep optimizations as future work.

### 2021-09-09 draft/rebuttal.txt
Changes

POPL 2022 Paper #575 Reviews and Comments
===========================================================================
Paper #575 Symbolic Execution for Randomized Programs

Review #575A
===========================================================================

Overall merit
-------------
B. Weak Accept

Reviewer expertise
------------------
X. Expert

Paper summary
-------------
This paper shows that symbolic execution, which turns a program into a stream of execution paths paired with symbolic conditions on them, can be extended to probabilistic programs and used to verify and disprove bounds on discrete probabilities. The paper describes the probabilistic symbolic execution algorithm. The authors have implemented the algorithm on top of KLEE. The paper evaluates the implementation by applying it to concrete instances of several practically relevant properties of interesting probabilistic programs.

Strengths
---------
To my knowledge, this is the first time symbolic reasoning has been applied to probabilistic programs written in (or compiled to) a language as general-purpose and popular as LLVM. Unlike so-called "lightweight" inference methods, which run the program in a controlled environment, symbolic reasoning can handle (even universally quantify over) unknown inputs.

Weaknesses
----------
The paper is coy about the language of symbolic formulas generated by probabilistic symbolic execution and shipped off to an SMT solver. The size and form of this formula can greatly affect the efficacy of SMT solving, so reproducing the results in this paper depends on details about p in Algorithm 1 -- details as small as the $\cdot$ denoting symbolic multiplication on lines 27-28. In Algorithm 3 in particular, does line 4 assign to $p_c$ an expression that contains two summation _loops_, or do the $\sum$s indicate that the algorithm loops over values $v_1,\ldots,v_n$ to build large expressions that contain the binary operator $+$? Here "large" means enumerating the entire probability space!

The paper should be more helpful in contrasting the present work with related work.
- It is clear that "inputs that are unknown values" and "not drawn from a known distribution" are key distinctions of the present work, but the paper only presents the uniform distribution (L420), and does not say what is hard about, or how to deal with, unknown distributions. As for unknown inputs, the word "Most" (L1174, in contrast to "all", L1160) needs to come with details about the complement of "most".
- The "variety of approaches" (L1171) to probabilistic program inference is very large. It is inaccurate to describe Claret et al. 2013 as applying computer algebra systems, and even Gehr et al. roll their own computer algebra instead of applying an existing system. Which of these approaches and systems, if any, handle unknown inputs? Hakaru does [Carette & Shan 2016, Walia et al. 2019].
- Model checking's answer to large or infinite state spaces is abstraction. Without discussing abstraction and without empirical evaluation, it is not clear that "our examples...are far too large to encode in existing model checking tools" (L1191). It is also unclear that "our technique applies to infinite state systems", without worked-out examples and without details about SMT solving.
- It is unclear why conditioning would be "challenging" to handle (L1178). Why not just conjoin the predicate $\psi$ with the condition?

Comments for author
-------------------
On page 4, $=$ is used both in the metalanguage (to equate expressions) and in the object language (to equate numbers, like $\ne$ is used). This is confusing, especially on L150 and L187. Two different symbols should be used (perhaps `==` and `!=` in the object language), and parentheses should be used to clarify precedence.

L188-189 "this tree ... it does": But this single tree for car_door=1 does not tell us that "it is possible to win the car with any choice of initial door and decision to switch", because if (for example) the choice of initial door is 1 and the decision is to switch, then the car is not won. It takes multiple trees, one for each car_door value, to tell us that "it is possible ...".

L190-191 "how likely it was to take one branch over another": But in a tree where car_door is specified, there is no notion of "likely", so this sentence doesn't make sense.

L194 "universal symbolic variables": add "such as $\alpha$ and $\beta$"

L213 "from...from": superfluous repetition

L260 "jumps execution to statement T": I was expecting jumps to target labels, not statements. How are loops expressed in pWhile?

L267, L271: Given the explanation of $\mu$ on L268, it doesn't make sense for Prog as a function to take $\psi$ as second input, even if Algorithm 1 takes $\psi$ as input.

Algorithm 1:
- Line 2 and line 7 both bind $\sigma$, which is confusing as to whether there are two variables or one.
- On line 4, shouldn't the first $\emptyset$ be $\sigma$ instead?
- On line 7, $P,p$ should be shaded.
- Is it a problem that Algorithm 1 might not terminate when Prog contains a (terminating, even) loop?

L417 "is denotes"

L478 "line 3" -> "line 4"

L506.5 $e$ appears out of nowhere and is not explained.

L512-513 Even if "$\psi_{sym}$ is satisfiable", it might be too much to add all of $p$ to $Enc_\psi$. For example, suppose Prog is `x ~ uniform_int(1,3); halt` and $\psi$ is `x=1`. This Prog does not contain `if`, so Algorithm 1 only has one path to follow, and $p$ stays at $1.0$. Yet the probability that $\psi$ holds is not 1 but 1/3. It seems that Algorithm 1 line 34 and Algorithm 4 line 2 should take $\psi_{sym}$ into account.

L519-520: What are $p_1$ and $p_2$? Also, parentheses seem missing before "/3"

L522: To clarify "for all", add "total" before "probability". Also here, defer explicitly explaining Algorithm 1 line 36.

L527 "not complete": This important fact should not be buried here. Also, give an example.

L529 "some missing paths might violate the lower bound" is confusing because paths do not violate bounds. Reword: perhaps "missing some paths might give the false appearance that the program violates a lower bound"

L545.5 "With can" -> "We can"

L548.5: Is $\psi := \beta \land \mathsf{win}$ really the predicate we're interested in? If $\beta$ is false, then the probability of $\psi$ is 0, not 2/3 as claimed later in this paragraph!

L753: But if $A[1]=A[2]$ then $\psi$ has probability $0$, not $k/n$ as required by the query!

L792: But if $\mathsf{DistToMono}(f)\ne k$ then $\psi$ has probability $0$, not $>k/n$ as required by the query! Also, the query is missing $\forall k$

L822 $\mathbb{E}[\texttt{num\_comps}]$: What is the distribution that this expected value is computed over? Is each element of $A$ chosen independently from the same uniform distribution? What is the query whose form is described on L570?

Algorithm 10 line 11 should use $\sim$ rather than $\leftarrow$

Don't use both $\epsilon$ and $\varepsilon$ (page 19).

L927: Remind the reader that $e$ means the base of the natural logarithm.

L929 "updated" -> "incremented" to be more specific

Algorithm 12 line 21 uses $n$, which is inconsistent with $N$ on L961, L962

L968: Clarify that this predicate $\psi$ only tests the special case where $a_{X[1]} = 1$

Section 5 should clarify up front what is "verification" (L1005, L1140), what is "bug finding" (L1010), and which of these is achieved in each evaluated example. This is especially confusing in the discussion of (4) on page 23.
- It has to be acknowledged that using AllOff or FirstOff may leave some bugs not found. For example, using AllOff or FirstOff in $\psi$ would not test Freivalds' Algorithm for $A,B,C$ such that $(A\times B)_{0,0}=C_{0,0}$ but $(A\times B)_{2,3}\ne C_{2,3}$. Thus, any "increased performance" may come at the cost of no longer performing "verification" or even "bug finding".
- What is the difference between SomeOff and OneOff? What does "we represent $i$ and $j$ as universal symbolic variables and universally quantify them in Equation (2)" mean? Give the actual $\psi$ used. Why does SomeOff provide a stronger guarantee than OneOff (L1116)?
- Some indices in (4) start at 0, others at 1.

L997 ", for" -> " for,"

L1021 "experiments a" -> "experiments on a"

L1070 "this suggests that constraint solving is the main bottleneck in our approach, not path exploration": The concretizations (Table 1 rightmost column) are pretty small, and that may be why path exploration is not yet a bottleneck.

In table columns, align numbers to the right to ease comparison.

Number all displayed equations.

Spell check.

Review #575B
===========================================================================

Overall merit
-------------
B. Weak Accept

Reviewer expertise
------------------
Y. Knowledgeable

Paper summary
-------------
Symbolic execution is a well-known technique for exploring programs. This work contributes the ability to combine universally quantified input variables with randomly drawn stochastic variables inside the program. Existing techniques that account for probabilities usually do not allow input variables or assume that they are drawn from a uniform distribution.

The standard symbolic execution algorithm is extended to keep track of probability distributions, as well as the probability associated with the current branch being explored. This information can be collected and summed to calculate the probability of a particular property holding or being violated. A base language and semantics is given, and the algorithm is shown to calculate the probabilities correctly. An implementation is provided and a number of case studies show that several small real-world algorithms can be analysed.

Strengths
---------
Probabilities can be useful when modelling situations where the expected outcome is more important than pathological cases. Similarly, many random algorithms achieve speed ups over non-random algorithms at the cost of some possibility of error. Being able to analyse these programs to confirm that the probabilities of outcomes match the guarantees claimed is a welcome extension to the symbolic execution framework.

Although only a small number of case studies are considered, they have been manually curated, and at least show the feasibility of the work.

The work is a natural extension to the standard algorithm, and careful proofs appear to have been provided, though I would have preferred a nicer presentation of the formal work in the main body.

Weaknesses
----------
I did not dig through the supplementary material, but the intuition behind the approach is natural, and the authors did not claim any particular challenges that needed to be overcome.

The experiments cover only a small number of benchmarks, and notably do not show how the algorithm would cope with a program that is large enough to prevent a full path exploration completing. In some sense, all benchmarks were verifiable. It is claimed in the related work that existing probabilistic model checkers would not be able to cope with the state-spaces of the benchmarks. I would like to see more evidence for this. E.g. PRISM uses a BDD data structure that can potentially handle large state spaces.

The experiments only really answer Q2 and Q3 for a specific benchmark. Is there anything we can generalise from this?

Only a naive version of symbolic execution is considered, though all work must start somewhere.

Comments for author
-------------------
I did not find the formal treatment in Section 3.4 to be illuminating. I had the feeling that there were too many latin/greek letters that were hard to keep track of, several appearing to take on similar roles, with no overarching sense of purpose.

Theorem 3.2 is presented rather oddly -- it shows that p matches the semantics, but is presented as if the semantics needs to justify not tracking p when the algorithm does! More generally, the section is presented as a formalisation of Algorithm 1's behaviour. I think it would be more natural to define the pWhile language, then the semantics of the pWhile language and what the probabilities should be independently of the Algorithm, then show that Algorithm 1 respects these semantics. I believe this is what has been done, but the presentation is a little back-to-front.

Theorems 3.3-3.5 show individual steps towards an overall statement of correctness that is not given.

It is odd to me that the definition of "μ satisfies our abstraction R" does not seem to care about the probabilities calculated, only that they are greater than 0, yet somehow, for the entire algorithm to be correct, the precise probabilities should matter. Precise probabilities are only treated in Theorem 3.5. Possibly Theorem 3.2 shows that things are indeed tracked correctly?

Is there a typo somewhere in the definition of "μ satisfies our abstraction R"? I could not see where μ occurs in Line 624. The "and if" on Line 624 also seems to imply that μ can only satisfy R if the definition of ν_φ somehow succeeds.

μ seems to be key to the semantics and proof, but it is not really explained or motivated.

The use of the Pr[...] notation causes a bit of confusion with the Iverson brackets [...].

Section 4 takes up a lot of space, but I do not find it as interesting as I would a cleaner presentation of the formalisation. The details of the case study algorithms are not crucial to the results and can be looked up elsewhere if needed.

Review #575C
===========================================================================

Overall merit
-------------
C. Weak Reject

Reviewer expertise
------------------
Y. Knowledgeable

Paper summary
-------------

This paper presents a symbolic execution algorithm that can 
handle both traditional inputs and variables drawn 
from a probability distribution.

Strengths
---------
Pros:
+ Intuitive algorithm with proof of correctness.
+ Well explained.

Weaknesses
----------
Cons:
- The proposed algorithm for handling (potentially probabilistic)
branches is essentially exhaustive, which means that the domains 
of probabilistic variables must be very small for the algorithm 
to terminate. This is evident from the evaluation where the concretization
limits for Freivalds, Quicksort, Bloom filters, etc are in the low 
single digits.
- Perhaps the most interesting application for this work would be probabilistic 
programming inference. Unfortunately, it doesn't handle conditional
probabilities, and it doesn't seem like there is a reasonable way to 
extend the algorithm to handle them.

Comments for author
-------------------
Minor:

- With respect to the Bloom filter case study, it might be interesting to not only
try and find the bug in the original algorithm, but also the known 
proposed fix (which was left undiscovered for quite sometime). See Ilya Sergey's
and Kiran Gopinathan's work in CAV'20 for more.

- l 1069: analyzine

Questions for the response period
---------------------------------
Question:
- While you do state that you made little effort to optimize your symbolic
execution, the "optimization" direction of future work seems to convey that 
you believe it's just a matter of developing heuristics. While I whole-heartedly agree 
that a solid foundation, like the one presented, should be at the core of 
any reasonable symbolic executor, can you give any intuition as to why you 
expect your approach to scale, when the computation of path probabilities 
and solving them with Z3 seems to already dominate the execution time?

### 2021-09-24 paper/parts/experiments.tex
Paper

@@
 
+\subsection{(RQ1) \baseaxp vs. \tool}
 \begin{itemize}
-	\item (RQ1) Experiments
-	\item (RQ2) Additional Examples
+	\item We run \axp with default settings where it samples the values of the forall variables at random and simulates multiple runs of the program with different values of the probabilistic variables for each sampled value of the forall variables.
+	\item \tool is also run with default settings, the values of the forall variables are determined by solving the path constraints via symbolic execution using \klee and for each setting of the forall variables, the program is run multiple times with different values of the probabilistic variables.
 \end{itemize}
+\subsection{(RQ2) Hybrid Strategy}
+We run \tool under a hybrid strategy here.
+Symbolic Execution is used to find the worst case forall settings that lead to the violation of the probabilistic assert in the program.
+For each of the worst case setting found using symbolic execution, \axp runs the program multiple times over different values of the probabilistic variables.
+Any error detected by \axp is considered a violation of the probabilistic assert.
